### 2018-07-23 AutoAlgorithmLinearFunctionalDataVerB.tex
Initial ShareLaTeX Import

\documentclass[final]{elsarticle}
\setlength{\marginparwidth}{0.5in}
\usepackage{amsmath,amssymb,amsthm,natbib,mathtools,graphicx,color}
\input FJHDef.tex

\newcommand{\chin}{\ch_{\text{\rm{in}}}}
\newcommand{\chout}{\ch_{\text{\rm{out}}}}
\newcommand{\pin}{p_{\text{\rm{in}}}}
\newcommand{\pout}{p_{\text{\rm{out}}}}
%\newcommand{\cc}{\mathcal{C}}
\newcommand{\cq}{\mathcal{Q}}
\newcommand{\co}{\mathcal{O}}
\newcommand{\bbW}{\mathbb{W}}
%\newcommand{\tP}{\widetilde{P}}
\newcommand{\bg}{{\bf g}}
\newcommand{\bu}{{\bf u}}
\newcommand{\bbu}{\bar{\bf u}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bbv}{\bar{\bf v}}
\newcommand{\bw}{{\bf w}}
\newcommand{\bbw}{\bar{\bf w}}
%\newcommand{\hv}{\hat{v}}
\newcommand{\bgamma}{\boldsymbol\gamma}
\DeclareMathOperator{\MSE}{MSE}
\DeclareMathOperator{\RMSE}{RMSE}
\DeclareMathOperator{\rnd}{rnd}
\DeclareMathOperator{\abso}{abs}
\DeclareMathOperator{\rel}{rel}
\DeclareMathOperator{\nor}{nor}
\DeclareMathOperator{\err}{err}
\DeclareMathOperator{\lin}{lin}
%\DeclareMathOperator{\std}{std}
\DeclareMathOperator{\prob}{prob}
\DeclareMathOperator{\trunc}{trc}
\DeclareMathOperator{\third}{third}
\DeclareMathOperator{\non}{non}
%\DeclareMathOperator{\fourth}{fourth}
\newtheorem{theorem}{Theorem}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{lem}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{algo}{Algorithm}
\newtheorem{condit}{Condition}
%\newtheorem{assump}{Assumption}
\theoremstyle{remark}
\newtheorem{rem}{Remark}
\DeclareMathOperator{\fix}{fix}
\DeclareMathOperator{\up}{up}
\DeclareMathOperator{\lo}{lo}

\definecolor{orange}{rgb}{1.0,0.3,0.0}
\definecolor{violet}{rgb}{0.75,0,1}
\newcommand{\frednote}[1]{  {\textcolor{red}  {\mbox{**Fred:} #1}}}
\newcommand{\yuhannote}[1]{ {\textcolor{violet}  {\mbox{**Yuhan:} #1}}}
\newcommand{\tonynote}[1]{ {\textcolor{orange}  {\mbox{**Tony:} #1}}}

\journal{Journal of Complexity}

\begin{document}

\begin{frontmatter}

\title{The Complexity of Automatic Algorithms Employing Continuous Linear Functionals}
\author{Yuhan Ding}
\address{MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612}
\author{Fred J. Hickernell}
\address{Pritzker Science Ctr Rm 106, Center for Interdisciplinary Scientific Computation, \\3105 S Dearborn St, Chicago, IL 60616}
\author{Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
\address{Room E1-120, Department of Applied Mathematics, Illinois Institute of Technology,\\ 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616}
\begin{abstract}
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}
\end{frontmatter}

\section{The Basic Problem}
Let $\cf$ be a separable Banach space of input functions with basis $\{u_i\}_{i\in\ci}$, where $\ci$ is a countable index set, and let the norm for this Banach space be defined as the $\ell_{\pin}$-norm terms of the Fourier coefficients as follows:
\begin{equation*}
f = \sum_{i \in \ci} \hf_i u_i \in \cf, \qquad \norm[\cf]{f}=\big\lVert\big(\hf_i\big)_{i\in \ci}\big\rVert_{\pin}, \qquad 1 \le \pin \le \infty.
\end{equation*}
Here the $\hf_i$ denotes the $i^{\text{th}}$ Fourier coefficient of a function $f\in \cf$.  If $\pin=2$, then $\cf$ is a Hilbert space.  Similarly, let $\cg$ be a separable Banach space of outputs  with basis $\{v_i\}_{i \in \ci}$, whose norm may be defined as follows:
\begin{equation*}
f = \sum_{i \in \ci} \tf_i v_i \in \cg, \qquad \norm[\cg]{f}=\big\lVert\big(\tf_i\big)_{i\in \ci}\big\rVert_{\pout}, \qquad 1 \le \pout \le \infty.
\end{equation*}
In this case $\tf_i$ denotes the $i^{\text{th}}$ Fourier coefficient of a function $f\in \cg$.  Define the solution operator $S$ by $S(u_i) = \lambda_i v_i$, and so
\begin{equation} \label{HilbertS}
S(f) = \sum_{i \in \ci}^\infty \lambda_i \hf_i v_i, \qquad \forall f \in \cf.
\end{equation}
Here the $\lambda_i$ are the bounded singular values of the operator $S$.  A generalization of H\"older's inequality is
\begin{multline} \label{HoldIneq}
\norm[r]{(a_ib_i)_{i \in \ci}} \le \norm[p]{(a_i)_{i \in \ci}} \norm[q]{(b_i)_{i \in \ci}}, \\
1 \le r, p \le \infty, \quad  q= \frac{pr}{\max(p-r,0)}.
\end{multline}
Thus, to ensure that the solution operator is bounded, it is assumed that
\begin{equation} \label{lamcond}
\norm[q]{(\lambda_i)_{i \in \ci}}<\infty, \quad  q= \frac{\pin\pout}{\max(\pin-\pout,0)}.
\end{equation}

This problem definition is rather general in some ways, e.g., allowing the inputs and outputs to lie in Banach spaces, rather than Hilbert spaces.  However, a key requirement is that $S(u_i)=\lambda_i v_i$ for the solution operator of interest, which is a serious restriction on the choice of bases.  Moreover, the norms of the Banach spaces cannot be arbitrarily defined, but must be defined in terms of the coefficients of the series expansions of the inputs and outputs.

For example, if $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f$ is the embedding operator, then one may choose a trigonometric polynomial basis:
\begin{gather*}
\norm[\cf]{f} = \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=1, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}
If $S$ computes the derivative of a function, $S: f \mapsto f'$, then the space $\cf$ must have a stronger inner product to ensure that the $\lambda_i$ are bounded, e.g.,
\begin{gather*}
\norm[\cf]{f} = \left[\int_0^1 \left\{\abs{f(x)}^2 + \abs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

Suppose that one may choose arbitrary linear functionals to obtain data, and let $i_1, i_2, \ldots$ be an ordering of the elements in $\ci$. Then one may approximate $S(f)$ by the first $n$ terms of its infinite series representation:
\begin{subequations}
\begin{gather} \label{Andef}
A_n(f) = \sum_{j=1}^n \lambda_{i_j} \hf_{i_j} v_{i_j} \qquad \forall f \in \cf, \ n \in \naturals, \\
\label{errsum}
\norm[\cg]{S(f)-A_n(f)} = \norm[\pout]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n+1}}
\end{gather}
Again by the generalization of H\"older's inequality, \eqref{HoldIneq}, it follows that
\begin{equation}
\label{erreig}
\sup_{0 \ne f \in \cf}\frac{\norm[\cg]{S(f)-A_n(f)}}{\norm[\cf]{f}} = \norm[q]{\left(\lambda_{i_j} \right)_{j\ge n+1}},
\end{equation}
\end{subequations}
where $q$ was defined in \eqref{lamcond}. For the example above, a natural ordering would be $i_j=(-1)^{j-1}\left \lceil (j-1)/2 \right \rceil$.
An automatic algorithm for approximating $S(f)$ must have a way of reliably bounding

\[
\norm[\pout]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n+1}} \quad \text{or} \quad \norm[q]{\left(\lambda_{i_j} \right)_{j\ge n+1}} 
\]
in terms of function data.

\section{Assuming a Gentle Decay in the Terms of the Series}

Another method for estimating the error of $A_n$ assumes that the decay of the Fourier coefficients of $f$ follows some general rate of decay, which need not be known precisely.  Suppose again that we have some ordering of the linear functionals, as in the previous section, and let $0=n_0 < n_1 < n_2 < \ldots$ be an ordered, unbounded sequence of integers.  Define the sums
\begin{equation} \label{sumdef}
\sigma_k(f) = \norm[\pout]{ \left(\lambda_{i_j} \hf_{i_j} \right)_{j=n_{k-1}+1}^{n_k}}, \qquad k=1, 2, \ldots
\end{equation}
and the cone of functions in $\cf$ as those whose Fourier coefficients decay at a given rate:
\begin{equation} \label{decayconedef}
\cc = \left\{ f \in \cf : \sigma_{k+r}(f) \le \gamma(r) \sigma_k (f), \ \forall k \in \naturals \right\}.
\end{equation}
where the sequence $\gamma(r)$ has to verify $\lim_{n\rightarrow\infty}\gamma(n)=0$, $\gamma(r) > 0$ and that
\begin{equation} \label{constcone}
\norm[\pout]{\bgamma}=\norm[\pout]{ \left(\gamma(r)\right)_{r=1}^\infty}<\infty
\end{equation}

\begin{rem}
The definition of the cone can be rewritten as
\begin{equation}\label{coneredef}
\cc = \left\{ f \in \cf : \sigma_k(f) \le \min_{1 \le i < k}\{\gamma(i)\sigma_{k-i}(f)\}, \ \forall k \in \naturals \right\}.
\end{equation}
\end{rem}

From the definition of the cone and \eqref{errsum}, one can show that
\begin{equation}\label{algoineq}
\begin{aligned}
\norm[\cg]{S(f)-A_{n_k}(f)} &= \norm[\pout]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n_k+1}} \\
&= \left\{\sum_{r=1}^\infty \sum_{j=n_{k+r-1}+1}^{n_{k+r}}  \abs{\lambda_{i_j}\tf_{i_j} }^{\pout}  \right\}^{1/\pout}\\
&= \norm[\pout]{ \left(\sigma_{k+r}(f)\right)_{r=1}^{\infty}} \\
&\le \norm[\pout]{ \left(\gamma(r)\sigma_{k}(f)\right)_{r=1}^{\infty}} \\
&= \sigma_{k}(f)\norm[\pout]{\bgamma}
\end{aligned}
\end{equation}

Since the right hand side depends on the data, we have a data-driven error bound.  Note also that $\sigma_k(f)$ decays as quickly with respect to $n$ as the true error.  Unlike the earlier method, one does not need to know the decay rate.  In practice, one increases $k$ until the right hand side is smaller than the error tolerance.
\begin{itemize}
\item  $\sigma_k(f)$ decaying \emph{algebraically} and the $n_k$ increasing \emph{geometrically}:\\

To see some examples on how these conditions might arise naturally, consider the case where $\gamma(r)=s_1s_2^{-r}$ with the terms in the sum defining $\sigma_k(f)$ decaying \emph{algebraically} and the $n_k$ increasing \emph{geometrically}:
\begin{gather*}
C_{\lo} j^{-p} \le \abs{\lambda_{i_j} \ip[\cf]{u_{i_j}}{f}} \le C_{\up} j^{-p}, \quad  p>1, \ j \in \naturals, \\
n_k = a b^k  \quad a, b, k \in \naturals, \ b \ge 2.
\end{gather*}
The sum of positive integers raised to a power can be interpreted as a left or right rectangle rule for approximating an integral.  This leads to upper and lower bounds for the sums:
\begin{align*}
\sum_{j=n_{\lo}}^{n_{\up}} j^{-p}  & \ge \int_{n_{\lo}}^{n_{\up}+1} x^{-p}\, \dif x  = \frac{n_{\lo} ^{1-p} - (n_{\up}+1)^{1-p}}{p-1}, \\
\sum_{j=n_{\lo}}^{n_{\up}} j^{-p}  & \le \int_{n_{\lo}-1}^{n_{\up}} x^{-p}\, \dif x = \frac{(n_{\lo}-1) ^{1-p} - n_{\up}^{1-p}}{p-1}.
\end{align*}
These two bounds can be used to prove that $f$ lies in the cone \eqref{decayconedef} for appropriately chosen $s_1$ and $s_2$:
\begin{multline*}
\sigma_k(f) \ge C_{\lo} \left\{\frac{(n_{k-1}+1) ^{1-p\pout} - (n_{k}+1)^{1-p \pout}}{p \pout-1}\right\}^{1/\pout} \\
= C_{\lo} \left\{\frac{[ab^{k-1}]^{1-p \pout}}{p \pout-1} \left[(1+a^{-1}b^{1-k})^{1-p \pout} - (b+a^{-1}b^{1-k})^{1-p \pout}\right] \right\}^{1/\pout},
\end{multline*}
\begin{multline*}
\sigma_k(f) \le C_{\up}\left\{\frac{n_{k-1} ^{1-p \pout} - n_{k}^{1-p \pout}}{p \pout-1}\right\}^{1/\pout} \\
= C_{\up}\left\{\frac{[ab^{k-1}]^{1-p \pout} (1 - b^{1-p \pout})}{p \pout-1}\right\}^{1/p} ,
\end{multline*}
\begin{align*}
\frac{\sigma_{k+r}(f)}{\sigma_k(f)} &\le \frac{C_{\up}}  {C_{\lo}}
\left\{\frac{ (1 - b^{1-p \pout}) b^{(p \pout -1)(-r)} }  {(1+a^{-1}b^{1-k})^{1-p\pout} - (b+a^{-1}b^{1-k})^{1-p\pout}} \right\}^{1/\pout}\\
& \le \frac{C_{\up}}  {C_{\lo}}
\left\{\frac{(1 - b^{1-p\pout}) b^{(p \pout -1)(-r)} }  {(1+a^{-1})^{1-p\pout} - (b+a^{-1})^{1-p\pout}} \right\}^{1/\pout}   = s_1 s_2^{-r},
\end{align*}
where
\[
s_1 = \frac{ C_{\up}}  {C_{\lo}}\left\{\frac{(1 - b^{1-p\pout})}  {(1+a^{-1})^{1-p\pout} - (b+a^{-1})^{1-p\pout} } \right\}^{1/\pout}, \qquad s_2 = b^{p-1/\pout}.
\]

The properties we will use for these particular polynomials can be found in \cite{AbrSte64}: derivatives, explicit Fourier coefficients, etc. To deal with this example, now $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f'$ with,
\begin{gather*}
\norm[\cf]{f} = \left[\int_0^1 \left\{\abs{f(x)}^2 + \abs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

Like in the previous example, the index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$ has the following ordering
\begin{gather*}
i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
n_0=0,\quad n_k=2^k, \qquad k\in\naturals.
\end{gather*}

For this case,
\begin{equation*}
B_n(x)=-\frac{n!}{(2\pi\sqrt{-1})^n}\sum_{k\in\integers\setminus\{0\}}\frac{\me^{2\pi\sqrt{-1}kx}}{k^n}\Longrightarrow
\left\{\begin{array}{l}
\widehat{B_n}_0=0 \\
\widehat{B_n}_{i_j}=-\frac{n!\sqrt{1+4 \pi^2 i_j^2}}{(2\pi\sqrt{-1}i_j)^n},\quad i_j\in\integers\setminus\{0\}
\end{array}\right.
\end{equation*}

Using that $B'_n(x)=nB_{n-1}(x)$ and $\int_0^1B_n(t)B_m(t)\dif t=(-1)^{n-1}\frac{m!n!}{(m+n)!}B_{n+m}$, the real solution comes automatically,
\begin{equation*}
\norm[\cg]{S(B_n(x))}=n\norm[\cg]{B_{n-1}(x)}=n!\sqrt{\frac{\abs{B_{2(n-1)}}}{[2(n-1)]!}}
\end{equation*}
where $B_n=B_n(0)$ are the Bernoulli numbers.

If we consider $\gamma(r)=s_1s_2^{-r}$ and that
\begin{equation}\label{bound}
\frac{n!}{\sqrt{2}\pi^n}j^{-n} \le \abs{\lambda_{i_j}\widehat{B_n}_{i_j}} \le \frac{n!2^n}{\pi^n}j^{-n},\quad j\in\naturals\setminus\{1\}
\end{equation}
then $C_{\up}=2^{n+\frac{1}{2}}C_{\lo}=\frac{n!2^n}{\pi^n}$. Thus, as shown in the example example at the beginning of this section we can take
\begin{equation*}
s_1=2\times11^{n-\frac{1}{2}},\quad s_2=2^{n-\frac{1}{2}}
\end{equation*}
There is still one thing to check because $j=1$ was not taken into account in the inequality (\ref{bound}). However, see that $\sigma_1(f) \ge C_{\lo}\left(\frac{5}{36}\right)^{n-\frac{1}{2}}$ what means that the $\gamma(r)=s_1s_2^{-r}$ found satisfies our needs.

\item $\sigma_k(f)$ decay \emph{exponentially} and the $n_k$ increase \emph{linearly}:\\
In our example, consider $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f$ the embedding operator with:
\begin{gather*}
\norm[\cf]{f} = \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x},\quad \lambda_i=1, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

For our index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$,
\begin{gather*}
i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
n_0=0,\quad n_k=2k+1, \qquad k\in\naturals.
\end{gather*}

The Fourier coefficients of this function can be easily found:
\begin{align*}
f(x)&=\frac{b^2-1}{b^2+1-2b\cos(2\pi x)}\\
&=\frac{1-b^{-2}+b^{-1}(\me^{-2\pi\sqrt{-1}x}-\me^{-2\pi\sqrt{-1}x})}{1+b^{-2}-b^{-1}(\me^{2\pi\sqrt{-1}x}+\me^{-2\pi\sqrt{-1}x})}\\
&=\frac{(1-b^{-1}\me^{-2\pi\sqrt{-1}x})+(1-b^{-1}\me^{2\pi\sqrt{-1}x})b^{-1}\me^{-2\pi\sqrt{-1}x}}{(1-b^{-1}\me^{2\pi\sqrt{-1}x})(1-b^{-1}\me^{-2\pi\sqrt{-1}x})}\\
&=\frac{1}{1-b^{-1}\me^{2\pi\sqrt{-1}x}}+\frac{b^{-1}\me^{-2\pi\sqrt{-1}x}}{1-b^{-1}\me^{-2\pi\sqrt{-1}x}}\\
&=\sum_{k\in\naturals_0}\left(b^{-1}\me^{2\pi\sqrt{-1}x}\right)^k+\sum_{k\in\naturals}\left(b^{-1}\me^{-2\pi\sqrt{-1}x}\right)^k\\
&=\sum_{k\in\integers}b^{-\abs{k}}\me^{2\pi\sqrt{-1}kx}\Longrightarrow\hf_{i_j}=b^{-\abs{i_j}}
\end{align*}

Because we are interested in seeing how far the approximation is from the real solution, the norm of the exact solution has to be found. Knowing the Fourier coefficients leads us to an easy way to calculate it:
\begin{align*}
\norm[\cg]{S(f)}&=\left(\sum_{j\in\naturals}\lambda_{i_j}^2\hf_{i_j}^2\right)^{\frac{1}{2}} =\left(1+2\sum_{k\in\naturals}b^{-2k}\right)^{\frac{1}{2}}=\left(\frac{b^2+1}{b^2-1}\right)^{\frac{1}{2}}
\end{align*}

We can also give the sums of coefficients,
\begin{align*}
&\sigma_1(f)=\sqrt{1+2b^{-2}}\\
&\sigma_k(f)=\sqrt{2}b^{-k}, \qquad k \in\naturals\setminus\{1\}.
\end{align*}
Here we can choose  $\gamma(r)=b^{-r}$ , thus we have 
\begin{equation*}
\sigma_k(f) \le \min_{1 \le i <k}\{\gamma(i)\sigma_{k-i}(f)\}=\min\left\{1 \; , \; \sqrt{1+\frac{b^2}{2}} \right\}\sigma_k(f)
\end{equation*}

In this case, $\norm[\pout]{\bgamma}=\frac{1}{\sqrt{b^2-1}}$.

%One may also consider the case where the terms in the sum defining $\sigma_k(f)$ decay \emph{exponentially} and the $n_k$ increase \emph{linearly}:
%\begin{gather*}
%C_{\lo} p^{-j} \le \abs{\lambda_{i_j} \ip[\cf]{u_{i_j}}{f}} \le C_{\up} p^{-j}, \quad  p>1, \ j \in \naturals, \\
%n_k = a +kb  \quad a, b, k \in \naturals.
%\end{gather*}
%The geometric sum that now arises in a bound on the  definition of $\sigma_k(f)$ takes the form
%\begin{equation*}
%\sum_{j=n_{\lo}}^{n_{\up}} p^{-j} = \frac{p^{-n_{\lo}} - p^{-n_{\up}-1}}{1-p^{-1}}, \\
%\end{equation*}
%which implies that
%\begin{align*}
%\frac{\sigma_{k+r}(f)}{\sigma_k(f)} & \le
%\frac{C_{\up}}  {C_{\lo}} \left\{\frac{p^{-\pout( n_{k+r-1}+1)} - p^{- \pout(n_{k+r}+1)}]}  {[p^{-\pout(n_{k-1}+1)} - p^{-\pout(n_{k}+1)}]}\right\}^{1/\pout} \\
%& =
%\frac{C_{\up} p^{n_{k-1}-n_{k+r-1}}} {C_{\lo}}  \left\{\frac{1 - p^{\pout(n_{k+r-1}-n_{k+r})}} {1 - p^{\pout(n_{k-1}-n_{k})}} \right\}^{1/\pout}\\
%& = \frac{ C_{\up} p^{b(-r)}}  {C_{\lo}}  = s_1 s_2^{-r},
%\end{align*}
%where
%\[
%s_1 = \frac{ C_{\up}}  {C_{\lo}} , \qquad s_2 = p^b.
%\]

\end{itemize}

\subsection{Adaptive algorithm}

The approximate solution to the problem $S:\cc\rightarrow\cg$ depends on
Given the error tolerance $\varepsilon$, we have to find $k^*$ such that
\begin{equation*}
         \sigma_{k^*}(f) \le \frac{\varepsilon}{\norm[\pout]{\bgamma}} < \sigma_{k^*-1}(f)
\end{equation*}

According to the inequality (\ref{algoineq}) above, this $k^*$ is ensuring
\begin{equation*}
\norm[\cg]{S(f)-A_{n_{k^*}}(f)} \le \varepsilon
\end{equation*}

Remember that in order to build our algorithm, we need to define a countable, non-negative-valued index set such that,
\begin{equation} \label{indexdef}
\cn=\{n_1, n_2, \ldots\} \quad \text{with } n_k < n_{k+1}, \quad \text{satisfying } \sup_k \frac{n_{k+1}}{n_k} <\infty.
\end{equation}

\begin{algo}\label{algo2}
 Consider the set of functions $\cc$, the error tolerance $\varepsilon$ and the sequence $\{A_n\}_{n \in \ci}$ as described before.
The algorithm starts by setting $k=1$.
\begin{description}
\item[Stage 1. Computing $\sigma(f)$.] First we compute $\sigma_{k}(f)$.
\item[Stage 2. Check for Convergence.] Check whether $k$ is large enough to satisfy the error tolerance, i.e.,
    \begin{equation}
          \sigma_{k}(f) \le \frac{\varepsilon}{\norm[\pout]{\bgamma}}
    \end{equation}
    If this is true, then we return $A_{n_{k}}(f)$ and terminate the algorithm.
\item[Stage 3. Increasing $k$.] Otherwise, we increase $k$ by $1$ and return to Stage $1$.
\end{description}
\end{algo}

 By construction, the cost of this Algorithm \ref{algo2} is
\begin{equation}\label{costalgo}
\cost(A,f;\varepsilon)=n_{k^*}
\end{equation}

\subsection{Optimality of the Algorithm \ref{algo2}}

The sequence $\cn$ is used to gather the Fourier coefficients into groups to smooth the peaks we could encounter if we take these coefficients one by one. Flattening the peaks is a must to fit functions into the cone. Nevertheless, the solution of our algorithm is in this set $\cn$ which means that the sequence does not have to distance the optimal number of data needed in our algorithm (defined below) more than a constant.

We define the optimal number of data needed in our algorithm as
\begin{equation*}
N_{\opt}(f,\varepsilon)=\min\left\{n\in\naturals:\,\norm[\pout]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n+1}} \le \varepsilon \right\}
\end{equation*}

The index set for our algorithm defined in (\ref{indexdef}) is called \emph{optimal} for the Algorithm \ref{algo2} and the problem $(\cc,\cg,S,\Lambda)$ if it essentially tracks the optimal number of data needed,
\begin{equation} \label{nearoptdef}
\sup_{0 < \varepsilon \le 1} \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty.
\end{equation}

\begin{theorem}\label{nopt}
The index set defined in (\ref{indexdef}) is optimal for Algorithm \ref{algo2}.
\end{theorem}
\begin{proof}
For a given $f$ and $\varepsilon$, consider $k^*$ depending on $\varepsilon$ such that
\begin{equation*}
\sigma_{k^*}(f) \le \frac{\varepsilon}{\norm[\pout]{\bgamma}} < \sigma_{k^*-1}(f)
\end{equation*}

From the definition of $N_{\opt}(f,\varepsilon)$, it is clear that $N_{\opt}(f,\varepsilon)=n^*\le n_{k^*}$.

Because $\lim_{n\rightarrow\infty}\gamma(n)=0$, we can take $r=\min\{n: \gamma(n)\norm[\pout]{\bgamma} \le 1\}$. Define also $\sup_k\frac{n_{k+1}}{n_k}=C$ according to the properties in (\ref{indexdef}).

Then, if $k^*>r+1$,
\begin{align*}
& \varepsilon \le \frac{\varepsilon}{\gamma(r)\norm[\pout]{\bgamma}} < \sigma_{k^*-1-r}(f) \le \norm[\pout]{S(f)-A_{n_{k^*-1-r}}(f)} \\
\norm[\pout]{S(f)-A_{n^*}(f)} \le & \varepsilon
\end{align*}
what means that $n_{k^*-1-r} < n^* \le n_{k^*}$. Therefore,
\begin{equation*}
\frac{n_{k^*}}{n^*} < \frac{n_{k^*}}{n_{k^*-1}}\times\cdots\times\frac{n_{k^*-r}}{n_{k^*-1-r}} \le C^{r+1}
\end{equation*}

If $k^* \le r+1$,
\begin{equation*}
\frac{n_{k^*}}{n^*} \le \frac{n_{k^*}}{n_{k^*-1}}\times\cdots\times\frac{n_{2}}{n_{1}}\times n_{1} \le n_{1}C^{k^*-1}
\end{equation*}

Thus,
\begin{equation*}
\sup_{0 < \varepsilon \le 1} \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} \le n_1C^{r+1}.
\end{equation*}
\end{proof}

The cost of any algorithm $A\in\ca(\cf,\cg,S,\Lambda)$ may also depend not only on a function, but on a set of functions $\cb\subseteq\cf$. To represent this idea one defines
\begin{equation*}
\cost(A,\cb,\varepsilon)=\sup_{f\in\cb}\{\cost(A,f;\varepsilon)\}.
\end{equation*}

The next step is comparing our Algorithm \ref{algo2} to the whole set of possible algorithms in $\ca(\cc,\cg,S,\Lambda)$. If the conditions describing the cone $\cc$ are well stated, then our algorithm will not have a greater cost than a constant times the best algorithm in $\ca(\cc,\cg,S,\Lambda)$.

Lets define now the following set of functions,
\begin{equation*}
\cj_{n,\varepsilon}=\left\{f\in\cf:\norm[\pout]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n+1}} \le \varepsilon \right\}
\end{equation*}
One can see that $\cj_{n,\varepsilon}\subseteq\cj_{m,\varepsilon}$ if $n\le m$, and $\lim_{n\rightarrow\infty}\cj_{n,\varepsilon}=\cf$.
\begin{theorem}\label{supcost}
   Given $A\in\ca(\cj_{n,\varepsilon},\cg,S,\Lambda)$, if $\,$ $\norm[\cg]{S(f)-A(f)}\le\varepsilon$ $\forall f\in\cj_{n,\varepsilon}$, then
 \begin{equation*}
 \cost(A,\cj_{n,\varepsilon},\varepsilon)\ge n
 \end{equation*}
\end{theorem}
\begin{proof}
Consider the following subsets of $\cj_{n,\varepsilon}$,
\begin{gather*}
\cf_n=\spn\{u_{i_1}(x),\ldots,u_{i_n}(x)\}=\{\hf_{i_1}u_{i_1}(x)+\ldots+\hf_{i_n}u_{i_n}(x),\, \hf_{i_j}\in\complex\},\\
\cf_{n,A}=\{f\in\cf_n:\, L_1(f)=\ldots=L_m(f)=0,\, m<n\}.
\end{gather*}
where $m$ is the cost that we suppose lower than $n$. Remark that,
\begin{gather*}
 \forall\varepsilon,\;\cf_n\subseteq\cj_{n,\varepsilon},\\
 \forall f\in\cf_{n,A},\;A(f)=A(0)
\end{gather*}

Therefore, there is the following contradiction
\begin{align*}
\sup_{f\in\cf_{n,A}}\norm[\cg]{S(f)-A(f)}&=\sup_{f\in\cf_{n,A}}\norm[\cg]{S(f)-A(0)}\\
&\ge\sup_{f\in\cf_{n,A}}\norm[\cg]{S(f)}-\norm[\cg]{A(0)}\\
&>\varepsilon
\end{align*}
For the last last inequality we are using
\begin{equation*}
\sup_{f\in\cf_{n,A}}\norm[\cg]{S(f)}\ge\lim_{\substack{\lambda_{i_l}\neq 0 \\ |\hf_{i_l}|\rightarrow\infty}}\norm[\cg]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j=1}^n}
\end{equation*}
\end{proof}

The complexity of a problem for the set of algorithms $\ca(\cb,\cg,S,\Lambda)$ is defined as the cost of the cheapest algorithm that satisfies the specified error tolerance, $\varepsilon$:
\begin{equation}\label{complexity2}
\begin{aligned}
\comp(\varepsilon,&\ca(\cb,\cg,S,\Lambda))\\
&=\inf_{A\in\ca(\cb,\cg,S,\Lambda)}\left\{\cost(A,\cb,\varepsilon):\norm[\cg]{S(f)-A(f)}\le\varepsilon,\; \forall f\in\cb\right\}
\end{aligned}
\end{equation}

According to notation in equation (\ref{indexdef}), if $n\in\cn$, $\forall f\in\cc\cap\cj_{n,\varepsilon}$, for Algorithm \ref{algo2} we have that $n\ge\cost(A;f,\varepsilon)\ge N_{\opt}(f,\varepsilon)$. Thus, using Theorem \ref{supcost} we know that
\begin{equation*}
\comp(\varepsilon,\ca(\cc\cap\cj_{n,\varepsilon},\cg,S,\Lambda))=n
\end{equation*}

\begin{prop}[for Theorem \ref{optimality}]\label{optimcost}
The cost of our second algorithm tracks the optimal cost for all $f\in\cc$
\begin{equation*}
\sup_{0 < \varepsilon \le 1}\sup_{f\in\cc} \frac{\cost(A,f;\varepsilon)} {\min\{n:f\in\cj_{n,\varepsilon}\}} <\infty
\end{equation*}
\end{prop}
\begin{proof}
First of all
\begin{equation*}
\min\{n:f\in\cj_{n,\varepsilon}\}=N_{\opt}(f,\varepsilon)
\end{equation*}
Recalling the proof of Theorem \ref{nopt}, remark that $r=\min\{n: \gamma(n)\norm[\pout]{\bgamma} \le 1\}$ does not depend on $k^*$ which means that $r$ does not depend on $f$
\begin{equation*}
\sup_{0 < \varepsilon \le 1} \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} \le n_1C^{r+1},\quad\forall f\in\cc
\end{equation*}
\end{proof}

\begin{theorem}\label{optimality}
Our Algorithm $\ref{algo2}$ is optimal for the problem $(\cc,\cg,S,\Lambda)$,
\begin{equation*}
\sup_{0 < \varepsilon \le 1}\frac{\cost(A,\cc,\varepsilon)} {\comp(\varepsilon,\ca(\cc,\cg,S,\Lambda))} <\infty
\end{equation*}
\end{theorem}
\begin{proof}
Because $\lim_{n\rightarrow\infty}\cj_{n,\varepsilon}=\cf$, there is $m$ such that $\cc\cap\cj_{m,\varepsilon}\neq\emptyset$. Then,
\begin{align*}
\comp(\varepsilon,\ca(\cc,\cg,S,\Lambda))&\ge\comp(\varepsilon,\ca(\cc\cap\cj_{m,\varepsilon},\cg,S,\Lambda))\\
&\ge\inf_{f\in\cc}\min\{j\in\naturals:f\in\cj_{j,\varepsilon}\}
\end{align*}
The first inequality comes from the fact that $\cc\supseteq\cc\cap\cj_{m,\varepsilon}$ and for the second one, $m\ge\inf_{f\in\cc}\min\{j\in\naturals:f\in\cj_{j,\varepsilon}\}$ as there exists $f\in\cc\cap\cj_{m,\varepsilon}$.
.........................................
%Then we can apply Proposition \ref{optimcost} to obtain the proof:
%\begin{equation*}
%\sup_{0 < \varepsilon \le 1}\frac{\cost(A,\cc,\varepsilon)} {\comp(\varepsilon,\ca(\cc,\cg,S,\Lambda))} <\infty
%\end{equation*}
\end{proof}

\subsection{Lower Complexity Bounds for Algorithms \ref{algo1} and \ref{algo2}}

\subsection{Examples}
\subsubsection{The embedding of $f(x)=\frac{(b^2-1)}{b^2+1-2b\cos(2\pi x)}$}

In our example, consider $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f$ the embedding operator with:
\begin{gather*}
\norm[\cf]{f} = \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x},\quad \lambda_i=1, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

For our index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$,
\begin{gather*}
i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
n_0=0,\quad n_k=2k+1, \qquad k\in\naturals.
\end{gather*}

The Fourier coefficients of this function can be easily found:
\begin{align*}
f(x)&=\frac{b^2-1}{b^2+1-2b\cos(2\pi x)}\\
&=\frac{1-b^{-2}+b^{-1}(\me^{-2\pi\sqrt{-1}x}-\me^{-2\pi\sqrt{-1}x})}{1+b^{-2}-b^{-1}(\me^{2\pi\sqrt{-1}x}+\me^{-2\pi\sqrt{-1}x})}\\
&=\frac{(1-b^{-1}\me^{-2\pi\sqrt{-1}x})+(1-b^{-1}\me^{2\pi\sqrt{-1}x})b^{-1}\me^{-2\pi\sqrt{-1}x}}{(1-b^{-1}\me^{2\pi\sqrt{-1}x})(1-b^{-1}\me^{-2\pi\sqrt{-1}x})}\\
&=\frac{1}{1-b^{-1}\me^{2\pi\sqrt{-1}x}}+\frac{b^{-1}\me^{-2\pi\sqrt{-1}x}}{1-b^{-1}\me^{-2\pi\sqrt{-1}x}}\\
&=\sum_{k\in\naturals_0}\left(b^{-1}\me^{2\pi\sqrt{-1}x}\right)^k+\sum_{k\in\naturals}\left(b^{-1}\me^{-2\pi\sqrt{-1}x}\right)^k\\
&=\sum_{k\in\integers}b^{-\abs{k}}\me^{2\pi\sqrt{-1}kx}\Longrightarrow\hf_{i_j}=b^{-\abs{i_j}}
\end{align*}

Because we are interested in seeing how far the approximation is from the real solution, the norm of the exact solution has to be found. Knowing the Fourier coefficients leads us to an easy way to calculate it:
\begin{align*}
\norm[\cg]{S(f)}&=\left(\sum_{j\in\integers}\lambda_{i_j}^2\hf_{i_j}^2\right)^{\frac{1}{2}} =\left(1+2\sum_{k\in\naturals}b^{-2k}\right)^{\frac{1}{2}}=\left(\frac{b^2+1}{b^2-1}\right)^{\frac{1}{2}}
\end{align*}

We can also give the sums of coefficients,
\begin{align*}
&\sigma_1(f)=\sqrt{1+2b^{-2}}\\
&\sigma_k(f)=\sqrt{2}b^{-k}, \qquad k \in\naturals\setminus\{1\}.
\end{align*}
Recalling the alternative definition of the cone in (\ref{coneredef}), with these sums, $f\in\cc$ for $\gamma(r)=b^{-r}$ since
\begin{equation*}
\sigma_k(f) \le \min_{1 \le i <k}\{\gamma(i)\sigma_{k-i}(f)\}=\min\left\{1 \; , \; \sqrt{1+\frac{b^2}{2}} \right\}\sigma_k(f)
\end{equation*}

In this case, $\norm[\pout]{\bgamma}=\frac{1}{\sqrt{b^2-1}}$. If we use our Algorithm \ref{algo2}, we have to check first whether $\sqrt{\frac{b^2+2}{b^4-b^2}}\le\varepsilon$. If this inequality states, then $k^*=1$. If not,
\begin{equation*}
k^*=\min\left\{k\in\naturals\setminus\{1\}:\frac{1}{2\log(b)}\log\left(\frac{2}{(b^2-1)\varepsilon^2}\right) \le k \right\}
\end{equation*}

For a numerical application, set $b=3$ and find below a table of results for this example,

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(f)}-\norm[\cg]{A_{n_{k^*}}(f)}$ \\
  \hline
  $1$ & $1$ & $3$ & $1.2492\cdot10^{-2}$ \\
  $10^{-1}$ & $2$ & $5$ & $1.3811\cdot10^{-3}$ \\
  $10^{-2}$ & $4$ & $9$ & $1.7041\cdot10^{-5}$ \\
  $10^{-3}$ & $6$ & $13$ & $2.1038\cdot10^{-7}$ \\
  $10^{-4}$ & $8$ & $17$ & $2.5973\cdot10^{-9}$ \\
  $10^{-5}$ & $10$ & $21$ & $3.2065\cdot10^{-11}$ \\
  $10^{-6}$ & $12$ & $25$ & $3.9591\cdot10^{-13}$ \\
  $10^{-7}$ & $15$ & $31$ & $4.4409\cdot10^{-16}$ \\
  \hline
\end{tabular}
\end{center}

\subsubsection{Derivation of the Bernoulli polynomials}

The properties we will use for these particular polynomials can be found in \cite{AbrSte64}: derivatives, explicit Fourier coefficients, etc. To deal with this example, now $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f'$ with,
\begin{gather*}
\norm[\cf]{f} = \left[\int_0^1 \left\{\abs{f(x)}^2 + \abs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

Like in the previous example, the index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$ has the following ordering
\begin{gather*}
i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
n_0=0,\quad n_k=2^k, \qquad k\in\naturals.
\end{gather*}

For this case,
\begin{equation*}
B_n(x)=-\frac{n!}{(2\pi\sqrt{-1})^n}\sum_{k\in\integers\setminus\{0\}}\frac{\me^{2\pi\sqrt{-1}kx}}{k^n}\Longrightarrow
\left\{\begin{array}{l}
\widehat{B_n}_0=0 \\
\widehat{B_n}_{i_j}=-\frac{n!\sqrt{1+4 \pi^2 i_j^2}}{(2\pi\sqrt{-1}i_j)^n},\quad i_j\in\integers\setminus\{0\}
\end{array}\right.
\end{equation*}

Using that $B'_n(x)=nB_{n-1}(x)$ and $\int_0^1B_n(t)B_m(t)\dif t=(-1)^{n-1}\frac{m!n!}{(m+n)!}B_{n+m}$, the real solution comes automatically,
\begin{equation*}
\norm[\cg]{S(B_n(x))}=n\norm[\cg]{B_{n-1}(x)}=n!\sqrt{\frac{\abs{B_{2(n-1)}}}{[2(n-1)]!}}
\end{equation*}
where $B_n=B_n(0)$ are the Bernoulli numbers.

If we consider $\gamma(r)=s_1s_2^{-r}$ and that
\begin{equation}\label{bound}
\frac{n!}{\sqrt{2}\pi^n}j^{-n} \le \abs{\lambda_{i_j}\widehat{B_n}_{i_j}} \le \frac{n!2^n}{\pi^n}j^{-n},\quad j\in\naturals\setminus\{1\}
\end{equation}
then $C_{\up}=2^{n+\frac{1}{2}}C_{\lo}=\frac{n!2^n}{\pi^n}$. Thus, as shown in the example example at the beginning of this section we can take
\begin{equation*}
s_1=2\times11^{n-\frac{1}{2}},\quad s_2=2^{n-\frac{1}{2}}
\end{equation*}
There is still one thing to check because $j=1$ was not taken into account in the inequality (\ref{bound}). However, see that $\sigma_1(f) \ge C_{\lo}\left(\frac{5}{36}\right)^{n-\frac{1}{2}}$ what means that the $\gamma(r)=s_1s_2^{-r}$ found satisfies our needs.

For a numerical application, find below the results for the case $n=5$ and $n=10$,

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  \multicolumn{4}{|c|}{$B_5(x)=x^5-\frac{5}{2}x^4+\frac{5}{3}x^3-\frac{1}{6}x$} \\
  \hline
  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(B_5(x))}-\norm[\cg]{A_{n_{k^*}}(B_5(x))}$ \\
  \hline
  $1$ & $5$ & $32$ & $2.9439\cdot10^{-11}$ \\
  $10^{-1}$ & $6$ & $64$ & $2.2703\cdot10^{-13}$ \\
  $10^{-2}$ & $7$ & $128$ & $1.8735\cdot10^{-15}$ \\
  $10^{-3}$ & $7$ & $128$ & $1.8735\cdot10^{-15}$ \\
  $10^{-4}$ & $8$ & $256$ & $1.1102\cdot10^{-16}$ \\
  $10^{-5}$ & $9$ & $512$ & $9.7145\cdot10^{-17}$ \\
  \hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  \multicolumn{4}{|c|}{$B_{10}(x)=x^{10}-5x^9+\frac{15}{2}x^8-7x^6+5x^4-\frac{3}{2}x^2+\frac{5}{66}$} \\
  \hline
  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(B_{10}(x))}-\norm[\cg]{A_{n_{k^*}}(B_{10}(x))}$ \\
  \hline
  $1$ & $5$ & $32$ & $7.7716\cdot10^{-16}$ \\
  $10^{-1}$ & $5$ & $32$ & $7.7716\cdot10^{-16}$ \\
  $10^{-2}$ & $6$ & $64$ & $7.7716\cdot10^{-16}$ \\
  $10^{-3}$ & $6$ & $64$ & $7.7716\cdot10^{-16}$ \\
  $10^{-4}$ & $7$ & $128$ & $7.7716\cdot10^{-16}$ \\
  $10^{-5}$ & $7$ & $128$ & $7.7716\cdot10^{-16}$ \\
  \hline
\end{tabular}
\end{center}

\begin{rem}
MATLAB's machine epsilon is $2.2204\cdot10^{-16}$.
\end{rem}

%\subsection{Examples: Approximating the divergence of a vector field}
%
%In this case, $\cf=\{f:\reals^n\mapsto\reals^m,\, f\in C^1(\Omega)\}$ and $\cg=\{g:\reals^n\mapsto\reals,\, g\in C^0(\Omega)\}$ and $S: f\mapsto \nabla\cdot f=\sum_{j=1}^{m}\partial_{x_j}f_j$.
%
%\begin{gather*}
%\norm[\cf]{f} =\left[\int_\Omega \sum_{j=1}^{m}\abs{f_j(x)}^2+\sum_{j=1}^{m}\abs{f'_j(x)}^2 \, \dif x \right]^{1/2},\\
%\norm[\cg]{g} = \left[\int_\Omega \abs{g(x)}^2 \, \dif x \right]^{1/2}, \\
%u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} <i,x>}}{\sqrt{mV(\omega)+4\pi<i,i>}}, \\
%v_i(x) = \me^{2 \pi \sqrt{-1} <i,x>},\\
% \lambda_i=\frac{2\pi\sqrt{-1}\sum_{j=1}^{m}i_j}{\sqrt{mV(\omega)+4\pi<i,i>}}, \qquad i \in \integers^m,\\
%\pin=\pout=2,\quad q=\infty.
%\end{gather*}

\section*{References}
%\nocite{*}
\bibliographystyle{elsarticle-num}
\bibliography{FJH23,FJHown23}

\end{document}

### 2018-07-23 AutoAlgorithmLinearFunctionalDataVerC.tex
Initial ShareLaTeX Import

\documentclass[final]{elsarticle}
\setlength{\marginparwidth}{0.5in}
\usepackage{amsmath,amssymb,amsthm,natbib,bbm,mathtools,booktabs,graphicx,color}
\input FJHDef.tex

\newcommand{\chin}{\ch_{\text{\rm{in}}}}
\newcommand{\chout}{\ch_{\text{\rm{out}}}}
\newcommand{\pin}{p_{\text{\rm{in}}}}
\newcommand{\pout}{p_{\text{\rm{out}}}}
%\newcommand{\cc}{\mathcal{C}}
\newcommand{\cq}{\mathcal{Q}}
\newcommand{\co}{\mathcal{O}}
\newcommand{\bbW}{\mathbb{W}}
%\newcommand{\tP}{\widetilde{P}}
\newcommand{\bg}{{\bf g}}
\newcommand{\bu}{{\bf u}}
\newcommand{\bbu}{\bar{\bf u}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bbv}{\bar{\bf v}}
\newcommand{\bw}{{\bf w}}
\newcommand{\bbw}{\bar{\bf w}}
%\newcommand{\tcf}{\widetilde{\cf}}
%\newcommand{\hv}{\hat{v}}
\newcommand{\tca}{\widetilde{\ca}}
\newcommand{\bgamma}{\boldsymbol\gamma}
\DeclareMathOperator{\MSE}{MSE}
\DeclareMathOperator{\RMSE}{RMSE}
\DeclareMathOperator{\rnd}{rnd}
\DeclareMathOperator{\abso}{abs}
\DeclareMathOperator{\rel}{rel}
\DeclareMathOperator{\nor}{nor}
\DeclareMathOperator{\err}{err}
\DeclareMathOperator{\lin}{lin}
%\DeclareMathOperator{\std}{std}
\DeclareMathOperator{\prob}{prob}
\DeclareMathOperator{\trunc}{trc}
\DeclareMathOperator{\third}{third}
\DeclareMathOperator{\non}{non}
%\DeclareMathOperator{\fourth}{fourth}
\newtheorem{theorem}{Theorem}
\newtheorem{cor}[theorem]{Corollary}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{lem}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{algo}{Algorithm}
\newtheorem{condit}{Condition}
%\newtheorem{assump}{Assumption}
\theoremstyle{remark}
\newtheorem{rem}{Remark}
\newtheorem{exmp}{Example}

\DeclareMathOperator{\fix}{fix}
\DeclareMathOperator{\up}{up}
\DeclareMathOperator{\lo}{lo}

\newcommand{\arbAn}{A^*_n}
\newcommand{\optAn}{A_n}

\definecolor{orange}{rgb}{1.0,0.3,0.0}
\definecolor{violet}{rgb}{0.75,0,1}
\newcommand{\frednote}[1]{  {\textcolor{red}  {\mbox{**Fred:} #1}}}
\newcommand{\yuhannote}[1]{ {\textcolor{violet}  {\mbox{**Yuhan:} #1}}}
\newcommand{\tonynote}[1]{ {\textcolor{orange}  {\mbox{**Tony:} #1}}}

\journal{Journal of Complexity}

\begin{document}

\begin{frontmatter}

\title{Adaptive Algorithms Employing Continuous Linear Functionals}
\author{Yuhan Ding}
\address{MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612}
\author{Fred J. Hickernell}
\address{Center for Interdisciplinary Scientific Computation and \\
Department of Applied Mathematics, Illinois Institute of Technology \\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616}
\author{Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
\address{Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616}
\begin{abstract}
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}
\end{frontmatter}

\section{Introduction}
Adaptive algorithms determine the design and sample size needed to solve problems to the desired accuracy.  A priori upper bounds on some norm of the input function are not required, but there may be some underlying assumptions about the input function required for the adaptive algorithm to be successful.  Here we consider general linear problems where the series coefficients of the input function are used to obtain an approximate solution.  The algorithm proposed guarantees the accuracy of the approximate solution.  Moreover, our algorithm is shown to have a computational cost that is asymptotically optimal in comparison to the best possible algorithm.  The set of functions on which our adaptive algorithm is defined is a cone.

Let $\cf$ be a separable Hilbert space of input functions with orthonormal basis $\{u_i\}_{i=1}^\infty$, and let $\cg$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$:  
\begin{subequations}\label{probDef}
\begin{gather}
f = \sum_{i=1}^\infty \hf_i u_i \in \cf, \qquad \norm[\cf]{f}=\bignorm[2]{(\hf_i\big)_{i=1}^\infty}, \\
g = \sum_{i=1}^\infty \hg_i v_i \in \cg, \qquad \norm[\cg]{g}=\bignorm[2]{(\hg_i\big)_{i=1}^\infty}.
\end{gather}
Let these bases be chosen by the singular value decomposition so that the linear solution operator, $S:\cf \to \cg$, satisfies
\begin{gather}
S(u_i) = \lambda_i v_i, \quad i \in \naturals, \qquad S(f) = \sum_{i=1}^n \lambda_i \hf_i v_i, \\
\lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
\norm[\cf \to \cg]{S} := \sup_{f \ne 0} \frac{\norm[\cg]{S(f)}}{\norm[\cf]{f}} = \lambda_1.
\end{gather}
\end{subequations}
This setting includes, for example, the recovery of functions, derivatives, and indefinite integrals.  We are interested in cases where the exact solution generally requires an infinite number of series coefficients, $\hf_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.

Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution to some error tolerance for all inputs in $\ch$:
\begin{multline} \label{adapErrCrit}
\ca(\ch) : = \left\{ \text{algorithms } A:\ch \times (0,\infty) \rightarrow \cg : 
\right . \\ \left .
\bignorm[\cg]{S(f) - A(f,\varepsilon)} \le \varepsilon \ \forall f \in \ch, \ \varepsilon > 0 
\right \}.
\end{multline}
Algorithms in $\ca(\ch)$ are allowed to sample adaptively any bounded, linear functionals
of the input function $f$.  The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.

The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.  By overloading the notation, we define for arbitrary algorithms $A \in \ca(\ch)$, 
\begin{equation*}
\cost(A,\ch,\varepsilon) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \} \qquad \forall \varepsilon > 0.
\end{equation*}
For unbounded sets, $\ch$, this cost may be infinite.  Therefore, it is also helpful to define the cost for input functions in $\ch \cap \cb_{\rho}$, where $\cb_{\rho} : = \{ f \in \cf : \norm[\cf]{f} \le \rho \}$ is the ball of radius $\rho$:
\begin{equation*}
\cost(A,\ch,\varepsilon,\rho) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \cap \cb_{\rho} \} \qquad \forall \rho > 0, \ \varepsilon > 0.
\end{equation*}
Note that $\cost(A,\ch,\varepsilon,\rho)$ is no less than---but possibly greater than---$\cost(A,\ch \cap \cb_{\rho},\varepsilon)$.  In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.  
Finally, we define the complexity of the problem as computational cost of the best algorithm:
\begin{gather*}
\comp(\ca(\ch),\varepsilon) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon), \\
\comp(\ca(\ch),\varepsilon,\rho) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon, \rho).
\end{gather*}

An optimal algorithm for $\cb_{\rho}$ can be constructed in terms of the interpolation based on the first $n$ series coefficients of the input, namely,
\begin{gather}  \label{optAdef}
\optAn(f) := \sum_{i=1}^n \lambda_{i} \hf_{i} v_{i}, \\
\label{errOpt}
\norm[\cg]{S(f) - \optAn(f)} = \Bignorm[2]{\left(\lambda_{i} \hf_{i} \right)_{i= n+1}^{\infty}} \le \lambda_{n+1} \norm[\cf]{f}.
\end{gather}
Define the non-adaptive, algorithm as
\begin{equation} \label{optBallalg}
\hA(f,\varepsilon) = A_{n^*}(f), \quad \text{where } n^* = \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}, \qquad \hA \in \ca(\cb_{\rho}).
\end{equation}
This algorithm is optimal among algorithms in $\ca(\cb_{\rho})$, i.e.,
\[
\comp(\ca(\cb_{\rho}),\varepsilon) = \cost(\hA,\cb_{\rho},\varepsilon) =
\min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}.
\]

To prove this, let $A^*$ be an arbitrary algorithm in $\ca(\cb_{\rho})$, and let $L_1, \ldots, L_n$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.  Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_n(0)) = (0, \ldots, 0)$.  Let $f$ be a linear combination of $u_1, \ldots, u_{n+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_n(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
\begin{align*}
\varepsilon & \ge \max_{\pm} \norm[\cg]{S(\pm f) - A^*(\pm f)} =  \max_{\pm} \norm[\cg]{\pm S( f) - A^*(0)} \\
& \ge \frac 12 \left [ \norm[\cg]{S( f) - A^*(0)} + \norm[\cg]{- S( f) - A^*(0)}\right] \\
& \ge \norm[\cg]{S(f)} 
= \bignorm[2]{\big(\lambda_i\hf_i\big)_{i=1}^{n+1}} \\
& \ge \lambda_{n+1} \bignorm[2]{\big(\hf_i\big)_{i=1}^{n+1}} = \lambda_{n+1} \norm[\cf]{f} = \lambda_{n+1} \rho.
\end{align*}
Thus, $\lambda_{n+1} \le \varepsilon/\rho$, and $n \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}$.  Hence, algorithm $\hA$ defined in \eqref{optBallalg} is optimal for $\ca(\cb_{\rho})$.

We defined an algorithm $A \in \ca(\ch)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \ca(\ch^*)$ if for some number $\omega$,
\begin{gather}
\cost(A,\ch,\varepsilon) \le \cost(A^*,\ch^*,\omega\varepsilon), \qquad \forall \varepsilon > 0, \\
\cost(A,\ch,\varepsilon,\rho) \le \cost(A^*,\ch^*,\omega\varepsilon,\rho), \qquad \forall \varepsilon,\rho > 0.
\end{gather}
If the costs of two algorithms are essentially no worse than each other, then we call them essentially the same.  An algorithm whose cost is essentially no worse than the best possible algorithm, is called \emph{essentially optimal}.

To illustrate these concepts, consider a nondecreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \naturals$.  Also consider an unbounded strictly increasing sequence of nonnegative integers $\vn = \{n_0, n_1, \ldots \}$.  Define an algorithm $A^*$ analogously to $\hA$ defined in \eqref{optBallalg}:
\begin{equation} \label{altBallalg}
A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \ca(\cb_{\rho}).
\end{equation}
Algorithm $A^*$ may or may not have essentially no worse cost than $\hA$ depending on the choice of $\vlambda^*$ and $\vn$.  The table below shows some examples.  Each different case of $A^*$ is labeled as having a cost that is either essentially no worse or essentially worse than that of $\hA$.
\[
\everymath{\displaystyle}
\begin{array}{rllll}
\toprule
&\lambda_i = \frac{C}{i^p}
& 
\cost(\hA,\cb_\rho,\varepsilon) \ge \left ( \frac{C\rho}{\varepsilon} \right)^{1/p} - 1
\\[2ex]
& &
\cost(\hA,\cb_\rho,\varepsilon) 
<  \left ( \frac{C\rho}{\varepsilon} \right)^{1/p}
\\[2ex]
\midrule
\text{no worse}
&
\lambda^*_i = \frac{C^*}{i^p}, \ n_j = 2^j
&
\cost(A^*,\cb_\rho,\varepsilon) \le 
2 \left ( \frac{C^*\rho}{\varepsilon} \right)^{1/p}
\\[2ex]
\midrule
\text{worse}
&
\lambda^*_i = \frac{C^*}{i^q}, \ q<p, \ n_j = j
&
\cost(A^*,\cb_\rho,\varepsilon)  \ge 
\left ( \frac{C^*\rho}{\varepsilon} \right)^{1/q} - 1 
\\[2ex]
\toprule
&\lambda_i = \frac{C}{p^i}, \ p > 1
& 
\cost(\hA,\cb_\rho,\varepsilon) \ge \frac{\log (C\rho/\varepsilon)}{\log(p)} - 1
\\[2ex]
&&
\cost(\hA,\cb_\rho,\varepsilon) < \frac{\log (C\rho/\varepsilon)}{\log(p)}
\\[2ex]
\midrule
\text{no worse}
&
\lambda^*_i = \frac{C^*}{p^i}, \ n_j = 2j
&
\cost(A^*,\cb_\rho,\varepsilon) < \frac{\log (C^*\rho/\varepsilon)}{\log(p)} + 1
\\[2ex]
\midrule
\text{worse}
&
\lambda^*_i = \frac{C^*}{p^i}, \ n_j = 2^j
&
\cost(A^*,\cb_\rho,\varepsilon) > 1.999 \frac{\log (C^*\rho/\varepsilon)}{\log(p)} 
\\[1ex]
&& \qquad \qquad \text{for some } \varepsilon
\\
\midrule
\text{worse}
&
\lambda^*_i = \frac{C^*}{i^q}, \ q<p, \ n_j = j
&
\cost(A^*,\cb_\rho,\varepsilon)  \ge 
\frac{\log (C^*\rho/\varepsilon)}{\log(q)} - 1
\\[2ex]
\toprule
\end{array}
\]

For bounded sets of input functions, such as balls, non-adaptive algorithms, such as $\hA$, make sense.  However, it is typically unknown which ball the input function lies in.  Thus, we consider unbounded sets of input functions, whose properties can be inferred from the data we collect.  We will use the interpolatory algorithm $\optAn$, defined in \eqref{optAdef}, but we will propose an alternative way to bound the error other than assuming an a priori bound on $\norm[\cf]{f}$.

Adaptive algorithms encountered in practice typically employ heuristic error bounds.  While any algorithm can be fooled, we would like precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.  That is what our adaptive algorithm accomplishes.

Our rigorous, data-driven error bound assumes the input to have steadily---but not necessarily monotonically---decaying series coefficients.  The cone of nice inputs, $\cc$, is defined in Section \ref{sec:cone}.  For such inputs, we construct an adaptive algorithm, $\tA \in \ca(\cc)$, in Section \ref{sec:adaptalgo},  where $\tA(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$.  The number of series coefficients sampled, $n^*$, is adaptively determined so that $\tA(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.  The computational cost of $\tA$ is given in  Theorem \ref{thm:compcost}.  Section \ref{sec:opt} shows that our new algorithm is asymptotically optimal, i.e., ???.  Section \ref{sec:examp} provides an example of our algorithm.  Concluding remarks are give in Section \ref{sec:conc}.  We close this section with an example of the function spaces and solution operator that we consider.

\begin{exmp} Consider the case of function approximation for periodic functions defined on the [0,1], and algorithm $\hA$ defined in \eqref{optBallalg}:
\begin{align*}
f &= \sum_{k \in \integers} \hf(k) \hu_{k} (\vx) = \sum_{i=1}^n \hf_i u_i(x), 
& S(f) & = \sum_{k \in \integers} \hf(k) \hlambda_k \hv_k = \sum_{i=1}^n \hf_i \lambda_i \hv_i, \\
\hv_{k} (x) &:= \begin{cases} 1, & k = 0, \\
\displaystyle \sqrt{2} \sin(2\pi k x), & k > 0, \\
\displaystyle \sqrt{2} \cos(2\pi k x), & k < 0, \\
\end{cases} 
& v_i(x) &= \begin{cases} \hv_{-i/2}, & i \text{ even},\\
\hv_{(i-1)/2}, & i \text{ odd},
\end{cases} \\
\hlambda_{k} &:= \begin{cases} 1, & k = 0, \\
\displaystyle \frac{1}{\abs{k}^r}, & k \ne 0,
\end{cases}
& \lambda_i &= \hlambda_{\lfloor i/2\rfloor} = \frac{1}{\max(1,\lfloor i/2\rfloor)^r}, \\
\hu_{k} (x) &:= \hlambda_k\hv_k(x),
& u_i(x) &= \begin{cases} \hu_{-i/2}, & i \text{ even},\\
\hu_{(i-1)/2}, & i \text{ odd},
\end{cases}
\\
&&\hf_i& = \begin{cases} \hf(-i/2), & i \text{ even},\\
\hf((i-1)/2), & i \text{ odd},
\end{cases}
\end{align*}
\begin{align*}
\comp(\ca(\cb_{\rho}),\varepsilon) &= \cost(\hA,\cb_{\rho},\varepsilon) 
=\min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} \\
& = \min \left\{ n : \frac{1}{\lfloor (n+1)/2 \rfloor^r} \le \frac{\varepsilon}{\rho} \right\} 
= 2 \left \lceil \left(\frac{\rho}{\varepsilon} \right)^{1/r} \right \rceil - 1.
% & \lambda_{n+1} = \frac{1}{\lceil (n+1)/2 \rceil^r}.
\end{align*}
Here $\cg=\cl_2[0,1]$.  The larger the non-negative parameter $r$ is, the smaller $\cb_\rho$ is, and the smaller  $\cost(\hA,\cb_{\rho},\varepsilon)$ is.  For $r = 0$, $\cost(\hA,\cb_{\rho},\varepsilon) = \infty$.
\end{exmp}

\section{Assuming that the Series Coefficients of the Solution Decay \\ Steadily} \label{sec:cone}

Recall from \eqref{errOpt} that the error of the fixed sample size interpolatory algorithm $\optAn$ is $\norm[\cg]{S(f) - \optAn(f)} = \bignorm[2]{\bigl(\lambda_{i} \hf_{i} \bigr)_{i= n+1}^{\infty}}$.  The error depends on the series coefficients not yet observed, so at first glance this error seems to be impossible to bound in terms of observed series coefficients.

However, we can observe, say the partial sums 
\begin{equation} \label{sumdef}
\sigma_j(f) :
= \norm[2]{ \left(\lambda_{i} \hf_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j=1, 2, \ldots,
\end{equation}
where $\vn  = \{n_0, n_1, \ldots\}$ is a strictly increasing, unbounded sequence of non-negative integers.  We define the cone of nice input functions to consist of those functions for which the $\sigma_j(f)$ decay at a given rate with respect to one another:
\begin{align} \label{decayconedef}
\cc &= \left\{ f \in \cf : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \forall j,r \in \naturals \right\} \\
\nonumber
& = \left\{ f \in \cf : \sigma_j(f) \le \min_{1 \le r < j}\{ab^r\sigma_{j-r}(f)\} \ \forall j \in \naturals \right\}.
\end{align}
Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\cc$ and 
\begin{equation} \label{abcond}
b <1 < a.
\end{equation}
The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \cc$. We do not expect the series coefficients of the solution $S(f)$, to decay monotonically. However, we expect their partial sums to decay steadily.

Using the expression for the error in \eqref{errOpt} and the definition of the cone in  \eqref{decayconedef}, one can now derive a data-driven error bound for $j \in \naturals$:
\begin{align}
\nonumber
\norm[\cg]{S(f)-A_{n_j}(f)} &= \norm[2]{\left(\lambda_{i} \hf_{i} \right)_{i = n_j+1}^\infty} = \left\{\sum_{r=1}^\infty \sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \abs{\lambda_{i}\hf_{i} }^{2}  \right\}^{1/2}\\
\nonumber
&= \norm[2]{ \left(\sigma_{j+r}(f)\right)_{r=1}^{\infty}} \\
&\le \norm[2]{ \left(ab^r\sigma_{j}(f)\right)_{r=1}^{\infty}}
 = \displaystyle ab \sqrt{\frac{1}{1 - b^2}}\sigma_{j}(f)
 \label{algoineq}
\end{align}
The upper and lower error bounds depend only on the function data and the parameters defining $\cc$.  The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.  Moreover, the error of $A_{n_j}(f)$ is asymptotically the no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance. Our adaptive algorithm in the Section \ref{sec:adaptalgo} increases $j$ until the right hand side is smaller than the error tolerance.

Consider the choice 
\begin{equation} \label{geonj}
n_j = 2^{j}n_0,
\end{equation}
where the number of terms in the sums, $\sigma_j(f)$, are doubled at each step.  If the series coefficients of the solution decay like $\lambda_{i} \abs{f_{i}} = \Order(i^{-p})$ for some $p>1$, then it is reasonable to expect that the $\sigma_j(f)$ are bounded above and below as
\begin{equation} \label{algDecJ}
C_{\lo} (n_02^j)^{1-p} \le \sigma_j(f) \le C_{\up} (n_02^j)^{1-p}, \quad   j \in \naturals,
\end{equation}
for some constants $C_{\lo}$ and $C_{\up}$, unless the series coefficients drop precipitously in magnitude for some $n_{j-1} < i \le n_j$, and then jump back up for larger $i$.  When \eqref{algDecJ} holds, it follows that
\begin{equation*} 
\frac{\sigma_{j+r}(f)}{\sigma_j(f)} \le \frac{C_{\up} (n_02^{j+r})^{1-p}}{C_{\lo} (n_02^j)^{1-p}} = \frac{C_{\up} 2^{r(1-p)}}{C_{\lo}}\quad   j \in \naturals.
\end{equation*}
Thus, choosing $a \ge C_{\up}/C_{\lo}$ and $b \ge 2^{1-p}$ ensures that reasonable inputs $f$ lie inside the cone $\cc$.

\section{Adaptive Algorithm} \label{sec:adaptalgo}

Now we introduce our adaptive algorithm, $\tA \in \ca(\cc)$, which yields an approximate solution to the problem $S:\cc\rightarrow\cg$ that meets the absolute error tolerance $\varepsilon$.

\begin{algo}\label{algo2}
Given $a$, $b$, the sequence $\vn$, the cone $\cc$, and the input function $f \in \cc$, and the absolute error tolerance $\varepsilon$, set $j=1$.
\begin{description}
\item[Step 1.] Compute $\sigma_{j}(f)$ as defined in \eqref{sumdef}.
\item[Step 2.] Check whether $j$ is large enough to satisfy the error tolerance, i.e.,
    \begin{equation}\label{covcrit}
          \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab} .
    \end{equation}
    If this is true, then return $\tA(f,\varepsilon) = A_{n_{j}}(f)$, where $\optAn$ is defined in \eqref{optAdef}, and terminate the algorithm.
\item[Step 3.] Otherwise, increase $j$ by $1$ and return to Step $1$.
\end{description}
\end{algo}

\begin{theorem}\label{thm:compcost}
The algorithm, $\tA$, defined in Algorithm \ref{algo2} lies in $\ca(\cc)$ and has computational cost $\cost(\tA,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly by the inequalities 
\[
\sigma_{j^*}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  < \sigma_{j}(f), \quad 1 \le j < j^*.
\]
Moreover, $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
\begin{equation} \label{jdagger}
j^\dagger \le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}.
\end{equation}

\end{theorem}

\begin{proof}
This algorithm terminates for some $j = j^*$ because $\sigma_j(f) \le ab^{j-1} \sigma_{1}(f) \to 0$ as $j \to \infty$. The value of $j^*$ follows directly from this termination criterion in Step 2.  It then follows that the error bound on $A_{n_{j^*}}(f)$ in \eqref{algoineq} is no greater than the error tolerance $\varepsilon$.  So, $\tA \in \ca(\cc)$.

To derive an upper bound on $\cost(\tA,\rho,\varepsilon)$ we start by noting some properties of $\sigma_j(f)$ for all $f \in \cc$:
\begin{multline} \label{normsigineq}
\lambda_{n_j} \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}} \le 
\bignorm[2]{\big( \lambda_i \hf_i \big)_{i=n_{j-1}+1}^{n_j}} = \sigma_j(f) 
\\
\le \lambda_{n_{j-1}+1} \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}}.
\end{multline}
A rough upper bound on $\cost(\tA,\rho,\varepsilon)$ may be obtained by noting that  for any $f \in \cc$ that also lies in the ball of radius $\rho$, and for any $j < j^\dagger$, it follows by \eqref{normsigineq} and  Theorem \ref{thm:compcost} that 
\begin{equation*}
\rho \ge \norm[\cf]{f} \ge \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
\end{equation*}
Thus, one upper bound on $j^\dagger$ is the smallest $j$ violating the above inequality:
\begin{equation} \label{jdaggerlast}
j^\dagger \le \min \left \{j \in \naturals :  \lambda_{n_{j-1}+1} \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\}.
\end{equation}

The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by an argument in a similar vein to the one above.  
For any $f \in \cc$ that also lies in the ball of radius $\rho$,
\begin{align*}
\rho^2 &\ge \norm[\cf]{f}^2 = \bignorm[2]{\big( \hf_i \big)_{i=1}^{\infty}}^2 \\
& \ge \sum_{k=1}^j \bignorm[2]{\big( \hf_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \qquad \forall j \ge 1\\
& \ge \sum_{k=1}^j \frac{\sigma_k^2(f)}{\lambda_{n_{k-1}+1}^2} \qquad \text{by \eqref{normsigineq}}\\
& \ge \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}\sigma_j^2(f)}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{\sigma_j^2(f)}{\lambda_{n_{j-1}+1}^2} \qquad \text{by \eqref{decayconedef}} \\
& = \sigma_j^2(f) \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^{2} \lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
\end{align*}
Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum becomes more inclusive and $b^{2(k-j)}$ also increases.

For all $j < j^\dagger$ it follows from the definition of the algorithm and Theorem \ref{thm:compcost} above that 
\begin{equation*}
\rho^2 > \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
\end{equation*}
Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$.
\end{proof}

We note in passing that for our adaptive algorithm
\begin{equation*}
 \min \{\cost(\tA,f,\varepsilon) : f \in \cc, \ \norm[\cf]{f} \ge \rho \} 
 \begin{cases} = n_1, & n_0 > 0, \\
 \le n_2, & n_0 = 0, 
 \end{cases}
 \qquad \forall \rho > 0, \ \varepsilon > 0.
\end{equation*}
This result may be obtained by considering functions where only $\hf_1$ is nonzero.  For $n_0 > 0$, $\sigma_1(f) = 0$, and for $n_0 = 0$, $\sigma_2(f) = 0$.

The upper bound on $\cost(\tA,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.  This in turn depends both on the increasing sequence $\vn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$. Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation} \label{keysum}
\sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}.
\end{equation}
One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.  These simplifications lead to two simpler, but coarser upper bounds on the cost of $\tA$

\begin{cor} For the algorithm, $\tA$, defined in Algorithm \ref{algo2}, then $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
\begin{equation} \label{jdaggerfirst}
j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}+1} }{\varepsilon \sqrt{1 - b^2}}\right) \div \log\left(\frac{1}{b}\right) \right \rceil.
\end{equation}
Moreover, if the $\lambda_{n_{j-1}+1}$ decay as quickly as
\begin{equation}
\label{lambdankbd}
\lambda_{n_{j-1}+1} \le \alpha \beta^j,  \quad j \in \naturals,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
\end{equation}
then $j^\dagger$ also satisfies the following upper bound:
\begin{equation}
\label{jdaggerlastsimple}
j^\dagger \le
\left \lceil \log\left(\frac{\rho a\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \div \log\left(\frac{1}{\beta}\right) \right \rceil.
\end{equation}
\end{cor}

\begin{proof}
Ignoring all but the first term in the sum in \eqref{keysum} implies that 
\begin{equation} \label{jsumupperbd}
j^\dagger \le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2}    \right\}.
\end{equation}
This implies \eqref{jdaggerfirst}.

Ignoring all but the term outside the sum leads to the simpler upper bound in \eqref{jdaggerlast}.  If the $\lambda_{n_{j-1}+1}$ decay as assumed in \eqref{lambdankbd} then
\[
j^\dagger \le \min \left \{j \in \naturals :  \alpha \beta^j < \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
\]
which implies \eqref{jdaggerlastsimple}.
\end{proof}

This corollary highlights two limiting factors on the computational cost of our adaptive algorithm, $\tA$. When $j$ is large enough to make $\lambda_{n_{j-1}+1}\norm[\cf]{f}/\varepsilon$ small enough, $\tA(f,\varepsilon)$ stops.  This is statement \eqref{jdaggerlastsimple}, and its precursor, \eqref{jdaggerlast}.  Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\cc$ in \eqref{cdef}, means that $\tA(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\norm[\cf]{f}/\varepsilon$.

Assumption \eqref{lambdankbd} is not very restrictive.  It holds if the $\lambda_i$ decay algebraically and the $n_j$ increase geometrically.  It also holds if the $\lambda_i$ decay geometrically and the $n_j$ increase arithmetically.

The adaptive algorithm $\tA$, which does not know an upper bound on $\norm[\cf]{f}$ a priori, may cost more than the non-adaptive algorithm $\hA$, which assumes an upper bound on $\norm[\cf]{f}$, but under reasonable assumptions, the extra cost will be small.

\begin{cor} \label{cor:tAsameCosthA} Suppose that the sequence $\vn$ is chosen to satisfy
\begin{equation} \label{lambdaDecay}
\lambda_{n_{j+1}+1} \ge c_\lambda \lambda_{n_j+1}, \qquad j \in \naturals, 
\end{equation}
for some positive $c_\lambda$.  Then $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially no worse than \linebreak[4]
$\cost(\hA,\cb_{\rho},\varepsilon)$.

\end{cor}

\begin{proof}
Combining the upper bound on $n_{j^\dagger} = \cost(\tA,\cc,\varepsilon,\rho)$ in \eqref{jdaggerlast} plus  \eqref{lambdaDecay} above, it follows that
\begin{equation*}
\lambda_{n_{j^\dagger}+1} \ge c_{\lambda}^2 \lambda_{n_{j^\dagger-2}+1} > \frac{\varepsilon c_{\lambda}^2\sqrt{1 - b^2}}{ab \rho} \ge \lambda_{n+1},
\end{equation*}
where $n = \cost(\hA,\cb_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab)$.
Since the $\lambda_i$ are non-increasing,
\begin{equation*}
\cost(\tA,\cc,\varepsilon,\rho) = n_{j^\dagger} \le n_{j^\dagger}+1 < n = \cost(\hA,\cb_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
\end{equation*}
\end{proof}

\section{Optimality of the Adaptive Algorithm} \label{sec:opt}

From Corollary \ref{cor:tAsameCosthA} it is known that $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially no worse than
$\cost(\hA,\cb_{\rho},\varepsilon) = \comp(\ca(\cb_{\rho}),\varepsilon)$.  We would like to show that $\tA \in \ca(\cc)$ is  essentially optimal, i.e., $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially the same as  $\comp(\ca(\cc),\varepsilon,\rho)$.  However,  $\comp(\ca(\cc),\varepsilon,\rho)$ may be smaller than $\comp(\ca(\cb_{\rho}),\varepsilon)$ because $\cc \cap \cb_\rho$ is a strict subset of  $ \cb_\rho$.  This presents a challenge.

The proof is accomplished by constructing fooling functions in $\cc$ with norms no greater than $\varrho$.

\begin{theorem} \label{thm:lowbdcomp}
A lower bound on the complexity of the linear problem defined in \eqref{probDef} is
\begin{subequations} \label{compbd}
\begin{align}
 \label{compbdA}
\comp(\ca(\cc),\varepsilon,\rho) &\ge n_{j^*},  \\
\label{compbdB}
\text{where} \qquad j^* &= \max \left \{ j \in \naturals : \sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}   < \frac{\rho(a-1)}{2a \varepsilon}
\right \}.
\end{align}
\end{subequations}
\end{theorem}

\begin{proof}
Consider a fixed $\rho$ and $\varepsilon$.  Choose any positive integer $j$ such that $n_j$ exceeds $\comp(\ca(\cc),\varepsilon,\rho)$.  The proof proceeds by constructing test input functions, $f$ and $f^*_{\pm}$, all lying in $\cc$ and in the ball with radius $\rho$, which yield the same approximate solution while yielding different true solutions.  This leads to a lower bound on $n_j$, which can be translated into a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.

The first test function $f \in \cc$ is defined in terms of its series coefficients:
\begin{align}
\nonumber
\hf_i &:= \begin{cases}
\displaystyle
\frac{c b^{k-j}}{\lambda_{n_{k}}},  & i =  n_{k}, \ k = 1, \ldots, j,
\\
0, & \text{otherwise}
\end{cases}
\\
\label{cdef}
c &:= \frac{\rho (a+1)}{2a} \left[\sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}} \right]^{-1}.
\end{align}
It can be verified that the test function lies in a ball of radius $\rho$ and also in the cone $\cc$:
\begin{align}
\label{testfunnorm}
\norm[\cf]{f} & \le c \sum_{k=1}^j \norm[\cf]{\hf_{n_k} u_{n_k}} = c \sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}  \le \rho,
\\
\nonumber
\sigma_k(f) &= \begin{cases}
\displaystyle
c b^{k-j}, & k =1, \ldots, j, \\
0, & \text{otherwise},
\end{cases}
\\
\nonumber
\sigma_{k+r}(f) &= \begin{cases}
\displaystyle 
b^{r} \sigma_k(f) \le a b^r \sigma_k(f), & k+r \le j, \ r \ge 1,
\\
0 \le a b^r \sigma_k(f), & k+r > j, \ r \ge 1.
\end{cases}
\end{align}

Now suppose that $A^*(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where $n \le \comp(\rho,\varepsilon) < n_j$.  Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$ constructed to have unit norm and satisfy $L_1(u) = \cdots = L_n(u) = 0$.  Let 
\begin{gather}
\label{etadef}
f^*_\pm = f \pm \eta u, \quad \eta : = \max_{1 \le k \le j} \frac {c(a-1)b^{k-j}}{(a+1) \lambda_{n_k}}, \\
\nonumber
\norm[\cf]{f^*_\pm} \le \norm[\cf]{f} + \eta \le \frac{2ac}{a+1} \sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}  \le \rho.
\end{gather} 
By design, $A^*(f^*_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.

Now we must check that $f^*_\pm \in \cc$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$
\begin{align*}
\sigma_k(f^*_\pm) & \begin{cases} 
\displaystyle
\le \sigma_k(f) + \eta \lambda_{n_k} = \frac{2a b^{k-j}}{a+1}, 
\\[1ex]
\displaystyle
\ge \sigma_k(f) - \eta \lambda_{n_k}  = \frac{2 b^{k-j}}{a+1}, 
\end{cases}
\\
\sigma_{k+r}(f^*_\pm) & 
\le \frac{2a b^{k+r-j}}{a+1} \le ab^r \frac{2 b^{k-j}}{a+1} \le a b^r \sigma_{k}(f^*_\pm).
\end{align*}

Given the two test functions $f^*_\pm$ and our successful algorithm, $A^*$, we note that
\begin{align*}
\varepsilon &\ge \max \bigl\{\norm[\cg]{S(f^*_+) - A^*(f^*_+,\varepsilon)}, \norm[\cg]{S(f^*_-) - A^*(f^*_-,\varepsilon)} \bigr\} \\
&\ge \frac 12 \bigl[\norm[\cg]{S(f^*_+) - A^*(f,\varepsilon)} + \norm[\cg]{S(f^*_-) - A^*(f,\varepsilon)}  \bigr] \\
&\qquad \qquad \text{since } A^*(f^*_\pm,\varepsilon) = A^*(f,\varepsilon) \\
&\ge \frac 12 \norm[\cg]{S(f^*_+) - S(f^*_-)} \quad \text{by the triangle inequality}\\
&\ge \frac 12 \norm[\cg]{S(f^*_+ - f^*_-)} \quad \text{since $S$ is linear}\\
&= \eta \norm[\cg]{S(u)} \ge \eta \lambda_{n_j} \ge \frac {c(a-1)}{(a+1)} \quad \text{by \eqref{etadef}} \\
& = \frac{\rho(a-1)}{2a} \left[\sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}} \right]^{-1}.
\end{align*}
This lower bound must be satisfied by $j$ to be consistent with the assumption $\comp(\rho,\varepsilon) < n_j$.  Any $j$ violating this inequality then provides a lower bound on $\comp(\rho,\varepsilon)$.
\end{proof}

\begin{theorem}
If the $\lambda_{n_j}$ satisfy the lower bound
\begin{equation} \label{lambdaalphabetabd}
\lambda_{n_j} \ge \xi \zeta^{j}, \qquad j \in \naturals,
\end{equation}
for some non-negative $\xi$ and $\zeta$ with $\zeta < 1$, then $\cost(\tA,\cc,\varepsilon,\rho)$ is essentially the same as $\comp(\ca(\cc),\varepsilon,\rho)$ for all positive $\varepsilon$ and $\rho$.  Thus, our adaptive algorithm, $\tA$ is essentially optimal for problems defined on $\cc$.
\end{theorem}
\begin{proof}  Fix positive $\varepsilon$ and $\rho$.  Without loss of generality, we may choose $\zeta$ in \eqref{lambdaalphabetabd} different from $b$.  Let $j^*$ be defined as in \eqref{compbdB}, and consider the sum in its definition.  For all $j \in \naturals$, 
\begin{align*}
\sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}
& \le 
\frac{1}{\xi b^j} \sum_{k=1}^j \left(\frac{b}{\zeta} \right)^{k-j} 
= 
\frac{1}{\xi b^j} \frac{b/\zeta - (b/\zeta)^{j+1}}{1 - b/\zeta}
\\
&\le
\begin{cases}
\displaystyle 
\frac{b}{\xi \zeta^{j}(b -  \zeta)},
& \zeta < b
\\
\displaystyle 
\frac{b}{\xi b^{j}(\zeta - b)}, & \zeta > b.
\end{cases}
\end{align*}

Let $n_{j^\dagger} = \cost(\tA,\cc,\varepsilon,\rho)$.  We consider two cases.

If $\zeta > b$, then 
\begin{align*}
\sum_{k=1}^{j^\dagger} \frac{b^{k-j^\dagger}}{\lambda_{n_{k}}}
& \le \frac{b}{\xi b^{j^\dagger}(\zeta - b)} \\ 
& < \frac{\rho a^2 b \lambda_{n_0+1}}{\varepsilon \xi \sqrt{1-b^2}(\zeta - b) } \\
& = \frac{\rho (a-1)}{2 a (\omega\varepsilon)}, \quad \text{where } \omega = \frac{\xi (a-1)\sqrt{1-b^2}(\zeta - b)}{2a^3b \lambda_{n_0+1}}  
\end{align*}
Thus, by \eqref{compbd}, $\cost(\tA,\cc,\varepsilon,\rho) = n_{j^\dagger} \le \comp(\ca(\cc),\omega \varepsilon,\rho)$.

Alternatively, if $\zeta < b$, then 
\begin{align*}
\sum_{k=1}^{j^\dagger} \frac{b^{k-j^\dagger}}{\lambda_{n_{k}}}
& \le \frac{b}{\xi \zeta^{j^\dagger}(b - \zeta)} \\ 
& < \frac{\rho a^2 b \lambda_{n_0+1}}{\varepsilon \xi \sqrt{1-b^2}(\zeta - b) } \\
& = \frac{\rho (a-1)}{2 a (\omega\varepsilon)}, \quad \text{where } \omega = \frac{\xi (a-1)\sqrt{1-b^2}(\zeta - b)}{2a^3b \lambda_{n_0+1}}  
\end{align*}

\end{proof}

\section{Examples} \label{sec:examp}

Consider the case of approximating the first partial derivatives of periodic functions defined on the $d$-dimensional unit cube:
\begin{align*}
f &= \sum_{\vk \in \integers^d} \hf(\vk) u_{\vk} (\vx), \\
u_{\vk} (\vx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j k_j)},  \\
S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\vk \in \integers^d} \hf(\vk) \lambda_{\vk} v_{\vk} (\vx), \\
v_{\vk}(\vx) & : =  -\sign(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
& \qquad \qquad \times \prod_{j=2}^d 2^{(1-\delta_{k_j,0})/2} \cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ), \\
\lambda_{\vk} &:= \frac{2 \pi \abs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}
\end{align*}

%\subsection{Examples: Approximating the divergence of a vector field}
%
%In this case, $\cf=\{f:\reals^n\mapsto\reals^m,\, f\in C^1(\Omega)\}$ and $\cg=\{g:\reals^n\mapsto\reals,\, g\in C^0(\Omega)\}$ and $S: f\mapsto \nabla\cdot f=\sum_{j=1}^{m}\partial_{x_j}f_j$.
%
%\begin{gather*}
%\norm[\cf]{f} =\left[\int_\Omega \sum_{j=1}^{m}\abs{f_j(x)}^2+\sum_{j=1}^{m}\abs{f'_j(x)}^2 \, \dif x \right]^{1/2},\\
%\norm[\cg]{g} = \left[\int_\Omega \abs{g(x)}^2 \, \dif x \right]^{1/2}, \\
%u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} <i,x>}}{\sqrt{mV(\omega)+4\pi<i,i>}}, \\
%v_i(x) = \me^{2 \pi \sqrt{-1} <i,x>},\\
% \lambda_i=\frac{2\pi\sqrt{-1}\sum_{j=1}^{m}i_j}{\sqrt{mV(\omega)+4\pi<i,i>}}, \qquad i \in \integers^m,\\
%\pin=\pout=2,\quad q=\infty.
%\end{gather*}

\section{Discussion and Conclusions} \label{sec:conc}

\section*{References}
%\nocite{*}
\bibliographystyle{elsarticle-num}
\bibliography{FJH23,FJHown23}

\end{document}

\begin{rem}
For the algorithm, $\tA$, defined in Algorithm \ref{algo2}, $\cost(\tA,\rho,\varepsilon) \le n_{j^*}$, where $j^*$ satisfies the following upper bound:
\[
j^* \le \min \left \{j \in \naturals : \rho^2 \le \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\up}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right]\right\}.
\]
\end{rem}

\begin{proof}
First, we have a rough upper bound on $\cost(\tA,\rho,\varepsilon)$ in the proof of  Theorem  \ref{thm:compcost} by finding the smallest $j$ violating the following inequality:
\begin{equation*}
\rho \ge \norm[\cf]{f} \ge \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
\end{equation*}
If we consider $\lambda_{i}$ is bounded above
\begin{equation} \label{lambdaDecI}
\lambda_i \le C_{\up} i^{1-p}, \quad   i \in \naturals,
\end{equation}
where $p > 1$, we obtain
\begin{align*}
\rho & > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}} \\
& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}(n_{j-1}+1)^{1-p}} \qquad \text{by \eqref{lambdaDecI}} \\
& > \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}n_{j-1}^{1-p}} \\
& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}(2^{j-1}n_0)^{1-p}} \qquad \text{by \eqref{geonj}} \\
& = \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}n_0^{1-p} 2^{(j-1)(1-p)}}
\end{align*}
Thus, one upper bound on $j^*$ is the smallest $j$ violating the above inequality:
\[
j^* \le \min \left \{j \in \naturals :  
j \ge \frac{\log\left[\frac{\varepsilon \sqrt{1-b^2}}{\rho ab C_{\up}n_0^{1-p}}\right]}{(1-p)\log 2}+ 1\right\}
\]

We could also obtain another upper bound similar to the tighter upper bound in Theorem \ref{thm:compcost}.  
The tighter cost is the smallest $j$ that violates the following inequality
\begin{equation*}
\rho^2 > \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
\end{equation*}
From \eqref{lambdaDecI}, we can obtain for any $k=1, \ldots,j-1$
\[\lambda_{n_{k-1}+1} \le C_{\up}(n_{k-1}+1)^{1-p} 
<  C_{\up}(n_{k-1})^{1-p} < C_{\up}n_0^{1-p}.\]
Thus, we have 
\begin{align*}
\rho^2 &> \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]\\
& >  \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}(C_{\up}n_0^{1-p})^2} + \frac{1}{(C_{\up}(n_{j-1})^{1-p} )^2}\right] \\
& = \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}C_{\up}^2n_0^{2(1-p)}} + \frac{1}{C^2_{\up}(2^{j-1}n_0)^{2(1-p)}}\right] \qquad \text{by \eqref{geonj}}\\
&  =\frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\up}^2n_0^{2(1-p)}} \left[ \frac{1}{a^2b^{2j}}\sum_{k=1}^{j-1} b^{2k }+ \frac{1}{2^{2(j-1)(1-p)}}\right] \\
& > \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\up}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right] .
\end{align*}
Hence, any $j$ that violates the above inequality, must satisfy $j \ge j^*$.
\end{proof}

/fi
\iffalse
\subsection{The embedding of $f(x)=\frac{(b^2-1)}{b^2+1-2b\cos(2\pi x)}$}

In our example, consider $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f$ the embedding operator with:
\begin{gather*}
\norm[\cf]{f} = \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x},\quad \lambda_i=1, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

For our index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$,
\begin{gather*}
i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
n_0=0,\quad n_k=2k+1, \qquad k\in\naturals.
\end{gather*}

The Fourier coefficients of this function can be easily found:
\begin{align*}
f(x)&=\frac{b^2-1}{b^2+1-2b\cos(2\pi x)}\\
&=\frac{1-b^{-2}+b^{-1}(\me^{-2\pi\sqrt{-1}x}-\me^{-2\pi\sqrt{-1}x})}{1+b^{-2}-b^{-1}(\me^{2\pi\sqrt{-1}x}+\me^{-2\pi\sqrt{-1}x})}\\
&=\frac{(1-b^{-1}\me^{-2\pi\sqrt{-1}x})+(1-b^{-1}\me^{2\pi\sqrt{-1}x})b^{-1}\me^{-2\pi\sqrt{-1}x}}{(1-b^{-1}\me^{2\pi\sqrt{-1}x})(1-b^{-1}\me^{-2\pi\sqrt{-1}x})}\\
&=\frac{1}{1-b^{-1}\me^{2\pi\sqrt{-1}x}}+\frac{b^{-1}\me^{-2\pi\sqrt{-1}x}}{1-b^{-1}\me^{-2\pi\sqrt{-1}x}}\\
&=\sum_{k\in\naturals_0}\left(b^{-1}\me^{2\pi\sqrt{-1}x}\right)^k+\sum_{k\in\naturals}\left(b^{-1}\me^{-2\pi\sqrt{-1}x}\right)^k\\
&=\sum_{k\in\integers}b^{-\abs{k}}\me^{2\pi\sqrt{-1}kx}\Longrightarrow\hf_{i_j}=b^{-\abs{i_j}}
\end{align*}

Because we are interested in seeing how far the approximation is from the real solution, the norm of the exact solution has to be found. Knowing the Fourier coefficients leads us to an easy way to calculate it:
\begin{align*}
\norm[\cg]{S(f)}&=\left(\sum_{j\in\integers}\lambda_{i_j}^2\hf_{i_j}^2\right)^{\frac{1}{2}} =\left(1+2\sum_{k\in\naturals}b^{-2k}\right)^{\frac{1}{2}}=\left(\frac{b^2+1}{b^2-1}\right)^{\frac{1}{2}}
\end{align*}

We can also give the sums of coefficients,
\begin{align*}
&\sigma_1(f)=\sqrt{1+2b^{-2}}\\
&\sigma_k(f)=\sqrt{2}b^{-k}, \qquad k \in\naturals\setminus\{1\}.
\end{align*}
Recalling the alternative definition of the cone in (\ref{decayconedef}), with these sums, $f\in\cc$ for $\gamma_r=b^{-r}$ since
\begin{equation*}
\sigma_k(f) \le \min_{1 \le i <k}\{\gamma_i\sigma_{k-i}(f)\}=\min\left\{1 \; , \; \sqrt{1+\frac{b^2}{2}} \right\}\sigma_k(f)
\end{equation*}

In this case, $\norm[\pout]{\bgamma}=\frac{1}{\sqrt{b^2-1}}$. If we use our Algorithm \ref{algo2}, we have to check first whether $\sqrt{\frac{b^2+2}{b^4-b^2}}\le\varepsilon$. If this inequality states, then $k^*=1$. If not,
\begin{equation*}
k^*=\min\left\{k\in\naturals\setminus\{1\}:\frac{1}{2\log(b)}\log\left(\frac{2}{(b^2-1)\varepsilon^2}\right) \le k \right\}
\end{equation*}

For a numerical application, set $b=3$ and find below a table of results for this example,

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(f)}-\norm[\cg]{A_{n_{k^*}}(f)}$ \\
  \hline
  $1$ & $1$ & $3$ & $1.2492\cdot10^{-2}$ \\
  $10^{-1}$ & $2$ & $5$ & $1.3811\cdot10^{-3}$ \\
  $10^{-2}$ & $4$ & $9$ & $1.7041\cdot10^{-5}$ \\
  $10^{-3}$ & $6$ & $13$ & $2.1038\cdot10^{-7}$ \\
  $10^{-4}$ & $8$ & $17$ & $2.5973\cdot10^{-9}$ \\
  $10^{-5}$ & $10$ & $21$ & $3.2065\cdot10^{-11}$ \\
  $10^{-6}$ & $12$ & $25$ & $3.9591\cdot10^{-13}$ \\
  $10^{-7}$ & $15$ & $31$ & $4.4409\cdot10^{-16}$ \\
  \hline
\end{tabular}
\end{center}

\subsection{Derivation of the Bernoulli polynomials}

The properties we will use for these particular polynomials can be found in \cite{AbrSte64}: derivatives, explicit Fourier coefficients, etc. To deal with this example, now $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f'$ with,
\begin{gather*}
\norm[\cf]{f} = \left[\int_0^1 \left\{\abs{f(x)}^2 + \abs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \integers,\\
\pin=\pout=2,\quad q=\infty.
\end{gather*}

Like in the previous example, the index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$ has the following ordering
\begin{gather*}
i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
n_0=0,\quad n_k=2^k, \qquad k\in\naturals.
\end{gather*}

For this case,
\begin{equation*}
B_n(x)=-\frac{n!}{(2\pi\sqrt{-1})^n}\sum_{k\in\integers\setminus\{0\}}\frac{\me^{2\pi\sqrt{-1}kx}}{k^n}\Longrightarrow
\left\{\begin{array}{l}
\widehat{B_n}_0=0 \\
\widehat{B_n}_{i_j}=-\frac{n!\sqrt{1+4 \pi^2 i_j^2}}{(2\pi\sqrt{-1}i_j)^n},\quad i_j\in\integers\setminus\{0\}
\end{array}\right.
\end{equation*}

Using that $B'_n(x)=nB_{n-1}(x)$ and $\int_0^1B_n(t)B_m(t)\dif t=(-1)^{n-1}\frac{m!n!}{(m+n)!}B_{n+m}$, the real solution comes automatically,
\begin{equation*}
\norm[\cg]{S(B_n(x))}=n\norm[\cg]{B_{n-1}(x)}=n!\sqrt{\frac{\abs{B_{2(n-1)}}}{[2(n-1)]!}}
\end{equation*}
where $B_n=B_n(0)$ are the Bernoulli numbers.

If we consider $\gamma_r=s_1s_2^{-r}$ and that
\begin{equation}\label{bound}
\frac{n!}{\sqrt{2}\pi^n}j^{-n} \le \abs{\lambda_{i_j}\widehat{B_n}_{i_j}} \le \frac{n!2^n}{\pi^n}j^{-n},\quad j\in\naturals\setminus\{1\}
\end{equation}
then $C_{\up}=2^{n+\frac{1}{2}}C_{\lo}=\frac{n!2^n}{\pi^n}$. Thus, as shown in the example example at the beginning of this section we can take
\begin{equation*}
s_1=2\times11^{n-\frac{1}{2}},\quad s_2=2^{n-\frac{1}{2}}
\end{equation*}
There is still one thing to check because $j=1$ was not taken into account in the inequality (\ref{bound}). However, see that $\sigma_1(f) \ge C_{\lo}\left(\frac{5}{36}\right)^{n-\frac{1}{2}}$ what means that the $\gamma_r=s_1s_2^{-r}$ found satisfies our needs.

For a numerical application, find below the results for the case $n=5$ and $n=10$,

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  \multicolumn{4}{|c|}{$B_5(x)=x^5-\frac{5}{2}x^4+\frac{5}{3}x^3-\frac{1}{6}x$} \\
  \hline
  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(B_5(x))}-\norm[\cg]{A_{n_{k^*}}(B_5(x))}$ \\
  \hline
  $1$ & $5$ & $32$ & $2.9439\cdot10^{-11}$ \\
  $10^{-1}$ & $6$ & $64$ & $2.2703\cdot10^{-13}$ \\
  $10^{-2}$ & $7$ & $128$ & $1.8735\cdot10^{-15}$ \\
  $10^{-3}$ & $7$ & $128$ & $1.8735\cdot10^{-15}$ \\
  $10^{-4}$ & $8$ & $256$ & $1.1102\cdot10^{-16}$ \\
  $10^{-5}$ & $9$ & $512$ & $9.7145\cdot10^{-17}$ \\
  \hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
  \multicolumn{4}{|c|}{$B_{10}(x)=x^{10}-5x^9+\frac{15}{2}x^8-7x^6+5x^4-\frac{3}{2}x^2+\frac{5}{66}$} \\
  \hline
  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(B_{10}(x))}-\norm[\cg]{A_{n_{k^*}}(B_{10}(x))}$ \\
  \hline
  $1$ & $5$ & $32$ & $7.7716\cdot10^{-16}$ \\
  $10^{-1}$ & $5$ & $32$ & $7.7716\cdot10^{-16}$ \\
  $10^{-2}$ & $6$ & $64$ & $7.7716\cdot10^{-16}$ \\
  $10^{-3}$ & $6$ & $64$ & $7.7716\cdot10^{-16}$ \\
  $10^{-4}$ & $7$ & $128$ & $7.7716\cdot10^{-16}$ \\
  $10^{-5}$ & $7$ & $128$ & $7.7716\cdot10^{-16}$ \\
  \hline
\end{tabular}
\end{center}

\begin{rem}
MATLAB's machine epsilon is $2.2204\cdot10^{-16}$.
\end{rem}
\fi

\iffalse

We do not expect the series coefficients of the solution $S(f)$, to decay monotonically.  The sequence $\vn$ is used to average finite sequences of Fourier coefficients into groups to smooth the peaks we could encounter if we take these coefficients one by one. Flattening the peaks is a must to fit functions into the cone. Nevertheless, the solution of our algorithm is in this set $\cn$ which means that the sequence does not have to distance the optimal number of data needed in our algorithm (defined below) more than a constant.

We define the optimal number of data needed to solve the problem defined as \eqref{errCond} is 
\begin{equation*}
N_{\opt}(f,\varepsilon)=\min\left\{n\in\naturals:\,\norm[2]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n+1}} \le \varepsilon \right\}
\end{equation*}

Any algorithm is called \emph{asymptotically  optimal} if it essentially tracks the optimal number of data needed,
\begin{equation} \label{nearoptdef}
\sup_{\varepsilon > 0 } \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty 
\end{equation}
or
\[
\sup_{\varepsilon > 0 } [\cost(A,f;\varepsilon)- N_{\opt}(f,\varepsilon)] <\infty.
\]

Next, we prove our algorithm is optimal.

\begin{theorem}\label{nopt}
Algorithm \ref{algo2} is optimal for this problem.

\end{theorem}
\begin{proof}
Given $f \in \cc$ and $\varepsilon$, denote $n^*= N_{\opt}(f,\varepsilon)$. Let 
\[n_{k^*-r-1} < n^{*}  \le n_{k^*-r} \le n_{k^*},\]
where $n_{k^*}$ is the cost of our algorithm.
Thus by \eqref{sumdef}, we obtain
\[\sigma_{k^*-r+1}(f) = \norm[2]{ \left(\lambda_{i_j} \hf_{i_j} \right)_{j=n_{k^*-r}+1}^{n_{k^*-r+1}}}
 \le \norm[2]{ \left(\lambda_{i_j} \hf_{i_j} \right)_{j=n^*}^{\infty}} \le \varepsilon.\]
By the cone condition \eqref{decayconedef} , we have 
\[\sigma_{k^*-r+m}(f) \le \gamma_{m-1}\sigma_{k^*-r+1}(f) \le\gamma_{m-1} \cdot \varepsilon.\]
Choose $m$ such that $\gamma_{m-1} \le \frac{1}{\norm[2]{\vgamma}},$
thus we obtain
\[\sigma_{k^*-r+m}(f) \le\gamma_{m-1} \cdot \varepsilon \le \frac{\varepsilon}{\norm[2]{\vgamma}}.\]
Suppose $\gamma_r$ decays geometrically, $n_k$ increases geometrically $n_k = n_0 2^k $, we have
\[\frac{\cost(\tA,f;\varepsilon)}{N_{\opt}(f,\varepsilon)} \le 
\frac{n_{k^*-r+m}}{n_{k^*-r-1}} = \frac{n_0 2^{k^*-r+m}}{n_0 2^{k^*-r-1}}
= 2^{m+1}.\]

As $m$ satisfied 
\begin{align*}\
\gamma_{m-1} \le \frac{1}{\norm[2]{\vgamma}} 
& \Longleftrightarrow C_1C_2^{-m+1} \le \frac{\sqrt{C_2^2-1}}{C_1} \\
& \Longrightarrow C_2^{-m+1} \le \frac{\sqrt{C_2^2-1}}{C^2_1} \\
& \Longrightarrow  m \ge 1+ 
\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}.
\end{align*}
Therefore we can choose 
\[m = \left\lceil 1+ 
\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)} \right\rceil
 < 2 + \frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}. \]
Hence,
 \[\frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} 
 \le 2^{m+1} < 2^{3+\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}} \Longrightarrow \sup_{f,\varepsilon} \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty.\]

Suppose $\gamma_r$ decays geometrically, $n_k$ increases linearly $n_k = n_0 + 2k $, we have
\begin{align*}
\cost(\tA,f;\varepsilon)-N_{\opt}(f,\varepsilon) & \le 
n_{k^*-r+m}-n_{k^*-r-1} \\ & = (n_0 +2(k^*-r+m))-(n_0+2(k^*-r-1))\\
& = 2(m+1).
\end{align*}
Still choose
\[m = \left\lceil 1+ 
\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)} \right\rceil
 < 2 + \frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}. \]
 We have
\begin{align*}
\cost(\tA,f;\varepsilon)-N_{\opt}(f,\varepsilon) 
& = 2(m+1) \\
&  = 2\left(3+ \frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}\right)\\
\Longrightarrow &
\sup_{f,\varepsilon} \left[\cost(A,f;\varepsilon) -N_{\opt}(f,\varepsilon) \right]< \infty
\end{align*}
\end{proof}

\fi

### 2018-07-23 ProgramsImages/sim_FourCoef.m

@@ -1,0 +1,102 @@
+% Simulations:
+% - Complex Exponential
+% - Direct Fourier sampling (no f'n evals)
+
+%% Simulation settings
+close all
+clearvars
+format short e
+d = 3;     %dimension
+coord_wt_vec = 2.^(0:-1:-d+1);
+wt_pow = 4;
+wv_num_max = 20;
+wv_num_mtx = permn(-wv_num_max:wv_num_max,d); %compute this just once for all
+nBasis = size(wv_num_mtx,1); %number of basis elements
+n_app = 2^10; %number of points to use for approximating L_inf norm
+% Assume that
+%  x is nX x d
+%  k is nK x d
+u_wt_fun = @(k) prod(2.^((k~=0)/2) ./ max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
+v_wt_fun = @(k) -sign(k(:,1)) .* 2.^(sum(k~=0,2)/2); %nK x 1
+basisName = 'CompExp'; %complex Exponential
+% inp_basis_fun = @(k,x) exp((2*pi*sqrt(-1))* (x * k'))./u_wt_fun(k)'; %nX x nK
+% out_basis_fun = @(k,x) -exp((2*pi*sqrt(-1))* (x * k')); %nX x nK
+inp_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
+   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* u_wt_fun(k)'; %nX x nK
+out_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
+   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* v_wt_fun(k)'; %nX x nK
+lambda = @(k) (2*pi)*(abs(k(:,1)).*u_wt_fun(k)); %nK x 1;
+[~,wh_ordLambda] = sort(lambda(wv_num_mtx),'descend');
+
+% Error tolerances
+num_eps = 10; %no. of errors
+min_log10_eps = -1;
+max_log10_eps = 1;
+eps_vec = 10.^(linspace(min_log10_eps,max_log10_eps,num_eps))';
+eps_vec = flipud(eps_vec); %so that we visualize the smallest tolerance
+
+%% Compute true function
+
+% Compute Fourier coef and gammas for true function
[…]

### 2018-07-23 ProgramsImages/sim_FourCoef_plot_results.m

@@ -1,0 +1,126 @@
+%%Plot results
+function sim_FourCoef_plot_results(basisName)
+
+load(['sim_FourCoef_results_basis_' basisName '.mat'], ...
+   'rat_vec', 'eps_vec', 'n_vec', 'd', 'inp_basis_fun', 'out_basis_fun', ...
+   'wv_num_mtx', 'wh_ordLambda', 'four_coef', 'lambda', ...
+   'min_log10_eps', 'max_log10_eps') %load results for plotting
+
+gail.InitializeDisplay %add some variables for nice plotting
+
+figure
+log10epsVec = log10(eps_vec);
+h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+hold on
+set(gca,'XScale','log', 'YScale','log')
+xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
+ max([10.^(ceil(log10(rat_vec*1.2))); 1])])
+ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
+%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size \(n\)'})
+hcb = colorbar; %showing tolerance values
+title(hcb,'\(\varepsilon\)','interpreter','latex')
+tickVals = floor(min_log10_eps):ceil(max_log10_eps);
+tickLabels = 10.^tickVals;
+set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
+   'Limits',[tickVals(1) tickVals(end)])
+[~,leg_icons] = legend(h, ...
+   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
+   }, ...
+   'box','off','location','north','orientation','horizontal');
+set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
+leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
+print -depsc SimFourCoefErr.eps
+
[…]

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
John
revising intro

@@
 Algorithms in $\ca(\ch)$ are allowed to sample adaptively any bounded, linear functionals
-of the input function $f$.  The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
+of the input function $f$.
+They must require only a finite number of linear functionals for each input function and positive tolerance.
+The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
+Following \cite{KunEtal19a}
 
@@
  \label{compbdA}
-\comp(\ca(\cc),\varepsilon,\rho) &\ge n_{j^*},  \\
+\comp(&\ca(\cc),\varepsilon,\rho) \ge n_{j^*},  \\
+\nonumber
+\text{where} & \\
 \label{compbdB}
-\text{where} \qquad j^* &= \max \left \{ j \in \naturals : \sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}   < \frac{\rho(a-1)}{2a \varepsilon}
+& j^* = \max \left \{ j \in \naturals : \left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   < 
+\frac{(a-1)^2\rho^2}{(a+1)^2A^2\varepsilon^2}
 \right \}.
@@
 \label{cdef}
-c &:= \frac{\rho (a+1)}{2a} \left[\sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}} \right]^{-1}.
+c^2 &:=  \rho^2 \left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1},
 \end{align}
+where 
+\[A = \max_{1 \le k \le j} \frac{\lambda_{n_{k-1}+1}}{\lambda_{n_k}}.\]
 It can be verified that the test function lies in a ball of radius $\rho$ and also in the cone $\cc$:
@@
 \label{testfunnorm}
-\norm[\cf]{f} & \le c \sum_{k=1}^j \norm[\cf]{\hf_{n_k} u_{n_k}} = c \sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}  \le \rho,
+\norm[\cf]{f}^2 &=  c^2\sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \le \rho^2,
 \\
@@
 
-Now suppose that $A^*(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where $n \le \comp(\rho,\varepsilon) < n_j$.
-Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$ constructed to have unit norm and satisfy $L_1(u) = \cdots = L_n(u) = 0$.
+Now suppose that $A^* \in \ca(\cc)$ is an optimal algorithm, i.e., $\cost(A^*,\cc,\varepsilon,\rho) =  \comp(\ca(\cc),\varepsilon,\rho)$ for all $\varepsilon, \rho > 0$.
+For our particular input $f$ defined above, suppose that $A^*(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where
+\[n + 1
+\le \comp(\ca(\cc),\varepsilon,\rho) +1 < n_j.\]  Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$ constructed to have unit norm and satisfy $L_1(u) = \cdots = L_n(u) = 0$ and $\langle u,f \rangle_{\cf} = 0$.
+Denote
+\[u = \sum_{k=1}^{j}u^{(k)}\frac{b^{k-j}}{\lambda_{n_k}}\]
+where $u^{k}= \sum_{i = n_{k-1}+1}^{n_k} \hu_i u_i$ and
+$\max_{1\le k\le j} \norm[\cf]{u^{(k)}} = 1.$
 Let 
@@
 \label{etadef}
-f^*_\pm = f \pm \eta u, \quad \eta : = \max_{1 \le k \le j} \frac {c(a-1)b^{k-j}}{(a+1) \lambda_{n_k}}, \\
+f^*_\pm = f \pm \eta u, \quad \eta : =  \frac {(a-1)}{(a+1)A}c, \\
 \nonumber
-\norm[\cf]{f^*_\pm} \le \norm[\cf]{f} + \eta \le \frac{2ac}{a+1} \sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}  \le \rho.
+\norm[\cf]{f^*_\pm}^2 \le \norm[\cf]{f}^2 + \norm[\cf]{\eta u } 
+\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \norm[\cf]{u^{(k)}}^2\right)\\
+\nonumber
+\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \right)  \le \rho^2.
 \end{gather} 
@@
 \displaystyle
-\le \sigma_k(f) + \eta \lambda_{n_k} = \frac{2a b^{k-j}}{a+1}, 
+\le \sigma_k(f) + \sigma_k(\eta u)\le 
+c b^{k-j} + \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\norm[\cf]{u^{(k)} } }{\lambda_{n_k}}
+\le b^{k-j}\left(c+\eta A \right) 
 \\[1ex]
 \displaystyle
-\ge \sigma_k(f) - \eta \lambda_{n_k}  = \frac{2 b^{k-j}}{a+1}, 
+\ge \sigma_k(f) - \sigma_k(\eta u)\ge 
+c b^{k-j} - \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\norm[\cf]{u^{(k)} } }{\lambda_{n_k}}
+\ge b^{k-j}\left(c-\eta A \right) , 
 \end{cases}
 \\
-\sigma_{k+r}(f^*_\pm) & 
-\le \frac{2a b^{k+r-j}}{a+1} \le ab^r \frac{2 b^{k-j}}{a+1} \le a b^r \sigma_{k}(f^*_\pm).
+\sigma_{k+r}(f^*_\pm)&
+\le b^{k+r-j}(c+\eta A) = ab^r b^{k-j}\frac{2c}{a+1}
+=ab^r b^{k-j}\left(c-\eta A \right) \le a b^r \sigma_{k}(f^*_\pm).
 \end{align*}
@@
 &\ge \frac 12 \norm[\cg]{S(f^*_+ - f^*_-)} \quad \text{since $S$ is linear}\\
-&= \eta \norm[\cg]{S(u)} \ge \eta \lambda_{n_j} \ge \frac {c(a-1)}{(a+1)} \quad \text{by \eqref{etadef}} \\
-& = \frac{\rho(a-1)}{2a} \left[\sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}} \right]^{-1}.
-\end{align*}
-This lower bound must be satisfied by $j$ to be consistent with the assumption $\comp(\rho,\varepsilon) < n_j$.
-Any $j$ violating this inequality then provides a lower bound on $\comp(\rho,\varepsilon)$.
+&= \eta \norm[\cg]{S(u)}
+\end{align*}
+Thus, we have
+\begin{align*}
+\varepsilon^2 \ge \eta \norm[\cg]{S(u)}^2 & = 
+\eta^2\sum_{k=1}^{j} \norm[\cf]{S(u^{(k)}}^2 
+\left(\frac{b^{k-j}}{\lambda_{n_k}}\right)^2\\
+& \ge \eta^2 
+\sum_{k=1}^{j} {\sigma_k(u)}^2 
+\left(\frac{b^{k-j}}{\lambda_{n_k}}\right)^2\\
+& \ge \eta^2 
+\sum_{k=1}^{j} \norm[\cf]{u^{(k)}}^2 
+b^{2(k-j)}\\
+& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \arg\max_{k} \norm[\cf]{u^{(k)}} = 1\\
+& \ge \eta^2 = \frac{(a-1)^2}{(a+1)^2A^2}c^2 \\
+&
+=\frac{(a-1)^2 \rho^2}{(a+1)^2A^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1}
+\end{align*}
+
+This lower bound must be satisfied by $j$ to be consistent with the assumption $\comp(\ca(\cc),\varepsilon,\rho) < n_j$.
+Any $j$ violating this inequality then provides a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
 \end{proof}
@@
 \end{align*}
+
+\yuhannote{The figure is here in comment}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width = 8 cm]{ProgramsImages/SimDirectSolErr.eps}
+%\end{figure}
 

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX

@@
 The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
-Following \cite{KunEtal19a}
+Following \cite{KunEtal19a} we call a problem \emph{solvable} for inputs $\ch$ if $\ca(\ch)$ is non-empty.
+
+Note that our problem is not solvable for $\cf$.
+This can be proven by contradiction.
+We show that there is some function, $f \in \cf$, that looks like the zero function, but whose corresponding solution, $S(f)$, is far from $0$.
+Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$.
+Since only a finite number of samples is used, there exists some nonzero $f \in \cf$ that  appears exactly like $0$ to the algorithm, but which has a non-zero solution, $S(f)$.
+This means that $L_1(f) = \cdots = L_n(f) = 0$, and so $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.
+Since our algorithm successfully produces an approximation with error no greater than $\varepsilon$,
+\begin{align*}
+    \varepsilon &\ge \frac 12 \left[ \norm[\cg]{S(0) - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(cf,\varepsilon)}\right] \\
+    & =  \frac 12 \left[ \norm[\cg]{0 - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(0,\varepsilon)}\right] \\
+    & \ge  \frac {\abs{c}\norm[\cg]{S(f)}}2  \qquad \text{by the triangle inequality}.
+\end{align*}
+Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.
+Thus, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.
+However, it is solvable for well-chosen subsets of $\cf$.
 

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
revising "solvable"

@@
 
-Note that our problem is not solvable for $\cf$.
-This can be proven by contradiction.
-We show that there is some function, $f \in \cf$, that looks like the zero function, but whose corresponding solution, $S(f)$, is far from $0$.
+Our problem is not solvable for $\cf$, as can be demonstrated by contradiction.
+For any potential algorithm, we show that there is some $f \in \cf$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
 Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$.
-Since only a finite number of samples is used, there exists some nonzero $f \in \cf$ that  appears exactly like $0$ to the algorithm, but which has a non-zero solution, $S(f)$.
-This means that $L_1(f) = \cdots = L_n(f) = 0$, and so $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.
-Since our algorithm successfully produces an approximation with error no greater than $\varepsilon$,
+Since $n$ is finite, there exists some nonzero $f \in \cf$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
+This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.
+Since $A$ successfully produces an approximation with error no greater than $\varepsilon$ for both $0$ and $cf$,
 \begin{align*}

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
fixed a comment in the intro

@@
 \end{equation*}
-Note that $\cost(A,\ch,\varepsilon,\rho)$ is no less than---but possibly greater than---$\cost(A,\ch \cap \cb_{\rho},\varepsilon)$.
-In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
 Finally, we define the complexity of the problem as computational cost of the best algorithm:
@@
 \end{gather*}
+Note that $\comp(\ca(\ch),\varepsilon,\rho) \ge \comp(\ca(\ch \cap \cb_{\rho}),\varepsilon)$.  In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
 

### 2018-08-04 AutoAlgorithmLinearFunctionalDataVerC.tex
revised proof in Section 4

@@
 
-The proof is accomplished by constructing fooling functions in $\cc$ with norms no greater than $\varrho$.
+A lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$ is established by   proof is accomplished by constructing fooling functions in $\cc$ with norms no greater than $\rho$.
+To obtain a result that can be compared with the cost of our algorithm, we assume that
+\begin{equation} \label{lambdaRatio}
+R = \sup_{k \in \naturals} \frac{\lambda_{n_{k-1}}}{\lambda_{n_k}} < \infty.
+\end{equation}
+This means that the $n_k$ are not too far apart with respect to the decay of $\lambda_i$ as $i \to \infty$
 
 \begin{theorem} \label{thm:lowbdcomp}
-A lower bound on the complexity of the linear problem defined in \eqref{probDef} is
+Under assumption  \eqref{lambdaRatio}, a lower bound on the complexity of the linear problem defined in \eqref{probDef} is
 \begin{subequations} \label{compbd}
@@
  \label{compbdA}
-\comp(&\ca(\cc),\varepsilon,\rho) \ge n_{j^*},  \\
-\nonumber
-\text{where} & \\
+&\comp(\ca(\cc),\varepsilon,\rho) \ge n_{j^*}, 
+\intertext{where}
 \label{compbdB}
-& j^* = \max \left \{ j \in \naturals : \left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   < 
-\frac{(a-1)^2\rho^2}{(a+1)^2A^2\varepsilon^2}
+j^* & = \max \left \{ j \in \naturals : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
+\frac{\rho^2}{\varepsilon^2}
 \right \}.
@@
 Choose any positive integer $j$ such that $n_j$ exceeds $\comp(\ca(\cc),\varepsilon,\rho)$.
-The proof proceeds by constructing test input functions, $f$ and $f^*_{\pm}$, all lying in $\cc$ and in the ball with radius $\rho$, which yield the same approximate solution while yielding different true solutions.
+The proof proceeds by carefully constructing thre  test input functions, $f$ and $f_{\pm}$, lying in $\cc \cap \cb_{\rho}$, which yield the same approximate solution but different true solutions.
 This leads to a lower bound on $n_j$, which can be translated into a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
@@
 \\
-0, & \text{otherwise}
+0, & \text{otherwise},
 \end{cases}
@@
 \label{cdef}
-c^2 &:=  \rho^2 \left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1},
+c^2 &:=  \rho^2 \left[ \left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1}.
 \end{align}
-where 
-\[A = \max_{1 \le k \le j} \frac{\lambda_{n_{k-1}+1}}{\lambda_{n_k}}.\]
-It can be verified that the test function lies in a ball of radius $\rho$ and also in the cone $\cc$:
+It can be verified that the test function lies both in $\cb_{\rho}$ and in $\cc$:
 \begin{align}
@@
 For our particular input $f$ defined above, suppose that $A^*(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where
-\[n + 1
-\le \comp(\ca(\cc),\varepsilon,\rho) +1 < n_j.\]  Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$ constructed to have unit norm and satisfy $L_1(u) = \cdots = L_n(u) = 0$ and $\langle u,f \rangle_{\cf} = 0$.
-Denote
-\[u = \sum_{k=1}^{j}u^{(k)}\frac{b^{k-j}}{\lambda_{n_k}}\]
-where $u^{k}= \sum_{i = n_{k-1}+1}^{n_k} \hu_i u_i$ and
-$\max_{1\le k\le j} \norm[\cf]{u^{(k)}} = 1.$
-Let 
-\begin{gather}
+\[
+n + 1\le \comp(\ca(\cc),\varepsilon,\rho) +1 < n_j.
+\]
+
+Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$, expressed as
+\[
+u =  \sum_{k=0}^{j}\frac{b^{k-j}u^{(k)}}{\lambda_{n_k}},
+\]
+where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(k)}$ is a linear combination of $u_{n_k+1}, \ldots, u_{n_k}$, for $k =1, \ldots, j$.  We constrain $u$ to satisfy:
+\begin{equation}\label{uConstraint}
+L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\cf} = 0, \qquad 
+\max_{0\le k\le j} \bignorm[\cf]{u^{(k)}} = 1.
+\end{equation}
+Since $u$ is a linear combination of $n_j >n+1$ basis functions, these constraints can be satisfied.
+
+Let the other two test functions be constructed in terms of $u$ as 
+\begin{align}
 \label{etadef}
-f^*_\pm = f \pm \eta u, \quad \eta : =  \frac {(a-1)}{(a+1)A}c, \\
+f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)R}, \\
 \nonumber
-\norm[\cf]{f^*_\pm}^2 \le \norm[\cf]{f}^2 + \norm[\cf]{\eta u } 
-\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \norm[\cf]{u^{(k)}}^2\right)\\
+\norm[\cf]{f^*_\pm}^2 & \le \norm[\cf]{f}^2 + \norm[\cf]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
+& \le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \bignorm[\cf]{u^{(k)}}^2\right) + \eta^2 \bignorm[\cf]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
 \nonumber
-\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \right)  \le \rho^2.
-\end{gather} 
-By design, $A^*(f^*_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
-
-Now we must check that $f^*_\pm \in \cc$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$
-\begin{align*}
-\sigma_k(f^*_\pm) & \begin{cases} 
+& \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}  \qquad \text{by \eqref{uConstraint}}\\
+&  \le \rho^2,
+\end{align} 
+so $f_{\pm} \in \cb_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
+
+Now we must check that $f_\pm \in \cc$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$
+\begin{equation*}
+\sigma_k(f_\pm)  \begin{cases} 
 \displaystyle
@@
 c b^{k-j} + \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\norm[\cf]{u^{(k)} } }{\lambda_{n_k}}
-\le b^{k-j}\left(c+\eta A \right) 
+\le b^{k-j}\left(c+\eta R \right) 
 \\[1ex]
@@
 c b^{k-j} - \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\norm[\cf]{u^{(k)} } }{\lambda_{n_k}}
-\ge b^{k-j}\left(c-\eta A \right) , 
+\ge b^{k-j}\left(c-\eta R \right) , 
 \end{cases}
-\\
-\sigma_{k+r}(f^*_\pm)&
-\le b^{k+r-j}(c+\eta A) = ab^r b^{k-j}\frac{2c}{a+1}
-=ab^r b^{k-j}\left(c-\eta A \right) \le a b^r \sigma_{k}(f^*_\pm).
-\end{align*}
-
-Given the two test functions $f^*_\pm$ and our successful algorithm, $A^*$, we note that
-\begin{align*}
-\varepsilon &\ge \max \bigl\{\norm[\cg]{S(f^*_+) - A^*(f^*_+,\varepsilon)}, \norm[\cg]{S(f^*_-) - A^*(f^*_-,\varepsilon)} \bigr\} \\
+\end{equation*}
+Therefore, 
+\begin{equation*}
+\sigma_{k+r}(f_\pm)
+\le b^{k+r-j}(c+\eta R) = ab^r b^{k-j}\frac{2c}{a+1}
+=ab^r b^{k-j}\left(c-\eta R \right) \le a b^r \sigma_{k}(f_\pm),
+\end{equation*}
+which establishes that $f_\pm \in \cc$.
+
+Although two test functions $f_\pm$ yield the same approximate solution, they have different true solutions.  In particular,
+\begin{align*}
+\varepsilon &\ge \max \bigl\{\norm[\cg]{S(f_+) - A^*(f_+,\varepsilon)}, \norm[\cg]{S(f_-) - A^*(f_-,\varepsilon)} \bigr\} \\
 &\ge \frac 12 \bigl[\norm[\cg]{S(f^*_+) - A^*(f,\varepsilon)} + \norm[\cg]{S(f^*_-) - A^*(f,\varepsilon)}  \bigr] \\
@@
 &\ge \frac 12 \norm[\cg]{S(f^*_+ - f^*_-)} \quad \text{since $S$ is linear}\\
-&= \eta \norm[\cg]{S(u)}
+&= \eta \norm[\cg]{S(u)}.
 \end{align*}
@@
 \begin{align*}
-\varepsilon^2 \ge \eta \norm[\cg]{S(u)}^2 & = 
-\eta^2\sum_{k=1}^{j} \norm[\cf]{S(u^{(k)}}^2 
-\left(\frac{b^{k-j}}{\lambda_{n_k}}\right)^2\\
+\varepsilon^2  & \ge \eta \norm[\cg]{S(u)}^2= 
+\eta^2 \sum_{k=0}^{j} \bignorm[\cg]{S(u^{(k)})}^2  \frac{b^{2(k-j)}}{\lambda_{n_k}^2}\\
 & \ge \eta^2 
-\sum_{k=1}^{j} {\sigma_k(u)}^2 
-\left(\frac{b^{k-j}}{\lambda_{n_k}}\right)^2\\
-& \ge \eta^2 
-\sum_{k=1}^{j} \norm[\cf]{u^{(k)}}^2 
+\sum_{k=0}^{j} \bignorm[\cf]{u^{(k)}}^2 
 b^{2(k-j)}\\
-& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \arg\max_{k} \norm[\cf]{u^{(k)}} = 1\\
-& \ge \eta^2 = \frac{(a-1)^2}{(a+1)^2A^2}c^2 \\
-&
-=\frac{(a-1)^2 \rho^2}{(a+1)^2A^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1}
-\end{align*}
-
-This lower bound must be satisfied by $j$ to be consistent with the assumption $\comp(\ca(\cc),\varepsilon,\rho) < n_j$.
-Any $j$ violating this inequality then provides a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
-\end{proof}
-
-\begin{theorem}
-If the $\lambda_{n_j}$ satisfy the lower bound
-\begin{equation} \label{lambdaalphabetabd}
-\lambda_{n_j} \ge \xi \zeta^{j}, \qquad j \in \naturals,
-\end{equation}
-for some non-negative $\xi$ and $\zeta$ with $\zeta < 1$, then $\cost(\tA,\cc,\varepsilon,\rho)$ is essentially the same as $\comp(\ca(\cc),\varepsilon,\rho)$ for all positive $\varepsilon$ and $\rho$.
-Thus, our adaptive algorithm, $\tA$ is essentially optimal for problems defined on $\cc$.
-\end{theorem}
-\begin{proof}  Fix positive $\varepsilon$ and $\rho$.
-Without loss of generality, we may choose $\zeta$ in \eqref{lambdaalphabetabd} different from $b$.
-Let $j^*$ be defined as in \eqref{compbdB}, and consider the sum in its definition.
-For all $j \in \naturals$,
-\begin{align*}
-\sum_{k=1}^j \frac{b^{k-j}}{\lambda_{n_{k}}}
-& \le 
-\frac{1}{\xi b^j} \sum_{k=1}^j \left(\frac{b}{\zeta} \right)^{k-j} 
-= 
-\frac{1}{\xi b^j} \frac{b/\zeta - (b/\zeta)^{j+1}}{1 - b/\zeta}
-\\
-&\le
-\begin{cases}
-\displaystyle 
-\frac{b}{\xi \zeta^{j}(b -  \zeta)},
-& \zeta < b
-\\
-\displaystyle 
-\frac{b}{\xi b^{j}(\zeta - b)}, & \zeta > b.
-\end{cases}
-\end{align*}
-
-Let $n_{j^\dagger} = \cost(\tA,\cc,\varepsilon,\rho)$.  We consider two cases.
-
-If $\zeta > b$, then 
-\begin{align*}
-\sum_{k=1}^{j^\dagger} \frac{b^{k-j^\dagger}}{\lambda_{n_{k}}}
-& \le \frac{b}{\xi b^{j^\dagger}(\zeta - b)} \\ 
-& < \frac{\rho a^2 b \lambda_{n_0+1}}{\varepsilon \xi \sqrt{1-b^2}(\zeta - b) } \\
-& = \frac{\rho (a-1)}{2 a (\omega\varepsilon)}, \quad \text{where } \omega = \frac{\xi (a-1)\sqrt{1-b^2}(\zeta - b)}{2a^3b \lambda_{n_0+1}}  
-\end{align*}
-Thus, by \eqref{compbd}, $\cost(\tA,\cc,\varepsilon,\rho) = n_{j^\dagger} \le \comp(\ca(\cc),\omega \varepsilon,\rho)$.
-
-Alternatively, if $\zeta < b$, then 
-\begin{align*}
-\sum_{k=1}^{j^\dagger} \frac{b^{k-j^\dagger}}{\lambda_{n_{k}}}
-& \le \frac{b}{\xi \zeta^{j^\dagger}(b - \zeta)} \\ 
-& < \frac{\rho a^2 b \lambda_{n_0+1}}{\varepsilon \xi \sqrt{1-b^2}(\zeta - b) } \\
-& = \frac{\rho (a-1)}{2 a (\omega\varepsilon)}, \quad \text{where } \omega = \frac{\xi (a-1)\sqrt{1-b^2}(\zeta - b)}{2a^3b \lambda_{n_0+1}}  
-\end{align*}
-
+& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \bignorm[\cf]{u^{(k)}} \\
+& \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2R^2} \\
+&
+=\frac{(a-1)^2 \rho^2}{(a+1)^2A^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
+& = \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+\end{align*}
+
+This lower bound must be satisfied by $j$ to be consistent with the assumption $\comp(\ca(\cc),\varepsilon,\rho) \le n_j - 1$.
+Thus, for any $j$ violating this inequality it follows that $\comp(\ca(\cc),\varepsilon,\rho) \ge n_j$.
+This implication provides a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
 \end{proof}
@@
 \yuhannote{The figure is here in comment}
-%\begin{figure}
-%	\centering
-%	\includegraphics[width = 8 cm]{ProgramsImages/SimDirectSolErr.eps}
-%\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width = 8 cm]{ProgramsImages/SimDirectSolErr.eps}
+\end{figure}
 

### 2018-08-07 AutoAlgorithmLinearFunctionalDataVerC.tex
uploaded figures to Overleaf and added note.
Added optimality theorem

@@
 
-\section{Assuming that the Series Coefficients of the Solution Decay \\ Steadily} \label{sec:cone}
+\section{Assuming a Steady Decay of the Series Coefficients of the Solution} \label{sec:cone}
 
@@
 
-\section{Optimality of the Adaptive Algorithm} \label{sec:opt}
+\section{Essential Optimality of the Adaptive Algorithm} \label{sec:opt}
 
@@
 \end{equation}
-This means that the $n_k$ are not too far apart with respect to the decay of $\lambda_i$ as $i \to \infty$
+This means that the $n_k$ are not too far apart with respect to the decay of $\lambda_i$ as $i \to \infty$.
+
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\cc$.
+After that we show that the cost of our algorithm as given in Theorem \ref{thm:compcost} is essentially no worse than this lower bound.
 
@@
 
-Now we must check that $f_\pm \in \cc$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$
+Now we must check that $f_\pm \in \cc$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$,
 \begin{equation*}
@@
 &
-=\frac{(a-1)^2 \rho^2}{(a+1)^2A^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
-& = \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=1}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+=\frac{(a-1)^2 \rho^2}{(a+1)^2A^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
+& \le  \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
 \end{align*}
@@
 This implication provides a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
+\end{proof}
+
+The next step is to show that the cost of our algorithm is essentially no worse than that of the optimal algorithm.
+
+\begin{theorem}
+\label{thm:CostNoWorse}
+Under assumption \eqref{lambdaRatio} $\cost(\tA,\rho,\varepsilon)$ is essentially no worse than $\comp(\ca(\cc),\rho,\varepsilon)$.
+\end{theorem}
+\begin{proof}
+Let  
+\begin{equation} \label{omegadef}
+    \omega = \sqrt{\frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}}
+\end{equation}
+For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$ where 
+\begin{align*} 
+j^\dagger &\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
+&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2} \right\} \qquad \text{since } a > 1\\
+&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2} \right\} \\
+&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
+&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)} \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{lambdaRatio} } \\
+&\le \min \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{omegadef} } \\
+&\le \max \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^*.
+\end{align*}
+By Theorem \ref{thm:lowbdcomp}, $\comp(\ca(\cc),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above $n_{j^*} \ge n_{j^\dagger} \ge \cost(\tA,\varepsilon,\rho)$.
+Thus, our algorithm is essentially no more costly than the optimal algorithm.
 \end{proof}
@@
 
-\yuhannote{The figure is here in comment}
+\yuhannote{The figure is here in comment} \frednote{The figure looked bad when I compiled it on my screen so I re-ran Matlab and then uploaded the new figures.}
 \begin{figure}

### 2018-08-07 AutoAlgorithmLinearFunctionalDataVerC.tex
corrected typo found by Yuhan in the optimality proof.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Adaptive Algorithm} \label{sec:adaptalgo}
@@
 \]
-Moreover, $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\cost(\tA,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
@@
 
-To derive an upper bound on $\cost(\tA,\rho,\varepsilon)$ we start by noting some properties of $\sigma_j(f)$ for all $f \in \cc$:
+To derive an upper bound on $\cost(\tA,\varepsilon,\rho)$ we start by noting some properties of $\sigma_j(f)$ for all $f \in \cc$:
 \begin{multline} \label{normsigineq}
@@
 
-\begin{cor} For the algorithm, $\tA$, defined in Algorithm \ref{algo2}, then $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+\begin{cor} For the algorithm, $\tA$, defined in Algorithm \ref{algo2}, then $\cost(\tA,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdaggerfirst}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Essential Optimality of the Adaptive Algorithm} \label{sec:opt}
@@
 \label{thm:CostNoWorse}
-Under assumption \eqref{lambdaRatio} $\cost(\tA,\rho,\varepsilon)$ is essentially no worse than $\comp(\ca(\cc),\rho,\varepsilon)$.
+Under assumption \eqref{lambdaRatio} $\cost(\tA,\varepsilon,\rho)$ is essentially no worse than $\comp(\ca(\cc),\varepsilon,\rho)$.
 \end{theorem}
@@
 &\le \min \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{omegadef} } \\
-&\le \max \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^*.
+&= \max \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^*.
 \end{align*}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Examples} \label{sec:examp}

### 2018-08-08 AutoAlgorithmLinearFunctionalDataVerC.tex
Polishing and correcting typos

@@
 Adaptive algorithms determine the design and sample size needed to solve problems to the desired accuracy.
-A priori upper bounds on some norm of the input function are not required, but there may be some underlying assumptions about the input function required for the adaptive algorithm to be successful.
-Here we consider general linear problems where the series coefficients of the input function are used to obtain an approximate solution.
-The algorithm proposed guarantees the accuracy of the approximate solution.
-Moreover, our algorithm is shown to have a computational cost that is asymptotically optimal in comparison to the best possible algorithm.
-The set of functions on which our adaptive algorithm is defined is a cone.
-
-Let $\cf$ be a separable Hilbert space of input functions with orthonormal basis $\{u_i\}_{i=1}^\infty$, and let $\cg$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$:
+A priori upper bounds on some norm of the input function are not needed, but some underlying assumptions about the input function are required for the adaptive algorithm to succeed.
+Here we consider general linear problems where a finite number of series coefficients of the input function are used to obtain an approximate solution.
+The proposed algorithm produces an approximation with guaranteed accuracy.
+Moreover, we demonstrate that  computational cost of our algorithm is essentially no worse than that of the best possible algorithm.
+The set of input functions for which our adaptive algorithm is defined is a cone.
+
+Let $\cf$ be a separable Hilbert space of input functions with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\cg$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
 \begin{subequations}\label{probDef}
@@
 \end{gather}
-Let these bases be chosen by the singular value decomposition so that the linear solution operator, $S:\cf \to \cg$, satisfies
+Let the bases of spaces of inputs and outputs be chosen by the singular value decomposition so that the linear solution operator, $S:\cf \to \cg$, satisfies
 \begin{gather}
@@
 
-Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution to some error tolerance for all inputs in $\ch$:
+Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \ch \to \cg$ to within some error tolerance for all inputs in $\ch$:
 \begin{multline} \label{adapErrCrit}
@@
 Algorithms in $\ca(\ch)$ are allowed to sample adaptively any bounded, linear functionals
-of the input function $f$.
+of the input function.
 They must require only a finite number of linear functionals for each input function and positive tolerance.
-The definition of $\ch$ can be used in constructing algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
+The definition of $\ch$ can be used to construct algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
 Following \cite{KunEtal19a} we call a problem \emph{solvable} for inputs $\ch$ if $\ca(\ch)$ is non-empty.
@@
 Our problem is not solvable for $\cf$, as can be demonstrated by contradiction.
-For any potential algorithm, we show that there is some $f \in \cf$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
+For any potential algorithm, we show that there exists some $f \in \cf$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
 Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$.
-Since $n$ is finite, there exists some nonzero $f \in \cf$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
+Since the output space, $\cg$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \cf$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
 This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.
@@
 Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.
-Thus, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.
-However, it is solvable for well-chosen subsets of $\cf$.
+The presumed $A$ does not exist, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.
+However, it is solvable for well-chosen subsets of $\cf$, as will be shown in the sections below.
 
 The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
-By overloading the notation, we define for arbitrary algorithms $A \in \ca(\ch)$,
+By overloading the notation, we define the cost of algorithms as
 \begin{equation*}
@@
 For unbounded sets, $\ch$, this cost may be infinite.
-Therefore, it is also helpful to define the cost for input functions in $\ch \cap \cb_{\rho}$, where $\cb_{\rho} : = \{ f \in \cf : \norm[\cf]{f} \le \rho \}$ is the ball of radius $\rho$:
+Therefore, it is also helpful to define the cost of algorithms for input functions in $\ch \cap \cb_{\rho}$, where $\cb_{\rho} : = \{ f \in \cf : \norm[\cf]{f} \le \rho \}$ is the ball of radius $\rho$:
 \begin{equation*}
@@
 
-To prove this, let $A^*$ be an arbitrary algorithm in $\ca(\cb_{\rho})$, and let $L_1, \ldots, L_n$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.
-Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_n(0)) = (0, \ldots, 0)$.
-Let $f$ be a linear combination of $u_1, \ldots, u_{n+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_n(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
+To prove this, let $A^*$ be an arbitrary algorithm in $\ca(\cb_{\rho})$, and let $L_1, \ldots, L_N$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.
+Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.
+Let $f$ be a linear combination of $u_1, \ldots, u_{n+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
 \begin{align*}
@@
 & \ge \norm[\cg]{S(f)} 
-= \bignorm[2]{\big(\lambda_i\hf_i\big)_{i=1}^{n+1}} \\
-& \ge \lambda_{n+1} \bignorm[2]{\big(\hf_i\big)_{i=1}^{n+1}} = \lambda_{n+1} \norm[\cf]{f} = \lambda_{n+1} \rho.
-\end{align*}
-Thus, $\lambda_{n+1} \le \varepsilon/\rho$, and $n \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}$.  Hence, algorithm $\hA$ defined in \eqref{optBallalg} is optimal for $\ca(\cb_{\rho})$.
-
-We defined an algorithm $A \in \ca(\ch)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \ca(\ch^*)$ if for some number $\omega$,
+= \bignorm[2]{\big(\lambda_i\hf_i\big)_{i=1}^{N+1}} \\
+& \ge \lambda_{N+1} \bignorm[2]{\big(\hf_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \norm[\cf]{f} = \lambda_{N+1} \rho.
+\end{align*}
+Thus, $\lambda_{N+1} \le \varepsilon/\rho$, and $N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \cost(\tA,\cb_\rho,\varepsilon)$.
+Hence, algorithm $\hA$ defined in \eqref{optBallalg} is optimal for $\ca(\cb_{\rho})$.
+
+Our goal is not only to construct algorithms in $\ca(\ch)$ for some $\ch$, but also to determine whether the computational cost of our algorithms are reasonable.
+We define an algorithm $A \in \ca(\ch)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \ca(\ch^*)$ if for some number $\omega$,
 \begin{gather}
@@
 The computational cost of $\tA$ is given in  Theorem \ref{thm:compcost}.
-Section \ref{sec:opt} shows that our new algorithm is asymptotically optimal, i.e., ???.
+Section \ref{sec:opt} shows that our new algorithm is essentially optimal (see Theorem \ref{thm:CostNoWorse}).
 Section \ref{sec:examp} provides an example of our algorithm.
@@
 \begin{align*}
-f &= \sum_{k \in \integers} \hf(k) \hu_{k} (\vx) = \sum_{i=1}^n \hf_i u_i(x), 
+f &= \sum_{k \in \integers} \hf(k) \hu_{k}  = \sum_{i=1}^n \hf_i u_i, 
 & S(f) & = \sum_{k \in \integers} \hf(k) \hlambda_k \hv_k = \sum_{i=1}^n \hf_i \lambda_i \hv_i, \\
@@
 & \lambda_i &= \hlambda_{\lfloor i/2\rfloor} = \frac{1}{\max(1,\lfloor i/2\rfloor)^r}, \\
-\hu_{k} (x) &:= \hlambda_k\hv_k(x),
-& u_i(x) &= \begin{cases} \hu_{-i/2}, & i \text{ even},\\
+\hu_{k} &:=  \hlambda_k \hv_k,
+& u_i & \lambda_i v_i = \begin{cases} \hu_{-i/2}, & i \text{ even},\\
 \hu_{(i-1)/2}, & i \text{ odd},
@@
 Here $\cg=\cl_2[0,1]$.
-The larger the non-negative parameter $r$ is, the smaller $\cb_\rho$ is, and the smaller  $\cost(\hA,\cb_{\rho},\varepsilon)$ is.
+The larger the non-negative parameter $r$ is, the faster the $\lambda_i$ tend to 0 as $ i \to 0$, the smaller $\cb_\rho$ is, and the smaller  $\cost(\hA,\cb_{\rho},\varepsilon)$ is.
 For $r = 0$, $\cost(\hA,\cb_{\rho},\varepsilon) = \infty$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Assuming a Steady Decay of the Series Coefficients of the Solution} \label{sec:cone}
@@
 
-Using the expression for the error in \eqref{errOpt} and the definition of the cone in  \eqref{decayconedef}, one can now derive a data-driven error bound for $j \in \naturals$:
+From the expression for the error in \eqref{errOpt} and the definition of the cone in  \eqref{decayconedef}, one can now derive a data-driven error bound for $j \in \naturals$:
 \begin{align}
@@
 \nonumber
-&= \norm[2]{ \left(\sigma_{j+r}(f)\right)_{r=1}^{\infty}} \\
-&\le \norm[2]{ \left(ab^r\sigma_{j}(f)\right)_{r=1}^{\infty}}
+&= \norm[2]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
+&\le \norm[2]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
  = \displaystyle ab \sqrt{\frac{1}{1 - b^2}}\sigma_{j}(f)
@@
 The algorithm, $\tA$, defined in Algorithm \ref{algo2} lies in $\ca(\cc)$ and has computational cost $\cost(\tA,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly by the inequalities 
-\[
-\sigma_{j^*}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  < \sigma_{j}(f), \quad 1 \le j < j^*.
-\]
+\begin{equation} \label{eq:OurAlgjstar}
+j^* = \min\left \{ j \in \naturals : \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  \right\}.
+\end{equation}
 Moreover, $\cost(\tA,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
@@
 
-To derive an upper bound on $\cost(\tA,\varepsilon,\rho)$ we start by noting some properties of $\sigma_j(f)$ for all $f \in \cc$:
+For the remainder of the proof consider $\rho$ and $\varepsilon$ fixed.
+To derive an upper bound on $n_{j^\dagger} = \cost(\tA,\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \cc$:
 \begin{multline} \label{normsigineq}
@@
 \end{multline}
-A rough upper bound on $\cost(\tA,\rho,\varepsilon)$ may be obtained by noting that  for any $f \in \cc$ that also lies in the ball of radius $\rho$, and for any $j < j^\dagger$, it follows by \eqref{normsigineq} and  Theorem \ref{thm:compcost} that
+
+A rough upper bound on $j^\dagger$ may be obtained by noting that for any $f \in \cc \cap \cb_\rho$ and for any $j < j^* \le j^\dagger$, it follows from \eqref{eq:OurAlgjstar} and \eqref{normsigineq} that
 \begin{equation*}
@@
 
-The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by an argument in a similar vein to the one above.  
-For any $f \in \cc$ that also lies in the ball of radius $\rho$,
+The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by a more careful argument in a similar vein.  
+For any $f \in  \cc \cap \cb_\rho$ and for any $j < j^* \le j^\dagger$,
 \begin{align*}
@@
 \end{align*}
-Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum becomes more inclusive and $b^{2(k-j)}$ also increases.
-
-For all $j < j^\dagger$ it follows from the definition of the algorithm and Theorem \ref{thm:compcost} above that 
+Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum becomes includes more terms and $b^{2(k-j)}$ also increases.
+
+For all $j < j^* \le j^\dagger$ it follows from \eqref{eq:OurAlgjstar} that
 \begin{equation*}
@@
 \end{equation*}
-Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$.
+Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$, establishing \eqref{jdagger}.
 \end{proof}
@@
 This is statement \eqref{jdaggerlastsimple}, and its precursor, \eqref{jdaggerlast}.
-Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\cc$ in \eqref{cdef}, means that $\tA(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\norm[\cf]{f}/\varepsilon$.
+Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\cc$ in \eqref{decayconedef}, means that $\tA(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\norm[\cf]{f}/\varepsilon$.
 
@@
 $\cost(\hA,\cb_{\rho},\varepsilon) = \comp(\ca(\cb_{\rho}),\varepsilon)$.
-We would like to show that $\tA \in \ca(\cc)$ is  essentially optimal, i.e., $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially the same as  $\comp(\ca(\cc),\varepsilon,\rho)$.
+We would like to show that $\tA \in \ca(\cc)$ is  essentially optimal, i.e., $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially no worse than  $\comp(\ca(\cc),\varepsilon,\rho)$.
 However,  $\comp(\ca(\cc),\varepsilon,\rho)$ may be smaller than $\comp(\ca(\cb_{\rho}),\varepsilon)$ because $\cc \cap \cb_\rho$ is a strict subset of  $ \cb_\rho$.
@@
 
-A lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$ is established by   proof is accomplished by constructing fooling functions in $\cc$ with norms no greater than $\rho$.
+A lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$ is established by constructing fooling functions in $\cc$ with norms no greater than $\rho$.
 To obtain a result that can be compared with the cost of our algorithm, we assume that
@@
 The following theorem establishes a lower bound on the complexity of our problem for input functions in $\cc$.
-After that we show that the cost of our algorithm as given in Theorem \ref{thm:compcost} is essentially no worse than this lower bound.
+The theorem after that shows that the cost of our algorithm as given in Theorem \ref{thm:compcost} is essentially no worse than this lower bound.
 
@@
 \begin{equation} \label{omegadef}
-    \omega = \sqrt{\frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}}
-\end{equation}
+    \omega = \sqrt{\frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}},
+\end{equation}
+and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\cc$. 
 For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$ where 
@@
 \end{align*}
-By Theorem \ref{thm:lowbdcomp}, $\comp(\ca(\cc),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above $n_{j^*} \ge n_{j^\dagger} \ge \cost(\tA,\varepsilon,\rho)$.
+By Theorem \ref{thm:lowbdcomp}, $\comp(\ca(\cc),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above, $n_{j^*} \ge n_{j^\dagger} \ge \cost(\tA,\varepsilon,\rho)$.
 Thus, our algorithm is essentially no more costly than the optimal algorithm.

### 2018-08-11 AutoAlgorithmLinearFunctionalDataVerC.tex
add contents of examples

@@
 
-\yuhannote{The figure is here in comment} \frednote{The figure looked bad when I compiled it on my screen so I re-ran Matlab and then uploaded the new figures.}
-\begin{figure}
+\begin{figure}[ht]
 	\centering
-	\includegraphics[width = 8 cm]{ProgramsImages/SimDirectSolErr.eps}
+	\begin{tabular}{cc}
+		\includegraphics[width =5.5 cm]{ProgramsImages/SimDirectSolAppx.eps} &
+		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectSolErr.eps}
+		\\ (a) & (b)
+	\end{tabular}
+	\caption{(a) The approximation of the first partial derivative of $f$
+		(b) The error of the approximation 
+		\label{solfig}} % 
 \end{figure}
+
+To do the simulation, we choose the Fourier coefficients $\hf$ to be normal distributed.
+Let $d=3, a= 2, b=\frac{1}{2},$ and $\varepsilon = 0.1.$ Based on our algorithm, we obtain $ n_{j^\dagger} = 1024.$ Using that, we can obtain the approximated solution and error in Figure \ref{solfig}.
+Based on Figure \ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.
+This shows our algorithm works.
+
+\begin{figure}[ht]
+	\centering
+	\begin{tabular}{cc}
+		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectInpFunAppx.eps}& 
+		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectInpFunErr.eps}
+		\\ (a) & (b)
+	\end{tabular}
+	\caption{(a) The approximation of the input function $f$
+		(b) The error of the approximation 
+		\label{inpfig}} % 
+\end{figure}
+
+Actually, we can also use these 1024 Fourier coefficients to approximate the input function.
+The above is the approximation of the input function $f$.
+Notice that, the errors in Figure \ref{inpfig}(b) are much smaller than the errors in Figure \ref{solfig}(b).
 

### 2018-08-14 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX
Revising

@@
 \setlength{\marginparwidth}{0.5in}
-\usepackage{amsmath,amssymb,amsthm,natbib,bbm,mathtools,booktabs,graphicx,color}
+\usepackage{amsmath,amssymb,amsthm,natbib,bbm,mathtools,array,longtable,booktabs,graphicx,color}
 \input FJHDef.tex
@@
 \section{Introduction}
-Adaptive algorithms determine the design and sample size needed to solve problems to the desired accuracy.
+Adaptive algorithms determine the design and sample size needed to solve problems to the desired accuracy based on the input function data sampled.
 A priori upper bounds on some norm of the input function are not needed, but some underlying assumptions about the input function are required for the adaptive algorithm to succeed.
-Here we consider general linear problems where a finite number of series coefficients of the input function are used to obtain an approximate solution.
+Here we consider \emph{general linear problems} where a finite number of series coefficients of the input function are used to obtain an approximate solution.
 The proposed algorithm produces an approximation with guaranteed accuracy.
 Moreover, we demonstrate that  computational cost of our algorithm is essentially no worse than that of the best possible algorithm.
-The set of input functions for which our adaptive algorithm is defined is a cone.
-
-Let $\cf$ be a separable Hilbert space of input functions with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\cg$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
+Our adaptive algorithm is defined on a \emph{cone} of input functions.
+
+\subsection{Input and Output Spaces}  Let $\cf$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\cg$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
 \begin{subequations}\label{probDef}
@@
 \end{gather}
-Let the bases of spaces of inputs and outputs be chosen by the singular value decomposition so that the linear solution operator, $S:\cf \to \cg$, satisfies
+Let these two bases be chosen by the singular value decomposition so that the linear solution operator, $S:\cf \to \cg$, satisfies
 \begin{gather}
@@
 \end{subequations}
-This setting includes, for example, the recovery of functions, derivatives, and indefinite integrals.
-We are interested in cases where the exact solution generally requires an infinite number of series coefficients, $\hf_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
-
-Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \ch \to \cg$ to within some error tolerance for all inputs in $\ch$:
+This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.
+We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\hf_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
+
+\subsection{Solvability}  Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \ch \to \cg$ to within some error tolerance for all inputs in $\ch$:
 \begin{multline} \label{adapErrCrit}
@@
 of the input function.
-They must require only a finite number of linear functionals for each input function and positive tolerance.
+They must sample only a finite number of linear functionals for each input function and positive tolerance.
 The definition of $\ch$ can be used to construct algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
@@
 Since the output space, $\cg$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \cf$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
-This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.
-Since $A$ successfully produces an approximation with error no greater than $\varepsilon$ for both $0$ and $cf$,
+This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$, and both of these have approximation error no greater than $\varepsilon$, i.e.,
 \begin{align*}
@@
 
-The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
+\subsection{Computational Cost and Complexity of the Problem} The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
 By overloading the notation, we define the cost of algorithms as
@@
 
-An optimal algorithm for $\cb_{\rho}$ can be constructed in terms of the interpolation based on the first $n$ series coefficients of the input, namely,
+An optimal algorithm for $\cb_{\rho}$ can be constructed in terms of interpolation based on the first $n$ series coefficients of the input, namely,
 \begin{gather}  \label{optAdef}
@@
 \end{align*}
-Thus, $\lambda_{N+1} \le \varepsilon/\rho$, and $N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \cost(\tA,\cb_\rho,\varepsilon)$.
+Thus, $\lambda_{N+1} \le \varepsilon/\rho$, and 
+\[
+\cost(A^*,\cb_\rho,\varepsilon) \ge \cost(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \cost(\tA,\cb_\rho,\varepsilon).
+\]
 Hence, algorithm $\hA$ defined in \eqref{optBallalg} is optimal for $\ca(\cb_{\rho})$.
-
-Our goal is not only to construct algorithms in $\ca(\ch)$ for some $\ch$, but also to determine whether the computational cost of our algorithms are reasonable.
-We define an algorithm $A \in \ca(\ch)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \ca(\ch^*)$ if for some number $\omega$,
-\begin{gather}
-\cost(A,\ch,\varepsilon) \le \cost(A^*,\ch^*,\omega\varepsilon), \qquad \forall \varepsilon > 0, \\
-\cost(A,\ch,\varepsilon,\rho) \le \cost(A^*,\ch^*,\omega\varepsilon,\rho), \qquad \forall \varepsilon,\rho > 0.
-\end{gather}
-If the costs of two algorithms are essentially no worse than each other, then we call them essentially the same.
-An algorithm whose cost is essentially no worse than the best possible algorithm, is called \emph{essentially optimal}.
-
-To illustrate these concepts, consider a nondecreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \naturals$.
-Also consider an unbounded strictly increasing sequence of nonnegative integers $\vn = \{n_0, n_1, \ldots \}$.
-Define an algorithm $A^*$ analogously to $\hA$ defined in \eqref{optBallalg}:
-\begin{equation} \label{altBallalg}
-A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \ca(\cb_{\rho}).
-\end{equation}
-Algorithm $A^*$ may or may not have essentially no worse cost than $\hA$ depending on the choice of $\vlambda^*$ and $\vn$.
-The table below shows some examples.
-Each different case of $A^*$ is labeled as having a cost that is either essentially no worse or essentially worse than that of $\hA$.
-\[
-\everymath{\displaystyle}
-\begin{array}{rllll}
-\toprule
-&\lambda_i = \frac{C}{i^p}
-& 
-\cost(\hA,\cb_\rho,\varepsilon) \ge \left ( \frac{C\rho}{\varepsilon} \right)^{1/p} - 1
-\\[2ex]
-& &
-\cost(\hA,\cb_\rho,\varepsilon) 
-<  \left ( \frac{C\rho}{\varepsilon} \right)^{1/p}
-\\[2ex]
-\midrule
-\text{no worse}
-&
-\lambda^*_i = \frac{C^*}{i^p}, \ n_j = 2^j
-&
-\cost(A^*,\cb_\rho,\varepsilon) \le 
-2 \left ( \frac{C^*\rho}{\varepsilon} \right)^{1/p}
-\\[2ex]
-\midrule
-\text{worse}
-&
-\lambda^*_i = \frac{C^*}{i^q}, \ q<p, \ n_j = j
-&
-\cost(A^*,\cb_\rho,\varepsilon)  \ge 
-\left ( \frac{C^*\rho}{\varepsilon} \right)^{1/q} - 1 
-\\[2ex]
-\toprule
-&\lambda_i = \frac{C}{p^i}, \ p > 1
-& 
-\cost(\hA,\cb_\rho,\varepsilon) \ge \frac{\log (C\rho/\varepsilon)}{\log(p)} - 1
-\\[2ex]
-&&
-\cost(\hA,\cb_\rho,\varepsilon) < \frac{\log (C\rho/\varepsilon)}{\log(p)}
-\\[2ex]
-\midrule
-\text{no worse}
-&
-\lambda^*_i = \frac{C^*}{p^i}, \ n_j = 2j
-&
-\cost(A^*,\cb_\rho,\varepsilon) < \frac{\log (C^*\rho/\varepsilon)}{\log(p)} + 1
-\\[2ex]
-\midrule
-\text{worse}
-&
-\lambda^*_i = \frac{C^*}{p^i}, \ n_j = 2^j
-&
-\cost(A^*,\cb_\rho,\varepsilon) > 1.999 \frac{\log (C^*\rho/\varepsilon)}{\log(p)} 
-\\[1ex]
-&& \qquad \qquad \text{for some } \varepsilon
-\\
-\midrule
-\text{worse}
-&
-\lambda^*_i = \frac{C^*}{i^q}, \ q<p, \ n_j = j
-&
-\cost(A^*,\cb_\rho,\varepsilon)  \ge 
-\frac{\log (C^*\rho/\varepsilon)}{\log(q)} - 1
-\\[2ex]
-\toprule
-\end{array}
-\]
-
-For bounded sets of input functions, such as balls, non-adaptive algorithms, such as $\hA$, make sense.
-However, it is typically unknown which ball the input function lies in.
-Thus, we consider unbounded sets of input functions, whose properties can be inferred from the data we collect.
-We will use the interpolatory algorithm $\optAn$, defined in \eqref{optAdef}, but we will propose an alternative way to bound the error other than assuming an a priori bound on $\norm[\cf]{f}$.
-
-Adaptive algorithms encountered in practice typically employ heuristic error bounds.
-While any algorithm can be fooled, we would like precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.
-That is what our adaptive algorithm accomplishes.
-
-Our rigorous, data-driven error bound assumes the input to have steadily---but not necessarily monotonically---decaying series coefficients.
-The cone of nice inputs, $\cc$, is defined in Section \ref{sec:cone}.
-For such inputs, we construct an adaptive algorithm, $\tA \in \ca(\cc)$, in Section \ref{sec:adaptalgo},  where $\tA(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$.
-The number of series coefficients sampled, $n^*$, is adaptively determined so that $\tA(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.
-The computational cost of $\tA$ is given in  Theorem \ref{thm:compcost}.
-Section \ref{sec:opt} shows that our new algorithm is essentially optimal (see Theorem \ref{thm:CostNoWorse}).
-Section \ref{sec:examp} provides an example of our algorithm.
-Concluding remarks are give in Section \ref{sec:conc}.
-We close this section with an example of the function spaces and solution operator that we consider.
 
@@
 
+Our goal is not only to construct algorithms in $\ca(\ch)$ for some $\ch$, but also to determine whether the computational cost of our algorithms are reasonable.
+We define an algorithm $A \in \ca(\ch)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \ca(\ch^*)$ if for some number $\omega$,
+\begin{gather}
+\cost(A,\ch,\varepsilon) \le \cost(A^*,\ch^*,\omega\varepsilon), \qquad \forall \varepsilon > 0, \\
+\cost(A,\ch,\varepsilon,\rho) \le \cost(A^*,\ch^*,\omega\varepsilon,\rho), \qquad \forall \varepsilon,\rho > 0.
+\end{gather}
+If the costs of two algorithms are essentially no worse than each other, then we call them essentially the same.
+An algorithm whose cost is essentially no worse than the best possible algorithm, is called \emph{essentially optimal}.
+
+To illustrate these concepts, consider a nondecreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \naturals$.
+Also consider an unbounded strictly increasing sequence of nonnegative integers $\vn = \{n_0, n_1, \ldots \}$.
+Define an algorithm $A^*$ analogously to $\hA$ defined in \eqref{optBallalg}:
+\begin{equation} \label{altBallalg}
+A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \ca(\cb_{\rho}).
+\end{equation}
+By definition, the cost of algorithm $A^*$ is no better than that of  $\hA$.
+Algorithm $A^*$ may or may not have essentially no worse cost than $\hA$ depending on the choice of $\vlambda^*$ and $\vn$.
+The table below shows some examples.
+Each different case of $A^*$ is labeled as having a cost that is either essentially no worse or essentially worse than that of $\hA$.
+%\[
+\everymath{\displaystyle}
+\begin{longtable}{>{$}r<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}}
+\toprule
+&\lambda_i = \frac{C}{i^p}
+& 
+\cost(\hA,\cb_\rho,\varepsilon) \ge \left ( \frac{C\rho}{\varepsilon} \right)^{1/p} - 1
+\\[2ex]
+& &
+\cost(\hA,\cb_\rho,\varepsilon) 
+<  \left ( \frac{C\rho}{\varepsilon} \right)^{1/p}
+\\[2ex]
+\midrule
+\text{no worse}
+&
+\lambda^*_i = \frac{C^*}{i^p}, \ n_j = 2^j
+&
+\cost(A^*,\cb_\rho,\varepsilon) \le 
+2 \left ( \frac{C^*\rho}{\varepsilon} \right)^{1/p}
+\\[2ex]
+\midrule
+\text{worse}
+&
+\lambda^*_i = \frac{C^*}{i^q}, \ q<p, \ n_j = j
+&
+\cost(A^*,\cb_\rho,\varepsilon)  \ge 
+\left ( \frac{C^*\rho}{\varepsilon} \right)^{1/q} - 1 
+\\[2ex]
+\toprule
+&\lambda_i = \frac{C}{p^i}, \ p > 1
+& 
+\cost(\hA,\cb_\rho,\varepsilon) \ge \frac{\log (C\rho/\varepsilon)}{\log(p)} - 1
+\\[2ex]
+&&
+\cost(\hA,\cb_\rho,\varepsilon) < \frac{\log (C\rho/\varepsilon)}{\log(p)}
+\\[2ex]
+\midrule
+\text{no worse}
+&
+\lambda^*_i = \frac{C^*}{p^i}, \ n_j = 2j
+&
+\cost(A^*,\cb_\rho,\varepsilon) < \frac{\log (C^*\rho/\varepsilon)}{\log(p)} + 1
+\\[2ex]
+\midrule
+\text{worse}
+&
+\lambda^*_i = \frac{C^*}{p^i}, \ n_j = 2^j
+&
+\cost(A^*,\cb_\rho,\varepsilon) > 1.999 \frac{\log (C^*\rho/\varepsilon)}{\log(p)} 
+\\[1ex]
+&& \qquad \qquad \text{for some } \varepsilon
+\\
+\midrule
+\text{worse}
+&
+\lambda^*_i = \frac{C^*}{i^q}, \ q<p, \ n_j = j
+&
+\cost(A^*,\cb_\rho,\varepsilon)  \ge 
+\frac{\log (C^*\rho/\varepsilon)}{\log(q)} - 1
+\\[2ex]
+\toprule
+\end{longtable}
+%\]
+
+\subsection{The Case for Adaptive Algorithms}
+For bounded sets of input functions, such as balls, non-adaptive algorithms, such as $\hA$, make sense.
+However, it is typically unknown which ball the input function lies in.
+Thus, we consider unbounded sets of input functions, whose properties can be inferred from the data we collect.
+We use the interpolatory algorithm $\optAn$, defined in \eqref{optAdef}, but we propose an alternative way to bound the error other than assuming an a priori bound on $\norm[\cf]{f}$.
+
+Adaptive algorithms encountered in practice typically employ heuristic error bounds.
+While any algorithm can be fooled, we would like precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.
+Our adaptive algorithm has such conditions.
+
+Our rigorous, data-driven error bound assumes the input to have steadily---but not necessarily monotonically---decaying series coefficients.
+The cone of nice inputs, $\cc$, is defined in Section \ref{sec:cone}.
+For such inputs, we construct an adaptive algorithm, $\tA \in \ca(\cc)$, in Section \ref{sec:adaptalgo},  where $\tA(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$ depending on the input data and the definition of $\cc$.
+The number of series coefficients sampled, $n^*$, is adaptively determined so that $\tA(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.
+The computational cost of $\tA$ is given in  Theorem \ref{thm:compcost}.
+Section \ref{sec:opt} shows that our new algorithm is essentially optimal (see Theorem \ref{thm:CostNoWorse}).
+Section \ref{sec:examp} provides an example of our algorithm.
+Concluding remarks are give in Section \ref{sec:conc}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-However, we can observe, say the partial sums 
+However, we can observe the partial sums 
 \begin{equation} \label{sumdef}
 \sigma_j(f) :
-= \norm[2]{ \left(\lambda_{i} \hf_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j=1, 2, \ldots,
+= \norm[2]{ \left(\lambda_{i} \hf_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j \in \naturals,
 \end{equation}

### 2018-08-14 AutoAlgorithmLinearFunctionalDataVerC.tex
Revising

@@
 \newcommand{\optAn}{A_n}
+\providecommand{\HickernellFJ}{Hickernell}
 
@@
 
-\subsection{Computational Cost and Complexity of the Problem} The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
+\subsection{Computational Cost of the Algorithm and Complexity of the Problem} The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
 By overloading the notation, we define the cost of algorithms as
@@
 	\hu_{k} &:=  \hlambda_k \hv_k,
-	& u_i & \lambda_i v_i = \begin{cases} \hu_{-i/2}, & i \text{ even},\\
+	& u_i & = \lambda_i v_i = \begin{cases} \hu_{-i/2}, & i \text{ even},\\
 	\hu_{(i-1)/2}, & i \text{ odd},
@@
 \begin{longtable}{>{$}r<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}}
-\toprule
+\toprule \toprule
 &\lambda_i = \frac{C}{i^p}
@@
 \\[2ex]
-\toprule
+\toprule \toprule
 &\lambda_i = \frac{C}{p^i}, \ p > 1
@@
 \\[2ex]
-\toprule
+\toprule \toprule
 \end{longtable}
@@
 While any algorithm can be fooled, we would like precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.
-Our adaptive algorithm has such conditions.
+Our adaptive algorithm has such conditions and follows in the vein of adaptive algorithms developed in \cite{HicEtal14a, HIcEtal14b, HicJim16a, JimHic16a}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples} \label{sec:examp}
-
-Consider the case of approximating the first partial derivatives of periodic functions defined on the $d$-dimensional unit cube:
+\section{Numerical Example} \label{sec:examp}
+
+Consider the case of approximating the  partial derivative with respect to $x_1$ of periodic functions defined on the $d$-dimensional unit cube:
 \begin{align*}
@@
 & \qquad \qquad \times \prod_{j=2}^d 2^{(1-\delta_{k_j,0})/2} \cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ), \\
-\lambda_{\vk} &:= \frac{2 \pi \abs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}
-\end{align*}
+\lambda_{\vk} &:= \frac{2 \pi \abs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}.
+\end{align*}
+We construct a function by choosing its Fourier coefficients $\hf$ to be normal distributed \textbf{What distribution (mean, standard deviation)?
+How many Fourier coefficients are chosen to construct the function?}.
+Let $d=3, a= 2, b=\frac{1}{2},$ and $\varepsilon = 0.1.$ Based on our algorithm, we obtain $ n_{j^\dagger} = 1024.$ Using that, we can obtain the approximated solution and error in Figure \ref{solfig}.
+Based on Figure \ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.
+This shows our algorithm works.
 
@@
 \end{figure}
-
-To do the simulation, we choose the Fourier coefficients $\hf$ to be normal distributed.
-Let $d=3, a= 2, b=\frac{1}{2},$ and $\varepsilon = 0.1.$ Based on our algorithm, we obtain $ n_{j^\dagger} = 1024.$ Using that, we can obtain the approximated solution and error in Figure \ref{solfig}.
-Based on Figure \ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.
-This shows our algorithm works.
 
@@
 
-\section*{References}
+%\section*{References}
 %\nocite{*}

### 2018-08-14 AutoAlgorithmLinearFunctionalDataVerC.tex
Switched to MCQMC style

@@
-\documentclass[final]{elsarticle}
-\setlength{\marginparwidth}{0.5in}
-\usepackage{amsmath,amssymb,amsthm,natbib,bbm,mathtools,array,longtable,booktabs,graphicx,color}
-\input FJHDef.tex
-
-\newcommand{\chin}{\ch_{\text{\rm{in}}}}
-\newcommand{\chout}{\ch_{\text{\rm{out}}}}
-\newcommand{\pin}{p_{\text{\rm{in}}}}
-\newcommand{\pout}{p_{\text{\rm{out}}}}
-%\newcommand{\cc}{\mathcal{C}}
-\newcommand{\cq}{\mathcal{Q}}
-\newcommand{\co}{\mathcal{O}}
-\newcommand{\bbW}{\mathbb{W}}
-%\newcommand{\tP}{\widetilde{P}}
-\newcommand{\bg}{{\bf g}}
-\newcommand{\bu}{{\bf u}}
-\newcommand{\bbu}{\bar{\bf u}}
-\newcommand{\bv}{{\bf v}}
-\newcommand{\bbv}{\bar{\bf v}}
-\newcommand{\bw}{{\bf w}}
-\newcommand{\bbw}{\bar{\bf w}}
-%\newcommand{\tcf}{\widetilde{\cf}}
-%\newcommand{\hv}{\hat{v}}
-\newcommand{\tca}{\widetilde{\ca}}
-\newcommand{\bgamma}{\boldsymbol\gamma}
-\DeclareMathOperator{\MSE}{MSE}
-\DeclareMathOperator{\RMSE}{RMSE}
-\DeclareMathOperator{\rnd}{rnd}
-\DeclareMathOperator{\abso}{abs}
-\DeclareMathOperator{\rel}{rel}
-\DeclareMathOperator{\nor}{nor}
-\DeclareMathOperator{\err}{err}
-\DeclareMathOperator{\lin}{lin}
-%\DeclareMathOperator{\std}{std}
-\DeclareMathOperator{\prob}{prob}
-\DeclareMathOperator{\trunc}{trc}
-\DeclareMathOperator{\third}{third}
-\DeclareMathOperator{\non}{non}
-%\DeclareMathOperator{\fourth}{fourth}
-\newtheorem{theorem}{Theorem}
-\newtheorem{cor}[theorem]{Corollary}
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\theoremstyle{definition}
-\newtheorem{algo}{Algorithm}
-\newtheorem{condit}{Condition}
-%\newtheorem{assump}{Assumption}
-\theoremstyle{remark}
-\newtheorem{rem}{Remark}
-\newtheorem{exmp}{Example}
-
-\DeclareMathOperator{\fix}{fix}
-\DeclareMathOperator{\up}{up}
-\DeclareMathOperator{\lo}{lo}
-
-\newcommand{\arbAn}{A^*_n}
-\newcommand{\optAn}{A_n}
+%
+% sample root file for your "contribution" to a contributed volume
+%
+% Use this file as a template for your own input.
+%
+%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[graybox,footinfo]{svmult}
+
+\smartqed
+\usepackage{mathptmx}       % selects Times Roman as basic font
+\usepackage{helvet}         % selects Helvetica as sans-serif font
+\usepackage{courier}        % selects Courier as typewriter font
+\usepackage{type1cm}        % activate if the above 3 fonts are
+% not available on your system
+\usepackage{graphicx}       % standard LaTeX graphics tool
+% when including figure files
+
+\usepackage{array,colortbl}
+\usepackage{amsmath,amsfonts,amssymb,bm} % no amsthm, Springer defines Theorem, Lemma, etc themselves
+%\usepackage[mathx]{mathabx}
+\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
+\DeclareFontShape{U}{mathx}{m}{n}{
+	<5> <6> <7> <8> <9> <10>
+	<10.95> <12> <14.4> <17.28> <20.74> <24.88>
+	mathx10
+}{}
+\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
+\DeclareFontSubstitution{U}{mathx}{m}{n}
+\DeclareMathAccent{\widecheck}      {0}{mathx}{"71}
+
+% Note that Springer defines the following already:
+%
+% \D upright d for differential d
+% \I upright i for imaginary unit
+% \E upright e for exponential function
+% \tens depicts tensors as sans serif upright
+% \vec depicts vectors as boldface characters instead of the arrow accent
+%
+% Additionally we throw in the following common used macro's:
+\input{macros}
+
+% Macros below are now inclded in macros.tex from MCQMC 2016 web site
+% This spot formerly included macros that are now in macros.tex
+
+% indicator boldface 1:
+\DeclareSymbolFont{bbold}{U}{bbold}{m}{n}
+\DeclareSymbolFontAlphabet{\mathbbold}{bbold}
+%\newcommand{\ind}{\mathbbold{1}}
+
+\usepackage{microtype} % good font tricks
+
+\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
+\urlstyle{same}
+\usepackage{bookmark}
+\pdfstringdefDisableCommands{\def\and{, }}
+\makeatletter % to avoid hyperref warnings:
+\providecommand*{\toclevel@author}{999}
+\providecommand*{\toclevel@title}{0}
+\makeatother
+
+\usepackage{bbm,mathtools,array,longtable,booktabs,graphicx,color}
+%\input FJHDef.tex
+
+\newcommand{\DHJRnorm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
+\newcommand{\DHJRbignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
+\newcommand{\DHJRabs}[1]{\ensuremath{{\left \lvert #1 \right \rvert}}}
+
 \providecommand{\HickernellFJ}{Hickernell}
@@
 
-\journal{Journal of Complexity}
+%\journal{Journal of Complexity}
 
@@
 
-\begin{frontmatter}
-
-\title{Adaptive Algorithms Employing Continuous Linear Functionals}
-\author{Yuhan Ding}
-\address{MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612}
-\author{Fred J. Hickernell}
-\address{Center for Interdisciplinary Scientific Computation and \\
-Department of Applied Mathematics, Illinois Institute of Technology \\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616}
-\author{Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
-\address{Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616}
-\begin{abstract}
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-\end{frontmatter}
+\title*{Adaptive Algorithms Employing Continuous Linear Functionals}
+\author{Yuhan Ding \and Fred J. Hickernell \and Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
+\institute{Yuhan Ding \at MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612 \email{}
+\and
+Fred J. Hickernell \at Center for Interdisciplinary Scientific Computation and \\
+Department of Applied Mathematics, Illinois Institute of Technology \\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{hickernell@iit.edu}
+\and Llu\'{\i}s Antoni Jim\'{e}nez Rugama \at
+Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{}}
+
+\maketitle
+
+\abstract{}
 
@@
 
-\subsection{Input and Output Spaces}  Let $\cf$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\cg$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
+\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
 \begin{subequations}\label{probDef}
 \begin{gather}
-f = \sum_{i=1}^\infty \hf_i u_i \in \cf, \qquad \norm[\cf]{f}=\bignorm[2]{(\hf_i\big)_{i=1}^\infty}, \\
-g = \sum_{i=1}^\infty \hg_i v_i \in \cg, \qquad \norm[\cg]{g}=\bignorm[2]{(\hg_i\big)_{i=1}^\infty}.
+f = \sum_{i\in \bbN} \widehat{f}_i u_i \in \calF, \qquad 
+\DHJRnorm[\calF]{f}=\DHJRbignorm[2]{(\widehat{f}_i\big)_{i\in \bbN}}, \\
+g = \sum_{i\in \bbN} \widehat{g}_i v_i \in \calG, \qquad \DHJRnorm[\calG]{g}=\DHJRbignorm[2]{(\widehat{g}_i\big)_{i\in \bbN}}.
 \end{gather}
-Let these two bases be chosen by the singular value decomposition so that the linear solution operator, $S:\cf \to \cg$, satisfies
+Let these two bases be chosen by the singular value decomposition so that the linear solution operator, $S:\calF \to \calG$, satisfies
 \begin{gather}
-S(u_i) = \lambda_i v_i, \quad i \in \naturals, \qquad S(f) = \sum_{i=1}^n \lambda_i \hf_i v_i, \\
+S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i=1}^n \lambda_i \widehat{f}_i v_i, \\
 \lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
-\norm[\cf \to \cg]{S} := \sup_{f \ne 0} \frac{\norm[\cg]{S(f)}}{\norm[\cf]{f}} = \lambda_1.
+\DHJRnorm[\calF \to \calG]{S} := \sup_{f \ne 0} \frac{\DHJRnorm[\calG]{S(f)}}{\DHJRnorm[\calF]{f}} = \lambda_1.
 \end{gather}
@@
 This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.
-We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\hf_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
-
-\subsection{Solvability}  Let $\ch$ be any subset of $\cf$, and let $\ca(\ch)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \ch \to \cg$ to within some error tolerance for all inputs in $\ch$:
+We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
+
+\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ to within some error tolerance for all inputs in $\calH$:
 \begin{multline} \label{adapErrCrit}
-\ca(\ch) : = \left\{ \text{algorithms } A:\ch \times (0,\infty) \rightarrow \cg : 
+\calA(\calH) : = \left\{ \text{algorithms } A:\calH \times (0,\infty) \rightarrow \calG : 
 \right . \\ \left .
-\bignorm[\cg]{S(f) - A(f,\varepsilon)} \le \varepsilon \ \forall f \in \ch, \ \varepsilon > 0 
+\DHJRbignorm[\calG]{S(f) - A(f,\varepsilon)} \le \varepsilon \ \forall f \in \calH, \ \varepsilon > 0 
 \right \}.
 \end{multline}
-Algorithms in $\ca(\ch)$ are allowed to sample adaptively any bounded, linear functionals
+Algorithms in $\calA(\calH)$ are allowed to sample adaptively any bounded, linear functionals
 of the input function.
 They must sample only a finite number of linear functionals for each input function and positive tolerance.
-The definition of $\ch$ can be used to construct algorithms in $\ca(\ch)$, but no other a priori knowledge about the input functions is available.
-Following \cite{KunEtal19a} we call a problem \emph{solvable} for inputs $\ch$ if $\ca(\ch)$ is non-empty.
-
-Our problem is not solvable for $\cf$, as can be demonstrated by contradiction.
-For any potential algorithm, we show that there exists some $f \in \cf$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
-Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$.
-Since the output space, $\cg$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \cf$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
+The definition of $\calH$ can be used to construct algorithms in $\calA(\calH)$, but no other a priori knowledge about the input functions is available.
+Following \cite{KunEtal19a} we call a problem \emph{solvable} for inputs $\calH$ if $\calA(\calH)$ is non-empty.
+
+Our problem is not solvable for $\calF$, as can be demonstrated by contradiction.
+For any potential algorithm, we show that there exists some $f \in \calF$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
+Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$.
+Since the output space, $\calG$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \calF$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
 This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$, and both of these have approximation error no greater than $\varepsilon$, i.e.,
 \begin{align*}
-    \varepsilon &\ge \frac 12 \left[ \norm[\cg]{S(0) - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(cf,\varepsilon)}\right] \\
-    & =  \frac 12 \left[ \norm[\cg]{0 - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(0,\varepsilon)}\right] \\
-    & \ge  \frac {\abs{c}\norm[\cg]{S(f)}}2  \qquad \text{by the triangle inequality}.
+    \varepsilon &\ge \frac 12 \left[ \DHJRnorm[\calG]{S(0) - A(0,\varepsilon)} + \DHJRnorm[\calG]{S(cf) - A(cf,\varepsilon)}\right] \\
+    & =  \frac 12 \left[ \DHJRnorm[\calG]{0 - A(0,\varepsilon)} + \DHJRnorm[\calG]{S(cf) - A(0,\varepsilon)}\right] \\
+    & \ge  \frac {\DHJRabs{c}\DHJRnorm[\calG]{S(f)}}2  \qquad \text{by the triangle inequality}.
 \end{align*}
 Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.
-The presumed $A$ does not exist, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.
-However, it is solvable for well-chosen subsets of $\cf$, as will be shown in the sections below.
-
-\subsection{Computational Cost of the Algorithm and Complexity of the Problem} The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
+The presumed $A$ does not exist, $\calA(\calF)$ is empty, and our problem is not solvable for $\calF$.
+However, it is solvable for well-chosen subsets of $\calF$, as will be shown in the sections below.
+
+\subsection{Computational Cost of the Algorithm and Complexity of the Problem} The computational cost of an algorithm $A \in \calA(\calH)$ for $f \in \calH$ and error tolerance $\varepsilon$ is denoted $\textup{cost}(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
 By overloading the notation, we define the cost of algorithms as
 \begin{equation*}
-\cost(A,\ch,\varepsilon) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \} \qquad \forall \varepsilon > 0.
-\end{equation*}
-For unbounded sets, $\ch$, this cost may be infinite.
-Therefore, it is also helpful to define the cost of algorithms for input functions in $\ch \cap \cb_{\rho}$, where $\cb_{\rho} : = \{ f \in \cf : \norm[\cf]{f} \le \rho \}$ is the ball of radius $\rho$:
-\begin{equation*}
-\cost(A,\ch,\varepsilon,\rho) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \cap \cb_{\rho} \} \qquad \forall \rho > 0, \ \varepsilon > 0.
+\textup{cost}(A,\calH,\varepsilon) : = \sup \{\textup{cost}(A,f,\varepsilon) : f \in \calH \} \qquad \forall \varepsilon > 0.
+\end{equation*}
+For unbounded sets, $\calH$, this cost may be infinite.
+Therefore, it is also helpful to define the cost of algorithms for input functions in $\calH \cap \calB_{\rho}$, where $\calB_{\rho} : = \{ f \in \calF : \DHJRnorm[\calF]{f} \le \rho \}$ is the ball of radius $\rho$:
+\begin{equation*}
+\textup{cost}(A,\calH,\varepsilon,\rho) : = \sup \{\textup{cost}(A,f,\varepsilon) : f \in \calH \cap \calB_{\rho} \} \qquad \forall \rho > 0, \ \varepsilon > 0.
 \end{equation*}
@@
 \begin{gather*}
-\comp(\ca(\ch),\varepsilon) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon), \\
-\comp(\ca(\ch),\varepsilon,\rho) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon, \rho).
+\textup{comp}(\calA(\calH),\varepsilon) := \min_{A \in \calA(\calH)} \textup{cost}(A, \calH, \varepsilon), \\
+\textup{comp}(\calA(\calH),\varepsilon,\rho) := \min_{A \in \calA(\calH)} \textup{cost}(A, \calH, \varepsilon, \rho).
 \end{gather*}
-Note that $\comp(\ca(\ch),\varepsilon,\rho) \ge \comp(\ca(\ch \cap \cb_{\rho}),\varepsilon)$.  In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
-
-An optimal algorithm for $\cb_{\rho}$ can be constructed in terms of interpolation based on the first $n$ series coefficients of the input, namely,
+Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$.
+In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
+
+An optimal algorithm for $\calB_{\rho}$ can be constructed in terms of interpolation based on the first $n$ series coefficients of the input, namely,
 \begin{gather}  \label{optAdef}
-\optAn(f) := \sum_{i=1}^n \lambda_{i} \hf_{i} v_{i}, \\
+A_n(f) := \sum_{i=1}^n \lambda_{i} \widehat{f}_{i} v_{i}, \\
 \label{errOpt}
-\norm[\cg]{S(f) - \optAn(f)} = \Bignorm[2]{\left(\lambda_{i} \hf_{i} \right)_{i= n+1}^{\infty}} \le \lambda_{n+1} \norm[\cf]{f}.
+\DHJRnorm[\calG]{S(f) - A_n(f)} = \DHJRbignorm[2]{\left(\lambda_{i} \widehat{f}_{i} \right)_{i= n+1}^{\infty}} \le \lambda_{n+1} \DHJRnorm[\calF]{f}.
 \end{gather}
@@
 \begin{equation} \label{optBallalg}
-\hA(f,\varepsilon) = A_{n^*}(f), \quad \text{where } n^* = \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}, \qquad \hA \in \ca(\cb_{\rho}).
-\end{equation}
-This algorithm is optimal among algorithms in $\ca(\cb_{\rho})$, i.e.,
+\widehat{A}(f,\varepsilon) = A_{n^*}(f), \quad \text{where } n^* = \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}, \qquad \widehat{A} \in \calA(\calB_{\rho}).
+\end{equation}
+This algorithm is optimal among algorithms in $\calA(\calB_{\rho})$, i.e.,
 \[
-\comp(\ca(\cb_{\rho}),\varepsilon) = \cost(\hA,\cb_{\rho},\varepsilon) =
+\textup{comp}(\calA(\calB_{\rho}),\varepsilon) = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon) =
 \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}.
@@
 
-To prove this, let $A^*$ be an arbitrary algorithm in $\ca(\cb_{\rho})$, and let $L_1, \ldots, L_N$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.
+To prove this, let $A^*$ be an arbitrary algorithm in $\calA(\calB_{\rho})$, and let $L_1, \ldots, L_N$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.
 Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.
@@
 \begin{align*}
-\varepsilon & \ge \max_{\pm} \norm[\cg]{S(\pm f) - A^*(\pm f)} =  \max_{\pm} \norm[\cg]{\pm S( f) - A^*(0)} \\
-& \ge \frac 12 \left [ \norm[\cg]{S( f) - A^*(0)} + \norm[\cg]{- S( f) - A^*(0)}\right] \\
-& \ge \norm[\cg]{S(f)} 
-= \bignorm[2]{\big(\lambda_i\hf_i\big)_{i=1}^{N+1}} \\
-& \ge \lambda_{N+1} \bignorm[2]{\big(\hf_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \norm[\cf]{f} = \lambda_{N+1} \rho.
+\varepsilon & \ge \max_{\pm} \DHJRnorm[\calG]{S(\pm f) - A^*(\pm f)} =  \max_{\pm} \DHJRnorm[\calG]{\pm S( f) - A^*(0)} \\
+& \ge \frac 12 \left [ \DHJRnorm[\calG]{S( f) - A^*(0)} + \DHJRnorm[\calG]{- S( f) - A^*(0)}\right] \\
+& \ge \DHJRnorm[\calG]{S(f)} 
+= \DHJRbignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{N+1}} \\
+& \ge \lambda_{N+1} \DHJRbignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \DHJRnorm[\calF]{f} = \lambda_{N+1} \rho.
 \end{align*}
@@
 \[
-\cost(A^*,\cb_\rho,\varepsilon) \ge \cost(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \cost(\tA,\cb_\rho,\varepsilon).
+\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widetilde{A},\calB_\rho,\varepsilon).
 \]
-Hence, algorithm $\hA$ defined in \eqref{optBallalg} is optimal for $\ca(\cb_{\rho})$.
-
-\begin{exmp} Consider the case of function approximation for periodic functions defined on the [0,1], and algorithm $\hA$ defined in \eqref{optBallalg}:
-	\begin{align*}
-	f &= \sum_{k \in \integers} \hf(k) \hu_{k}  = \sum_{i=1}^n \hf_i u_i, 
-	& S(f) & = \sum_{k \in \integers} \hf(k) \hlambda_k \hv_k = \sum_{i=1}^n \hf_i \lambda_i \hv_i, \\
-	\hv_{k} (x) &:= \begin{cases} 1, & k = 0, \\
+Hence, algorithm $\widehat{A}$ defined in \eqref{optBallalg} is optimal for $\calA(\calB_{\rho})$.
+
+\begin{example} Consider the case of function approximation for periodic functions defined on the [0,1], and algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
+	\begin{align*}
+	f &= \sum_{k \in \bbZ} \widehat{f}(k) \widehat{u}_{k}  = \sum_{i=1}^n \widehat{f}_i u_i, 
+	& S(f) & = \sum_{k \in \bbZ} \widehat{f}(k) \widehat{\lambda}_k \widehat{v}_k = \sum_{i=1}^n \widehat{f}_i \lambda_i \widehat{v}_i, \\
+	\widehat{v}_{k} (x) &:= \begin{cases} 1, & k = 0, \\
 	\displaystyle \sqrt{2} \sin(2\pi k x), & k > 0, \\
@@
 	\end{cases} 
-	& v_i(x) &= \begin{cases} \hv_{-i/2}, & i \text{ even},\\
-	\hv_{(i-1)/2}, & i \text{ odd},
+	& v_i(x) &= \begin{cases} \widehat{v}_{-i/2}, & i \text{ even},\\
+	\widehat{v}_{(i-1)/2}, & i \text{ odd},
 	\end{cases} \\
-	\hlambda_{k} &:= \begin{cases} 1, & k = 0, \\
-	\displaystyle \frac{1}{\abs{k}^r}, & k \ne 0,
+	\widehat{\lambda}_{k} &:= \begin{cases} 1, & k = 0, \\
+	\displaystyle \frac{1}{\DHJRabs{k}^r}, & k \ne 0,
 	\end{cases}
-	& \lambda_i &= \hlambda_{\lfloor i/2\rfloor} = \frac{1}{\max(1,\lfloor i/2\rfloor)^r}, \\
-	\hu_{k} &:=  \hlambda_k \hv_k,
-	& u_i & = \lambda_i v_i = \begin{cases} \hu_{-i/2}, & i \text{ even},\\
-	\hu_{(i-1)/2}, & i \text{ odd},
+	& \lambda_i &= \widehat{\lambda}_{\lfloor i/2\rfloor} = \frac{1}{\max(1,\lfloor i/2\rfloor)^r}, \\
+	\widehat{u}_{k} &:=  \widehat{\lambda}_k \widehat{v}_k,
+	& u_i & = \lambda_i v_i = \begin{cases} \widehat{u}_{-i/2}, & i \text{ even},\\
+	\widehat{u}_{(i-1)/2}, & i \text{ odd},
 	\end{cases}
 	\\
-	&&\hf_i& = \begin{cases} \hf(-i/2), & i \text{ even},\\
-	\hf((i-1)/2), & i \text{ odd},
+	&&\widehat{f}_i& = \begin{cases} \widehat{f}(-i/2), & i \text{ even},\\
+	\widehat{f}((i-1)/2), & i \text{ odd},
 	\end{cases}
@@
 	\begin{align*}
-	\comp(\ca(\cb_{\rho}),\varepsilon) &= \cost(\hA,\cb_{\rho},\varepsilon) 
+	\textup{comp}(\calA(\calB_{\rho}),\varepsilon) &= \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon) 
 	=\min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} \\
@@
 	\end{align*}
-	Here $\cg=\cl_2[0,1]$.
-The larger the non-negative parameter $r$ is, the faster the $\lambda_i$ tend to 0 as $ i \to 0$, the smaller $\cb_\rho$ is, and the smaller  $\cost(\hA,\cb_{\rho},\varepsilon)$ is.
-For $r = 0$, $\cost(\hA,\cb_{\rho},\varepsilon) = \infty$.
-\end{exmp}
-
-Our goal is not only to construct algorithms in $\ca(\ch)$ for some $\ch$, but also to determine whether the computational cost of our algorithms are reasonable.
-We define an algorithm $A \in \ca(\ch)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \ca(\ch^*)$ if for some number $\omega$,
+	Here $\calG=L^2[0,1]$.
+The larger the non-negative parameter $r$ is, the faster the $\lambda_i$ tend to 0 as $ i \to 0$, the smaller $\calB_\rho$ is, and the smaller  $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ is.
+For $r = 0$, $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon) = \infty$.
+\end{example}
+
+Our goal is not only to construct algorithms in $\calA(\calH)$ for some $\calH$, but also to determine whether the computational cost of our algorithms are reasonable.
+We define an algorithm $A \in \calA(\calH)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \calA(\calH^*)$ if for some number $\omega$,
 \begin{gather}
-\cost(A,\ch,\varepsilon) \le \cost(A^*,\ch^*,\omega\varepsilon), \qquad \forall \varepsilon > 0, \\
-\cost(A,\ch,\varepsilon,\rho) \le \cost(A^*,\ch^*,\omega\varepsilon,\rho), \qquad \forall \varepsilon,\rho > 0.
+\textup{cost}(A,\calH,\varepsilon) \le \textup{cost}(A^*,\calH^*,\omega\varepsilon), \qquad \forall \varepsilon > 0, \\
+\textup{cost}(A,\calH,\varepsilon,\rho) \le \textup{cost}(A^*,\calH^*,\omega\varepsilon,\rho), \qquad \forall \varepsilon,\rho > 0.
 \end{gather}
@@
 
-To illustrate these concepts, consider a nondecreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \naturals$.
-Also consider an unbounded strictly increasing sequence of nonnegative integers $\vn = \{n_0, n_1, \ldots \}$.
-Define an algorithm $A^*$ analogously to $\hA$ defined in \eqref{optBallalg}:
+To illustrate these concepts, consider a nondecreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
+Also consider an unbounded strictly increasing sequence of nonnegative integers $\bsn = \{n_0, n_1, \ldots \}$.
+Define an algorithm $A^*$ analogously to $\widehat{A}$ defined in \eqref{optBallalg}:
 \begin{equation} \label{altBallalg}
-A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \ca(\cb_{\rho}).
-\end{equation}
-By definition, the cost of algorithm $A^*$ is no better than that of  $\hA$.
-Algorithm $A^*$ may or may not have essentially no worse cost than $\hA$ depending on the choice of $\vlambda^*$ and $\vn$.
+A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \calA(\calB_{\rho}).
+\end{equation}
+By definition, the cost of algorithm $A^*$ is no better than that of  $\widehat{A}$.
+Algorithm $A^*$ may or may not have essentially no worse cost than $\widehat{A}$ depending on the choice of $\bslambda^*$ and $\bsn$.
 The table below shows some examples.
-Each different case of $A^*$ is labeled as having a cost that is either essentially no worse or essentially worse than that of $\hA$.
+Each different case of $A^*$ is labeled as having a cost that is either essentially no worse or essentially worse than that of $\widehat{A}$.
 %\[
@@
 & 
-\cost(\hA,\cb_\rho,\varepsilon) \ge \left ( \frac{C\rho}{\varepsilon} \right)^{1/p} - 1
+\textup{cost}(\widehat{A},\calB_\rho,\varepsilon) \ge \left ( \frac{C\rho}{\varepsilon} \right)^{1/p} - 1
 \\[2ex]
 & &
-\cost(\hA,\cb_\rho,\varepsilon) 
+\textup{cost}(\widehat{A},\calB_\rho,\varepsilon) 
 <  \left ( \frac{C\rho}{\varepsilon} \right)^{1/p}
@@
 &
-\cost(A^*,\cb_\rho,\varepsilon) \le 
+\textup{cost}(A^*,\calB_\rho,\varepsilon) \le 
 2 \left ( \frac{C^*\rho}{\varepsilon} \right)^{1/p}
@@
 &
-\cost(A^*,\cb_\rho,\varepsilon)  \ge 
+\textup{cost}(A^*,\calB_\rho,\varepsilon)  \ge 
 \left ( \frac{C^*\rho}{\varepsilon} \right)^{1/q} - 1 
@@
 & 
-\cost(\hA,\cb_\rho,\varepsilon) \ge \frac{\log (C\rho/\varepsilon)}{\log(p)} - 1
+\textup{cost}(\widehat{A},\calB_\rho,\varepsilon) \ge \frac{\log (C\rho/\varepsilon)}{\log(p)} - 1
 \\[2ex]
 &&
-\cost(\hA,\cb_\rho,\varepsilon) < \frac{\log (C\rho/\varepsilon)}{\log(p)}
+\textup{cost}(\widehat{A},\calB_\rho,\varepsilon) < \frac{\log (C\rho/\varepsilon)}{\log(p)}
 \\[2ex]
@@
 &
-\cost(A^*,\cb_\rho,\varepsilon) < \frac{\log (C^*\rho/\varepsilon)}{\log(p)} + 1
+\textup{cost}(A^*,\calB_\rho,\varepsilon) < \frac{\log (C^*\rho/\varepsilon)}{\log(p)} + 1
 \\[2ex]
@@
 &
-\cost(A^*,\cb_\rho,\varepsilon) > 1.999 \frac{\log (C^*\rho/\varepsilon)}{\log(p)} 
+\textup{cost}(A^*,\calB_\rho,\varepsilon) > 1.999 \frac{\log (C^*\rho/\varepsilon)}{\log(p)} 
 \\[1ex]
@@
 &
-\cost(A^*,\cb_\rho,\varepsilon)  \ge 
+\textup{cost}(A^*,\calB_\rho,\varepsilon)  \ge 
 \frac{\log (C^*\rho/\varepsilon)}{\log(q)} - 1
@@
 \subsection{The Case for Adaptive Algorithms}
-For bounded sets of input functions, such as balls, non-adaptive algorithms, such as $\hA$, make sense.
+For bounded sets of input functions, such as balls, non-adaptive algorithms, such as $\widehat{A}$, make sense.
 However, it is typically unknown which ball the input function lies in.
 Thus, we consider unbounded sets of input functions, whose properties can be inferred from the data we collect.
-We use the interpolatory algorithm $\optAn$, defined in \eqref{optAdef}, but we propose an alternative way to bound the error other than assuming an a priori bound on $\norm[\cf]{f}$.
+We use the interpolatory algorithm $A_n$, defined in \eqref{optAdef}, but we propose an alternative way to bound the error other than assuming an a priori bound on $\DHJRnorm[\calF]{f}$.
 
@@
 Our rigorous, data-driven error bound assumes the input to have steadily---but not necessarily monotonically---decaying series coefficients.
-The cone of nice inputs, $\cc$, is defined in Section \ref{sec:cone}.
-For such inputs, we construct an adaptive algorithm, $\tA \in \ca(\cc)$, in Section \ref{sec:adaptalgo},  where $\tA(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$ depending on the input data and the definition of $\cc$.
-The number of series coefficients sampled, $n^*$, is adaptively determined so that $\tA(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.
-The computational cost of $\tA$ is given in  Theorem \ref{thm:compcost}.
+The cone of nice inputs, $\calC$, is defined in Section \ref{sec:cone}.
+For such inputs, we construct an adaptive algorithm, $\widetilde{A} \in \calA(\calC)$, in Section \ref{sec:adaptalgo},  where $\widetilde{A}(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$ depending on the input data and the definition of $\calC$.
+The number of series coefficients sampled, $n^*$, is adaptively determined so that $\widetilde{A}(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.
+The computational cost of $\widetilde{A}$ is given in  Theorem \ref{thm:compcost}.
 Section \ref{sec:opt} shows that our new algorithm is essentially optimal (see Theorem \ref{thm:CostNoWorse}).
@@
 
-Recall from \eqref{errOpt} that the error of the fixed sample size interpolatory algorithm $\optAn$ is $\norm[\cg]{S(f) - \optAn(f)} = \bignorm[2]{\bigl(\lambda_{i} \hf_{i} \bigr)_{i= n+1}^{\infty}}$.
+Recall from \eqref{errOpt} that the error of the fixed sample size interpolatory algorithm $A_n$ is $\DHJRnorm[\calG]{S(f) - A_n(f)} = \DHJRbignorm[2]{\bigl(\lambda_{i} \widehat{f}_{i} \bigr)_{i= n+1}^{\infty}}$.
 The error depends on the series coefficients not yet observed, so at first glance this error seems to be impossible to bound in terms of observed series coefficients.
@@
 \sigma_j(f) :
-= \norm[2]{ \left(\lambda_{i} \hf_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j \in \naturals,
-\end{equation}
-where $\vn  = \{n_0, n_1, \ldots\}$ is a strictly increasing, unbounded sequence of non-negative integers.
+= \DHJRnorm[2]{ \left(\lambda_{i} \widehat{f}_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j \in \bbN,
+\end{equation}
+where $\bsn  = \{n_0, n_1, \ldots\}$ is a strictly increasing, unbounded sequence of non-negative integers.
 We define the cone of nice input functions to consist of those functions for which the $\sigma_j(f)$ decay at a given rate with respect to one another:
 \begin{align} \label{decayconedef}
-\cc &= \left\{ f \in \cf : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \forall j,r \in \naturals \right\} \\
+\calC &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \forall j,r \in \bbN \right\} \\
 \nonumber
-& = \left\{ f \in \cf : \sigma_j(f) \le \min_{1 \le r < j}\{ab^r\sigma_{j-r}(f)\} \ \forall j \in \naturals \right\}.
+& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}\{ab^r\sigma_{j-r}(f)\} \ \forall j \in \bbN \right\}.
 \end{align}
-Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\cc$ and 
+Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\calC$ and 
 \begin{equation} \label{abcond}
@@
 \end{equation}
-The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \cc$.
+The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
 We do not expect the series coefficients of the solution $S(f)$, to decay monotonically.
@@
 
-From the expression for the error in \eqref{errOpt} and the definition of the cone in  \eqref{decayconedef}, one can now derive a data-driven error bound for $j \in \naturals$:
+From the expression for the error in \eqref{errOpt} and the definition of the cone in  \eqref{decayconedef}, one can now derive a data-driven error bound for $j \in \bbN$:
 \begin{align}
 \nonumber
-\norm[\cg]{S(f)-A_{n_j}(f)} &= \norm[2]{\left(\lambda_{i} \hf_{i} \right)_{i = n_j+1}^\infty} = \left\{\sum_{r=1}^\infty \sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \abs{\lambda_{i}\hf_{i} }^{2}  \right\}^{1/2}\\
+\DHJRnorm[\calG]{S(f)-A_{n_j}(f)} &= \DHJRnorm[2]{\left(\lambda_{i} \widehat{f}_{i} \right)_{i = n_j+1}^\infty} = \left\{\sum_{r=1}^\infty \sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \DHJRabs{\lambda_{i}\widehat{f}_{i} }^{2}  \right\}^{1/2}\\
 \nonumber
-&= \norm[2]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
-&\le \norm[2]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
+&= \DHJRnorm[2]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
+&\le \DHJRnorm[2]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
  = \displaystyle ab \sqrt{\frac{1}{1 - b^2}}\sigma_{j}(f)
@@
 \end{align}
-The upper and lower error bounds depend only on the function data and the parameters defining $\cc$.
+The upper and lower error bounds depend only on the function data and the parameters defining $\calC$.
 The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.
@@
 where the number of terms in the sums, $\sigma_j(f)$, are doubled at each step.
-If the series coefficients of the solution decay like $\lambda_{i} \abs{f_{i}} = \Order(i^{-p})$ for some $p>1$, then it is reasonable to expect that the $\sigma_j(f)$ are bounded above and below as
+If the series coefficients of the solution decay like $\lambda_{i} \DHJRabs{f_{i}} = \calO(i^{-p})$ for some $p>1$, then it is reasonable to expect that the $\sigma_j(f)$ are bounded above and below as
 \begin{equation} \label{algDecJ}
-C_{\lo} (n_02^j)^{1-p} \le \sigma_j(f) \le C_{\up} (n_02^j)^{1-p}, \quad   j \in \naturals,
-\end{equation}
-for some constants $C_{\lo}$ and $C_{\up}$, unless the series coefficients drop precipitously in magnitude for some $n_{j-1} < i \le n_j$, and then jump back up for larger $i$.
+C_{\textup{lo}} (n_02^j)^{1-p} \le \sigma_j(f) \le C_{\textup{up}} (n_02^j)^{1-p}, \quad   j \in \bbN,
+\end{equation}
+for some constants $C_{\textup{lo}}$ and $C_{\textup{up}}$, unless the series coefficients drop precipitously in magnitude for some $n_{j-1} < i \le n_j$, and then jump back up for larger $i$.
 When \eqref{algDecJ} holds, it follows that
 \begin{equation*} 
-\frac{\sigma_{j+r}(f)}{\sigma_j(f)} \le \frac{C_{\up} (n_02^{j+r})^{1-p}}{C_{\lo} (n_02^j)^{1-p}} = \frac{C_{\up} 2^{r(1-p)}}{C_{\lo}}\quad   j \in \naturals.
-\end{equation*}
-Thus, choosing $a \ge C_{\up}/C_{\lo}$ and $b \ge 2^{1-p}$ ensures that reasonable inputs $f$ lie inside the cone $\cc$.
+\frac{\sigma_{j+r}(f)}{\sigma_j(f)} \le \frac{C_{\textup{up}} (n_02^{j+r})^{1-p}}{C_{\textup{lo}} (n_02^j)^{1-p}} = \frac{C_{\textup{up}} 2^{r(1-p)}}{C_{\textup{lo}}}\quad   j \in \bbN.
+\end{equation*}
+Thus, choosing $a \ge C_{\textup{up}}/C_{\textup{lo}}$ and $b \ge 2^{1-p}$ ensures that reasonable inputs $f$ lie inside the cone $\calC$.
 
@@
 
-Now we introduce our adaptive algorithm, $\tA \in \ca(\cc)$, which yields an approximate solution to the problem $S:\cc\rightarrow\cg$ that meets the absolute error tolerance $\varepsilon$.
+Now we introduce our adaptive algorithm, $\widetilde{A} \in \calA(\calC)$, which yields an approximate solution to the problem $S:\calC\rightarrow\calG$ that meets the absolute error tolerance $\varepsilon$.
 
 \begin{algo}\label{algo2}
-Given $a$, $b$, the sequence $\vn$, the cone $\cc$, and the input function $f \in \cc$, and the absolute error tolerance $\varepsilon$, set $j=1$.
+Given $a$, $b$, the sequence $\bsn$, the cone $\calC$, and the input function $f \in \calC$, and the absolute error tolerance $\varepsilon$, set $j=1$.
 \begin{description}
@@
     \end{equation}
-    If this is true, then return $\tA(f,\varepsilon) = A_{n_{j}}(f)$, where $\optAn$ is defined in \eqref{optAdef}, and terminate the algorithm.
+    If this is true, then return $\widetilde{A}(f,\varepsilon) = A_{n_{j}}(f)$, where $A_n$ is defined in \eqref{optAdef}, and terminate the algorithm.
 \item[Step 3.] Otherwise, increase $j$ by $1$ and return to Step $1$.
@@
 \begin{theorem}\label{thm:compcost}
-The algorithm, $\tA$, defined in Algorithm \ref{algo2} lies in $\ca(\cc)$ and has computational cost $\cost(\tA,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly by the inequalities 
+The algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2} lies in $\calA(\calC)$ and has computational cost $\textup{cost}(\widetilde{A},f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly by the inequalities
 \begin{equation} \label{eq:OurAlgjstar}
-j^* = \min\left \{ j \in \naturals : \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  \right\}.
-\end{equation}
-Moreover, $\cost(\tA,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+j^* = \min\left \{ j \in \bbN : \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  \right\}.
+\end{equation}
+Moreover, $\textup{cost}(\widetilde{A},\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
-j^\dagger \le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}.
+j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}.
 \end{equation}
@@
 It then follows that the error bound on $A_{n_{j^*}}(f)$ in \eqref{algoineq} is no greater than the error tolerance $\varepsilon$.
-So, $\tA \in \ca(\cc)$.
+So, $\widetilde{A} \in \calA(\calC)$.
 
 For the remainder of the proof consider $\rho$ and $\varepsilon$ fixed.
-To derive an upper bound on $n_{j^\dagger} = \cost(\tA,\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \cc$:
+To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
 \begin{multline} \label{normsigineq}
-\lambda_{n_j} \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}} \le 
-\bignorm[2]{\big( \lambda_i \hf_i \big)_{i=n_{j-1}+1}^{n_j}} = \sigma_j(f) 
+\lambda_{n_j} \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \le 
+\DHJRbignorm[2]{\big( \lambda_i \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} = \sigma_j(f) 
 \\
-\le \lambda_{n_{j-1}+1} \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}}.
+\le \lambda_{n_{j-1}+1} \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}}.
 \end{multline}
 
-A rough upper bound on $j^\dagger$ may be obtained by noting that for any $f \in \cc \cap \cb_\rho$ and for any $j < j^* \le j^\dagger$, it follows from \eqref{eq:OurAlgjstar} and \eqref{normsigineq} that
-\begin{equation*}
-\rho \ge \norm[\cf]{f} \ge \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
+A rough upper bound on $j^\dagger$ may be obtained by noting that for any $f \in \calC \cap \calB_\rho$ and for any $j < j^* \le j^\dagger$, it follows from \eqref{eq:OurAlgjstar} and \eqref{normsigineq} that
+\begin{equation*}
+\rho \ge \DHJRnorm[\calF]{f} \ge \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
 \end{equation*}
@@
 \begin{equation} \label{jdaggerlast}
-j^\dagger \le \min \left \{j \in \naturals :  \lambda_{n_{j-1}+1} \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\}.
+j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}+1} \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\}.
 \end{equation}
@@
 The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by a more careful argument in a similar vein.  
-For any $f \in  \cc \cap \cb_\rho$ and for any $j < j^* \le j^\dagger$,
-\begin{align*}
-\rho^2 &\ge \norm[\cf]{f}^2 = \bignorm[2]{\big( \hf_i \big)_{i=1}^{\infty}}^2 \\
-& \ge \sum_{k=1}^j \bignorm[2]{\big( \hf_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \qquad \forall j \ge 1\\
+For any $f \in  \calC \cap \calB_\rho$ and for any $j < j^* \le j^\dagger$,
+\begin{align*}
+\rho^2 &\ge \DHJRnorm[\calF]{f}^2 = \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=1}^{\infty}}^2 \\
+& \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \qquad \forall j \ge 1\\
 & \ge \sum_{k=1}^j \frac{\sigma_k^2(f)}{\lambda_{n_{k-1}+1}^2} \qquad \text{by \eqref{normsigineq}}\\
@@
 \begin{equation*}
- \min \{\cost(\tA,f,\varepsilon) : f \in \cc, \ \norm[\cf]{f} \ge \rho \} 
+ \min \{\textup{cost}(\widetilde{A},f,\varepsilon) : f \in \calC, \ \DHJRnorm[\calF]{f} \ge \rho \} 
  \begin{cases} = n_1, & n_0 > 0, \\
@@
 \end{equation*}
-This result may be obtained by considering functions where only $\hf_1$ is nonzero.  For $n_0 > 0$, $\sigma_1(f) = 0$, and for $n_0 = 0$, $\sigma_2(f) = 0$.
-
-The upper bound on $\cost(\tA,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
-This in turn depends both on the increasing sequence $\vn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$.
+This result may be obtained by considering functions where only $\widehat{f}_1$ is nonzero.  For $n_0 > 0$, $\sigma_1(f) = 0$, and for $n_0 = 0$, $\sigma_2(f) = 0$.
+
+The upper bound on $\textup{cost}(\widetilde{A},\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
+This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$.
 Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation} \label{keysum}
@@
 One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.
-These simplifications lead to two simpler, but coarser upper bounds on the cost of $\tA$
-
-\begin{cor} For the algorithm, $\tA$, defined in Algorithm \ref{algo2}, then $\cost(\tA,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}$
+
+\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, then $\textup{cost}(\widetilde{A},\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdaggerfirst}
@@
 \label{lambdankbd}
-\lambda_{n_{j-1}+1} \le \alpha \beta^j,  \quad j \in \naturals,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
+\lambda_{n_{j-1}+1} \le \alpha \beta^j,  \quad j \in \bbN,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
 \end{equation}
@@
 \end{equation}
-\end{cor}
+\end{corollary}
 
@@
 \begin{equation} \label{jsumupperbd}
-j^\dagger \le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2}    \right\}.
+j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2}    \right\}.
 \end{equation}
@@
 \[
-j^\dagger \le \min \left \{j \in \naturals :  \alpha \beta^j < \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
+j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^j < \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
 \]
@@
 
-This corollary highlights two limiting factors on the computational cost of our adaptive algorithm, $\tA$.
-When $j$ is large enough to make $\lambda_{n_{j-1}+1}\norm[\cf]{f}/\varepsilon$ small enough, $\tA(f,\varepsilon)$ stops.
+This corollary highlights two limiting factors on the computational cost of our adaptive algorithm, $\widetilde{A}$.
+When $j$ is large enough to make $\lambda_{n_{j-1}+1}\DHJRnorm[\calF]{f}/\varepsilon$ small enough, $\widetilde{A}(f,\varepsilon)$ stops.
 This is statement \eqref{jdaggerlastsimple}, and its precursor, \eqref{jdaggerlast}.
-Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\cc$ in \eqref{decayconedef}, means that $\tA(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\norm[\cf]{f}/\varepsilon$.
+Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\calC$ in \eqref{decayconedef}, means that $\widetilde{A}(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\DHJRnorm[\calF]{f}/\varepsilon$.
 
@@
 
-The adaptive algorithm $\tA$, which does not know an upper bound on $\norm[\cf]{f}$ a priori, may cost more than the non-adaptive algorithm $\hA$, which assumes an upper bound on $\norm[\cf]{f}$, but under reasonable assumptions, the extra cost will be small.
-
-\begin{cor} \label{cor:tAsameCosthA} Suppose that the sequence $\vn$ is chosen to satisfy
+The adaptive algorithm $\widetilde{A}$, which does not know an upper bound on $\DHJRnorm[\calF]{f}$ a priori, may cost more than the non-adaptive algorithm $\widehat{A}$, which assumes an upper bound on $\DHJRnorm[\calF]{f}$, but under reasonable assumptions, the extra cost will be small.
+
+\begin{corollary} \label{cor:tAsameCosthA} Suppose that the sequence $\bsn$ is chosen to satisfy
 \begin{equation} \label{lambdaDecay}
-\lambda_{n_{j+1}+1} \ge c_\lambda \lambda_{n_j+1}, \qquad j \in \naturals, 
-\end{equation}
-for some positive $c_\lambda$.  Then $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially no worse than \linebreak[4]
-$\cost(\hA,\cb_{\rho},\varepsilon)$.
-
-\end{cor}
+\lambda_{n_{j+1}+1} \ge c_\lambda \lambda_{n_j+1}, \qquad j \in \bbN, 
+\end{equation}
+for some positive $c_\lambda$.  Then $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than \linebreak[4]
+$\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$.
+
+\end{corollary}
 
 \begin{proof}
-Combining the upper bound on $n_{j^\dagger} = \cost(\tA,\cc,\varepsilon,\rho)$ in \eqref{jdaggerlast} plus  \eqref{lambdaDecay} above, it follows that
+Combining the upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$ in \eqref{jdaggerlast} plus  \eqref{lambdaDecay} above, it follows that
 \begin{equation*}
@@
 \end{equation*}
-where $n = \cost(\hA,\cb_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab)$.
+where $n = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab)$.
 Since the $\lambda_i$ are non-increasing,
 \begin{equation*}
-\cost(\tA,\cc,\varepsilon,\rho) = n_{j^\dagger} \le n_{j^\dagger}+1 < n = \cost(\hA,\cb_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
+\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = n_{j^\dagger} \le n_{j^\dagger}+1 < n = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
 \end{equation*}
@@
 
-From Corollary \ref{cor:tAsameCosthA} it is known that $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially no worse than
-$\cost(\hA,\cb_{\rho},\varepsilon) = \comp(\ca(\cb_{\rho}),\varepsilon)$.
-We would like to show that $\tA \in \ca(\cc)$ is  essentially optimal, i.e., $\cost(\tA,\cc, \varepsilon,\rho)$ is essentially no worse than  $\comp(\ca(\cc),\varepsilon,\rho)$.
-However,  $\comp(\ca(\cc),\varepsilon,\rho)$ may be smaller than $\comp(\ca(\cb_{\rho}),\varepsilon)$ because $\cc \cap \cb_\rho$ is a strict subset of  $ \cb_\rho$.
+From Corollary \ref{cor:tAsameCosthA} it is known that $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than
+$\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon) = \textup{comp}(\calA(\calB_{\rho}),\varepsilon)$.
+We would like to show that $\widetilde{A} \in \calA(\calC)$ is  essentially optimal, i.e., $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than  $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
+However,  $\textup{comp}(\calA(\calC),\varepsilon,\rho)$ may be smaller than $\textup{comp}(\calA(\calB_{\rho}),\varepsilon)$ because $\calC \cap \calB_\rho$ is a strict subset of  $ \calB_\rho$.
 This presents a challenge.
 
-A lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$ is established by constructing fooling functions in $\cc$ with norms no greater than $\rho$.
+A lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$ is established by constructing fooling functions in $\calC$ with norms no greater than $\rho$.
 To obtain a result that can be compared with the cost of our algorithm, we assume that
 \begin{equation} \label{lambdaRatio}
-R = \sup_{k \in \naturals} \frac{\lambda_{n_{k-1}}}{\lambda_{n_k}} < \infty.
+R = \sup_{k \in \bbN} \frac{\lambda_{n_{k-1}}}{\lambda_{n_k}} < \infty.
 \end{equation}
@@
 
-The following theorem establishes a lower bound on the complexity of our problem for input functions in $\cc$.
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC$.
 The theorem after that shows that the cost of our algorithm as given in Theorem \ref{thm:compcost} is essentially no worse than this lower bound.
@@
  \label{compbdA}
-&\comp(\ca(\cc),\varepsilon,\rho) \ge n_{j^*}, 
+&\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_{j^*}, 
 \intertext{where}
 \label{compbdB}
-j^* & = \max \left \{ j \in \naturals : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
+j^* & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
 \frac{\rho^2}{\varepsilon^2}
@@
 Consider a fixed $\rho$ and $\varepsilon$.
-Choose any positive integer $j$ such that $n_j$ exceeds $\comp(\ca(\cc),\varepsilon,\rho)$.
-The proof proceeds by carefully constructing thre  test input functions, $f$ and $f_{\pm}$, lying in $\cc \cap \cb_{\rho}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $n_j$, which can be translated into a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
-
-The first test function $f \in \cc$ is defined in terms of its series coefficients:
+Choose any positive integer $j$ such that $n_j$ exceeds $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
+The proof proceeds by carefully constructing thre  test input functions, $f$ and $f_{\pm}$, lying in $\calC \cap \calB_{\rho}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $n_j$, which can be translated into a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
+
+The first test function $f \in \calC$ is defined in terms of its series coefficients:
 \begin{align}
 \nonumber
-\hf_i &:= \begin{cases}
+\widehat{f}_i &:= \begin{cases}
 \displaystyle
@@
 \end{align}
-It can be verified that the test function lies both in $\cb_{\rho}$ and in $\cc$:
+It can be verified that the test function lies both in $\calB_{\rho}$ and in $\calC$:
 \begin{align}
 \label{testfunnorm}
-\norm[\cf]{f}^2 &=  c^2\sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \le \rho^2,
+\DHJRnorm[\calF]{f}^2 &=  c^2\sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \le \rho^2,
 \\
@@
 
-Now suppose that $A^* \in \ca(\cc)$ is an optimal algorithm, i.e., $\cost(A^*,\cc,\varepsilon,\rho) =  \comp(\ca(\cc),\varepsilon,\rho)$ for all $\varepsilon, \rho > 0$.
+Now suppose that $A^* \in \calA(\calC)$ is an optimal algorithm, i.e., $\textup{cost}(A^*,\calC,\varepsilon,\rho) =  \textup{comp}(\calA(\calC),\varepsilon,\rho)$ for all $\varepsilon, \rho > 0$.
 For our particular input $f$ defined above, suppose that $A^*(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where
 \[
-n + 1\le \comp(\ca(\cc),\varepsilon,\rho) +1 < n_j.
+n + 1\le \textup{comp}(\calA(\calC),\varepsilon,\rho) +1 < n_j.
 \]
@@
 \begin{equation}\label{uConstraint}
-L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\cf} = 0, \qquad 
-\max_{0\le k\le j} \bignorm[\cf]{u^{(k)}} = 1.
+L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\calF} = 0, \qquad 
+\max_{0\le k\le j} \DHJRbignorm[\calF]{u^{(k)}} = 1.
 \end{equation}
@@
 \nonumber
-\norm[\cf]{f^*_\pm}^2 & \le \norm[\cf]{f}^2 + \norm[\cf]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
-& \le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \bignorm[\cf]{u^{(k)}}^2\right) + \eta^2 \bignorm[\cf]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
+\DHJRnorm[\calF]{f^*_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
+& \le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \DHJRbignorm[\calF]{u^{(k)}}^2\right) + \eta^2 \DHJRbignorm[\calF]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
 \nonumber
@@
 \end{align} 
-so $f_{\pm} \in \cb_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
-
-Now we must check that $f_\pm \in \cc$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$,
+so $f_{\pm} \in \calB_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
+
+Now we must check that $f_\pm \in \calC$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$,
 \begin{equation*}
@@
 \le \sigma_k(f) + \sigma_k(\eta u)\le 
-c b^{k-j} + \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\norm[\cf]{u^{(k)} } }{\lambda_{n_k}}
+c b^{k-j} + \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\DHJRnorm[\calF]{u^{(k)} } }{\lambda_{n_k}}
 \le b^{k-j}\left(c+\eta R \right) 
@@
 \ge \sigma_k(f) - \sigma_k(\eta u)\ge 
-c b^{k-j} - \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\norm[\cf]{u^{(k)} } }{\lambda_{n_k}}
+c b^{k-j} - \eta\lambda_{n_{k-1}+1}\frac{b^{k-j}\DHJRnorm[\calF]{u^{(k)} } }{\lambda_{n_k}}
 \ge b^{k-j}\left(c-\eta R \right) , 
@@
 \end{equation*}
-which establishes that $f_\pm \in \cc$.
+which establishes that $f_\pm \in \calC$.
 
@@
 \begin{align*}
-\varepsilon &\ge \max \bigl\{\norm[\cg]{S(f_+) - A^*(f_+,\varepsilon)}, \norm[\cg]{S(f_-) - A^*(f_-,\varepsilon)} \bigr\} \\
-&\ge \frac 12 \bigl[\norm[\cg]{S(f^*_+) - A^*(f,\varepsilon)} + \norm[\cg]{S(f^*_-) - A^*(f,\varepsilon)}  \bigr] \\
+\varepsilon &\ge \max \bigl\{\DHJRnorm[\calG]{S(f_+) - A^*(f_+,\varepsilon)}, \DHJRnorm[\calG]{S(f_-) - A^*(f_-,\varepsilon)} \bigr\} \\
+&\ge \frac 12 \bigl[\DHJRnorm[\calG]{S(f^*_+) - A^*(f,\varepsilon)} + \DHJRnorm[\calG]{S(f^*_-) - A^*(f,\varepsilon)}  \bigr] \\
 &\qquad \qquad \text{since } A^*(f^*_\pm,\varepsilon) = A^*(f,\varepsilon) \\
-&\ge \frac 12 \norm[\cg]{S(f^*_+) - S(f^*_-)} \quad \text{by the triangle inequality}\\
-&\ge \frac 12 \norm[\cg]{S(f^*_+ - f^*_-)} \quad \text{since $S$ is linear}\\
-&= \eta \norm[\cg]{S(u)}.
+&\ge \frac 12 \DHJRnorm[\calG]{S(f^*_+) - S(f^*_-)} \quad \text{by the triangle inequality}\\
+&\ge \frac 12 \DHJRnorm[\calG]{S(f^*_+ - f^*_-)} \quad \text{since $S$ is linear}\\
+&= \eta \DHJRnorm[\calG]{S(u)}.
 \end{align*}
@@
 \begin{align*}
-\varepsilon^2  & \ge \eta \norm[\cg]{S(u)}^2= 
-\eta^2 \sum_{k=0}^{j} \bignorm[\cg]{S(u^{(k)})}^2  \frac{b^{2(k-j)}}{\lambda_{n_k}^2}\\
+\varepsilon^2  & \ge \eta \DHJRnorm[\calG]{S(u)}^2= 
+\eta^2 \sum_{k=0}^{j} \DHJRbignorm[\calG]{S(u^{(k)})}^2  \frac{b^{2(k-j)}}{\lambda_{n_k}^2}\\
 & \ge \eta^2 
-\sum_{k=0}^{j} \bignorm[\cf]{u^{(k)}}^2 
+\sum_{k=0}^{j} \DHJRbignorm[\calF]{u^{(k)}}^2 
 b^{2(k-j)}\\
-& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \bignorm[\cf]{u^{(k)}} \\
+& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \DHJRbignorm[\calF]{u^{(k)}} \\
 & \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2R^2} \\
@@
 
-This lower bound must be satisfied by $j$ to be consistent with the assumption $\comp(\ca(\cc),\varepsilon,\rho) \le n_j - 1$.
-Thus, for any $j$ violating this inequality it follows that $\comp(\ca(\cc),\varepsilon,\rho) \ge n_j$.
-This implication provides a lower bound on $\comp(\ca(\cc),\varepsilon,\rho)$.
+This lower bound must be satisfied by $j$ to be consistent with the assumption $\textup{comp}(\calA(\calC),\varepsilon,\rho) \le n_j - 1$.
+Thus, for any $j$ violating this inequality it follows that $\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_j$.
+This implication provides a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
 \end{proof}
@@
 \label{thm:CostNoWorse}
-Under assumption \eqref{lambdaRatio} $\cost(\tA,\varepsilon,\rho)$ is essentially no worse than $\comp(\ca(\cc),\varepsilon,\rho)$.
+Under assumption \eqref{lambdaRatio} $\textup{cost}(\widetilde{A},\varepsilon,\rho)$ is essentially no worse than $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
 \end{theorem}
@@
 \end{equation}
-and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\cc$. 
-For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\cost(\tA,\rho,\varepsilon) \le n_{j^\dagger}$ where 
-\begin{align*} 
-j^\dagger &\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
-&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2} \right\} \qquad \text{since } a > 1\\
-&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2} \right\} \\
-&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
-&\le \min \left \{j \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)} \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{lambdaRatio} } \\
-&\le \min \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{omegadef} } \\
-&= \max \left \{j \in \naturals : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^*.
-\end{align*}
-By Theorem \ref{thm:lowbdcomp}, $\comp(\ca(\cc),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above, $n_{j^*} \ge n_{j^\dagger} \ge \cost(\tA,\varepsilon,\rho)$.
+and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$. 
+For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\rho,\varepsilon) \le n_{j^\dagger}$ where 
+\begin{align*} 
+j^\dagger &\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
+&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2} \right\} \qquad \text{since } a > 1\\
+&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2} \right\} \\
+&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
+&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)} \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{lambdaRatio} } \\
+&\le \min \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{omegadef} } \\
+&= \max \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^*.
+\end{align*}
+By Theorem \ref{thm:lowbdcomp}, $\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above, $n_{j^*} \ge n_{j^\dagger} \ge \textup{cost}(\widetilde{A},\varepsilon,\rho)$.
 Thus, our algorithm is essentially no more costly than the optimal algorithm.
@@
 \begin{align*}
-f &= \sum_{\vk \in \integers^d} \hf(\vk) u_{\vk} (\vx), \\
-u_{\vk} (\vx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j k_j)},  \\
-S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\vk \in \integers^d} \hf(\vk) \lambda_{\vk} v_{\vk} (\vx), \\
-v_{\vk}(\vx) & : =  -\sign(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
+f &= \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) u_{\bsk} (\bsx), \\
+u_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j k_j)},  \\
+S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \lambda_{\bsk} v_{\bsk} (\bsx), \\
+v_{\bsk}(\bsx) & : =  -\textup{sign}(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
 & \qquad \qquad \times \prod_{j=2}^d 2^{(1-\delta_{k_j,0})/2} \cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ), \\
-\lambda_{\vk} &:= \frac{2 \pi \abs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}.
-\end{align*}
-We construct a function by choosing its Fourier coefficients $\hf$ to be normal distributed \textbf{What distribution (mean, standard deviation)?
+\lambda_{\bsk} &:= \frac{2 \pi \DHJRabs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}.
+\end{align*}
+We construct a function by choosing its Fourier coefficients $\widehat{f}$ to be normal distributed \textbf{What distribution (mean, standard deviation)?
 How many Fourier coefficients are chosen to construct the function?}.
@@
 %
-%In this case, $\cf=\{f:\reals^n\mapsto\reals^m,\, f\in C^1(\Omega)\}$ and $\cg=\{g:\reals^n\mapsto\reals,\, g\in C^0(\Omega)\}$ and $S: f\mapsto \nabla\cdot f=\sum_{j=1}^{m}\partial_{x_j}f_j$.
+%In this case, $\calF=\{f:\reals^n\mapsto\reals^m,\, f\in C^1(\Omega)\}$ and $\calG=\{g:\reals^n\mapsto\reals,\, g\in C^0(\Omega)\}$ and $S: f\mapsto \nabla\cdot f=\sum_{j=1}^{m}\partial_{x_j}f_j$.
 %
 %\begin{gather*}
-%\norm[\cf]{f} =\left[\int_\Omega \sum_{j=1}^{m}\abs{f_j(x)}^2+\sum_{j=1}^{m}\abs{f'_j(x)}^2 \, \dif x \right]^{1/2},\\
-%\norm[\cg]{g} = \left[\int_\Omega \abs{g(x)}^2 \, \dif x \right]^{1/2}, \\
+%\DHJRnorm[\calF]{f} =\left[\int_\Omega \sum_{j=1}^{m}\DHJRabs{f_j(x)}^2+\sum_{j=1}^{m}\DHJRabs{f'_j(x)}^2 \, \dif x \right]^{1/2},\\
+%\DHJRnorm[\calG]{g} = \left[\int_\Omega \DHJRabs{g(x)}^2 \, \dif x \right]^{1/2}, \\
 %u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} <i,x>}}{\sqrt{mV(\omega)+4\pi<i,i>}}, \\
 %v_i(x) = \me^{2 \pi \sqrt{-1} <i,x>},\\
-% \lambda_i=\frac{2\pi\sqrt{-1}\sum_{j=1}^{m}i_j}{\sqrt{mV(\omega)+4\pi<i,i>}}, \qquad i \in \integers^m,\\
+% \lambda_i=\frac{2\pi\sqrt{-1}\sum_{j=1}^{m}i_j}{\sqrt{mV(\omega)+4\pi<i,i>}}, \qquad i \in \bbZ^m,\\
 %\pin=\pout=2,\quad q=\infty.
@@
 
-\begin{rem}
-For the algorithm, $\tA$, defined in Algorithm \ref{algo2}, $\cost(\tA,\rho,\varepsilon) \le n_{j^*}$, where $j^*$ satisfies the following upper bound:
+\begin{remark}
+For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, $\textup{cost}(\widetilde{A},\rho,\varepsilon) \le n_{j^*}$, where $j^*$ satisfies the following upper bound:
 \[
-j^* \le \min \left \{j \in \naturals : \rho^2 \le \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\up}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right]\right\}.
+j^* \le \min \left \{j \in \bbN : \rho^2 \le \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\textup{up}}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right]\right\}.
 \]
-\end{rem}
+\end{remark}
 
 \begin{proof}
-First, we have a rough upper bound on $\cost(\tA,\rho,\varepsilon)$ in the proof of  Theorem  \ref{thm:compcost} by finding the smallest $j$ violating the following inequality:
-\begin{equation*}
-\rho \ge \norm[\cf]{f} \ge \bignorm[2]{\big( \hf_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
+First, we have a rough upper bound on $\textup{cost}(\widetilde{A},\rho,\varepsilon)$ in the proof of  Theorem  \ref{thm:compcost} by finding the smallest $j$ violating the following inequality:
+\begin{equation*}
+\rho \ge \DHJRnorm[\calF]{f} \ge \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
 \end{equation*}
@@
 \begin{equation} \label{lambdaDecI}
-\lambda_i \le C_{\up} i^{1-p}, \quad   i \in \naturals,
+\lambda_i \le C_{\textup{up}} i^{1-p}, \quad   i \in \bbN,
 \end{equation}
@@
 \rho & > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}} \\
-& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}(n_{j-1}+1)^{1-p}} \qquad \text{by \eqref{lambdaDecI}} \\
-& > \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}n_{j-1}^{1-p}} \\
-& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}(2^{j-1}n_0)^{1-p}} \qquad \text{by \eqref{geonj}} \\
-& = \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\up}n_0^{1-p} 2^{(j-1)(1-p)}}
+& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}(n_{j-1}+1)^{1-p}} \qquad \text{by \eqref{lambdaDecI}} \\
+& > \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}n_{j-1}^{1-p}} \\
+& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}(2^{j-1}n_0)^{1-p}} \qquad \text{by \eqref{geonj}} \\
+& = \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}n_0^{1-p} 2^{(j-1)(1-p)}}
 \end{align*}
@@
 \[
-j^* \le \min \left \{j \in \naturals :  
-j \ge \frac{\log\left[\frac{\varepsilon \sqrt{1-b^2}}{\rho ab C_{\up}n_0^{1-p}}\right]}{(1-p)\log 2}+ 1\right\}
+j^* \le \min \left \{j \in \bbN :  
+j \ge \frac{\log\left[\frac{\varepsilon \sqrt{1-b^2}}{\rho ab C_{\textup{up}}n_0^{1-p}}\right]}{(1-p)\log 2}+ 1\right\}
 \]
@@
 From \eqref{lambdaDecI}, we can obtain for any $k=1, \ldots,j-1$
-\[\lambda_{n_{k-1}+1} \le C_{\up}(n_{k-1}+1)^{1-p} 
-<  C_{\up}(n_{k-1})^{1-p} < C_{\up}n_0^{1-p}.\]
+\[\lambda_{n_{k-1}+1} \le C_{\textup{up}}(n_{k-1}+1)^{1-p} 
+<  C_{\textup{up}}(n_{k-1})^{1-p} < C_{\textup{up}}n_0^{1-p}.\]
 Thus, we have 
@@
 \rho^2 &> \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]\\
-& >  \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}(C_{\up}n_0^{1-p})^2} + \frac{1}{(C_{\up}(n_{j-1})^{1-p} )^2}\right] \\
-& = \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}C_{\up}^2n_0^{2(1-p)}} + \frac{1}{C^2_{\up}(2^{j-1}n_0)^{2(1-p)}}\right] \qquad \text{by \eqref{geonj}}\\
-&  =\frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\up}^2n_0^{2(1-p)}} \left[ \frac{1}{a^2b^{2j}}\sum_{k=1}^{j-1} b^{2k }+ \frac{1}{2^{2(j-1)(1-p)}}\right] \\
-& > \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\up}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right] .
+& >  \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}(C_{\textup{up}}n_0^{1-p})^2} + \frac{1}{(C_{\textup{up}}(n_{j-1})^{1-p} )^2}\right] \\
+& = \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}C_{\textup{up}}^2n_0^{2(1-p)}} + \frac{1}{C^2_{\textup{up}}(2^{j-1}n_0)^{2(1-p)}}\right] \qquad \text{by \eqref{geonj}}\\
+&  =\frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\textup{up}}^2n_0^{2(1-p)}} \left[ \frac{1}{a^2b^{2j}}\sum_{k=1}^{j-1} b^{2k }+ \frac{1}{2^{2(j-1)(1-p)}}\right] \\
+& > \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\textup{up}}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right] .
 \end{align*}
@@
 
-In our example, consider $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f$ the embedding operator with:
+In our example, consider $\calF=\calG=\cl_2[0,1]$, and $S: f \mapsto f$ the embedding operator with:
 \begin{gather*}
-\norm[\cf]{f} = \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
-u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x},\quad \lambda_i=1, \qquad i \in \integers,\\
+\DHJRnorm[\calF]{f} = \DHJRnorm[\calG]{f} = \left[\int_0^1 \DHJRabs{f(x)}^2 \, \dif x \right]^{1/2}, \\
+u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x},\quad \lambda_i=1, \qquad i \in \bbZ,\\
 \pin=\pout=2,\quad q=\infty.
@@
 
-For our index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$,
+For our index set $\ci=\bbZ=\{0,1,-1,2,-2,\ldots\}$,
 \begin{gather*}
-i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
-n_0=0,\quad n_k=2k+1, \qquad k\in\naturals.
+i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\bbN,\\
+n_0=0,\quad n_k=2k+1, \qquad k\in\bbN.
 \end{gather*}
@@
 &=\frac{1}{1-b^{-1}\me^{2\pi\sqrt{-1}x}}+\frac{b^{-1}\me^{-2\pi\sqrt{-1}x}}{1-b^{-1}\me^{-2\pi\sqrt{-1}x}}\\
-&=\sum_{k\in\naturals_0}\left(b^{-1}\me^{2\pi\sqrt{-1}x}\right)^k+\sum_{k\in\naturals}\left(b^{-1}\me^{-2\pi\sqrt{-1}x}\right)^k\\
-&=\sum_{k\in\integers}b^{-\abs{k}}\me^{2\pi\sqrt{-1}kx}\Longrightarrow\hf_{i_j}=b^{-\abs{i_j}}
+&=\sum_{k\in\bbN_0}\left(b^{-1}\me^{2\pi\sqrt{-1}x}\right)^k+\sum_{k\in\bbN}\left(b^{-1}\me^{-2\pi\sqrt{-1}x}\right)^k\\
+&=\sum_{k\in\bbZ}b^{-\DHJRabs{k}}\me^{2\pi\sqrt{-1}kx}\Longrightarrow\widehat{f}_{i_j}=b^{-\DHJRabs{i_j}}
 \end{align*}
@@
 \begin{align*}
-\norm[\cg]{S(f)}&=\left(\sum_{j\in\integers}\lambda_{i_j}^2\hf_{i_j}^2\right)^{\frac{1}{2}} =\left(1+2\sum_{k\in\naturals}b^{-2k}\right)^{\frac{1}{2}}=\left(\frac{b^2+1}{b^2-1}\right)^{\frac{1}{2}}
+\DHJRnorm[\calG]{S(f)}&=\left(\sum_{j\in\bbZ}\lambda_{i_j}^2\widehat{f}_{i_j}^2\right)^{\frac{1}{2}} =\left(1+2\sum_{k\in\bbN}b^{-2k}\right)^{\frac{1}{2}}=\left(\frac{b^2+1}{b^2-1}\right)^{\frac{1}{2}}
 \end{align*}
@@
 &\sigma_1(f)=\sqrt{1+2b^{-2}}\\
-&\sigma_k(f)=\sqrt{2}b^{-k}, \qquad k \in\naturals\setminus\{1\}.
-\end{align*}
-Recalling the alternative definition of the cone in (\ref{decayconedef}), with these sums, $f\in\cc$ for $\gamma_r=b^{-r}$ since
+&\sigma_k(f)=\sqrt{2}b^{-k}, \qquad k \in\bbN\setminus\{1\}.
+\end{align*}
+Recalling the alternative definition of the cone in (\ref{decayconedef}), with these sums, $f\in\calC$ for $\gamma_r=b^{-r}$ since
 \begin{equation*}
@@
 
-In this case, $\norm[\pout]{\bgamma}=\frac{1}{\sqrt{b^2-1}}$.
+In this case, $\DHJRnorm[\pout]{\bgamma}=\frac{1}{\sqrt{b^2-1}}$.
 If we use our Algorithm \ref{algo2}, we have to check first whether $\sqrt{\frac{b^2+2}{b^4-b^2}}\le\varepsilon$.
@@
 \begin{equation*}
-k^*=\min\left\{k\in\naturals\setminus\{1\}:\frac{1}{2\log(b)}\log\left(\frac{2}{(b^2-1)\varepsilon^2}\right) \le k \right\}
+k^*=\min\left\{k\in\bbN\setminus\{1\}:\frac{1}{2\log(b)}\log\left(\frac{2}{(b^2-1)\varepsilon^2}\right) \le k \right\}
 \end{equation*}
@@
   % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(f)}-\norm[\cg]{A_{n_{k^*}}(f)}$ \\
+  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\DHJRnorm[\calG]{S(f)}-\DHJRnorm[\calG]{A_{n_{k^*}}(f)}$ \\
   \hline
@@
 The properties we will use for these particular polynomials can be found in \cite{AbrSte64}: derivatives, explicit Fourier coefficients, etc.
-To deal with this example, now $\cf=\cg=\cl_2[0,1]$, and $S: f \mapsto f'$ with,
+To deal with this example, now $\calF=\calG=\cl_2[0,1]$, and $S: f \mapsto f'$ with,
 \begin{gather*}
-\norm[\cf]{f} = \left[\int_0^1 \left\{\abs{f(x)}^2 + \abs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \norm[\cg]{f} = \left[\int_0^1 \abs{f(x)}^2 \, \dif x \right]^{1/2}, \\
-u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \integers,\\
+\DHJRnorm[\calF]{f} = \left[\int_0^1 \left\{\DHJRabs{f(x)}^2 + \DHJRabs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \DHJRnorm[\calG]{f} = \left[\int_0^1 \DHJRabs{f(x)}^2 \, \dif x \right]^{1/2}, \\
+u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \bbZ,\\
 \pin=\pout=2,\quad q=\infty.
@@
 
-Like in the previous example, the index set $\ci=\integers=\{0,1,-1,2,-2,\ldots\}$ has the following ordering
+Like in the previous example, the index set $\ci=\bbZ=\{0,1,-1,2,-2,\ldots\}$ has the following ordering
 \begin{gather*}
-i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\naturals,\\
-n_0=0,\quad n_k=2^k, \qquad k\in\naturals.
+i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\bbN,\\
+n_0=0,\quad n_k=2^k, \qquad k\in\bbN.
 \end{gather*}
@@
 \begin{equation*}
-B_n(x)=-\frac{n!}{(2\pi\sqrt{-1})^n}\sum_{k\in\integers\setminus\{0\}}\frac{\me^{2\pi\sqrt{-1}kx}}{k^n}\Longrightarrow
+B_n(x)=-\frac{n!}{(2\pi\sqrt{-1})^n}\sum_{k\in\bbZ\setminus\{0\}}\frac{\me^{2\pi\sqrt{-1}kx}}{k^n}\Longrightarrow
 \left\{\begin{array}{l}
 \widehat{B_n}_0=0 \\
-\widehat{B_n}_{i_j}=-\frac{n!\sqrt{1+4 \pi^2 i_j^2}}{(2\pi\sqrt{-1}i_j)^n},\quad i_j\in\integers\setminus\{0\}
+\widehat{B_n}_{i_j}=-\frac{n!\sqrt{1+4 \pi^2 i_j^2}}{(2\pi\sqrt{-1}i_j)^n},\quad i_j\in\bbZ\setminus\{0\}
 \end{array}\right.
@@
 \begin{equation*}
-\norm[\cg]{S(B_n(x))}=n\norm[\cg]{B_{n-1}(x)}=n!\sqrt{\frac{\abs{B_{2(n-1)}}}{[2(n-1)]!}}
+\DHJRnorm[\calG]{S(B_n(x))}=n\DHJRnorm[\calG]{B_{n-1}(x)}=n!\sqrt{\frac{\DHJRabs{B_{2(n-1)}}}{[2(n-1)]!}}
 \end{equation*}
@@
 \begin{equation}\label{bound}
-\frac{n!}{\sqrt{2}\pi^n}j^{-n} \le \abs{\lambda_{i_j}\widehat{B_n}_{i_j}} \le \frac{n!2^n}{\pi^n}j^{-n},\quad j\in\naturals\setminus\{1\}
-\end{equation}
-then $C_{\up}=2^{n+\frac{1}{2}}C_{\lo}=\frac{n!2^n}{\pi^n}$. Thus, as shown in the example example at the beginning of this section we can take
+\frac{n!}{\sqrt{2}\pi^n}j^{-n} \le \DHJRabs{\lambda_{i_j}\widehat{B_n}_{i_j}} \le \frac{n!2^n}{\pi^n}j^{-n},\quad j\in\bbN\setminus\{1\}
+\end{equation}
+then $C_{\textup{up}}=2^{n+\frac{1}{2}}C_{\textup{lo}}=\frac{n!2^n}{\pi^n}$. Thus, as shown in the example example at the beginning of this section we can take
 \begin{equation*}
@@
 There is still one thing to check because $j=1$ was not taken into account in the inequality (\ref{bound}).
-However, see that $\sigma_1(f) \ge C_{\lo}\left(\frac{5}{36}\right)^{n-\frac{1}{2}}$ what means that the $\gamma_r=s_1s_2^{-r}$ found satisfies our needs.
+However, see that $\sigma_1(f) \ge C_{\textup{lo}}\left(\frac{5}{36}\right)^{n-\frac{1}{2}}$ what means that the $\gamma_r=s_1s_2^{-r}$ found satisfies our needs.
 
@@
   \hline
-  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(B_5(x))}-\norm[\cg]{A_{n_{k^*}}(B_5(x))}$ \\
+  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\DHJRnorm[\calG]{S(B_5(x))}-\DHJRnorm[\calG]{A_{n_{k^*}}(B_5(x))}$ \\
   \hline
@@
   \hline
-  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\norm[\cg]{S(B_{10}(x))}-\norm[\cg]{A_{n_{k^*}}(B_{10}(x))}$ \\
+  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\DHJRnorm[\calG]{S(B_{10}(x))}-\DHJRnorm[\calG]{A_{n_{k^*}}(B_{10}(x))}$ \\
   \hline
@@
 
-\begin{rem}
+\begin{remark}
 MATLAB's machine epsilon is $2.2204\cdot10^{-16}$.
-\end{rem}
+\end{remark}
 \fi
@@
 We do not expect the series coefficients of the solution $S(f)$, to decay monotonically.
-The sequence $\vn$ is used to average finite sequences of Fourier coefficients into groups to smooth the peaks we could encounter if we take these coefficients one by one.
+The sequence $\bsn$ is used to average finite sequences of Fourier coefficients into groups to smooth the peaks we could encounter if we take these coefficients one by one.
 Flattening the peaks is a must to fit functions into the cone.
@@
 \begin{equation*}
-N_{\opt}(f,\varepsilon)=\min\left\{n\in\naturals:\,\norm[2]{\left(\lambda_{i_j} \hf_{i_j} \right)_{j\ge n+1}} \le \varepsilon \right\}
+N_{\opt}(f,\varepsilon)=\min\left\{n\in\bbN:\,\DHJRnorm[2]{\left(\lambda_{i_j} \widehat{f}_{i_j} \right)_{j\ge n+1}} \le \varepsilon \right\}
 \end{equation*}
@@
 \begin{equation} \label{nearoptdef}
-\sup_{\varepsilon > 0 } \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty 
+\sup_{\varepsilon > 0 } \frac{\textup{cost}(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty 
 \end{equation}
@@
 \[
-\sup_{\varepsilon > 0 } [\cost(A,f;\varepsilon)- N_{\opt}(f,\varepsilon)] <\infty.
+\sup_{\varepsilon > 0 } [\textup{cost}(A,f;\varepsilon)- N_{\opt}(f,\varepsilon)] <\infty.
 \]
@@
 \begin{proof}
-Given $f \in \cc$ and $\varepsilon$, denote $n^*= N_{\opt}(f,\varepsilon)$. Let 
+Given $f \in \calC$ and $\varepsilon$, denote $n^*= N_{\opt}(f,\varepsilon)$. Let 
 \[n_{k^*-r-1} < n^{*}  \le n_{k^*-r} \le n_{k^*},\]
@@
 Thus by \eqref{sumdef}, we obtain
-\[\sigma_{k^*-r+1}(f) = \norm[2]{ \left(\lambda_{i_j} \hf_{i_j} \right)_{j=n_{k^*-r}+1}^{n_{k^*-r+1}}}
- \le \norm[2]{ \left(\lambda_{i_j} \hf_{i_j} \right)_{j=n^*}^{\infty}} \le \varepsilon.\]
+\[\sigma_{k^*-r+1}(f) = \DHJRnorm[2]{ \left(\lambda_{i_j} \widehat{f}_{i_j} \right)_{j=n_{k^*-r}+1}^{n_{k^*-r+1}}}
+ \le \DHJRnorm[2]{ \left(\lambda_{i_j} \widehat{f}_{i_j} \right)_{j=n^*}^{\infty}} \le \varepsilon.\]
 By the cone condition \eqref{decayconedef} , we have 
 \[\sigma_{k^*-r+m}(f) \le \gamma_{m-1}\sigma_{k^*-r+1}(f) \le\gamma_{m-1} \cdot \varepsilon.\]
-Choose $m$ such that $\gamma_{m-1} \le \frac{1}{\norm[2]{\vgamma}},$
+Choose $m$ such that $\gamma_{m-1} \le \frac{1}{\DHJRnorm[2]{\vgamma}},$
 thus we obtain
-\[\sigma_{k^*-r+m}(f) \le\gamma_{m-1} \cdot \varepsilon \le \frac{\varepsilon}{\norm[2]{\vgamma}}.\]
+\[\sigma_{k^*-r+m}(f) \le\gamma_{m-1} \cdot \varepsilon \le \frac{\varepsilon}{\DHJRnorm[2]{\vgamma}}.\]
 Suppose $\gamma_r$ decays geometrically, $n_k$ increases geometrically $n_k = n_0 2^k $, we have
-\[\frac{\cost(\tA,f;\varepsilon)}{N_{\opt}(f,\varepsilon)} \le 
+\[\frac{\textup{cost}(\widetilde{A},f;\varepsilon)}{N_{\opt}(f,\varepsilon)} \le 
 \frac{n_{k^*-r+m}}{n_{k^*-r-1}} = \frac{n_0 2^{k^*-r+m}}{n_0 2^{k^*-r-1}}
@@
 \begin{align*}\
-\gamma_{m-1} \le \frac{1}{\norm[2]{\vgamma}} 
+\gamma_{m-1} \le \frac{1}{\DHJRnorm[2]{\vgamma}} 
 & \Longleftrightarrow C_1C_2^{-m+1} \le \frac{\sqrt{C_2^2-1}}{C_1} \\
@@
 Hence,
- \[\frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} 
- \le 2^{m+1} < 2^{3+\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}} \Longrightarrow \sup_{f,\varepsilon} \frac{\cost(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty.\]
+ \[\frac{\textup{cost}(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} 
+ \le 2^{m+1} < 2^{3+\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}} \Longrightarrow \sup_{f,\varepsilon} \frac{\textup{cost}(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty.\]
 
@@
 \begin{align*}
-\cost(\tA,f;\varepsilon)-N_{\opt}(f,\varepsilon) & \le 
+\textup{cost}(\widetilde{A},f;\varepsilon)-N_{\opt}(f,\varepsilon) & \le 
 n_{k^*-r+m}-n_{k^*-r-1} \\ & = (n_0 +2(k^*-r+m))-(n_0+2(k^*-r-1))\\
@@
 \begin{align*}
-\cost(\tA,f;\varepsilon)-N_{\opt}(f,\varepsilon) 
+\textup{cost}(\widetilde{A},f;\varepsilon)-N_{\opt}(f,\varepsilon) 
 & = 2(m+1) \\
@@
 \Longrightarrow &
-\sup_{f,\varepsilon} \left[\cost(A,f;\varepsilon) -N_{\opt}(f,\varepsilon) \right]< \infty
+\sup_{f,\varepsilon} \left[\textup{cost}(A,f;\varepsilon) -N_{\opt}(f,\varepsilon) \right]< \infty
 \end{align*}

### 2018-08-14 AutoAlgorithmLinearFunctionalDataVerC.tex
tweaked notation at beginning

@@
 
-\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i=1}^\infty$, let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i=1}^\infty$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
+\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i \in \bbN}$, let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i\in \bbN}$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
 \begin{subequations}\label{probDef}

### 2018-08-17 AutoAlgorithmLinearFunctionalDataVerC.tex
Add abstract and modify numerical example

@@
 \abstract{}
+Automatic algorithms attempt to provide approximate solutions that differ from exact solutions by no more than a user-specified error tolerance.
+This paper describes an automatic adaptive algorithm for approximating the solution to a general linear problem on Hilbert spaces.
+The algorithm employs continuous linear functionals of the input function, specifically Fourier coefficients.
+We assume that the Fourier coefficients of the solution to be approximated decay sufficiently fast, but do not require the decay rate to be known a priori.
+We also assume that the Fourier coefficients decay steadily, although not necessarily monotonically.
+Under these assumptions, our adaptive algorithm is shown to achieve an approximation to the function satisfying the desired error tolerance, without prior knowledge of the norm of the function to be approximated.
+Moreover, the computational cost of our algorithm is shown to be essentially no worse than that of the optimal algorithm.
+We also proivde a numerical experiment to illustrate our algorithm.
 
@@
 \end{align*}
-We construct a function by choosing its Fourier coefficients $\widehat{f}$ to be normal distributed \textbf{What distribution (mean, standard deviation)?
-How many Fourier coefficients are chosen to construct the function?}.
-Let $d=3, a= 2, b=\frac{1}{2},$ and $\varepsilon = 0.1.$ Based on our algorithm, we obtain $ n_{j^\dagger} = 1024.$ Using that, we can obtain the approximated solution and error in Figure \ref{solfig}.
-Based on Figure \ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.
+We construct a function by choosing its Fourier coefficients $\widehat{f} \sim  \mathcal{N}(0,1)$ with size $68931$.  Let $ a= 2$ and  $b=\frac{1}{2}$ and 
+ $\bsn = \{0, 2^{3+1}, \ldots, 2^{3+k} \},$ where $k =\lfloor \log_2^{68931} \rfloor=13$.
+Thus, by \eqref{sumdef} we can obtain $\sigma_j(f), \ j = 1,\ldots, 13.$  Given $\varepsilon$, we can derive the error bound and find the $n_{j^\dagger}$ where
+ \[j^{\dagger} = \min \left\{j : \frac{ab\sigma_j(f)}{\sqrt{1-b^2}}  \le \varepsilon, \ 1 \le j \le 13. \right\}\]
+
+ \begin{figure}[ht]
+ 	\centering
+ 		\includegraphics[width =7.5 cm]{ProgramsImages/SimFourCoefErr.eps}
+ 	\caption{Sample size, error tolerance $\varepsilon$ and ratio \label{errfig}} % 
+ \end{figure}
+
+Fig.
+\ref{errfig} shows the number of sample size needed when we choose 10 different error tolerance from $10^{-1}$ to $10^{1}$.
+If we consider $\varepsilon = 0.1$, $ n_{j^\dagger} = 1024$ can reach the error tolerance.
+Using that, we can obtain the approximated solution and error in Figure \ref{solfig}.
+Based on Fig.
+\ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.
 This shows our algorithm works.
@@
 The above is the approximation of the input function $f$.
-Notice that, the errors in Figure \ref{inpfig}(b) are much smaller than the errors in Figure \ref{solfig}(b).
+Notice that, the errors in Fig.
+\ref{inpfig}(b) are much smaller than the errors in Fig.
+\ref{solfig}(b).
 

### 2018-08-24 ProgramsImages/sim_FourCoef.m
Update figures

@@ -16,16 +16,22 @@ n_app = 2^10; %number of points to use for approximating L_inf norm
 % Assume that
 %  x is nX x d
 %  k is nK x d
-u_wt_fun = @(k) prod(2.^((k~=0)/2) ./ max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
+denom_wt_fun = @(k) prod(max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
+pow_2_wt_fun = @(k) 2.^(sum(k~=0,2)/2); %nK x 1
+u_wt_fun = @(k) pow_2_wt_fun(k) ./ denom_wt_fun(k); %nK x 1
 v_wt_fun = @(k) -sign(k(:,1)) .* 2.^(sum(k~=0,2)/2); %nK x 1
-basisName = 'CompExp'; %complex Exponential
+%basisName = 'CompExp'; %complex Exponential
 % inp_basis_fun = @(k,x) exp((2*pi*sqrt(-1))* (x * k'))./u_wt_fun(k)'; %nX x nK
 % out_basis_fun = @(k,x) -exp((2*pi*sqrt(-1))* (x * k')); %nX x nK
+basisName = 'CosineSine'; %cosine and sine
 inp_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
-   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* u_wt_fun(k)'; %nX x nK
-out_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
-   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* v_wt_fun(k)'; %nX x nK
-lambda = @(k) (2*pi)*(abs(k(:,1)).*u_wt_fun(k)); %nK x 1;
+   + (reshape(k',1,d,size(k,1)) < 0)*(pi/2)),2)) .* u_wt_fun(k)'; %nX x nK
+out_basis_fun = @(k,x) sin((2*pi)* (x(:,1) .* k(:,1)') ...
+   + (k(:,1)' < 0)*(pi/2)) .* ...
+   squeeze(prod(cos((2*pi)* (x(:,2:d) .* reshape(k(:,2:d)',1,d-1,size(k,1))) ...
[…]

### 2018-08-24 ProgramsImages/sim_FourCoef_plot_results.m

@@ -16,7 +16,7 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
 ylabel({'Sample size \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
@@ -24,10 +24,10 @@ tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-[~,leg_icons] = legend(h, ...
-   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-   }, ...
-   'box','off','location','north','orientation','horizontal');
+% [~,leg_icons] = legend(h, ...
+%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
+%    }, ...
+%    'box','off','location','north','orientation','horizontal');
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 print -depsc SimFourCoefErr.eps

### 2018-08-24 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX

@@
 
+\allowdisplaybreaks[4]
+
 \begin{document}
@@
 \author{Yuhan Ding \and Fred J. Hickernell \and Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
-\institute{Yuhan Ding \at MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612 \email{}
+\institute{Yuhan Ding \at MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612 \email{yding@misericordia.edu}
 \and
@@
 \and Llu\'{\i}s Antoni Jim\'{e}nez Rugama \at
-Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{}}
+Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{ljimene1@hawk.iit.edu}}
 
@@
 
-\abstract{}
-Automatic algorithms attempt to provide approximate solutions that differ from exact solutions by no more than a user-specified error tolerance.
+\abstract{Automatic algorithms attempt to provide approximate solutions that differ from exact solutions by no more than a user-specified error tolerance.
 This paper describes an automatic adaptive algorithm for approximating the solution to a general linear problem on Hilbert spaces.
@@
 Moreover, the computational cost of our algorithm is shown to be essentially no worse than that of the optimal algorithm.
-We also proivde a numerical experiment to illustrate our algorithm.
+We also provide a numerical experiment to illustrate our algorithm.}
 
@@
 The proposed algorithm produces an approximation with guaranteed accuracy.
-Moreover, we demonstrate that  computational cost of our algorithm is essentially no worse than that of the best possible algorithm.
+Moreover, we demonstrate that {\color{red} the} computational cost of our algorithm is essentially no worse than that of the best possible algorithm.
 Our adaptive algorithm is defined on a \emph{cone} of input functions.
@@
 This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.
-We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$, Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
+We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$.
+Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
+{\color{red} The embedding operator is not considered either, right ($\lambda_i=1$)?
+When do these two basis exist?
+For instance, can we freely choose from exponential to Walsh bases?}
 
-\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ to within some error tolerance for all inputs in $\calH$:
+\subsection{Solvability}  Let $\calH$ be any subset {\color{red}(any subset?
+But $S$ will linearly defined over $\calH$?)} of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ to within some error tolerance for all inputs in $\calH$:
 \begin{multline} \label{adapErrCrit}
@@
 	\begin{align*}
-	f &= \sum_{k \in \bbZ} \widehat{f}(k) \widehat{u}_{k}  = \sum_{i=1}^n \widehat{f}_i u_i, 
-	& S(f) & = \sum_{k \in \bbZ} \widehat{f}(k) \widehat{\lambda}_k \widehat{v}_k = \sum_{i=1}^n \widehat{f}_i \lambda_i \widehat{v}_i, \\
+	f &= \sum_{k \in \bbZ} \widehat{f}(k) \widehat{u}_{k}  = \sum_{i \in \bbN} \widehat{f}_i u_i, 
+	& S(f) & = \sum_{k \in \bbZ} \widehat{f}(k) \widehat{\lambda}_k \widehat{v}_k = \sum_{i \in \bbN} \widehat{f}_i \lambda_i v_i, \\
 	\widehat{v}_{k} (x) &:= \begin{cases} 1, & k = 0, \\
@@
 \begin{align*}
-f &= \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) u_{\bsk} (\bsx), \\
+\allowdisplaybreaks
+f &= \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \widehat{u}_{\bsk} = \sum_{i \in \bbN} \widehat{f}_i u_i , \\
 u_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j k_j)},  \\ 
-S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \lambda_{\bsk} v_{\bsk} (\bsx), \\
+S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \lambda_{\bsk} v_{\bsk} (\bsx)
+= \sum_{i \in \bbN} \widehat{f}_i \lambda_i v_i, \\ 
 v_{\bsk}(\bsx) & : =  -\textup{sign}(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
@@
 \end{align*}
-We construct a function by choosing its Fourier coefficients $\widehat{f} \sim  \mathcal{N}(0,1)$ with size $68931$.  Let $ a= 2$ and  $b=\frac{1}{2}$ and 
- $\bsn = \{0, 2^{3+1}, \ldots, 2^{3+k} \},$ where $k =\lfloor \log_2^{68931} \rfloor=13$.
-Thus, by \eqref{sumdef} we can obtain $\sigma_j(f), \ j = 1,\ldots, 13.$  Given $\varepsilon$, we can derive the error bound and find the $n_{j^\dagger}$ where
- \[j^{\dagger} = \min \left\{j : \frac{ab\sigma_j(f)}{\sqrt{1-b^2}}  \le \varepsilon, \ 1 \le j \le 13. \right\}\]
+where $\gamma = [2^0, 2^{-1},\ldots, 2^{-d+1}].$
+
+\yuhannote{According to code, some expression should be as follows:}
+\begin{align*}
+u_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max^8(1,\gamma_j k_j)},  \\ 
+\lambda_{\bsk} &:= 2 \pi \DHJRabs{k_1}\frac{2^{(1-\delta_{k_j,0})/2}}{\prod_{j=1}^d\max^8(1,\gamma_j k_j)}.\\
+\end{align*}
+
+\yuhannote{$v_{\bsk}(\bsx) $ still doesn't match the code}
+\begin{align*}
+    v_{\bsk}(\bsx) & : =  -\textup{sign}(k_1)  \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
+& \qquad \qquad \times \prod_{j=2}^d
+\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) 
+\end{align*}
+
+We construct a function by choosing its Fourier coefficients $\widehat{f}_i \overset{\text{IID}}{\sim}  \mathcal{N}(0,1)$ for  $i = 1, \ldots, 68931$, and $\widehat{f}_i = 0$ otherwise.
+Let $ a= 2$ and  $b=\frac{1}{2}$ and
+ choose $\bsn = \{0, 2^{3+1}, \ldots, 2^{3+k}, \ldots \}.$
+ To  obtain $\sigma_j(f), \ j \in \bbN$ by \eqref{sumdef},
+ we need to sort $\lambda_i$ in the descending order and get corresponding $\widehat{f}_i$ and $\widehat{v}_i$, which is similar to the Example 1.
+To implement it efficiently, we use another vector to keep the index of the descending order of $\lambda_i$.
+Thus, we can obtain the correct
+ $\lambda_i$,  $\widehat{f}_i$, and $v_i$ according to $\bsn_k$.
+Thus, we can add them together to get $\sigma_j(f)$.
+Given $\varepsilon$, we can derive the error bound and find the $n_{j^\dagger}$ where
+ \[j^{\dagger} = \min \left\{j \in \bbN : \frac{ab\sigma_j(f)}{\sqrt{1-b^2}}  \le \varepsilon. \right\}\]
 
@@
  		\includegraphics[width =7.5 cm]{ProgramsImages/SimFourCoefErr.eps}
- 	\caption{Sample size, error tolerance $\varepsilon$ and ratio \label{errfig}} % 
+ 	\caption{Sample size $n$, error tolerance $\varepsilon$ and ratio \label{errfig}} % 
  \end{figure}
@@
 	\end{tabular}
-	\caption{(a) The approximation of the first partial derivative of $f$
-		(b) The error of the approximation 
+	\caption{For $\varepsilon = 0.1$:  (a) The approximation of the first partial derivative of $f$; 
+		(b) The error of the approximation.
 		\label{solfig}} % 
 \end{figure}
-
-\begin{figure}[ht]
-	\centering
-	\begin{tabular}{cc}
-		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectInpFunAppx.eps}& 
-		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectInpFunErr.eps}
-		\\ (a) & (b)
-	\end{tabular}
-	\caption{(a) The approximation of the input function $f$
-		(b) The error of the approximation 
-		\label{inpfig}} % 
-\end{figure}
-
-Actually, we can also use these 1024 Fourier coefficients to approximate the input function.
-The above is the approximation of the input function $f$.
-Notice that, the errors in Fig.
-\ref{inpfig}(b) are much smaller than the errors in Fig.
-\ref{solfig}(b).
-
-%\subsection{Examples: Approximating the divergence of a vector field}
-%
-%In this case, $\calF=\{f:\reals^n\mapsto\reals^m,\, f\in C^1(\Omega)\}$ and $\calG=\{g:\reals^n\mapsto\reals,\, g\in C^0(\Omega)\}$ and $S: f\mapsto \nabla\cdot f=\sum_{j=1}^{m}\partial_{x_j}f_j$.
-%
-%\begin{gather*}
-%\DHJRnorm[\calF]{f} =\left[\int_\Omega \sum_{j=1}^{m}\DHJRabs{f_j(x)}^2+\sum_{j=1}^{m}\DHJRabs{f'_j(x)}^2 \, \dif x \right]^{1/2},\\
-%\DHJRnorm[\calG]{g} = \left[\int_\Omega \DHJRabs{g(x)}^2 \, \dif x \right]^{1/2}, \\
-%u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} <i,x>}}{\sqrt{mV(\omega)+4\pi<i,i>}}, \\
-%v_i(x) = \me^{2 \pi \sqrt{-1} <i,x>},\\
-% \lambda_i=\frac{2\pi\sqrt{-1}\sum_{j=1}^{m}i_j}{\sqrt{mV(\omega)+4\pi<i,i>}}, \qquad i \in \bbZ^m,\\
-%\pin=\pout=2,\quad q=\infty.
-%\end{gather*}
 
@@
 \end{document}
-
-\begin{remark}
-For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, $\textup{cost}(\widetilde{A},\rho,\varepsilon) \le n_{j^*}$, where $j^*$ satisfies the following upper bound:
-\[
-j^* \le \min \left \{j \in \bbN : \rho^2 \le \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\textup{up}}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right]\right\}.
-\]
-\end{remark}
-
-\begin{proof}
-First, we have a rough upper bound on $\textup{cost}(\widetilde{A},\rho,\varepsilon)$ in the proof of  Theorem  \ref{thm:compcost} by finding the smallest $j$ violating the following inequality:
-\begin{equation*}
-\rho \ge \DHJRnorm[\calF]{f} \ge \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
-\end{equation*}
-If we consider $\lambda_{i}$ is bounded above
-\begin{equation} \label{lambdaDecI}
-\lambda_i \le C_{\textup{up}} i^{1-p}, \quad   i \in \bbN,
-\end{equation}
-where $p > 1$, we obtain
-\begin{align*}
-\rho & > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}} \\
-& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}(n_{j-1}+1)^{1-p}} \qquad \text{by \eqref{lambdaDecI}} \\
-& > \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}n_{j-1}^{1-p}} \\
-& \ge \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}(2^{j-1}n_0)^{1-p}} \qquad \text{by \eqref{geonj}} \\
-& = \frac{\varepsilon\sqrt{1 - b^2}}{ab C_{\textup{up}}n_0^{1-p} 2^{(j-1)(1-p)}}
-\end{align*}
-Thus, one upper bound on $j^*$ is the smallest $j$ violating the above inequality:
-\[
-j^* \le \min \left \{j \in \bbN :  
-j \ge \frac{\log\left[\frac{\varepsilon \sqrt{1-b^2}}{\rho ab C_{\textup{up}}n_0^{1-p}}\right]}{(1-p)\log 2}+ 1\right\}
-\]
-
-We could also obtain another upper bound similar to the tighter upper bound in Theorem \ref{thm:compcost}.  
-The tighter cost is the smallest $j$ that violates the following inequality
-\begin{equation*}
-\rho^2 > \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
-\end{equation*}
-From \eqref{lambdaDecI}, we can obtain for any $k=1, \ldots,j-1$
-\[\lambda_{n_{k-1}+1} \le C_{\textup{up}}(n_{k-1}+1)^{1-p} 
-<  C_{\textup{up}}(n_{k-1})^{1-p} < C_{\textup{up}}n_0^{1-p}.\]
-Thus, we have 
-\begin{align*}
-\rho^2 &> \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]\\
-& >  \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}(C_{\textup{up}}n_0^{1-p})^2} + \frac{1}{(C_{\textup{up}}(n_{j-1})^{1-p} )^2}\right] \\
-& = \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}C_{\textup{up}}^2n_0^{2(1-p)}} + \frac{1}{C^2_{\textup{up}}(2^{j-1}n_0)^{2(1-p)}}\right] \qquad \text{by \eqref{geonj}}\\
-&  =\frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\textup{up}}^2n_0^{2(1-p)}} \left[ \frac{1}{a^2b^{2j}}\sum_{k=1}^{j-1} b^{2k }+ \frac{1}{2^{2(j-1)(1-p)}}\right] \\
-& > \frac{\varepsilon^2(1 - b^2)}{a^2b^2C_{\textup{up}}^2n_0^{2(1-p)}} \left[ \frac{1-b^2}{a^2b^{2(j-1)}}+ \frac{1}{2^{2(j-1)(1-p)}}\right] .
-\end{align*}
-Hence, any $j$ that violates the above inequality, must satisfy $j \ge j^*$.
-\end{proof}
-
-/fi
-\iffalse
-\subsection{The embedding of $f(x)=\frac{(b^2-1)}{b^2+1-2b\cos(2\pi x)}$}
-
-In our example, consider $\calF=\calG=\cl_2[0,1]$, and $S: f \mapsto f$ the embedding operator with:
-\begin{gather*}
-\DHJRnorm[\calF]{f} = \DHJRnorm[\calG]{f} = \left[\int_0^1 \DHJRabs{f(x)}^2 \, \dif x \right]^{1/2}, \\
-u_{i}(x) = v_i(x) = \me^{2 \pi \sqrt{-1} i x},\quad \lambda_i=1, \qquad i \in \bbZ,\\
-\pin=\pout=2,\quad q=\infty.
-\end{gather*}
-
-For our index set $\ci=\bbZ=\{0,1,-1,2,-2,\ldots\}$,
-\begin{gather*}
-i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\bbN,\\
-n_0=0,\quad n_k=2k+1, \qquad k\in\bbN.
-\end{gather*}
-
-The Fourier coefficients of this function can be easily found:
-\begin{align*}
-f(x)&=\frac{b^2-1}{b^2+1-2b\cos(2\pi x)}\\
-&=\frac{1-b^{-2}+b^{-1}(\me^{-2\pi\sqrt{-1}x}-\me^{-2\pi\sqrt{-1}x})}{1+b^{-2}-b^{-1}(\me^{2\pi\sqrt{-1}x}+\me^{-2\pi\sqrt{-1}x})}\\
-&=\frac{(1-b^{-1}\me^{-2\pi\sqrt{-1}x})+(1-b^{-1}\me^{2\pi\sqrt{-1}x})b^{-1}\me^{-2\pi\sqrt{-1}x}}{(1-b^{-1}\me^{2\pi\sqrt{-1}x})(1-b^{-1}\me^{-2\pi\sqrt{-1}x})}\\
-&=\frac{1}{1-b^{-1}\me^{2\pi\sqrt{-1}x}}+\frac{b^{-1}\me^{-2\pi\sqrt{-1}x}}{1-b^{-1}\me^{-2\pi\sqrt{-1}x}}\\
-&=\sum_{k\in\bbN_0}\left(b^{-1}\me^{2\pi\sqrt{-1}x}\right)^k+\sum_{k\in\bbN}\left(b^{-1}\me^{-2\pi\sqrt{-1}x}\right)^k\\
-&=\sum_{k\in\bbZ}b^{-\DHJRabs{k}}\me^{2\pi\sqrt{-1}kx}\Longrightarrow\widehat{f}_{i_j}=b^{-\DHJRabs{i_j}}
-\end{align*}
-
-Because we are interested in seeing how far the approximation is from the real solution, the norm of the exact solution has to be found.
-Knowing the Fourier coefficients leads us to an easy way to calculate it:
-\begin{align*}
-\DHJRnorm[\calG]{S(f)}&=\left(\sum_{j\in\bbZ}\lambda_{i_j}^2\widehat{f}_{i_j}^2\right)^{\frac{1}{2}} =\left(1+2\sum_{k\in\bbN}b^{-2k}\right)^{\frac{1}{2}}=\left(\frac{b^2+1}{b^2-1}\right)^{\frac{1}{2}}
-\end{align*}
-
-We can also give the sums of coefficients,
-\begin{align*}
-&\sigma_1(f)=\sqrt{1+2b^{-2}}\\
-&\sigma_k(f)=\sqrt{2}b^{-k}, \qquad k \in\bbN\setminus\{1\}.
-\end{align*}
-Recalling the alternative definition of the cone in (\ref{decayconedef}), with these sums, $f\in\calC$ for $\gamma_r=b^{-r}$ since
-\begin{equation*}
-\sigma_k(f) \le \min_{1 \le i <k}\{\gamma_i\sigma_{k-i}(f)\}=\min\left\{1 \; , \; \sqrt{1+\frac{b^2}{2}} \right\}\sigma_k(f)
-\end{equation*}
-
-In this case, $\DHJRnorm[\pout]{\bgamma}=\frac{1}{\sqrt{b^2-1}}$.
-If we use our Algorithm \ref{algo2}, we have to check first whether $\sqrt{\frac{b^2+2}{b^4-b^2}}\le\varepsilon$.
-If this inequality states, then $k^*=1$.
-If not,
-\begin{equation*}
-k^*=\min\left\{k\in\bbN\setminus\{1\}:\frac{1}{2\log(b)}\log\left(\frac{2}{(b^2-1)\varepsilon^2}\right) \le k \right\}
-\end{equation*}
-
-For a numerical application, set $b=3$ and find below a table of results for this example,
-
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-  \hline
-  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\DHJRnorm[\calG]{S(f)}-\DHJRnorm[\calG]{A_{n_{k^*}}(f)}$ \\
-  \hline
-  $1$ & $1$ & $3$ & $1.2492\cdot10^{-2}$ \\
-  $10^{-1}$ & $2$ & $5$ & $1.3811\cdot10^{-3}$ \\
-  $10^{-2}$ & $4$ & $9$ & $1.7041\cdot10^{-5}$ \\
-  $10^{-3}$ & $6$ & $13$ & $2.1038\cdot10^{-7}$ \\
-  $10^{-4}$ & $8$ & $17$ & $2.5973\cdot10^{-9}$ \\
-  $10^{-5}$ & $10$ & $21$ & $3.2065\cdot10^{-11}$ \\
-  $10^{-6}$ & $12$ & $25$ & $3.9591\cdot10^{-13}$ \\
-  $10^{-7}$ & $15$ & $31$ & $4.4409\cdot10^{-16}$ \\
-  \hline
-\end{tabular}
-\end{center}
-
-\subsection{Derivation of the Bernoulli polynomials}
-
-The properties we will use for these particular polynomials can be found in \cite{AbrSte64}: derivatives, explicit Fourier coefficients, etc.
-To deal with this example, now $\calF=\calG=\cl_2[0,1]$, and $S: f \mapsto f'$ with,
-\begin{gather*}
-\DHJRnorm[\calF]{f} = \left[\int_0^1 \left\{\DHJRabs{f(x)}^2 + \DHJRabs{f'(x)}^2\right\}\, \dif x\right]^{1/2}, \quad \DHJRnorm[\calG]{f} = \left[\int_0^1 \DHJRabs{f(x)}^2 \, \dif x \right]^{1/2}, \\
-u_{i}(x) = \frac{\me^{2 \pi \sqrt{-1} i x}}{\sqrt{1+4 \pi^2 i^2}}, \quad v_i(x) = \me^{2 \pi \sqrt{-1} i x}, \quad \lambda_i=\frac{2 \pi \sqrt{-1} i}{\sqrt{1+4 \pi^2 i^2}}, \qquad i \in \bbZ,\\
-\pin=\pout=2,\quad q=\infty.
-\end{gather*}
-
-Like in the previous example, the index set $\ci=\bbZ=\{0,1,-1,2,-2,\ldots\}$ has the following ordering
-\begin{gather*}
-i_j=(-1)^{j}\left\lfloor\frac{j}{2}\right\rfloor,\qquad j\in\bbN,\\
-n_0=0,\quad n_k=2^k, \qquad k\in\bbN.
-\end{gather*}
-
-For this case,
-\begin{equation*}
-B_n(x)=-\frac{n!}{(2\pi\sqrt{-1})^n}\sum_{k\in\bbZ\setminus\{0\}}\frac{\me^{2\pi\sqrt{-1}kx}}{k^n}\Longrightarrow
-\left\{\begin{array}{l}
-\widehat{B_n}_0=0 \\
-\widehat{B_n}_{i_j}=-\frac{n!\sqrt{1+4 \pi^2 i_j^2}}{(2\pi\sqrt{-1}i_j)^n},\quad i_j\in\bbZ\setminus\{0\}
-\end{array}\right.
-\end{equation*}
-
-Using that $B'_n(x)=nB_{n-1}(x)$ and $\int_0^1B_n(t)B_m(t)\dif t=(-1)^{n-1}\frac{m!n!}{(m+n)!}B_{n+m}$, the real solution comes automatically,
-\begin{equation*}
-\DHJRnorm[\calG]{S(B_n(x))}=n\DHJRnorm[\calG]{B_{n-1}(x)}=n!\sqrt{\frac{\DHJRabs{B_{2(n-1)}}}{[2(n-1)]!}}
-\end{equation*}
-where $B_n=B_n(0)$ are the Bernoulli numbers.
-
-If we consider $\gamma_r=s_1s_2^{-r}$ and that
-\begin{equation}\label{bound}
-\frac{n!}{\sqrt{2}\pi^n}j^{-n} \le \DHJRabs{\lambda_{i_j}\widehat{B_n}_{i_j}} \le \frac{n!2^n}{\pi^n}j^{-n},\quad j\in\bbN\setminus\{1\}
-\end{equation}
-then $C_{\textup{up}}=2^{n+\frac{1}{2}}C_{\textup{lo}}=\frac{n!2^n}{\pi^n}$. Thus, as shown in the example example at the beginning of this section we can take
-\begin{equation*}
-s_1=2\times11^{n-\frac{1}{2}},\quad s_2=2^{n-\frac{1}{2}}
-\end{equation*}
-There is still one thing to check because $j=1$ was not taken into account in the inequality (\ref{bound}).
-However, see that $\sigma_1(f) \ge C_{\textup{lo}}\left(\frac{5}{36}\right)^{n-\frac{1}{2}}$ what means that the $\gamma_r=s_1s_2^{-r}$ found satisfies our needs.
-
-For a numerical application, find below the results for the case $n=5$ and $n=10$,
-
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-  \hline
-  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-  \multicolumn{4}{|c|}{$B_5(x)=x^5-\frac{5}{2}x^4+\frac{5}{3}x^3-\frac{1}{6}x$} \\
-  \hline
-  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\DHJRnorm[\calG]{S(B_5(x))}-\DHJRnorm[\calG]{A_{n_{k^*}}(B_5(x))}$ \\
-  \hline
-  $1$ & $5$ & $32$ & $2.9439\cdot10^{-11}$ \\
-  $10^{-1}$ & $6$ & $64$ & $2.2703\cdot10^{-13}$ \\
-  $10^{-2}$ & $7$ & $128$ & $1.8735\cdot10^{-15}$ \\
-  $10^{-3}$ & $7$ & $128$ & $1.8735\cdot10^{-15}$ \\
-  $10^{-4}$ & $8$ & $256$ & $1.1102\cdot10^{-16}$ \\
-  $10^{-5}$ & $9$ & $512$ & $9.7145\cdot10^{-17}$ \\
-  \hline
-\end{tabular}
-\end{center}
-
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-  \hline
-  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
-  \multicolumn{4}{|c|}{$B_{10}(x)=x^{10}-5x^9+\frac{15}{2}x^8-7x^6+5x^4-\frac{3}{2}x^2+\frac{5}{66}$} \\
-  \hline
-  $\varepsilon$ & $k^*$ & $n_{k^*}$ & $\operatorname{error}=\DHJRnorm[\calG]{S(B_{10}(x))}-\DHJRnorm[\calG]{A_{n_{k^*}}(B_{10}(x))}$ \\
-  \hline
-  $1$ & $5$ & $32$ & $7.7716\cdot10^{-16}$ \\
-  $10^{-1}$ & $5$ & $32$ & $7.7716\cdot10^{-16}$ \\
-  $10^{-2}$ & $6$ & $64$ & $7.7716\cdot10^{-16}$ \\
-  $10^{-3}$ & $6$ & $64$ & $7.7716\cdot10^{-16}$ \\
-  $10^{-4}$ & $7$ & $128$ & $7.7716\cdot10^{-16}$ \\
-  $10^{-5}$ & $7$ & $128$ & $7.7716\cdot10^{-16}$ \\
-  \hline
-\end{tabular}
-\end{center}
-
-\begin{remark}
-MATLAB's machine epsilon is $2.2204\cdot10^{-16}$.
-\end{remark}
-\fi
-
-\iffalse
-
-We do not expect the series coefficients of the solution $S(f)$, to decay monotonically.
-The sequence $\bsn$ is used to average finite sequences of Fourier coefficients into groups to smooth the peaks we could encounter if we take these coefficients one by one.
-Flattening the peaks is a must to fit functions into the cone.
-Nevertheless, the solution of our algorithm is in this set $\cn$ which means that the sequence does not have to distance the optimal number of data needed in our algorithm (defined below) more than a constant.
-
-We define the optimal number of data needed to solve the problem defined as \eqref{errCond} is 
-\begin{equation*}
-N_{\opt}(f,\varepsilon)=\min\left\{n\in\bbN:\,\DHJRnorm[2]{\left(\lambda_{i_j} \widehat{f}_{i_j} \right)_{j\ge n+1}} \le \varepsilon \right\}
-\end{equation*}
-
-Any algorithm is called \emph{asymptotically  optimal} if it essentially tracks the optimal number of data needed,
-\begin{equation} \label{nearoptdef}
-\sup_{\varepsilon > 0 } \frac{\textup{cost}(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty 
-\end{equation}
-or
-\[
-\sup_{\varepsilon > 0 } [\textup{cost}(A,f;\varepsilon)- N_{\opt}(f,\varepsilon)] <\infty.
-\]
-
-Next, we prove our algorithm is optimal.
-
-\begin{theorem}\label{nopt}
-Algorithm \ref{algo2} is optimal for this problem.
-
-\end{theorem}
-\begin{proof}
-Given $f \in \calC$ and $\varepsilon$, denote $n^*= N_{\opt}(f,\varepsilon)$. Let 
-\[n_{k^*-r-1} < n^{*}  \le n_{k^*-r} \le n_{k^*},\]
-where $n_{k^*}$ is the cost of our algorithm.
-Thus by \eqref{sumdef}, we obtain
-\[\sigma_{k^*-r+1}(f) = \DHJRnorm[2]{ \left(\lambda_{i_j} \widehat{f}_{i_j} \right)_{j=n_{k^*-r}+1}^{n_{k^*-r+1}}}
- \le \DHJRnorm[2]{ \left(\lambda_{i_j} \widehat{f}_{i_j} \right)_{j=n^*}^{\infty}} \le \varepsilon.\]
-By the cone condition \eqref{decayconedef} , we have 
-\[\sigma_{k^*-r+m}(f) \le \gamma_{m-1}\sigma_{k^*-r+1}(f) \le\gamma_{m-1} \cdot \varepsilon.\]
-Choose $m$ such that $\gamma_{m-1} \le \frac{1}{\DHJRnorm[2]{\vgamma}},$
-thus we obtain
-\[\sigma_{k^*-r+m}(f) \le\gamma_{m-1} \cdot \varepsilon \le \frac{\varepsilon}{\DHJRnorm[2]{\vgamma}}.\]
-Suppose $\gamma_r$ decays geometrically, $n_k$ increases geometrically $n_k = n_0 2^k $, we have
-\[\frac{\textup{cost}(\widetilde{A},f;\varepsilon)}{N_{\opt}(f,\varepsilon)} \le 
-\frac{n_{k^*-r+m}}{n_{k^*-r-1}} = \frac{n_0 2^{k^*-r+m}}{n_0 2^{k^*-r-1}}
-= 2^{m+1}.\]
-
-As $m$ satisfied 
-\begin{align*}\
-\gamma_{m-1} \le \frac{1}{\DHJRnorm[2]{\vgamma}} 
-& \Longleftrightarrow C_1C_2^{-m+1} \le \frac{\sqrt{C_2^2-1}}{C_1} \\
-& \Longrightarrow C_2^{-m+1} \le \frac{\sqrt{C_2^2-1}}{C^2_1} \\
-& \Longrightarrow  m \ge 1+ 
-\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}.
-\end{align*}
-Therefore we can choose 
-\[m = \left\lceil 1+ 
-\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)} \right\rceil
- < 2 + \frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}. \]
-Hence,
- \[\frac{\textup{cost}(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} 
- \le 2^{m+1} < 2^{3+\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}} \Longrightarrow \sup_{f,\varepsilon} \frac{\textup{cost}(A,f;\varepsilon)} {N_{\opt}(f,\varepsilon)} <\infty.\]
-
-Suppose $\gamma_r$ decays geometrically, $n_k$ increases linearly $n_k = n_0 + 2k $, we have
-\begin{align*}
-\textup{cost}(\widetilde{A},f;\varepsilon)-N_{\opt}(f,\varepsilon) & \le 
-n_{k^*-r+m}-n_{k^*-r-1} \\ & = (n_0 +2(k^*-r+m))-(n_0+2(k^*-r-1))\\
-& = 2(m+1).
-\end{align*}
-Still choose
-\[m = \left\lceil 1+ 
-\frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)} \right\rceil
- < 2 + \frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}. \]
- We have
-\begin{align*}
-\textup{cost}(\widetilde{A},f;\varepsilon)-N_{\opt}(f,\varepsilon) 
-& = 2(m+1) \\
-&  = 2\left(3+ \frac{\log\left(\frac{C_1^2}{\sqrt{C_2^2-1}}\right)}{\log(C_2)}\right)\\
-\Longrightarrow &
-\sup_{f,\varepsilon} \left[\textup{cost}(A,f;\varepsilon) -N_{\opt}(f,\varepsilon) \right]< \infty
-\end{align*}
-\end{proof}
-
-\fi

### 2018-08-24 ProgramsImages/sim_FourCoef.m
Any new stuff in Overleaf?

@@ -16,22 +16,16 @@ n_app = 2^10; %number of points to use for approximating L_inf norm
 % Assume that
 %  x is nX x d
 %  k is nK x d
-denom_wt_fun = @(k) prod(max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
-pow_2_wt_fun = @(k) 2.^(sum(k~=0,2)/2); %nK x 1
-u_wt_fun = @(k) pow_2_wt_fun(k) ./ denom_wt_fun(k); %nK x 1
+u_wt_fun = @(k) prod(2.^((k~=0)/2) ./ max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
 v_wt_fun = @(k) -sign(k(:,1)) .* 2.^(sum(k~=0,2)/2); %nK x 1
-%basisName = 'CompExp'; %complex Exponential
+basisName = 'CompExp'; %complex Exponential
 % inp_basis_fun = @(k,x) exp((2*pi*sqrt(-1))* (x * k'))./u_wt_fun(k)'; %nX x nK
 % out_basis_fun = @(k,x) -exp((2*pi*sqrt(-1))* (x * k')); %nX x nK
-basisName = 'CosineSine'; %cosine and sine
 inp_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
-   + (reshape(k',1,d,size(k,1)) < 0)*(pi/2)),2)) .* u_wt_fun(k)'; %nX x nK
-out_basis_fun = @(k,x) sin((2*pi)* (x(:,1) .* k(:,1)') ...
-   + (k(:,1)' < 0)*(pi/2)) .* ...
-   squeeze(prod(cos((2*pi)* (x(:,2:d) .* reshape(k(:,2:d)',1,d-1,size(k,1))) ...
-   + (reshape(k(:,2:d)',1,d-1,size(k,1)) < 0)*(pi/2)),2)) ...
-   .* v_wt_fun(k)'; %nX x nK
-lambda = @(k) (2*pi)*(abs(k(:,1)) ./ denom_wt_fun(k)); %nK x 1;
+   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* u_wt_fun(k)'; %nX x nK
[…]

### 2018-08-24 ProgramsImages/sim_FourCoef_plot_results.m

@@ -16,7 +16,7 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
 ylabel({'Sample size \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
@@ -24,10 +24,10 @@ tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-% [~,leg_icons] = legend(h, ...
-%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-%    }, ...
-%    'box','off','location','north','orientation','horizontal');
+[~,leg_icons] = legend(h, ...
+   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
+   }, ...
+   'box','off','location','north','orientation','horizontal');
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 print -depsc SimFourCoefErr.eps

### 2018-08-25 ProgramsImages/sim_FourCoef.m
revise figures

@@ -9,7 +9,7 @@ format short e
 d = 3;     %dimension
 coord_wt_vec = 2.^(0:-1:-d+1);
 wt_pow = 4;
-wv_num_max = 20;
+wv_num_max = 30;
 wv_num_mtx = permn(-wv_num_max:wv_num_max,d); %compute this just once for all
 nBasis = size(wv_num_mtx,1); %number of basis elements
 n_app = 2^10; %number of points to use for approximating L_inf norm

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m

@@ -17,7 +17,7 @@ xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
 xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size \(n\)'})
+ylabel({'Sample size, \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
@@ -65,8 +65,10 @@ Sf_true_Vis = reshape(Sf_true_Vis,[n_grd_val n_grd_val]);
 surf(x_grd,x_grd,Sf_true_Vis); shading interp
 xlabel(['\(x_{' int2str(xcoord) '}\)'])
 ylabel(['\(x_{' int2str(ycoord) '}\)'])
-zlabel(['\(\partial^{\{1\}}f(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
-   '}, ' num2str(nom_Val) ', \ldots)\)'])
+zlabel(['\(S(f)(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
+   '}, ' num2str(nom_Val) ')\)'])
+%zlabel(['\(\partial^{\{1\}}f(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
+%   '}, ' num2str(nom_Val) ', \ldots)\)'])
 print -depsc SimFourCoefSol.eps
 
 
@@ -76,8 +78,10 @@ Sf_app_Vis = reshape(Sf_app_Vis,[n_grd_val n_grd_val]);
 surf(x_grd,x_grd,Sf_app_Vis); shading interp
 xlabel(['\(x_{' int2str(xcoord) '}\)'])
 ylabel(['\(x_{' int2str(ycoord) '}\)'])
-zlabel(['\(\partial^{\{1\}}f_{\mbox{app}}(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
-   '}, ' num2str(nom_Val) ', \ldots)\)'])
[…]

### 2018-08-25 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX

@@
 f &= \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \widehat{u}_{\bsk} = \sum_{i \in \bbN} \widehat{f}_i u_i , \\
-u_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j k_j)},  \\ 
-S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \lambda_{\bsk} v_{\bsk} (\bsx)
+\widehat{u}_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j \DHJRabs{k_j})},  \\ 
+S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \lambda(\bsk) \widehat{v}_{\bsk} (\bsx)
 = \sum_{i \in \bbN} \widehat{f}_i \lambda_i v_i, \\ 
-v_{\bsk}(\bsx) & : =  -\textup{sign}(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
+\widehat{v}_{\bsk}(\bsx) & : =  -\textup{sign}(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
 & \qquad \qquad \times \prod_{j=2}^d 2^{(1-\delta_{k_j,0})/2} \cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ), \\ 
-\lambda_{\bsk} &:= \frac{2 \pi \DHJRabs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}.
+\lambda(\bsk) &:= \frac{2 \pi \DHJRabs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}, \\
+\boldsymbol{\gamma} & := (1,1/2, 1/4, \ldots, 2^{-d+1}).
 \end{align*}
-where $\gamma = [2^0, 2^{-1},\ldots, 2^{-d+1}].$
 
 \yuhannote{According to code, some expression should be as follows:}
+\frednote{I hope that it is fixed now.}
 \begin{align*}
 u_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max^8(1,\gamma_j k_j)},  \\ 
-\lambda_{\bsk} &:= 2 \pi \DHJRabs{k_1}\frac{2^{(1-\delta_{k_j,0})/2}}{\prod_{j=1}^d\max^8(1,\gamma_j k_j)}.\\
+\lambda(\bsk) &:= 2 \pi \DHJRabs{k_1}\frac{2^{(1-\delta_{k_j,0})/2}}{\prod_{j=1}^d\max^8(1,\gamma_j k_j)}.\\
 \end{align*}
@@
 
-We construct a function by choosing its Fourier coefficients $\widehat{f}_i \overset{\text{IID}}{\sim}  \mathcal{N}(0,1)$ for  $i = 1, \ldots, 68931$, and $\widehat{f}_i = 0$ otherwise.
+We construct a function by choosing its Fourier coefficients $\widehat{f}(\bsk) \overset{\text{IID}}{\sim}  \mathcal{N}(0,1)$ for  $\bsk \in \{-30, -29, \ldots, 30\}^d$, and $\widehat{f}(\bsk) = 0$ otherwise.
+This corresponds to $61^3 \approx 2 \times 10^5$ nonzero Fourier coefficients.
 Let $ a= 2$ and  $b=\frac{1}{2}$ and
- choose $\bsn = \{0, 2^{3+1}, \ldots, 2^{3+k}, \ldots \}.$
- To  obtain $\sigma_j(f), \ j \in \bbN$ by \eqref{sumdef},
- we need to sort $\lambda_i$ in the descending order and get corresponding $\widehat{f}_i$ and $\widehat{v}_i$, which is similar to the Example 1.
-To implement it efficiently, we use another vector to keep the index of the descending order of $\lambda_i$.
-Thus, we can obtain the correct
- $\lambda_i$,  $\widehat{f}_i$, and $v_i$ according to $\bsn_k$.
-Thus, we can add them together to get $\sigma_j(f)$.
-Given $\varepsilon$, we can derive the error bound and find the $n_{j^\dagger}$ where
+ choose $\bsn = \{0, 16, 32, 64, \ldots \}.$
+ To  compute $\sigma_j(f), \ j \in \bbN$ by \eqref{sumdef},
+ we need to sort $\bigl(\lambda(\bsk)\bigr)_{\bsk \in \bbZ^d}$ in descending order, $\lambda_1, \lambda_2, \ldots$.
+Given $\varepsilon$, we can then find the number of series coefficients needed to satisfy the the error criterion, i.e., $n_{j^\dagger}$ where
  \[j^{\dagger} = \min \left\{j \in \bbN : \frac{ab\sigma_j(f)}{\sqrt{1-b^2}}  \le \varepsilon. \right\}\]
+
+ Fig.\ \ref{solfig} shows
 
@@
 Fig.
-\ref{errfig} shows the number of sample size needed when we choose 10 different error tolerance from $10^{-1}$ to $10^{1}$.
-If we consider $\varepsilon = 0.1$, $ n_{j^\dagger} = 1024$ can reach the error tolerance.
-Using that, we can obtain the approximated solution and error in Figure \ref{solfig}.
+\ref{errfig} shows the sample size needed for ten different error tolerances from $10^{-1}$ to $10^{1}$.
+If we consider $\varepsilon = 0.1$, $ n_{j^\dagger} = 8192$ is sufficient to satisfy the error tolerance.
+For $\varepsilon = 0.1$, the approximate solution and the error in Figure \ref{solfig}.
 Based on Fig.
@@
 	\begin{tabular}{cc}
+		\includegraphics[width =5.5 cm]{ProgramsImages/SimFourCoefInpFun.eps} &
+		\includegraphics[width = 5.5 cm]{ProgramsImages/SimFourCoefSol.eps}
+		\\ (a) & (b) \\
 		\includegraphics[width =5.5 cm]{ProgramsImages/SimDirectSolAppx.eps} &
 		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectSolErr.eps}
-		\\ (a) & (b)
+		\\ (c) & (d)
 	\end{tabular}
-	\caption{For $\varepsilon = 0.1$:  (a) The approximation of the first partial derivative of $f$; 
-		(b) The error of the approximation.
+	\caption{For $\varepsilon = 0.1$:  (a) The input function, $f$; (b) The true first partial derivative of $f$; (c) The approximate first partial derivative of $f$; 
+		(d) The approximation error.
 		\label{solfig}} % 

### 2018-08-25 ProgramsImages/sim_FourCoef.m
revising example

@@ -9,7 +9,7 @@ format short e
 d = 3;     %dimension
 coord_wt_vec = 2.^(0:-1:-d+1);
 wt_pow = 4;
-wv_num_max = 30;
+wv_num_max = 20;
 wv_num_mtx = permn(-wv_num_max:wv_num_max,d); %compute this just once for all
 nBasis = size(wv_num_mtx,1); %number of basis elements
 n_app = 2^10; %number of points to use for approximating L_inf norm

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m

@@ -16,18 +16,18 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size, \(n\)'})
+%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-% [~,leg_icons] = legend(h, ...
-%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-%    }, ...
-%    'box','off','location','north','orientation','horizontal');
+[~,leg_icons] = legend(h, ...
+   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
+   }, ...
+   'box','off','location','north','orientation','horizontal');
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 print -depsc SimFourCoefErr.eps
@@ -65,10 +65,8 @@ Sf_true_Vis = reshape(Sf_true_Vis,[n_grd_val n_grd_val]);
 surf(x_grd,x_grd,Sf_true_Vis); shading interp
 xlabel(['\(x_{' int2str(xcoord) '}\)'])
 ylabel(['\(x_{' int2str(ycoord) '}\)'])
[…]

### 2018-08-25 AutoAlgorithmLinearFunctionalDataVerC.tex
revising figures

@@
 
- Fig.\ \ref{solfig} shows
-
- \begin{figure}[ht]
- 	\centering
- 		\includegraphics[width =7.5 cm]{ProgramsImages/SimFourCoefErr.eps}
- 	\caption{Sample size $n$, error tolerance $\varepsilon$ and ratio \label{errfig}} % 
- \end{figure}
-
+Fig.\ \ref{solfig} shows the input function, the solution, the approximate solution, and the error of the approximate solution for $d=3$ and $\varepsilon = 0.1$.
+For this example, $ n_{j^\dagger} = 8192$ is sufficient to satisfy the error tolerance, as is clear from Fig.\ \ref{solfig}(d).
 Fig.
-\ref{errfig} shows the sample size needed for ten different error tolerances from $10^{-1}$ to $10^{1}$.
-If we consider $\varepsilon = 0.1$, $ n_{j^\dagger} = 8192$ is sufficient to satisfy the error tolerance.
-For $\varepsilon = 0.1$, the approximate solution and the error in Figure \ref{solfig}.
-Based on Fig.
-\ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.
-This shows our algorithm works.
+\ref{errfig} shows the sample size, $n_{j^\dagger}$ needed for ten different error tolerances from $0.1$ to $10$.
+Because the possible sample sizes powers of $2$, some tolerances require the same sample size.
 
@@
 
+\begin{figure}[ht]
+ 	\centering
+ 		\includegraphics[width =7.5 cm]{ProgramsImages/SimFourCoefErr.eps}
+ 	\caption{Sample size $n$, error tolerance $\varepsilon$ and ratio \label{errfig}} % 
+ \end{figure}
+
 \section{Discussion and Conclusions} \label{sec:conc}

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
revised figures

@@ -10,14 +10,14 @@ gail.InitializeDisplay %add some variables for nice plotting
 
 figure
 log10epsVec = log10(eps_vec);
-h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+%h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
 hold on
 set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
 xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size, \(n\)'})
+ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
@@ -29,7 +29,7 @@ set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
 %    }, ...
 %    'box','off','location','north','orientation','horizontal');
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
-leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
+%leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 print -depsc SimFourCoefErr.eps
 
 %% Visualize (only a 2-d projection)

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
finished for now with example

@@ -10,26 +10,26 @@ gail.InitializeDisplay %add some variables for nice plotting
 
 figure
 log10epsVec = log10(eps_vec);
-%h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
 hold on
 set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
+%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-% [~,leg_icons] = legend(h, ...
-%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-%    }, ...
-%    'box','off','location','north','orientation','horizontal');
+[~,leg_icons] = legend(h, ...
+   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
+   }, ...
+   'box','off','location','north','orientation','horizontal');
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
[…]

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
updated figures

@@ -8,28 +8,30 @@ load(['sim_FourCoef_results_basis_' basisName '.mat'], ...
 
 gail.InitializeDisplay %add some variables for nice plotting
 
+rng(47)
 figure
 log10epsVec = log10(eps_vec);
-h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+%h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
 hold on
 set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size \(n\)'})
+xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-[~,leg_icons] = legend(h, ...
-   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-   }, ...
-   'box','off','location','north','orientation','horizontal');
+%[~,leg_icons] = legend(h, ...
+%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
[…]

### 2018-08-25 AutoAlgorithmLinearFunctionalDataVerC.tex

@@
 \end{align*}
+Note that $\lambda_1 \ge \lambda_2 \ge \cdots$ is an ordering of the $\lambda(\bsk)$.
+That ordering then determines the $\widehat{f}_i, u_i$, and $v_i$ in terms of the $\widehat{f}(\bsk), \widehat{u}(\bsk)$, and $\widehat{v}(\bsk)$, respectively.
 
@@
 This corresponds to $61^3 \approx 2 \times 10^5$ nonzero Fourier coefficients.
-Let $ a= 2$ and  $b=\frac{1}{2}$ and
+Let $ a= 2$ and  $b=1/2$ and
  choose $\bsn = \{0, 16, 32, 64, \ldots \}.$
@@
 
-\section{Discussion and Conclusions} \label{sec:conc}
+\section{Discussion and Conclusion} \label{sec:conc}
+\textbf{todo}
 

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
new figures

@@ -71,7 +71,7 @@ zlabel(['\(S(f)(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
    '}, ' num2str(nom_Val) ')\)'])
 % zlabel(['\(\partial^{\{1\}}f(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
 %    '}, ' num2str(nom_Val) ', \ldots)\)'])
-print -depsc SimFourCoefSol.eps
+gcf; print -depsc SimFourCoefSol.eps
 
 
 figure
@@ -84,7 +84,7 @@ zlabel(['\(\tilde{A}(f,\varepsilon)(x_{' int2str(xcoord) '}, x_{' int2str(ycoord
    '}, ' num2str(nom_Val) ')\)'])
 % zlabel(['\(\partial^{\{1\}}f_{\mbox{app}}(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
 %    '}, ' num2str(nom_Val) ', \ldots)\)'])
-print -depsc SimDirectSolAppx.eps
+gcf; print -depsc SimDirectSolAppx.eps
 
 figure
 rotate3d on
@@ -96,7 +96,7 @@ zlabel(['\((S(f) - \tilde{A}(f))(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) .
    '}, ' num2str(nom_Val) ')\)'])
 % zlabel(['\(\partial^{\{1\}}f_{\mbox{err}}(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
 %    '}, ' num2str(nom_Val) ', \ldots)\)'])
-print -depsc SimDirectSolErr.eps
+gcf; print -depsc SimDirectSolErr.eps
 
 
 figure
@@ -109,7 +109,7 @@ zlabel(['\(f(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
    '}, ' num2str(nom_Val) ')\)'])
 % zlabel(['\(f(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
 %    '}, ' num2str(nom_Val) ', \ldots)\)'])
-print -depsc SimFourCoefInpFun.eps
+gcf; print -depsc SimFourCoefInpFun.eps
 
 
 figure
@@ -120,7 +120,7 @@ xlabel(['\(x_{' int2str(xcoord) '}\)'])
[…]

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
Updates from ShareLaTeX

@@ -8,30 +8,28 @@ load(['sim_FourCoef_results_basis_' basisName '.mat'], ...
 
 gail.InitializeDisplay %add some variables for nice plotting
 
-rng(47)
 figure
 log10epsVec = log10(eps_vec);
-scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
-%h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
 hold on
 set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
+%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-%[~,leg_icons] = legend(h, ...
-%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-%    }, ...
-%    'box','off','location','north','orientation','horizontal');
+[~,leg_icons] = legend(h, ...
+   {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
[…]

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
enhancing, but these changes are not registering in Overleaf

@@ -32,7 +32,7 @@ set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
 %    'box','off','location','north','orientation','horizontal');
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 %leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
-print -depsc SimFourCoefErr.eps
+gcf; print -depsc SimFourCoefErr.eps
 
 %% Visualize (only a 2-d projection)
 xcoord = 1; % coordinate with the biggest w

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
Updates from ShareLaTeX

@@ -8,30 +8,28 @@ load(['sim_FourCoef_results_basis_' basisName '.mat'], ...
 
 gail.InitializeDisplay %add some variables for nice plotting
 
-rng(47)
 figure
 log10epsVec = log10(eps_vec);
-scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
-%h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
+h = scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance
 hold on
 set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
+%xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size \(n\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
 tickLabels = 10.^tickVals;
 set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
    'Limits',[tickVals(1) tickVals(end)])
-%[~,leg_icons] = legend(h, ...
-%    {'\(||\partial^{\{1\}}f-\partial^{\{1\}}f_{\mbox{app}}||_{2}/\varepsilon\) \quad', ...
-%    }, ...
-%    'box','off','location','north','orientation','horizontal');
+[~,leg_icons] = legend(h, ...
[…]

### 2018-08-25 ProgramsImages/sim_FourCoef_plot_results.m
Trying to fix it

@@ -133,4 +133,3 @@ zlabel(['\(f_{\mbox{err}}(x_{' int2str(xcoord) '}, x_{' int2str(ycoord) ...
 gcf; print -depsc SimDirectInpFunErr.eps
 
 figure(1)
-

### 2018-08-26 ProgramsImages/sim_FourCoef.m
Fixing mfiles and figs

@@ -6,26 +6,33 @@
 close all
 clearvars
 format short e
+rng(47)
 d = 3;     %dimension
 coord_wt_vec = 2.^(0:-1:-d+1);
 wt_pow = 4;
-wv_num_max = 20;
+wv_num_max = 30;
 wv_num_mtx = permn(-wv_num_max:wv_num_max,d); %compute this just once for all
 nBasis = size(wv_num_mtx,1); %number of basis elements
 n_app = 2^10; %number of points to use for approximating L_inf norm
 % Assume that
 %  x is nX x d
 %  k is nK x d
-u_wt_fun = @(k) prod(2.^((k~=0)/2) ./ max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
+denom_wt_fun = @(k) prod(max(1,coord_wt_vec .* abs(k)).^wt_pow ,2); %nK x 1
+pow_2_wt_fun = @(k) 2.^(sum(k~=0,2)/2); %nK x 1
+u_wt_fun = @(k) pow_2_wt_fun(k) ./ denom_wt_fun(k); %nK x 1
 v_wt_fun = @(k) -sign(k(:,1)) .* 2.^(sum(k~=0,2)/2); %nK x 1
-basisName = 'CompExp'; %complex Exponential
+%basisName = 'CompExp'; %complex Exponential
 % inp_basis_fun = @(k,x) exp((2*pi*sqrt(-1))* (x * k'))./u_wt_fun(k)'; %nX x nK
 % out_basis_fun = @(k,x) -exp((2*pi*sqrt(-1))* (x * k')); %nX x nK
+basisName = 'CosineSine'; %cosine and sine
 inp_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
-   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* u_wt_fun(k)'; %nX x nK
-out_basis_fun = @(k,x) squeeze(prod(cos((2*pi)* (x .* reshape(k',1,d,size(k,1))) ...
-   + reshape(k',1,d,size(k,1))*(pi/2)),2)) .* v_wt_fun(k)'; %nX x nK
-lambda = @(k) (2*pi)*(abs(k(:,1)).*u_wt_fun(k)); %nK x 1;
[…]

### 2018-08-26 ProgramsImages/sim_FourCoef_plot_results.m

@@ -8,7 +8,6 @@ load(['sim_FourCoef_results_basis_' basisName '.mat'], ...
 
 gail.InitializeDisplay %add some variables for nice plotting
 
-rng(47)
 figure
 log10epsVec = log10(eps_vec);
 scatter(rat_vec,n_vec,800,log10epsVec,'.'); %plot ratio of actual error to tolerance, with color corresonding to tolerance

### 2018-08-26 AutoAlgorithmLinearFunctionalDataVerC.tex

@@
 
-\title*{Adaptive Algorithms Employing Continuous Linear Functionals}
+\title*{Adaptive Algorithms Employing Continuous Linear Functionals {\color{red} An Adaptive Algorithm?}}
 \author{Yuhan Ding \and Fred J. Hickernell \and Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
@@
 \end{equation*}
-Finally, we define the complexity of the problem as computational cost of the best algorithm:
+Finally, we define the complexity of the problem as {\color{red} the} computational cost of the best algorithm:
 \begin{gather*}
@@
 \end{gather*}
-Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$.
+Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$ ({\color{red} $\leq$ ?}).
 In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
 
-An optimal algorithm for $\calB_{\rho}$ can be constructed in terms of interpolation based on the first $n$ series coefficients of the input, namely,
+An optimal algorithm for $\calB_{\rho}$ can be constructed in terms of interpolation {\color{red}truncation of the last $n+1$ series coefficients?} based on the first $n$ series coefficients of the input, namely,
 \begin{gather}  \label{optAdef}
@@
 \end{gather}
-Define the non-adaptive, algorithm as
+Define the non-adaptive algorithm as
 \begin{equation} \label{optBallalg}
@@
 Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.
-Let $f$ be a linear combination of $u_1, \ldots, u_{n+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
+Let $f$ be a linear combination of $u_1, \ldots, u_{n+1} {\color{red} u_{N+1}?}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
 \begin{align*}
@@
 \[
-\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widetilde{A},\calB_\rho,\varepsilon).
+\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widetilde{A}{\color{red}\widehat{A}},\calB_\rho,\varepsilon).
 \]
@@
 
-\begin{example} Consider the case of function approximation for periodic functions defined on the [0,1], and algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
+\begin{example} Consider the case of function approximation for periodic functions defined (on the $\rightarrow$ {\color{red} over}) [0,1], and algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
 	\begin{align*}
@@
 	\end{cases} 
-	& v_i(x) &= \begin{cases} \widehat{v}_{-i/2}, & i \text{ even},\\
+	& v_i &= \begin{cases} \widehat{v}_{-i/2}, & i \text{ even},\\
 	\widehat{v}_{(i-1)/2}, & i \text{ odd},
@@
 	\end{align*}
+	{\color{red} Perhaps worth mentioning what norm makes $\widehat{\lambda}_k\widehat{v}_{k}$ orthonormal in $\mathcal{F}$.}
 	Here $\calG=L^2[0,1]$.
@@
 
-Our goal is not only to construct algorithms in $\calA(\calH)$ for some $\calH$, but also to determine whether the computational cost of our algorithms are reasonable.
-We define an algorithm $A \in \calA(\calH)$ to have \emph{essentially no worse cost} then an algorithm $A^* \in \calA(\calH^*)$ if for some number $\omega$,
+Our goal is not only to construct algorithms in $\calA(\calH)$ for some $\calH$, but also to determine whether the computational cost of our algorithms (are $\rightarrow$ {\color{red} is}) reasonable.
+We define an algorithm $A \in \calA(\calH)$ to have \emph{essentially no worse cost} (then $\rightarrow$ {\color{red} than}) an algorithm $A^* \in \calA(\calH^*)$ if for some number $\omega$,
 \begin{gather}
@@
 By definition, the cost of algorithm $A^*$ is no better than that of  $\widehat{A}$.
-Algorithm $A^*$ may or may not have essentially no worse cost than $\widehat{A}$ depending on the choice of $\bslambda^*$ and $\bsn$.
+Algorithm $A^*$ may or may not have essentially no {\color{red}(this "no" needed?)} worse cost than $\widehat{A}$ depending on the choice of $\bslambda^*$ and $\bsn$.
 The table below shows some examples.
@@
 \end{align}
-The upper and lower error bounds depend only on the function data and the parameters defining $\calC$.
+The upper and lower error bounds {\color{red} (which is the lower bound?)} depend only on the function data and the parameters defining $\calC$.
 The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.
-Moreover, the error of $A_{n_j}(f)$ is asymptotically the no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
-Our adaptive algorithm in the Section \ref{sec:adaptalgo} increases $j$ until the right hand side is smaller than the error tolerance.
+Moreover, the error of $A_{n_j}(f)$ is asymptotically no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
+Our adaptive algorithm in Section \ref{sec:adaptalgo} increases $j$ until the right hand side is smaller than the error tolerance.
 
@@
 \begin{algo}\label{algo2}
-Given $a$, $b$, the sequence $\bsn$, the cone $\calC$, and the input function $f \in \calC$, and the absolute error tolerance $\varepsilon$, set $j=1$.
+Given $a$, $b$, the sequence $\bsn$, the cone $\calC$, the input function $f \in \calC$, and the absolute error tolerance $\varepsilon$, set $j=1$.
 \begin{description}
@@
 \end{equation}
-Moreover, $\textup{cost}(\widetilde{A},\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\textup{cost}(\widetilde{A},{\color{red}\mathcal{C},}\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
@@
 For the remainder of the proof consider $\rho$ and $\varepsilon$ fixed.
-To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
+To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},{\color{red}\mathcal{C},}\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
 \begin{multline} \label{normsigineq}
@@
 \section{Discussion and Conclusion} \label{sec:conc}
-\textbf{todo}
+There are few adaptive algorithms employing continuous linear functionals.
+The key idea of our algorithm is to derive an adaptive error bound by assuming the steady decay of the Fourier coefficients of the solution without the specific decay rate as a priori.
+	The upper bound on the computational cost of our algorithm is presented in Theorem \ref{thm:compcost}.
+Depending on which term is dominating in \eqref{keysum}, we also provide two simpler bounds on the cost.
+The lower bound on the complexity of the linear problem is also presented.
+Moreover, under assumption \eqref{lambdaRatio}, our algorithm is essentially optimal.
+The numerical example illustrates how to implement our algorithm and show it is practical.
+One interesting problem to consider is how to extend our algorithm to Banach space.
 

### 2018-08-27 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX

@@
 Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
-{\color{red} The embedding operator is not considered either, right ($\lambda_i=1$)?
-When do these two basis exist?
+{\color{red} When do these two basis exist?
 For instance, can we freely choose from exponential to Walsh bases?}
 
-\subsection{Solvability}  Let $\calH$ be any subset {\color{red}(any subset?
-But $S$ will linearly defined over $\calH$?)} of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ to within some error tolerance for all inputs in $\calH$:
+\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ to within some error tolerance for all inputs in $\calH$:
 \begin{multline} \label{adapErrCrit}
@@
 \end{equation}
-Moreover, $\textup{cost}(\widetilde{A},{\color{red}\mathcal{C},}\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\textup{cost}(\widetilde{A},{\color{red}\calC \cap \calB_\rho,}\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
@@
 For the remainder of the proof consider $\rho$ and $\varepsilon$ fixed.
-To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},{\color{red}\mathcal{C},}\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
+To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},{\color{red}\calC \cap \calB_\rho,}\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
 \begin{multline} \label{normsigineq}
@@
 \end{align*}
-Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum becomes includes more terms and $b^{2(k-j)}$ also increases.
+Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum includes more terms and $b^{2(k-j)}$ also increases.
 
@@
 
-The upper bound on $\textup{cost}(\widetilde{A},\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
+The upper bound on $\textup{cost}(\widetilde{A},{\color{red}\calC \cap \calB_\rho,}\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
 This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$.
@@
 One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.
-These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}$
+These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}${\color{red}.}
 
@@
 f &= \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \widehat{u}_{\bsk} = \sum_{i \in \bbN} \widehat{f}_i u_i , \\
-\widehat{u}_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max(1,\gamma_j \DHJRabs{k_j})},  \\ 
+\widehat{u}_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max^4(1,\gamma_j k_j)},  \\ 
 S(f) &: = \frac{\partial f}{\partial x_1} = \sum_{\bsk \in \bbZ^d} \widehat{f}(\bsk) \lambda(\bsk) \widehat{v}_{\bsk} (\bsx)
 = \sum_{i \in \bbN} \widehat{f}_i \lambda_i v_i, \\ 
-\widehat{v}_{\bsk}(\bsx) & : =  -\textup{sign}(k_1) 2^{(1-\delta_{k_1,0})/2} \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
-& \qquad \qquad \times \prod_{j=2}^d 2^{(1-\delta_{k_j,0})/2} \cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ), \\ 
-\lambda(\bsk) &:= \frac{2 \pi \DHJRabs{k_1}}{\prod_{j=1}^d\max(1,\gamma_j k_j)}, \\
+\widehat{v}_{\bsk}(\bsx) & : =  -\textup{sign}(k_1)  \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
+& \qquad \qquad \times \prod_{j=2}^d
+\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ), \\ 
+\lambda(\bsk) &:= 2 \pi \DHJRabs{k_1}\frac{\prod_{j=1}^d 2^{(1-\delta_{k_j,0})/2}}{\prod_{j=1}^d\max^4(1,\gamma_j k_j)}, \\
 \boldsymbol{\gamma} & := (1,1/2, 1/4, \ldots, 2^{-d+1}).
@@
 That ordering then determines the $\widehat{f}_i, u_i$, and $v_i$ in terms of the $\widehat{f}(\bsk), \widehat{u}(\bsk)$, and $\widehat{v}(\bsk)$, respectively.
-
-\yuhannote{According to code, some expression should be as follows:}
-\frednote{I hope that it is fixed now.}
-\begin{align*}
-u_{\bsk} (\bsx) &:= \prod_{j=1}^d \frac{2^{(1-\delta_{k_j,0})/2}\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 )}{\max^8(1,\gamma_j k_j)},  \\ 
-\lambda(\bsk) &:= 2 \pi \DHJRabs{k_1}\frac{2^{(1-\delta_{k_j,0})/2}}{\prod_{j=1}^d\max^8(1,\gamma_j k_j)}.\\
-\end{align*}
-
-\yuhannote{$v_{\bsk}(\bsx) $ still doesn't match the code}
-\begin{align*}
-    v_{\bsk}(\bsx) & : =  -\textup{sign}(k_1)  \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
-& \qquad \qquad \times \prod_{j=2}^d
-\cos(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) 
-\end{align*}
 

### 2018-08-27 AutoAlgorithmLinearFunctionalDataVerC.tex
Responding to Tony's comments.

@@
 
-\title*{Adaptive Algorithms Employing Continuous Linear Functionals {\color{red} An Adaptive Algorithm?}}
+\title*{An Adaptive Algorithm Employing Continuous Linear Functionals}
 \author{Yuhan Ding \and Fred J. Hickernell \and Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
@@
 \abstract{Automatic algorithms attempt to provide approximate solutions that differ from exact solutions by no more than a user-specified error tolerance.
-This paper describes an automatic adaptive algorithm for approximating the solution to a general linear problem on Hilbert spaces.
+This paper describes an automatic, adaptive algorithm for approximating the solution to a general linear problem on Hilbert spaces.
 The algorithm employs continuous linear functionals of the input function, specifically Fourier coefficients.
@@
 The proposed algorithm produces an approximation with guaranteed accuracy.
-Moreover, we demonstrate that {\color{red} the} computational cost of our algorithm is essentially no worse than that of the best possible algorithm.
+Moreover, we demonstrate that the computational cost of our algorithm is essentially no worse than that of the best possible algorithm.
 Our adaptive algorithm is defined on a \emph{cone} of input functions.
@@
 {\color{red} When do these two basis exist?
-For instance, can we freely choose from exponential to Walsh bases?}
+For instance, can we freely choose from exponential to Walsh bases?} \frednote{We can choose whatever bases we want, provided that they fit our problem.
+The existence is due to the singular value decomposition}
 
@@
 \end{equation*}
-Finally, we define the complexity of the problem as {\color{red} the} computational cost of the best algorithm:
+Finally, we define the complexity of the problem as the computational cost of the best algorithm:
 \begin{gather*}
@@
 \end{gather*}
-Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$ ({\color{red} $\leq$ ?}).
+Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$ ({\color{red} $\leq$ ?}) \frednote{The inequality is correct.
+The former problem is harder}.
 In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
 
-An optimal algorithm for $\calB_{\rho}$ can be constructed in terms of interpolation {\color{red}truncation of the last $n+1$ series coefficients?} based on the first $n$ series coefficients of the input, namely,
+An optimal algorithm for $\calB_{\rho}$ can be constructed in terms of interpolation with respect to the first $n$ series coefficients of the input, namely,
 \begin{gather}  \label{optAdef}
@@
 Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.
-Let $f$ be a linear combination of $u_1, \ldots, u_{n+1} {\color{red} u_{N+1}?}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
+Let $f$ be a linear combination of $u_1, \ldots, u_{N+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
 \begin{align*}
@@
 \[
-\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widetilde{A}{\color{red}\widehat{A}},\calB_\rho,\varepsilon).
+\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widehat{A},\calB_\rho,\varepsilon).
 \]
@@
 
-\begin{example} Consider the case of function approximation for periodic functions defined (on the $\rightarrow$ {\color{red} over}) [0,1], and algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
+\begin{example} Consider the case of function approximation for periodic functions defined over [0,1], and algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
 	\begin{align*}
@@
 	\end{align*}
-	{\color{red} Perhaps worth mentioning what norm makes $\widehat{\lambda}_k\widehat{v}_{k}$ orthonormal in $\mathcal{F}$.}
+	{\color{red} Perhaps worth mentioning what norm makes $\widehat{\lambda}_k\widehat{v}_{k}$ orthonormal in $\mathcal{F}$.} \frednote{They are orthonormal because we define the norm that way.}
 	Here $\calG=L^2[0,1]$.
@@
 
-Our goal is not only to construct algorithms in $\calA(\calH)$ for some $\calH$, but also to determine whether the computational cost of our algorithms (are $\rightarrow$ {\color{red} is}) reasonable.
-We define an algorithm $A \in \calA(\calH)$ to have \emph{essentially no worse cost} (then $\rightarrow$ {\color{red} than}) an algorithm $A^* \in \calA(\calH^*)$ if for some number $\omega$,
+Our goal is not only to construct algorithms in $\calA(\calH)$ for some $\calH$, but also to determine whether the computational cost of our algorithms is reasonable.
+We define an algorithm $A \in \calA(\calH)$ to have \emph{essentially no worse cost}  than an algorithm $A^* \in \calA(\calH^*)$ if for some number $\omega$,
 \begin{gather}
@@
 \end{gather}
+If these inequalities are not satisfied, we say that $A$ has \emph{essentially worse cost}  than $A^*$ .
 If the costs of two algorithms are essentially no worse than each other, then we call them essentially the same.
@@
 By definition, the cost of algorithm $A^*$ is no better than that of  $\widehat{A}$.
-Algorithm $A^*$ may or may not have essentially no {\color{red}(this "no" needed?)} worse cost than $\widehat{A}$ depending on the choice of $\bslambda^*$ and $\bsn$.
+Algorithm $A^*$ may or may not have essentially worse cost than $\widehat{A}$ depending on the choice of $\bslambda^*$ and $\bsn$.
 The table below shows some examples.
@@
 \end{align}
-The upper and lower error bounds {\color{red} (which is the lower bound?)} depend only on the function data and the parameters defining $\calC$.
+This upper bound depends only on the function data and the parameters defining $\calC$.
 The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.

### 2018-08-27 AutoAlgorithmLinearFunctionalDataVerC.tex
Revised discussion.  Answered Tony's comments.

@@
 Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
-{\color{red} When do these two basis exist?
-For instance, can we freely choose from exponential to Walsh bases?} \frednote{We can choose whatever bases we want, provided that they fit our problem.
-The existence is due to the singular value decomposition}
+
+The existence of the $( u_i )_{i \in \bbN}$, $ ( v_i )_{i \in \bbN}$, and $( \lambda_i )_{i \in \bbN}$ for a given $\calF$, $\calG$, and $S$ follows from the singular value decomposition.
+The ease of identifying explicit expressions for these quantities depends on the particular problem of interest.
+Alternatively, one may start with a choice of $( u_i )_{i \in \bbN}$, $ ( v_i )_{i \in \bbN}$, and $( \lambda_i )_{i \in \bbN}$, which then determine the solution operator and the spaces $\calF$ and $\calG$.
 
@@
 \end{equation}
-Moreover, $\textup{cost}(\widetilde{A},{\color{red}\calC \cap \calB_\rho,}\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, \frednote{Tony, I think you misunderstood.
+It was correct to begin with.} where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
@@
 For the remainder of the proof consider $\rho$ and $\varepsilon$ fixed.
-To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},{\color{red}\calC \cap \calB_\rho,}\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
+To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
 \begin{multline} \label{normsigineq}
@@
 
-The upper bound on $\textup{cost}(\widetilde{A},{\color{red}\calC \cap \calB_\rho,}\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
+The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
 This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$.
@@
 One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.
-These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}${\color{red}.}
+These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}$.
 
@@
 \section{Discussion and Conclusion} \label{sec:conc}
-There are few adaptive algorithms employing continuous linear functionals.
-The key idea of our algorithm is to derive an adaptive error bound by assuming the steady decay of the Fourier coefficients of the solution without the specific decay rate as a priori.
-	The upper bound on the computational cost of our algorithm is presented in Theorem \ref{thm:compcost}.
-Depending on which term is dominating in \eqref{keysum}, we also provide two simpler bounds on the cost.
-The lower bound on the complexity of the linear problem is also presented.
-Moreover, under assumption \eqref{lambdaRatio}, our algorithm is essentially optimal.
-The numerical example illustrates how to implement our algorithm and show it is practical.
-One interesting problem to consider is how to extend our algorithm to Banach space.
+Many practical adaptive algorithms lack theory, and many theoretically justified algorithms are non-adaptive.
+We have demonstrated for a general setting how to construct a theoretically justified, essentially optimal algorithm.
+The decay of the singular values determines the computational complexity of the problem and the computational cost of our algorithm.
+
+The key idea of our algorithm is to derive an adaptive error bound by assuming the steady decay of the Fourier series coefficients of the solution.
+We do not, however, need to know the decay rate of these coefficients a priori.
+The cost of our algorithm also serves as a goal for an algorithm that uses function values, which are more commonly available than Fourier series coefficients.
+An important next step is to identify an essentially optimal algorithm based on function values.
+Another research direction would be to extend this setting to Banach spaces.
 

### 2018-09-16 AutoAlgorithmLinearFunctionalDataVerC.tex
Tony-prompted revisions

@@
 \newcommand{\DHJRbignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
+\newcommand{\DHJRBignorm}[2][{}]{\ensuremath{\Bigl \lVert #2 \Bigr \rVert}_{#1}}
 \newcommand{\DHJRabs}[1]{\ensuremath{{\left \lvert #1 \right \rvert}}}
@@
 We also assume that the Fourier coefficients decay steadily, although not necessarily monotonically.
-Under these assumptions, our adaptive algorithm is shown to achieve an approximation to the function satisfying the desired error tolerance, without prior knowledge of the norm of the function to be approximated.
+Under these assumptions, our adaptive algorithm is shown to produce an approximate solution satisfying the desired error tolerance, without prior knowledge of the norm of the function to be approximated.
 Moreover, the computational cost of our algorithm is shown to be essentially no worse than that of the optimal algorithm.
-We also provide a numerical experiment to illustrate our algorithm.}
+We provide a numerical experiment to illustrate our algorithm.}
 
@@
 \end{gather}
-Let these two bases be chosen by the singular value decomposition so that the linear solution operator, $S:\calF \to \calG$, satisfies
+Let these two bases be chosen so that the linear solution operator, $S:\calF \to \calG$, satisfies
 \begin{gather}
@@
 We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$.
-Thus, this setting is not relevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
+Thus, our arguments are irrelevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
 
@@
 The ease of identifying explicit expressions for these quantities depends on the particular problem of interest.
-Alternatively, one may start with a choice of $( u_i )_{i \in \bbN}$, $ ( v_i )_{i \in \bbN}$, and $( \lambda_i )_{i \in \bbN}$, which then determine the solution operator and the spaces $\calF$ and $\calG$.
+Alternatively, one may start with a choice of $( u_i )_{i \in \bbN}$, $ ( v_i )_{i \in \bbN}$, and $( \lambda_i )_{i \in \bbN}$, which then determine the solution operator, $S$, and the spaces $\calF$ and $\calG$.
 
@@
     & =  \frac 12 \left[ \DHJRnorm[\calG]{0 - A(0,\varepsilon)} + \DHJRnorm[\calG]{S(cf) - A(0,\varepsilon)}\right] \\
-    & \ge  \frac {\DHJRabs{c}\DHJRnorm[\calG]{S(f)}}2  \qquad \text{by the triangle inequality}.
+    & \ge  \frac {\DHJRnorm[\calG]{cS(f)}}2 = \frac {\DHJRabs{c}\DHJRnorm[\calG]{S(f)}}2  \qquad \text{by the triangle inequality}.
 \end{align*}
@@
 For unbounded sets, $\calH$, this cost may be infinite.
-Therefore, it is also helpful to define the cost of algorithms for input functions in $\calH \cap \calB_{\rho}$, where $\calB_{\rho} : = \{ f \in \calF : \DHJRnorm[\calF]{f} \le \rho \}$ is the ball of radius $\rho$:
+Therefore, we also define the cost of algorithms for input functions in $\calH \cap \calB_{\rho}$, where $\calB_{\rho} : = \{ f \in \calF : \DHJRnorm[\calF]{f} \le \rho \}$ is the ball of radius $\rho$:
 \begin{equation*}
@@
 \end{gather*}
-Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$ ({\color{red} $\leq$ ?}) \frednote{The inequality is correct.
-The former problem is harder}.
+Note that $\textup{comp}(\calA(\calH),\varepsilon,\rho) \ge \textup{comp}(\calA(\calH \cap \calB_{\rho}),\varepsilon)$.
 In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
@@
 \label{errOpt}
-\DHJRnorm[\calG]{S(f) - A_n(f)} = \DHJRbignorm[2]{\left(\lambda_{i} \widehat{f}_{i} \right)_{i= n+1}^{\infty}} \le \lambda_{n+1} \DHJRnorm[\calF]{f}.
+\DHJRnorm[\calG]{S(f) - A_n(f)} = \DHJRBignorm[2]{\left(\lambda_{i} \widehat{f}_{i} \right)_{i= n+1}^{\infty}} \le \lambda_{n+1} \DHJRnorm[\calF]{f}.
 \end{gather}
@@
 & \ge \DHJRnorm[\calG]{S(f)} 
-= \DHJRbignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{N+1}} \\
-& \ge \lambda_{N+1} \DHJRbignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \DHJRnorm[\calF]{f} = \lambda_{N+1} \rho.
+= \DHJRBignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{N+1}} \\
+& \ge \lambda_{N+1} \DHJRBignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \DHJRnorm[\calF]{f} = \lambda_{N+1} \rho.
 \end{align*}
@@
 	\end{align*}
-	{\color{red} Perhaps worth mentioning what norm makes $\widehat{\lambda}_k\widehat{v}_{k}$ orthonormal in $\mathcal{F}$.} \frednote{They are orthonormal because we define the norm that way.}
-	Here $\calG=L^2[0,1]$.
-The larger the non-negative parameter $r$ is, the faster the $\lambda_i$ tend to 0 as $ i \to 0$, the smaller $\calB_\rho$ is, and the smaller  $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ is.
+	Here, $\calG=L^2[0,1]$.
+The larger the non-negative parameter $r$ is, the faster the $\lambda_i$ tend to 0 as $ i \to 0$, the more exclusive $\calB_\rho$ is, and the smaller  $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ is.
 For $r = 0$, $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon) = \infty$.
@@
 
-Our goal is not only to construct algorithms in $\calA(\calH)$ for some $\calH$, but also to determine whether the computational cost of our algorithms is reasonable.
-We define an algorithm $A \in \calA(\calH)$ to have \emph{essentially no worse cost}  than an algorithm $A^* \in \calA(\calH^*)$ if for some number $\omega$,
-\begin{gather}
-\textup{cost}(A,\calH,\varepsilon) \le \textup{cost}(A^*,\calH^*,\omega\varepsilon), \qquad \forall \varepsilon > 0, \\
-\textup{cost}(A,\calH,\varepsilon,\rho) \le \textup{cost}(A^*,\calH^*,\omega\varepsilon,\rho), \qquad \forall \varepsilon,\rho > 0.
-\end{gather}
-If these inequalities are not satisfied, we say that $A$ has \emph{essentially worse cost}  than $A^*$ .
+Our goal is to construct algorithms in $\calA(\calH)$ for some $\calH$ and also to determine whether their computational cost is reasonable.
+We define  $\textup{cost}(A,\calH,\varepsilon,\rho)$ to be \emph{essentially no worse} than $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ if for some number $\omega$,
+\begin{equation} \label{essNoWorseDef}
+    \textup{cost}(A,\calH,\varepsilon,\rho)
+    \le 
+    \textup{cost}(A^*,\calH^*,\omega\varepsilon,\rho)
+    \qquad \forall \varepsilon,\rho > 0.
+\end{equation}
+We extend this definition analogously if $\textup{cost}(A,\calH,\varepsilon,\rho)$ is replaced by $\textup{cost}(A,\calH,\varepsilon)$ and/or $\textup{cost}(A^*,\calH^*,\omega\varepsilon,\rho)$ is replaced by $\textup{cost}(A^*,\calH^*,\omega\varepsilon)$.
+If these inequalities are not satisfied, we say that the cost of  $A$ is \emph{essentially worse}  than the cost of $A^*$.
 If the costs of two algorithms are essentially no worse than each other, then we call them essentially the same.
@@
 
-To illustrate these concepts, consider a nondecreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
-Also consider an unbounded strictly increasing sequence of nonnegative integers $\bsn = \{n_0, n_1, \ldots \}$.
+To illustrate these concepts, consider a non-decreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
+Also consider an unbounded strictly increasing sequence of non-negative integers $\bsn = \{n_0, n_1, \ldots \}$.
 Define an algorithm $A^*$ analogously to $\widehat{A}$ defined in \eqref{optBallalg}:
@@
 \everymath{\displaystyle}
-\begin{longtable}{>{$}r<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}}
+\begin{longtable}{>{$}r<{$}@{\quad}>{$}l<{$}@{\qquad}>{$}l<{$}>{$}l<{$}>{$}l<{$}}
 \toprule \toprule
@@
 \subsection{The Case for Adaptive Algorithms}
-For bounded sets of input functions, such as balls, non-adaptive algorithms, such as $\widehat{A}$, make sense.
+For bounded sets of input functions, such as balls, non-adaptive algorithms like $\widehat{A}$ make sense.
 However, it is typically unknown which ball the input function lies in.
@@
 
-Our rigorous, data-driven error bound assumes the input to have steadily---but not necessarily monotonically---decaying series coefficients.
+Our rigorous, data-driven error bound assumes the series coefficients of the input to decay steadily---but not necessarily monotonically.
 The cone of nice inputs, $\calC$, is defined in Section \ref{sec:cone}.
@@
 Section \ref{sec:examp} provides an example of our algorithm.
-Concluding remarks are give in Section \ref{sec:conc}.
+We end with concluding remarks in Section \ref{sec:conc}.
 
@@
 Recall from \eqref{errOpt} that the error of the fixed sample size interpolatory algorithm $A_n$ is $\DHJRnorm[\calG]{S(f) - A_n(f)} = \DHJRbignorm[2]{\bigl(\lambda_{i} \widehat{f}_{i} \bigr)_{i= n+1}^{\infty}}$.
-The error depends on the series coefficients not yet observed, so at first glance this error seems to be impossible to bound in terms of observed series coefficients.
+The error depends on the series coefficients not yet observed, so at first it seems impossible to bound the error in terms of observed series coefficients.
 
@@
 \begin{align} \label{decayconedef}
-\calC &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \forall j,r \in \bbN \right\} \\
+\calC &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \ \forall j,r \in \bbN \right\} \\
 \nonumber
-& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}\{ab^r\sigma_{j-r}(f)\} \ \forall j \in \bbN \right\}.
+& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}\{ab^r\sigma_{j-r}(f)\} \ \ \forall j \in \bbN \right\}.
 \end{align}
@@
 \end{equation}
-Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, \frednote{Tony, I think you misunderstood.
-It was correct to begin with.} where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
@@
 
-\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, then $\textup{cost}(\widetilde{A},\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, then $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdaggerfirst}
@@
 \[
-j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^j < \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
+j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^j \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
 \]
@@
 for some positive $c_\lambda$.  Then $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than \linebreak[4]
-$\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$.
+$\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ in the sense of \eqref{essNoWorseDef}.
 
@@
 Choose any positive integer $j$ such that $n_j$ exceeds $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
-The proof proceeds by carefully constructing thre  test input functions, $f$ and $f_{\pm}$, lying in $\calC \cap \calB_{\rho}$, which yield the same approximate solution but different true solutions.
+The proof proceeds by carefully constructing three test input functions, $f$ and $f_{\pm}$, lying in $\calC \cap \calB_{\rho}$, which yield the same approximate solution but different true solutions.
 This leads to a lower bound on $n_j$, which can be translated into a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
@@
 \]
-where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(k)}$ is a linear combination of $u_{n_k+1}, \ldots, u_{n_k}$, for $k =1, \ldots, j$.  We constrain $u$ to satisfy:
+where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(k)}$ is a linear combination of $u_{n_{k-1}+1}, \ldots, u_{n_k}$, for $k =1, \ldots, j$.
+We constrain $u$ to satisfy:
 \begin{equation}\label{uConstraint}
@@
 \nonumber
-\DHJRnorm[\calF]{f^*_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
+\DHJRnorm[\calF]{f_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
 & \le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \DHJRbignorm[\calF]{u^{(k)}}^2\right) + \eta^2 \DHJRbignorm[\calF]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
@@
 \varepsilon &\ge \max \bigl\{\DHJRnorm[\calG]{S(f_+) - A^*(f_+,\varepsilon)}, \DHJRnorm[\calG]{S(f_-) - A^*(f_-,\varepsilon)} \bigr\} \\
-&\ge \frac 12 \bigl[\DHJRnorm[\calG]{S(f^*_+) - A^*(f,\varepsilon)} + \DHJRnorm[\calG]{S(f^*_-) - A^*(f,\varepsilon)}  \bigr] \\
-&\qquad \qquad \text{since } A^*(f^*_\pm,\varepsilon) = A^*(f,\varepsilon) \\
-&\ge \frac 12 \DHJRnorm[\calG]{S(f^*_+) - S(f^*_-)} \quad \text{by the triangle inequality}\\
-&\ge \frac 12 \DHJRnorm[\calG]{S(f^*_+ - f^*_-)} \quad \text{since $S$ is linear}\\
+&\ge \frac 12 \bigl[\DHJRnorm[\calG]{S(f_+) - A^*(f,\varepsilon)} + \DHJRnorm[\calG]{S(f_-) - A^*(f,\varepsilon)}  \bigr] \\
+&\qquad \qquad \text{since } A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon) \\
+&\ge \frac 12 \DHJRnorm[\calG]{S(f_+) - S(f_-)} \quad \text{by the triangle inequality}\\
+&\ge \frac 12 \DHJRnorm[\calG]{S(f_+ - f_-)} \quad \text{since $S$ is linear}\\
 &= \eta \DHJRnorm[\calG]{S(u)}.
@@
 \begin{align*}
-\varepsilon^2  & \ge \eta \DHJRnorm[\calG]{S(u)}^2= 
+\varepsilon^2  & \ge \eta^2 \DHJRnorm[\calG]{S(u)}^2= 
 \eta^2 \sum_{k=0}^{j} \DHJRbignorm[\calG]{S(u^{(k)})}^2  \frac{b^{2(k-j)}}{\lambda_{n_k}^2}\\
@@
 &
-=\frac{(a-1)^2 \rho^2}{(a+1)^2A^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} A^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
-& \le  \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+=\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
+& =  \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
 \end{align*}
@@
 \label{thm:CostNoWorse}
-Under assumption \eqref{lambdaRatio} $\textup{cost}(\widetilde{A},\varepsilon,\rho)$ is essentially no worse than $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
+Under assumption \eqref{lambdaRatio} $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than $\textup{comp}(\calA(\calC),\varepsilon,\rho)$. 
 \end{theorem}
@@
 and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$. 
-For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\rho,\varepsilon) \le n_{j^\dagger}$ where 
+For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where 
 \begin{align*} 
@@
 \end{align*}
-By Theorem \ref{thm:lowbdcomp}, $\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above, $n_{j^*} \ge n_{j^\dagger} \ge \textup{cost}(\widetilde{A},\varepsilon,\rho)$.
+By Theorem \ref{thm:lowbdcomp}, $\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above, $n_{j^*} \ge n_{j^\dagger} \ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$.
 Thus, our algorithm is essentially no more costly than the optimal algorithm.
@@
 = \sum_{i \in \bbN} \widehat{f}_i \lambda_i v_i, \\ 
-\widehat{v}_{\bsk}(\bsx) & : =  -\textup{sign}(k_1)  \sin(2\pi k_j x_j  + \bbone_{(-\infty,0)}(k_j) \pi/2 ) \\
+\widehat{v}_{\bsk}(\bsx) & : =  -\textup{sign}(k_1)  \sin(2\pi k_1 x_1  + \bbone_{(-\infty,0)}(k_1) \pi/2 ) \\
 & \qquad \qquad \times \prod_{j=2}^d
@@
 
-We construct a function by choosing its Fourier coefficients $\widehat{f}(\bsk) \overset{\text{IID}}{\sim}  \mathcal{N}(0,1)$ for  $\bsk \in \{-30, -29, \ldots, 30\}^d$, and $\widehat{f}(\bsk) = 0$ otherwise.
+We construct a function by choosing its Fourier coefficients $\widehat{f}(\bsk) \overset{\text{IID}}{\sim}  \mathcal{N}(0,1)$ for $d=3$, $\bsk \in \{-30, -29, \ldots, 30\}^3$, and $\widehat{f}(\bsk) = 0$ otherwise.
 This corresponds to $61^3 \approx 2 \times 10^5$ nonzero Fourier coefficients.
@@
 
-Fig.\ \ref{solfig} shows the input function, the solution, the approximate solution, and the error of the approximate solution for $d=3$ and $\varepsilon = 0.1$.
+Fig.\ \ref{solfig} shows the input function, the solution, the approximate solution, and the error of the approximate solution for $\varepsilon = 0.1$.
 For this example, $ n_{j^\dagger} = 8192$ is sufficient to satisfy the error tolerance, as is clear from Fig.\ \ref{solfig}(d).
@@
 \ref{errfig} shows the sample size, $n_{j^\dagger}$ needed for ten different error tolerances from $0.1$ to $10$.
-Because the possible sample sizes powers of $2$, some tolerances require the same sample size.
+Because the possible sample sizes are powers of $2$ , some tolerances require the same sample size.
 
@@
  		\includegraphics[width =7.5 cm]{ProgramsImages/SimFourCoefErr.eps}
- 	\caption{Sample size $n$, error tolerance $\varepsilon$ and ratio \label{errfig}} % 
+ 	\caption{Sample size $n_{j^{\dagger}}$, error tolerance $\varepsilon$, and ratio. \label{errfig}} % 
  \end{figure}
+
+\tonynote{It looks like the font size in Figure 2 is smaller than that of Figure 1. Perhaps it would be easier to read if a bit larger?}
+
+\tonynote{In the x-axis of Figure 2, we mention $\hat{f}$.
+Is it referring to the Fourier coefficients?
+As a suggestion, are we not interested in something like $\DHJRnorm[\mathcal{G}]{S(f)-\widetilde{A}({f},\varepsilon)}$?
+This could allow us to plot marks at the different $\varepsilon$ and see how conservative the algorithm is.}
 

### 2018-09-16 ProgramsImages/sim_FourCoef_plot_results.m
make plot label font sizes bigger

@@ -17,8 +17,8 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
-ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
+h = xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'},'FontSize',36)
+ylabel({'Sample size, \(n_{j^{\dagger}}\)'},'FontSize',36)
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
@@ -32,6 +32,7 @@ set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 %leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 gcf; print -depsc SimFourCoefErr.eps
+return
 
 %% Visualize (only a 2-d projection)
 xcoord = 1; % coordinate with the biggest w

### 2018-09-16 ProgramsImages/sim_FourCoef_plot_results.m
Fix Figure 2 some more

@@ -17,7 +17,7 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-h = xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'},'FontSize',36)
+xlabel({'\(||f-A(f,\varepsilon)||_{\infty}/\varepsilon\)'},'FontSize',36)
 ylabel({'Sample size, \(n_{j^{\dagger}}\)'},'FontSize',36)
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
@@ -32,7 +32,6 @@ set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 %leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 gcf; print -depsc SimFourCoefErr.eps
-return
 
 %% Visualize (only a 2-d projection)
 xcoord = 1; % coordinate with the biggest w

### 2018-09-16 ProgramsImages/sim_FourCoef_plot_results.m
Updates from ShareLaTeX

@@ -17,8 +17,8 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-h = xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'},'FontSize',36)
-ylabel({'Sample size, \(n_{j^{\dagger}}\)'},'FontSize',36)
+xlabel({'\(||f-\hat{f}||_{\infty}/\varepsilon\)'})
+ylabel({'Sample size, \(n_{j^{\dagger}}\)'})
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')
 tickVals = floor(min_log10_eps):ceil(max_log10_eps);
@@ -32,7 +32,6 @@ set(hcb,'Ticks',tickVals,'TickLabels',tickLabels, ...
 set(gcf,'Position',[200,200,1000,500]) %make figure big enough and the right aspect ratio
 %leg_icons(2).Children.MarkerSize = 30; %make legend icons large enough
 gcf; print -depsc SimFourCoefErr.eps
-return
 
 %% Visualize (only a 2-d projection)
 xcoord = 1; % coordinate with the biggest w

### 2018-09-16 ProgramsImages/sim_FourCoef_plot_results.m
still fixing Fig. 2

@@ -17,7 +17,7 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-A(f,\varepsilon)||_{\infty}/\varepsilon\)'},'FontSize',36)
+xlabel({'\(||f-\tilde{A}(f,\varepsilon)||_{2}/\varepsilon\)'},'FontSize',36)
 ylabel({'Sample size, \(n_{j^{\dagger}}\)'},'FontSize',36)
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')

### 2018-09-16 AutoAlgorithmLinearFunctionalDataVerC.tex

@@
 
-\tonynote{It looks like the font size in Figure 2 is smaller than that of Figure 1. Perhaps it would be easier to read if a bit larger?}
-
-\tonynote{In the x-axis of Figure 2, we mention $\hat{f}$.
-Is it referring to the Fourier coefficients?
-As a suggestion, are we not interested in something like $\DHJRnorm[\mathcal{G}]{S(f)-\widetilde{A}({f},\varepsilon)}$?
-This could allow us to plot marks at the different $\varepsilon$ and see how conservative the algorithm is.}
-
 \section{Discussion and Conclusion} \label{sec:conc}

### 2018-09-17 ProgramsImages/sim_FourCoef_plot_results.m
Added line to sim_FourCoef_plot_results.m for testing

@@ -1,4 +1,5 @@
 %%Plot results
+%Hello Overleaf
 function sim_FourCoef_plot_results(basisName)
 
 load(['sim_FourCoef_results_basis_' basisName '.mat'], ...

### 2018-09-19 ProgramsImages/sim_FourCoef_plot_results.m
fixed latexmkrc

@@ -1,5 +1,4 @@
 %%Plot results
-%Hello Overleaf
 function sim_FourCoef_plot_results(basisName)
 
 load(['sim_FourCoef_results_basis_' basisName '.mat'], ...

### 2018-09-23 AutoAlgorithmLinearFunctionalDataVerC.tex
Updates from ShareLaTeX
Update

@@
 
-\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ to within some error tolerance for all inputs in $\calH$:
+\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ within some error tolerance for all inputs in $\calH$:
 \begin{multline} \label{adapErrCrit}
@@
 
-To illustrate these concepts, consider a non-decreasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
+To illustrate these concepts, consider a non-increasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
 Also consider an unbounded strictly increasing sequence of non-negative integers $\bsn = \{n_0, n_1, \ldots \}$.
@@
  		\includegraphics[width =7.5 cm]{ProgramsImages/SimFourCoefErr.eps}
- 	\caption{Sample size $n_{j^{\dagger}}$, error tolerance $\varepsilon$, and ratio. \label{errfig}} % 
+ 	\caption{Sample size $n_{j^{\dagger}}$, error tolerance $\varepsilon$, and ratio of true error to error tolerance. \label{errfig}} % 
  \end{figure}

### 2018-09-24 ProgramsImages/sim_FourCoef_plot_results.m
fixed plot axis labels

@@ -17,7 +17,7 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||f-\tilde{A}(f,\varepsilon)||_{2}/\varepsilon\)'},'FontSize',36)
+xlabel({'\(||S(f)-\tilde{A}(f,\varepsilon)||_{2}/\varepsilon\)'},'FontSize',36)
 ylabel({'Sample size, \(n_{j^{\dagger}}\)'},'FontSize',36)
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')

### 2018-09-24 AutoAlgorithmLinearFunctionalDataVerC.tex

@@
 The algorithm employs continuous linear functionals of the input function, specifically Fourier coefficients.
-We assume that the Fourier coefficients of the solution to be approximated decay sufficiently fast, but do not require the decay rate to be known a priori.
+We assume that the Fourier coefficients of the solution decay sufficiently fast, but do not require the decay rate to be known a priori.
 We also assume that the Fourier coefficients decay steadily, although not necessarily monotonically.
@@
 We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$.
-Thus, our arguments are irrelevant for evaluating the definite integral or any other linear functional, since in those cases $\lambda_2 = \lambda_3 = \cdots = 0$.
 
@@
 
-Our problem is not solvable for $\calF$, as can be demonstrated by contradiction.
+Our problem is not solvable for the whole Hilbert space $\calF$, as can be demonstrated by contradiction.
 For any potential algorithm, we show that there exists some $f \in \calF$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
@@
 \subsection{Computational Cost of the Algorithm and Complexity of the Problem} The computational cost of an algorithm $A \in \calA(\calH)$ for $f \in \calH$ and error tolerance $\varepsilon$ is denoted $\textup{cost}(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
-By overloading the notation, we define the cost of algorithms as
+By overloading the notation, we define the cost of algorithms for sets of inputs, $\calH$, as
 \begin{equation*}
@@
 For unbounded sets, $\calH$, this cost may be infinite.
-Therefore, we also define the cost of algorithms for input functions in $\calH \cap \calB_{\rho}$, where $\calB_{\rho} : = \{ f \in \calF : \DHJRnorm[\calF]{f} \le \rho \}$ is the ball of radius $\rho$:
+Therefore, it is meaningful to define the cost of algorithms for input functions in $\calH \cap \calB_{\rho}$, where $\calB_{\rho} : = \{ f \in \calF : \DHJRnorm[\calF]{f} \le \rho \}$ is the ball of radius $\rho$:
 \begin{equation*}
@@
 
-To illustrate these concepts, consider a non-increasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
+Our condition for essentially no worse cost in \eqref{essNoWorseDef} is not the same as 
+\begin{equation} \label{NOTessNoWorseDef}
+    \textup{cost}(A,\calH,\varepsilon,\rho)
+    \le 
+    \omega \, \textup{cost}(A^*,\calH^*,\varepsilon,\rho)
+    \qquad \forall \varepsilon,\rho > 0.
+\end{equation}
+If the $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ is proportional to $\max(1,\varepsilon^{-p})$, then conditions \eqref{essNoWorseDef} and \eqref{NOTessNoWorseDef} are equivalent.
+If $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ is proportional to $[1+\log(\max(1,\varepsilon)]^{-p}$, then \eqref{essNoWorseDef} is stricter than \eqref{NOTessNoWorseDef}.
+
+To illustrate the comparison of costs, consider a non-increasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
 Also consider an unbounded strictly increasing sequence of non-negative integers $\bsn = \{n_0, n_1, \ldots \}$.
@@
 For bounded sets of input functions, such as balls, non-adaptive algorithms like $\widehat{A}$ make sense.
-However, it is typically unknown which ball the input function lies in.
-Thus, we consider unbounded sets of input functions, whose properties can be inferred from the data we collect.
-We use the interpolatory algorithm $A_n$, defined in \eqref{optAdef}, but we propose an alternative way to bound the error other than assuming an a priori bound on $\DHJRnorm[\calF]{f}$.
+However, an a priori upper bound on $\DHJRnorm[\calF]{f}$ is typically unavailable in practice, so it is unknown which $\calB_{\rho}$ contain the input function $f$.
+Our aim is to consider unbounded sets of $f$ for which the error of the interpolatory algorithm $A_n(f)$, defined in \eqref{optAdef}, can be bounded without an a priori upper bound on $\DHJRnorm[\calF]{f}$.
 
@@
 
-Our rigorous, data-driven error bound assumes the series coefficients of the input to decay steadily---but not necessarily monotonically.
-The cone of nice inputs, $\calC$, is defined in Section \ref{sec:cone}.
+Our rigorous, data-driven error bound assumes the series coefficients of the input function, $f$, to decay steadily---but not necessarily monotonically.
+The cone of nice input functions, $\calC$, is defined in Section \ref{sec:cone}.
 For such inputs, we construct an adaptive algorithm, $\widetilde{A} \in \calA(\calC)$, in Section \ref{sec:adaptalgo},  where $\widetilde{A}(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$ depending on the input data and the definition of $\calC$.
@@
 \end{align}
-Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\calC$ and 
+Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\calC$ and satisfy
 \begin{equation} \label{abcond}
@@
 The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
-We do not expect the series coefficients of the solution $S(f)$, to decay monotonically.
+Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $S(f)$, to decay monotonically.
 However, we expect their partial sums to decay steadily.

### 2018-09-24 ProgramsImages/sim_FourCoef_plot_results.m
tidying up article

@@ -17,7 +17,7 @@ set(gca,'XScale','log', 'YScale','log')
 xlim([min([10.^floor(log10(rat_vec*0.8)); 0.1]) ...
  max([10.^(ceil(log10(rat_vec*1.2))); 1])])
 ylim(10.^[floor(log10(min(n_vec))) ceil(log10(max(n_vec)))])
-xlabel({'\(||S(f)-\tilde{A}(f,\varepsilon)||_{2}/\varepsilon\)'},'FontSize',36)
+xlabel({'\(||f-\tilde{A}(f,\varepsilon)||_{2}/\varepsilon\)'},'FontSize',36)
 ylabel({'Sample size, \(n_{j^{\dagger}}\)'},'FontSize',36)
 hcb = colorbar; %showing tolerance values
 title(hcb,'\(\varepsilon\)','interpreter','latex')

### 2018-09-24 AutoAlgorithmLinearFunctionalDataVerC.tex
Fred's edits finished, I hope

@@
 
-For the remainder of the proof consider $\rho$ and $\varepsilon$ fixed.
+For the remainder of the proof consider $\rho$ and $\varepsilon$ to be fixed.
 To derive an upper bound on $n_{j^\dagger} = \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$ we first note some properties of $\sigma_j(f)$ for all $f \in \calC$:
@@
 
-The adaptive algorithm $\widetilde{A}$, which does not know an upper bound on $\DHJRnorm[\calF]{f}$ a priori, may cost more than the non-adaptive algorithm $\widehat{A}$, which assumes an upper bound on $\DHJRnorm[\calF]{f}$, but under reasonable assumptions, the extra cost will be small.
+The adaptive algorithm $\widetilde{A}$, which does not know an upper bound on $\DHJRnorm[\calF]{f}$ a priori, may cost more than the non-adaptive algorithm $\widehat{A}$, which assumes an upper bound on $\DHJRnorm[\calF]{f}$, but under reasonable assumptions, the extra cost is small.
 
@@
 The key idea of our algorithm is to derive an adaptive error bound by assuming the steady decay of the Fourier series coefficients of the solution.
-We do not, however, need to know the decay rate of these coefficients a priori.
+The set of such functions constitutes a cone.
+We do not need to know the decay rate of these coefficients a priori.
 The cost of our algorithm also serves as a goal for an algorithm that uses function values, which are more commonly available than Fourier series coefficients.
 An important next step is to identify an essentially optimal algorithm based on function values.
-Another research direction would be to extend this setting to Banach spaces.
+Another research direction is to extend this setting to Banach spaces of inputs and/or outputs.
 

### 2018-09-27 AutoAlgorithmLinearFunctionalDataVerC.tex
remove the unused number

@@
 Define an algorithm $A^*$ analogously to $\widehat{A}$ defined in \eqref{optBallalg}:
-\begin{equation} \label{altBallalg}
+\begin{equation*} \label{altBallalg}
 A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \calA(\calB_{\rho}).
-\end{equation}
+\end{equation*}
 By definition, the cost of algorithm $A^*$ is no better than that of  $\widehat{A}$.
@@
 Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\calC$ and satisfy
-\begin{equation} \label{abcond}
+\begin{equation*} \label{abcond}
 b <1 < a.
-\end{equation}
+\end{equation*}
 The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
@@
 Consider the choice 
-\begin{equation} \label{geonj}
+\begin{equation*} \label{geonj}
 n_j = 2^{j}n_0,
-\end{equation}
+\end{equation*}
 where the number of terms in the sums, $\sigma_j(f)$, are doubled at each step.
@@
 \item[Step 2.] Check whether $j$ is large enough to satisfy the error tolerance, i.e.,
-    \begin{equation}\label{covcrit}
+    \begin{equation*}\label{covcrit}
           \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab} .
-    \end{equation}
+    \end{equation*}
     If this is true, then return $\widetilde{A}(f,\varepsilon) = A_{n_{j}}(f)$, where $A_n$ is defined in \eqref{optAdef}, and terminate the algorithm.
@@
 This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$.
-Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation} \label{keysum}
+Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation*} \label{keysum}
 \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}.
-\end{equation}
+\end{equation*}
 One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.
@@
 Ignoring all but the first term in the sum in \eqref{keysum} implies that 
-\begin{equation} \label{jsumupperbd}
+\begin{equation*} \label{jsumupperbd}
 j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2}    \right\}.
-\end{equation}
+\end{equation*}
 This implies \eqref{jdaggerfirst}.
@@
 Under assumption  \eqref{lambdaRatio}, a lower bound on the complexity of the linear problem defined in \eqref{probDef} is
-\begin{subequations} \label{compbd}
-\begin{align}
- \label{compbdA}
+\begin{align*}
+ %\label{compbdA}
 &\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_{j^*}, 
 \intertext{where}
-\label{compbdB}
+%\label{compbdB}
 j^* & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
@@
 \right \}.
-\end{align}
-\end{subequations}
+\end{align*}
 \end{theorem}
@@
 \\
-\label{cdef}
+\nonumber
 c^2 &:=  \rho^2 \left[ \left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1}.
@@
 \begin{align}
-\label{testfunnorm}
+\nonumber
 \DHJRnorm[\calF]{f}^2 &=  c^2\sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \le \rho^2,
@@
 \begin{align}
-\label{etadef}
+\nonumber
 f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)R}, \\
@@
 \DHJRnorm[\calF]{f_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
-& \le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \DHJRbignorm[\calF]{u^{(k)}}^2\right) + \eta^2 \DHJRbignorm[\calF]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
+& \nonumber 
+\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \DHJRbignorm[\calF]{u^{(k)}}^2\right) + \eta^2 \DHJRbignorm[\calF]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
 \nonumber
 & \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}  \qquad \text{by \eqref{uConstraint}}\\
-&  \le \rho^2,
+& \nonumber 
+\le \rho^2,
 \end{align} 

### 2019-01-02 AutoAlgorithmLinearFunctionalDataVerD.tex
New version after first submission.  Caught some typos.

--- 2018-09-27 AutoAlgorithmLinearFunctionalDataVerC.tex
@@
 Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.
-Let $f$ be a linear combination of $u_1, \ldots, u_{N+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f) = A^*(0)$, and
+Let $f$ be a linear combination of $u_1, \ldots, u_{N+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f, \varepsilon) = A^*(0, \varepsilon)$, and
 \begin{align*}
-\varepsilon & \ge \max_{\pm} \DHJRnorm[\calG]{S(\pm f) - A^*(\pm f)} =  \max_{\pm} \DHJRnorm[\calG]{\pm S( f) - A^*(0)} \\
-& \ge \frac 12 \left [ \DHJRnorm[\calG]{S( f) - A^*(0)} + \DHJRnorm[\calG]{- S( f) - A^*(0)}\right] \\
+\varepsilon & \ge \max_{\pm} \DHJRnorm[\calG]{S(\pm f) - A^*(\pm f, \varepsilon)} =  \max_{\pm} \DHJRnorm[\calG]{\pm S( f) - A^*(0, \varepsilon)} \\
+& \ge \frac 12 \left [ \DHJRnorm[\calG]{S( f) - A^*(0, \varepsilon)} + \DHJRnorm[\calG]{- S( f) - A^*(0, \varepsilon)}\right] \\
 & \ge \DHJRnorm[\calG]{S(f)} 

### 2019-04-06 ReplyToReferee2019-Apr.tex
Updates from Overleaf

\documentclass[letter]{article}
\usepackage{bbm,mathtools,array,longtable,booktabs,graphicx,color,enumitem}

\textwidth 6.5in
\textheight 9in
\hoffset -1in
\voffset -1in
\input MACROS.tex
\begin{document}
\title{Reply to the Referees}
\maketitle

\subsection*{Report beginning ``The submitted paper \ldots''}

\begin{enumerate}
    \item[5.] The norm for $\calF$ has been identified.
\end{enumerate}

\subsection*{Report beginning ``This paper proposes \ldots''}

\begin{enumerate}[labelwidth = 10ex]
    \item[$6^{\text{th}}$ \bullet] The norm does depend on the $\lambda_i$ because the $u_i$ depend on the $\lambda_i$.  This is clearer not that the norm for $\calF$ has been identified.
\end{enumerate}

\subsection*{Report beginning ``This article studies \ldots''}

\begin{enumerate}
    \item[??] 
\end{enumerate}

\end{document}

### 2019-04-06 AutoAlgorithmLinearFunctionalDataVerE.tex
Updates from Overleaf

--- 2019-01-02 AutoAlgorithmLinearFunctionalDataVerD.tex
@@
 
-% Macros below are now inclded in macros.tex from MCQMC 2016 web site
+% Macros below are now included in macros.tex from MCQMC 2016 web site
 % This spot formerly included macros that are now in macros.tex
@@
 \newcommand{\DHJRnorm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
+\newcommand{\DHJRnormnorm}[2][{}]{\ensuremath{\lVert #2 \rVert}_{#1}}
 \newcommand{\DHJRbignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
@@
 	\\
-	&&\widehat{f}_i& = \begin{cases} \widehat{f}(-i/2), & i \text{ even},\\
+		\DHJRnorm[\calF]{f}^2 & = \left( \int_0^1 f(x) \, \D x \right)^2 + \frac{\DHJRnormnorm[2]{f^{(r)}}^2}{(2 \pi)^{2r}} 
+	&\widehat{f}_i& = \begin{cases} \widehat{f}(-i/2), & i \text{ even},\\
 	\widehat{f}((i-1)/2), & i \text{ odd},
 	\end{cases}
+		\\
+		\DHJRnorm[\calG]{g}& = \DHJRnorm[2]{g} 
 	\end{align*}
@@
 	\end{align*}
-	Here, $\calG=L^2[0,1]$.
-The larger the non-negative parameter $r$ is, the faster the $\lambda_i$ tend to 0 as $ i \to 0$, the more exclusive $\calB_\rho$ is, and the smaller  $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ is.
-For $r = 0$, $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon) = \infty$.
+	Here, $r$ is a positive integer, and $\calF$ consists of functions that have absolutely continuous, periodic $r-1$ derivatives.
+A larger $r$ implies a stronger $\calF$-norm, a more exclusive $\calB_\rho$, and a smaller  $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$.
 \end{example}

### 2019-05-08 ReplyToReferee2019-Apr.tex
Updates from Overleaf

@@
 
+Regarding the comment about why a cone is preferred above a ball \ldots
+
 \begin{enumerate}
+    \item[1.] The first sentence is Subsection 1.1 has been rephrased.
+    \item[2.] The sufficient and necessary conditions of the existence of singular value decomposition has been added  to  the last paragraph of Subsection 1.1
+    \item[3.] \textit{linear functionals are used} changed to 
+    \textit{linear functionals that are used}
+    \item[4.] Inserted \textit{the} before the algorithm
     \item[5.] The norm for $\calF$ has been identified.
@@
 \begin{enumerate}[labelwidth = 10ex]
-    \item[$6^{\text{th}}$ \bullet] The norm does depend on the $\lambda_i$ because the $u_i$ depend on the $\lambda_i$.  This is clearer not that the norm for $\calF$ has been identified.
+    \item[$1^{\text{st}}$ \bullet] Replaced
+    $\sum\limits_{i =1 }^n$ by $\sum\limits_{i \in \mathbb{N} }$
+    \item[$2^{\text{nd}}$ \bullet] Added one paragraph to end of \S 1.1 to foreshadow Example 1 and the numerical example.
+    \item[$3^{\text{rd}}$ \bullet] Inserted "that"
+    \item[$4^{\text{th}}$ \bullet] Replaced $A(0,\varepsilon)$ 
+    with $A(f,\varepsilon)$
+    \item[$5^{\text{th}}$ \bullet] Matched the notation for the sample size to the notation for the corresponding algorithm before Section 3,  for example,
+    $\widehat{A} \leftrightarrow \widehat{n}, \widetilde{A} \leftrightarrow \widetilde{n},
+    A^* \leftrightarrow n^*$. As after section 3, we used a sequence $\bsn = \{n_0, n_1, \ldots \}.$ 
+     \item[$6^{\text{th}}$ \bullet] The norm \emph{does} depend on the $\lambda_i$ because the $u_i$ depend on the $\lambda_i$.  This is clearer now that the norm for $\calF$ has been identified.
+    \item[$7^{\text{th}}$ \bullet] Added $\exists \omega >0:$ to the definition
+    \item[$8^{\text{th}}$ \bullet] Added for some $p>0$
+    \item[$9^{\text{th}}$ \bullet] Changed ``no better than'' to ``no smaller than''
+    \item[$10^{\text{th}}$ \bullet] Thanks for the correction. Changed to $1/2 -p$.
+     \item[$11^{\text{th}}$ \bullet] Changed ``then'' to ``we have''
+      \item[$12^{\text{th}}$ \bullet] Corrected the reference of the formula
+      \item[$13^{\text{th}}$ \bullet]
+       \begin{itemize}
+       \item[$-$] Changed the inequality to 
+      $n + 1\le \textup{comp}(\calA(\calC),\varepsilon,\rho) +1 \le n_j$ to make the proof consistent.
+      \item[$-$] As $n$ is the sample size for a particular function of the optimal algorithm, it is possible 
+      $n < \textup{cost}(A^*,\calC,\varepsilon,\rho) =  \textup{comp}(\calA(\calC),\varepsilon,\rho).$ 
+           \item[$-$] Removed ``by (21)''
+           \item[$-$] Added some derivation to illustrate it.
+            \item[$-$] Changed to round brackets
+            \item[$-$] Thanks for the suggestion. Changed to it. The last equality holds
+            because the sum in the $\min$ ends at $j+1$ term and the sum in the $\max$ ends at $j$ term.
+            \[\min \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} 
+= \max \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\}\]
+       \end{itemize}
 \end{enumerate}
 
-\subsection*{Report beginning ``This article studies \ldots''}
+\subsection*{Report beginning  \item[$9^{\text{th}}$ \bullet]This article studies \ldots''}
+
+Regarding the conditions (6) and (7), we have added some examples and explanation after we introduced these two conditions.
 
 \begin{enumerate}
-    \item[??] 
+    \item[1] Changed to ``Hence, the algorithm''
+    \item[2] Changed to ``and the algorithm''
+    \item[3] Changed to ``If for some $p > 0$ ''
+    \item[4] Thanks for the comment. Used a different function.
+    \item[5] Thanks for the comment. Added the examples.
+    \item[6] Have added the period at the end of the formula.
+    \item[7] Thanks for the comment. We added a clarification at the end of Section 2.
+    \item[8] Changed to $\lambda_i |\widehat{f}_i|$
+    \item[9] Changed the assumption to 
+    $\lambda_i |\widehat{f}_i| =\Theta(i^{-p})$
+    \item[10] Removed $\forall j  \ge 1$
+    \item[11] Changed $\div$ to $/$
+    \item[12] There is no $+1$ because there is no $b$ in the term
+    $ \log\left(\frac{\rho a^2\lambda_{n_{0}+1} }{\varepsilon \sqrt{1 - b^2}}\right)$.
+    It's been cancelled out as
+    \[\frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2} =  \frac{(1 - b^2)}{a^2} \frac{b^{-2j}}{a^2\lambda_{n_{0}+1}^2}\]
+    \item[13] Corrected the reference of the formula
+    \item[14] Erased $\le n_{j^\dagger}+1$ and changed the last inequality to
+    \[
+    \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = \widetilde{n}_{j^\dagger} \le  \widehat{n} = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
+    \]
+    \item[15] Changed $j^*$ to $j^{\ddagger}$
 \end{enumerate}

### 2019-05-08 AutoAlgorithmLinearFunctionalDataVerE.tex
Updates from Overleaf

@@
 \newcommand{\DHJRabs}[1]{\ensuremath{{\left \lvert #1 \right \rvert}}}
+\newcommand{\DHJRbigabs}[1]{\ensuremath{{\bigl \lvert #1 \bigr \rvert}}}
 
@@
 \abstract{Automatic algorithms attempt to provide approximate solutions that differ from exact solutions by no more than a user-specified error tolerance.
-This paper describes an automatic, adaptive algorithm for approximating the solution to a general linear problem on Hilbert spaces.
+This paper describes an automatic, adaptive algorithm for approximating the solution to a general linear problem defined on Hilbert spaces.
 The algorithm employs continuous linear functionals of the input function, specifically Fourier coefficients.
-We assume that the Fourier coefficients of the solution decay sufficiently fast, but do not require the decay rate to be known a priori.
+We assume that the Fourier coefficients of the solution decay sufficiently fast, but we do not require the decay rate to be known a priori.
 We also assume that the Fourier coefficients decay steadily, although not necessarily monotonically.
@@
 
-\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $\{u_i\}_{i \in \bbN}$, let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $\{v_i\}_{i\in \bbN}$, and let their norms be defined as the $\ell^2$-norms of their series coefficients:
+\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $(u_i)_{i \in \bbN}$, and let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $(v_i)_{i\in \bbN}$.
+Based on Parseval's identity  the norms for these two spaces may be expressed as the $\ell^2$-norms of their series coefficients:
 \begin{subequations}\label{probDef}
@@
 \begin{gather}
-S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i=1}^n \lambda_i \widehat{f}_i v_i, \\
+S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i\in \bbN} \lambda_i \widehat{f}_i v_i, \\
 \lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
@@
 This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.
-We focus on cases where the exact solution generally requires an infinite number of series coefficients, $\widehat{f}_i$.
+We focus on cases where the exact solution requires an infinite number of series coefficients, $\widehat{f}_i$, in general.
 
 The existence of the $( u_i )_{i \in \bbN}$, $ ( v_i )_{i \in \bbN}$, and $( \lambda_i )_{i \in \bbN}$ for a given $\calF$, $\calG$, and $S$ follows from the singular value decomposition.
+The singular value decomposition with singular values tending to zero (but never equal to zero) exists if (and only if ) the solution operator is compact and not finite rank.
 The ease of identifying explicit expressions for these quantities depends on the particular problem of interest.
@@
 
-\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ within some error tolerance for all inputs in $\calH$:
+Example \ref{exam:exam1} in Section \ref{subsec:costandcomplex} illustrates this general setting.  Section \ref{sec:examp} provides a numerical example based on this example.
+
+\subsection{Solvability}  Let $\calH$ be any subset of $\calF$, and let $\calA(\calH)$ denote the set of deterministic algorithms that successfully approximate the solution operator $S : \calH \to \calG$ within the specified error tolerance for all inputs in $\calH$:
 \begin{multline} \label{adapErrCrit}
@@
 of the input function.
-They must sample only a finite number of linear functionals for each input function and positive tolerance.
+They must sample only a finite number of linear functionals for each input function and positive error tolerance.
 The definition of $\calH$ can be used to construct algorithms in $\calA(\calH)$, but no other a priori knowledge about the input functions is available.
@@
 
-Our problem is not solvable for the whole Hilbert space $\calF$, as can be demonstrated by contradiction.
+Our problem is not solvable for the whole Hilbert space, $\calF$, as can be demonstrated by contradiction.
 For any potential algorithm, we show that there exists some $f \in \calF$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
-Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$.
+Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals that are used to compute $A(f,\varepsilon)$.
 Since the output space, $\calG$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \calF$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
@@
 \begin{align*}
-    \varepsilon &\ge \frac 12 \left[ \DHJRnorm[\calG]{S(0) - A(0,\varepsilon)} + \DHJRnorm[\calG]{S(cf) - A(cf,\varepsilon)}\right] \\
-    & =  \frac 12 \left[ \DHJRnorm[\calG]{0 - A(0,\varepsilon)} + \DHJRnorm[\calG]{S(cf) - A(0,\varepsilon)}\right] \\
-    & \ge  \frac {\DHJRnorm[\calG]{cS(f)}}2 = \frac {\DHJRabs{c}\DHJRnorm[\calG]{S(f)}}2  \qquad \text{by the triangle inequality}.
+    \varepsilon &\ge \frac 12 \left[ \DHJRnorm[\calG]{S(cf) - A(cf,\varepsilon)} + \DHJRnorm[\calG]{S(-cf) - A(-cf,\varepsilon)}\right] \\
+    & =  \frac 12 \left[ \DHJRnorm[\calG]{cS(f) - A(0,\varepsilon)} + \DHJRnorm[\calG]{-cS(f) - A(0,\varepsilon)}\right] \\
+    & \ge  \DHJRnorm[\calG]{cS(f)} = \DHJRabs{c}\DHJRnorm[\calG]{S(f)}  \qquad \text{by the triangle inequality}.
 \end{align*}
@@
 The presumed $A$ does not exist, $\calA(\calF)$ is empty, and our problem is not solvable for $\calF$.
-However, it is solvable for well-chosen subsets of $\calF$, as will be shown in the sections below.
+However, it is solvable for well-chosen subsets of $\calF$, as is shown in the sections below.
 
-\subsection{Computational Cost of the Algorithm and Complexity of the Problem} The computational cost of an algorithm $A \in \calA(\calH)$ for $f \in \calH$ and error tolerance $\varepsilon$ is denoted $\textup{cost}(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
+\subsection{Computational Cost of the Algorithm and Complexity of the Problem}
+\label{subsec:costandcomplex}
+The computational cost of an algorithm $A \in \calA(\calH)$ for $f \in \calH$ and error tolerance $\varepsilon$ is denoted $\textup{cost}(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.
 By overloading the notation, we define the cost of algorithms for sets of inputs, $\calH$, as
@@
 \begin{equation} \label{optBallalg}
-\widehat{A}(f,\varepsilon) = A_{n^*}(f), \quad \text{where } n^* = \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}, \qquad \widehat{A} \in \calA(\calB_{\rho}).
+\widehat{A}(f,\varepsilon) = A_{\widehat{n}}(f), \quad \text{where } \widehat{n}= \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \}, \qquad \widehat{A} \in \calA(\calB_{\rho}).
 \end{equation}
@@
 
-To prove this, let $A^*$ be an arbitrary algorithm in $\calA(\calB_{\rho})$, and let $L_1, \ldots, L_N$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.
-Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_N(0)) = (0, \ldots, 0)$.
-Let $f$ be a linear combination of $u_1, \ldots, u_{N+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_N(f) = 0$, then $A^*(\pm f, \varepsilon) = A^*(0, \varepsilon)$, and
+To prove this, let $A^*$ be an arbitrary algorithm in $\calA(\calB_{\rho})$, and let $L_1, \ldots, L_{n^*}$ be the linear functionals chosen when evaluating this algorithm for the zero function with tolerance $\varepsilon$.
+Thus, $A^*(0,\varepsilon)$ is some function of $(L_1(0) , \ldots, L_{n^*}(0)) = (0, \ldots, 0)$.
+Let $f$ be a linear combination of $u_1, \ldots, u_{n^*+1}$ with norm $\rho$ satisfying  $L_1(f) = \cdots = L_{n^*}(f) = 0$, then $A^*(\pm f, \varepsilon) = A^*(0, \varepsilon)$, and
 \begin{align*}
@@
 & \ge \DHJRnorm[\calG]{S(f)} 
-= \DHJRBignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{N+1}} \\
-& \ge \lambda_{N+1} \DHJRBignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{N+1}} = \lambda_{N+1} \DHJRnorm[\calF]{f} = \lambda_{N+1} \rho.
+= \DHJRBignorm[2]{\big(\lambda_i\widehat{f}_i\big)_{i=1}^{n^*+1}} \\
+& \ge \lambda_{n^*+1} \DHJRBignorm[2]{\big(\widehat{f}_i\big)_{i=1}^{n^*+1}} = \lambda_{n^*+1} \DHJRnorm[\calF]{f} = \lambda_{n^*+1} \rho.
 \end{align*}
-Thus, $\lambda_{N+1} \le \varepsilon/\rho$, and 
+Thus, $\lambda_{n^*+1} \le \varepsilon/\rho$, and 
 \[
-\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = N \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widehat{A},\calB_\rho,\varepsilon).
+\textup{cost}(A^*,\calB_\rho,\varepsilon) \ge \textup{cost}(A^*,0,\varepsilon)  = n^* \ge \min\{ n : \lambda_{n+1} \le \varepsilon/\rho \} = \textup{cost}(\widehat{A},\calB_\rho,\varepsilon).
 \]
-Hence, algorithm $\widehat{A}$ defined in \eqref{optBallalg} is optimal for $\calA(\calB_{\rho})$.
+Hence, the algorithm $\widehat{A}$ defined in \eqref{optBallalg} is optimal for $\calA(\calB_{\rho})$.
 
-\begin{example} Consider the case of function approximation for periodic functions defined over [0,1], and algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
+\begin{example}\label{exam:exam1} Consider the case of function approximation for periodic functions defined over [0,1], and the algorithm $\widehat{A}$ defined in \eqref{optBallalg}:
 	\begin{align*}
@@
 	\\
-		\DHJRnorm[\calF]{f}^2 & = \left( \int_0^1 f(x) \, \D x \right)^2 + \frac{\DHJRnormnorm[2]{f^{(r)}}^2}{(2 \pi)^{2r}} 
+		\DHJRnorm[\calF]{f}^2 & = \left( \int_0^1 f(x) \, \D x \right)^2 + \frac{\DHJRnormnorm[2]{f^{(r)}}^2}{(2 \pi)^{2r}}, \quad r \in \N, 
 	&\widehat{f}_i& = \begin{cases} \widehat{f}(-i/2), & i \text{ even},\\
@@
 		\\
-		\DHJRnorm[\calG]{g}& = \DHJRnorm[2]{g} 
+		\DHJRnorm[\calG]{g}& = \DHJRnorm[2]{g},
 	\end{align*}
@@
 	\end{align*}
-	Here, $r$ is a positive integer, and $\calF$ consists of functions that have absolutely continuous, periodic $r-1$ derivatives.
+	Here, $r$ is positive.
+If $r$ is an integer, then $\calF$ consists of functions that have absolutely continuous, periodic derivatives of up to order $r-1$.
 A larger $r$ implies a stronger $\calF$-norm, a more exclusive $\calB_\rho$, and a smaller  $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$.
@@
 
-Our goal is to construct algorithms in $\calA(\calH)$ for some $\calH$ and also to determine whether their computational cost is reasonable.
-We define  $\textup{cost}(A,\calH,\varepsilon,\rho)$ to be \emph{essentially no worse} than $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ if for some number $\omega$,
+Our goal is to construct algorithms in $\calA(\calH)$ for some $\calH$ and also to determine whether the computational cost of these algorithms is reasonable.
+We define  $\textup{cost}(A,\calH,\varepsilon,\rho)$ to be \emph{essentially no worse} than $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ if  there exists
+$\omega > 0$ such that
 \begin{equation} \label{essNoWorseDef}
@@
 If these inequalities are not satisfied, we say that the cost of  $A$ is \emph{essentially worse}  than the cost of $A^*$.
-If the costs of two algorithms are essentially no worse than each other, then we call them essentially the same.
+If the costs of two algorithms are essentially no worse than each other, then we call their costs essentially the same.
 An algorithm whose cost is essentially no worse than the best possible algorithm, is called \emph{essentially optimal}.
@@
 \end{equation}
-If the $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ is proportional to $\max(1,\varepsilon^{-p})$, then conditions \eqref{essNoWorseDef} and \eqref{NOTessNoWorseDef} are equivalent.
-If $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ is proportional to $[1+\log(\max(1,\varepsilon)]^{-p}$, then \eqref{essNoWorseDef} is stricter than \eqref{NOTessNoWorseDef}.
+If the cost grows polynomially in $\varepsilon^{-1}$, then conditions \eqref{essNoWorseDef} and \eqref{NOTessNoWorseDef} are basically the same.  If for some positive $p$ and $p^*$,
+\[
+\textup{cost}(A,\calH,\varepsilon,\rho) \le  C (1+\varepsilon^{-p}\rho^p) \quad \text{and} \quad C^* (1+\varepsilon^{-p^*}\rho^{p^*}) \le \textup{cost}(A^*,\calH^*,\varepsilon,\rho),
+\]
+then $\textup{cost}(A,\calH,\varepsilon,\rho)$ is essentially no worse than $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$ iff $p \le p^*$ under either condition \eqref{essNoWorseDef} or \eqref{NOTessNoWorseDef}.
+However, if the cost grows only logarithmically in $\varepsilon^{-p}$, then condition \eqref{essNoWorseDef} makes more sense than \eqref{NOTessNoWorseDef}.
+Specifically, if
+\begin{multline*}
+\textup{cost}(A,\calH,\varepsilon,\rho) \le  C + \log\bigl(1 + \varepsilon^{-p}\rho^p\bigr) \quad \text{and} \quad
+\\ C^* + \log\bigl(1+\varepsilon^{-p^*}\rho^{p^*}\bigr) \le \textup{cost}(A^*,\calH^*,\varepsilon,\rho),
+\end{multline*}
+then condition  \eqref{essNoWorseDef} requires $p \le p^*$ for  $\textup{cost}(A,\calH,\varepsilon,\rho)$ to be essentially no worse than $\textup{cost}(A^*,\calH^*,\varepsilon,\rho)$, whereas \eqref{NOTessNoWorseDef} allows this to be true even for $p > p^*$.
+We grant that if the cost grows faster than polynomially in $\varepsilon^{-1}$, then \eqref{NOTessNoWorseDef} may be the preferred condition.
 
-To illustrate the comparison of costs, consider a non-increasing sequence of positive numbers, $ \{\lambda^*_1, \lambda^*_2, \ldots \}$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
-Also consider an unbounded strictly increasing sequence of non-negative integers $\bsn = \{n_0, n_1, \ldots \}$.
+To illustrate the comparison of costs, consider a non-increasing sequence of positive numbers, $ \bslambda^*=(\lambda^*_1, \lambda^*_2, \ldots )$, which converges to $0$, where $\lambda^*_i \ge \lambda_i$ for all $i \in \bbN$.
+Also consider an unbounded, strictly increasing sequence of non-negative integers $\bsn = (n_0, n_1, \ldots )$.
 Define an algorithm $A^*$ analogously to $\widehat{A}$ defined in \eqref{optBallalg}:
 \begin{equation*} \label{altBallalg}
-A^*(f,\varepsilon) = A_{n_{j^\dagger}}(f), \quad \text{where } j^\dagger = \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \}, \qquad A^* \in \calA(\calB_{\rho}).
+A^*(f,\varepsilon) = A_{n^*}(f),  \text{ where } n^* = n_{j^*},\ j^*= \min\{ j : \lambda^*_{n_j+1} \le \varepsilon/\rho \},\quad  A^* \in \calA(\calB_{\rho}).
 \end{equation*}
-By definition, the cost of algorithm $A^*$ is no better than that of  $\widehat{A}$.
+By definition, the cost of algorithm $A^*$ is no smaller than that of  $\widehat{A}$.
 Algorithm $A^*$ may or may not have essentially worse cost than $\widehat{A}$ depending on the choice of $\bslambda^*$ and $\bsn$.
@@
 
-Adaptive algorithms encountered in practice typically employ heuristic error bounds.
-While any algorithm can be fooled, we would like precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.
+\begin{figure}[ht]
+	\centering
+	\begin{tabular}{cc}
+		\includegraphics[width=5.5cm]{ProgramsImages/Function.eps} &
+		\includegraphics[width=5.5cm]{ProgramsImages/FunctionWalshFourierCoeffDecay.eps}
+		\\ (a) & (b) \\
+		\includegraphics[width =5.5cm]{ProgramsImages/Scaled.eps} &
+		\includegraphics[width=5.5cm]{ProgramsImages/ScaledWalshFourierCoeffDecay.eps}
+		\\ (c) & (d) \\
+		\includegraphics[width=5.5cm]{ProgramsImages/Filtered.eps} &
+		\includegraphics[width=5.5cm]{ProgramsImages/FilteredWalshFourierCoeffDecay.eps}
+		\\ (e) & (f)
+	\end{tabular}
+	\caption{(a) The function $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$; (b) The first Fourier coefficients of $f$; (c) The function $f_{\text{big}}=100f$; (d) The first Fourier coefficients of $f_{\text{big}}$; (e) The function $f_{\text{fuzzy}}$ resulting from modifying some of $f$ coefficients; (f) The first Fourier coefficients of $f_{\text{fuzzy}}$.
+\label{fig:fourier_example}}
+\end{figure}
+
+Popular adaptive algorithms encountered typically employ heuristic error bounds.
+While any algorithm can be fooled, we would like to have precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.
 Our adaptive algorithm has such conditions and follows in the vein of adaptive algorithms developed in \cite{HicEtal14a, HIcEtal14b, HicJim16a, JimHic16a}.
 
-Our rigorous, data-driven error bound assumes the series coefficients of the input function, $f$, to decay steadily---but not necessarily monotonically.
+Our rigorous, data-driven error bound assumes that the series coefficients of the input function, $f$, decay steadily---but not necessarily monotonically.
 The cone of nice input functions, $\calC$, is defined in Section \ref{sec:cone}.
-For such inputs, we construct an adaptive algorithm, $\widetilde{A} \in \calA(\calC)$, in Section \ref{sec:adaptalgo},  where $\widetilde{A}(f,\varepsilon) = A_{n^*}(f)$ for some $n^*$ depending on the input data and the definition of $\calC$.
-The number of series coefficients sampled, $n^*$, is adaptively determined so that $\widetilde{A}(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.
+For such inputs, we construct an adaptive algorithm, $\widetilde{A} \in \calA(\calC)$, in Section \ref{sec:adaptalgo},  where $\widetilde{A}(f,\varepsilon) = A_{\widetilde{n}}(f)$ for some $\widetilde{n}$ depending on the input data and the definition of $\calC$.
+The number of series coefficients sampled, $\widetilde{n}$, is adaptively determined so that $\widetilde{A}(f,\varepsilon)$ satisfies the error condition in \eqref{adapErrCrit}.
 The computational cost of $\widetilde{A}$ is given in  Theorem \ref{thm:compcost}.
 Section \ref{sec:opt} shows that our new algorithm is essentially optimal (see Theorem \ref{thm:CostNoWorse}).
-Section \ref{sec:examp} provides an example of our algorithm.
-We end with concluding remarks in Section \ref{sec:conc}.
+Section \ref{sec:examp} provides a numerical example.
+We end with concluding remarks.
 
@@
 
-However, we can observe the partial sums 
+However, we can observe a finite number of partial sums, 
 \begin{equation} \label{sumdef}
@@
 \end{equation}
-where $\bsn  = \{n_0, n_1, \ldots\}$ is a strictly increasing, unbounded sequence of non-negative integers.
+where $\bsn  = (n_0, n_1, \ldots)$ is an unbounded, strictly increasing sequence of non-negative integers.
 We define the cone of nice input functions to consist of those functions for which the $\sigma_j(f)$ decay at a given rate with respect to one another:
@@
 \nonumber
-& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}\{ab^r\sigma_{j-r}(f)\} \ \ \forall j \in \bbN \right\}.
+& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}ab^r\sigma_{j-r}(f) \ \ \forall j \in \bbN \right\}.
 \end{align}
@@
 &\le \DHJRnorm[2]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
- = \displaystyle ab \sqrt{\frac{1}{1 - b^2}}\sigma_{j}(f)
+ = \displaystyle  \frac{ab}{\sqrt{1 - b^2}}\sigma_{j}(f).
  \label{algoineq}
@@
 The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.
-Moreover, the error of $A_{n_j}(f)$ is asymptotically no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
+Moreover, the error of $A_{n_j}(f)$ is asymptotically no worse than $\sigma_j(f)$.
 Our adaptive algorithm in Section \ref{sec:adaptalgo} increases $j$ until the right hand side is smaller than the error tolerance.
@@
 Consider the choice 
-\begin{equation*} \label{geonj}
-n_j = 2^{j}n_0,
-\end{equation*}
+$n_j = 2^{j}n_0$,
 where the number of terms in the sums, $\sigma_j(f)$, are doubled at each step.
-If the series coefficients of the solution decay like $\lambda_{i} \DHJRabs{f_{i}} = \calO(i^{-p})$ for some $p>1$, then it is reasonable to expect that the $\sigma_j(f)$ are bounded above and below as
+If the series coefficients of the solution decay like $\lambda_{i} \DHJRbigabs{\widehat{f}_{i}} = \Theta(i^{-p})$ for some $p>1/2$, then it is reasonable to expect that the $\sigma_j(f)$ are bounded above and below as
 \begin{equation} \label{algDecJ}
-C_{\textup{lo}} (n_02^j)^{1-p} \le \sigma_j(f) \le C_{\textup{up}} (n_02^j)^{1-p}, \quad   j \in \bbN,
+C_{\textup{lo}} (n_02^j)^{1/2-p} \le \sigma_j(f) \le C_{\textup{up}} (n_02^j)^{1/2-p}, \quad   j \in \bbN,
 \end{equation}
@@
 \begin{equation*} 
-\frac{\sigma_{j+r}(f)}{\sigma_j(f)} \le \frac{C_{\textup{up}} (n_02^{j+r})^{1-p}}{C_{\textup{lo}} (n_02^j)^{1-p}} = \frac{C_{\textup{up}} 2^{r(1-p)}}{C_{\textup{lo}}}\quad   j \in \bbN.
+\frac{\sigma_{j+r}(f)}{\sigma_j(f)} \le \frac{C_{\textup{up}} (n_02^{j+r})^{1/2-p}}{C_{\textup{lo}} (n_02^j)^{1/2-p}} = \frac{C_{\textup{up}} 2^{r(1/2-p)}}{C_{\textup{lo}}}\quad   j \in \bbN.
 \end{equation*}
-Thus, choosing $a \ge C_{\textup{up}}/C_{\textup{lo}}$ and $b \ge 2^{1-p}$ ensures that reasonable inputs $f$ lie inside the cone $\calC$.
+Thus, choosing $a \ge C_{\textup{up}}/C_{\textup{lo}}$ and $b \ge 2^{1/2-p}$ ensures that reasonable inputs $f$ lie inside the cone $\calC$.
+
+Although the definition of the cone in \eqref{decayconedef} constrains the decay rate of $\lambda_{i} \DHJRbigabs{\widehat{f}_{i}}$ it is a rather weak constraint.
+Specifying $a$ and $b$ only implies a lower bound---but not an upper bound---on the $p$ for which $\lambda_{i} \DHJRbigabs{\widehat{f}_{i}}$ can be $\Theta(i^{-p})$.
 
@@
 The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by a more careful argument in a similar vein.  
-For any $f \in  \calC \cap \calB_\rho$ and for any $j < j^* \le j^\dagger$,
+For any $f \in  \calC \cap \calB_\rho$ satisfying $n_{j^*} = \textup{cost}(\widetilde{A},f,\varepsilon) = \textup{cost}(\widetilde{A}, \calC, \varepsilon, \rho) = n_{j^{\dagger}}$ and for any $j < j^* = j^\dagger$,
 \begin{align*}
 \rho^2 &\ge \DHJRnorm[\calF]{f}^2 = \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=1}^{\infty}}^2 \\
-& \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \qquad \forall j \ge 1\\
+& \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \\
 & \ge \sum_{k=1}^j \frac{\sigma_k^2(f)}{\lambda_{n_{k-1}+1}^2} \qquad \text{by \eqref{normsigineq}}\\
@@
 
-For all $j < j^* \le j^\dagger$ it follows from \eqref{eq:OurAlgjstar} that
+So, for any $j < j^* = j^\dagger$ it follows from the termination criterion in \eqref{eq:OurAlgjstar} that
 \begin{equation*}
@@
 
-We note in passing that for our adaptive algorithm
+We note in passing that for our adaptive algorithm,
 \begin{equation*}
- \min \{\textup{cost}(\widetilde{A},f,\varepsilon) : f \in \calC, \ \DHJRnorm[\calF]{f} \ge \rho \} 
+ \min \{\textup{cost}(\widetilde{A},f,\varepsilon) : f \in \calC\setminus \calB_\rho \} 
  \begin{cases} = n_1, & n_0 > 0, \\
@@
 
-The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $\{(\lambda_{n_j})_{j=0}^\infty\}$.
-This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $\{(\lambda_i)_{i=1}^\infty\}$.
+The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $(\lambda_{n_j})_{j=0}^\infty$.
+This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $(\lambda_i)_{i=1}^\infty$.
 Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation*} \label{keysum}
@@
 
-\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, then $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, we have $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdaggerfirst}
-j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}+1} }{\varepsilon \sqrt{1 - b^2}}\right) \div \log\left(\frac{1}{b}\right) \right \rceil.
+j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}+1} }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{b}\right) \right \rceil.
 \end{equation}
@@
 j^\dagger \le
-\left \lceil \log\left(\frac{\rho a\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \div \log\left(\frac{1}{\beta}\right) \right \rceil.
+\left \lceil \log\left(\frac{\rho a\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{\beta}\right) \right \rceil.
 \end{equation}
@@
 \begin{proof}
-Ignoring all but the first term in the sum in \eqref{keysum} implies that 
+Ignoring all but the first term in the sum in \eqref{jdagger} implies that 
 \begin{equation*} \label{jsumupperbd}
@@
 $\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ in the sense of \eqref{essNoWorseDef}. 
-
 \end{corollary}
@@
 \begin{equation*}
-\lambda_{n_{j^\dagger}+1} \ge c_{\lambda}^2 \lambda_{n_{j^\dagger-2}+1} > \frac{\varepsilon c_{\lambda}^2\sqrt{1 - b^2}}{ab \rho} \ge \lambda_{n+1},
+\lambda_{n_{j^\dagger}+1} \ge c_{\lambda}^2 \lambda_{n_{j^\dagger-2}+1} > \frac{\varepsilon c_{\lambda}^2\sqrt{1 - b^2}}{ab \rho} \ge \lambda_{\widehat{n}+1},
 \end{equation*}
-where $n = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab)$.
+where $\widehat{n}
+= \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab)$.
 Since the $\lambda_i$ are non-increasing,
 \begin{equation*}
-\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = n_{j^\dagger} \le n_{j^\dagger}+1 < n = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
+\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = n_{j^\dagger} \le \widehat{n} = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
 \end{equation*}
@@
 \begin{equation} \label{lambdaRatio}
-R = \sup_{k \in \bbN} \frac{\lambda_{n_{k-1}}}{\lambda_{n_k}} < \infty.
+R = \sup_{j \in \bbN} \frac{\lambda_{n_{j-1}}}{\lambda_{n_j}} < \infty.
 \end{equation}
-This means that the $n_k$ are not too far apart with respect to the decay of $\lambda_i$ as $i \to \infty$.
+Hence, the $n_j$ are not too far apart with respect to the decay of the $\lambda_i$ as $i \to \infty$.
 
@@
 
+\frednote{Need to check this proof again}
 \begin{theorem} \label{thm:lowbdcomp}
@@
  %\label{compbdA}
-&\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_{j^*}, 
+&\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_{j^{\ddagger}} - 1, 
 \intertext{where}
 %\label{compbdB}
-j^* & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
+j^{\ddagger} & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
 \frac{\rho^2}{\varepsilon^2}
@@
 Consider a fixed $\rho$ and $\varepsilon$.
-Choose any positive integer $j$ such that $n_j$ exceeds $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
+Choose any positive integer $j$ such that $n_j \ge \textup{comp}(\calA(\calC),\varepsilon,\rho) + 2$.
 The proof proceeds by carefully constructing three test input functions, $f$ and $f_{\pm}$, lying in $\calC \cap \calB_{\rho}$, which yield the same approximate solution but different true solutions.
@@
 
-The first test function $f \in \calC$ is defined in terms of its series coefficients:
+The first test function $f \in \calC$ is defined in terms of its series coefficients as follows:
 \begin{align}
@@
 \[
-n + 1\le \textup{comp}(\calA(\calC),\varepsilon,\rho) +1 < n_j.
+n + 2\le \textup{comp}(\calA(\calC),\varepsilon,\rho) + 2 \le n_j.
 \]
@@
 \end{equation}
-Since $u$ is a linear combination of $n_j >n+1$ basis functions, these constraints can be satisfied.
+Since $u$ is a linear combination of $n_j  \ge n+2$ basis functions, these $n+2$ constraints can be satisfied.
 
@@
 \nonumber
-\DHJRnorm[\calF]{f_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
+\DHJRnorm[\calF]{f_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2  \\
 & \nonumber 
@@
 & \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}  \qquad \text{by \eqref{uConstraint}}\\
+& \nonumber = \left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)c^2 \sum_{k=0}^j\frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \\
 & \nonumber 
-\le \rho^2,
+\le \rho^2 \qquad \text{by the definition of $c$ above}.
 \end{align} 
-so $f_{\pm} \in \calB_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
+So, $f_{\pm} \in \calB_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
 
-Now we must check that $f_\pm \in \calC$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$,
+Now, we must check that $f_\pm \in \calC$. From the definition in \eqref{sumdef} it follows that for $k = 1, \ldots, j$ and $r \ge 1$,
 \begin{equation*}
@@
 =\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
-& =  \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+& =  \rho^2 \left[\left(\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
 \end{align*}
 
-This lower bound must be satisfied by $j$ to be consistent with the assumption $\textup{comp}(\calA(\calC),\varepsilon,\rho) \le n_j - 1$.
-Thus, for any $j$ violating this inequality it follows that $\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_j$.
+This lower bound must be satisfied by $j$ to be consistent with the assumption $\textup{comp}(\calA(\calC),\varepsilon,\rho) \le n_j - 2$.
+Thus, for any $j$ violating this inequality it follows that $\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_j - 1$.
 This implication provides a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
@@
 The next step is to show that the cost of our algorithm is essentially no worse than that of the optimal algorithm.
-
+\frednote{Now this proof needs fixing.}
 \begin{theorem}
@@
 and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$. 
-For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where 
+For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger(\varepsilon,\rho)}$, where 
+\[
+j^\dagger(\varepsilon,\rho) \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}, \]
+and we are showing the explicit dependence of $j^\dagger$ on $\varepsilon$ and $\rho$.  As we have
+\begin{align*} 
+ & \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \\
+&\ge  \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2}  \qquad \text{since } a > 1\\
+&\ge  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2}  \\
+&\ge  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
+&\ge  \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)} \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{by \eqref{lambdaRatio},}
+\end{align*}
+thus 
 \begin{align*} 
 j^\dagger &\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
-&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2} \right\} \qquad \text{since } a > 1\\
-&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2} \right\} \\
-&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
-&\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)} \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{lambdaRatio} } \\
 &\le \min \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{omegadef} } \\
-&= \max \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^*.
+&= \max \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^{\ddagger}.
 \end{align*}
-By Theorem \ref{thm:lowbdcomp}, $\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^*}$, and by the argument above, $n_{j^*} \ge n_{j^\dagger} \ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$.
+By Theorem \ref{thm:lowbdcomp}, $\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^{\ddagger}}$, and by the argument above, $n_{j^{\ddagger}} \ge n_{j^\dagger} \ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$.
 Thus, our algorithm is essentially no more costly than the optimal algorithm.
 \end{proof}
+\tonynote{
+\begin{align*}
+(b^2R^2)^\ell \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} & = (R^2)^\ell\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell}}^2} \\
+& \geq (R^2)^{\ell-1}\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell+1}}^2} \\
+& \geq \sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \\
+& \geq \frac{b^{2(\ell-1)}}{\lambda_{n_{j+\ell-1}}^2}
+\end{align*}
+}
+
+\yuhannote{Let  
+\begin{equation} \label{newomegadef}
+    \omega = \sqrt{\frac{(1 - b^2)b^2}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}},
+\end{equation}
+and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$. 
+For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger(\varepsilon,\rho)}$, where 
+\[
+j^\dagger(\varepsilon,\rho) \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}, \]
+and we are showing the explicit dependence of $j^\dagger$ on $\varepsilon$ and $\rho$.
+As we have
+\begin{align*} 
+ & \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \\
+&\ge  \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2}  \qquad \text{since } a > 1\\
+&=  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2}  \\
+&\ge  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1},\\
+\end{align*}
+and by \eqref{lambdaRatio}, for any $l \in \mathbb{N}$
+\begin{align*}
+(b^2R^2)^\ell \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} & = (R^2)^\ell\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell}}^2} \\
+& \geq (R^2)^{\ell-1}\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell+1}}^2} \\
+& \geq \sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \\
+& \geq \frac{b^{2(\ell-1)}}{\lambda_{n_{j+\ell-1}}^2},
+\end{align*}
+thus 
+\begin{align*} 
+ & \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \\
+&\ge  \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)} \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{by \eqref{lambdaRatio}}\\
+&=  \frac{\omega^2}{b^2}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \qquad \text{by \eqref{newomegadef}.}
+\end{align*}
+Hence,
+\begin{align*} 
+j^\dagger(\varepsilon,\rho) &\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
+&\le \min \left \{j \in \bbN : \frac{\rho^2}{ \varepsilon^2} \le \frac{\omega^2}{b^2}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \\
+&= \min \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+2} \frac{b^{2(k-j-1)}}{\lambda_{n_{k}}^2} \right\} \\
+&= \max \left \{j' \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j'+1} \frac{b^{2(k-j'-1)}}{\lambda_{n_{k}}^2} \right\} \\
+& = j^{\ddagger}(\omega\varepsilon,\rho) - 1.
+\end{align*}
+By the argument above, it follows that $j^\ddagger -1 \ge j^\dagger$ and by Theorem 2 so
+\[
+\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^{\ddagger}} -1 \ge n_{j^{\ddagger}-1} \ge  n_{j^\dagger}\ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) .\]
+Therefore, our algorithm is essentially no more costly than the optimal algorithm. }
 
@@
 Let $ a= 2$ and  $b=1/2$ and
- choose $\bsn = \{0, 16, 32, 64, \ldots \}.$
+ choose $\bsn = (0, 16, 32, 64, \ldots ).$
  To  compute $\sigma_j(f), \ j \in \bbN$ by \eqref{sumdef},

### 2019-05-08 ProgramsImages/WalshFourierCoeffDecay.m

@@ -1,0 +1,157 @@
+printc='bw';
+
+%if usejava('jvm') || MATLABVERSION <= 7.12
+%% Garbage collection and initialization
+format compact %remove blank lines from output
+format long e %lots of digits
+%clearvars %clear all variables
+close all %close all figures
+ColorOrder=get(gca,'ColorOrder'); close all
+set(0,'defaultaxesfontsize',21,'defaulttextfontsize',21) %make font larger
+set(0,'defaultLineLineWidth',3) %thick lines
+set(0,'defaultTextInterpreter','latex') %latex axis labels
+set(0,'defaultLegendInterpreter','latex') %latex axis labels
+set(0,'defaultLineMarkerSize',40) %latex axis labels
+
+%% Initialize parameters
+mmax=22;
+mplot=12;
+mlag=4; % the coefficients to shrink wrt mplot
+
+testfun=@(x) exp(-3*x).*sin(3*pi*x.^2);
+
+r=1;
+lambda_i=@(i,r) lambda_k(floor(i/2),r);
+pos_v=@(k,x,r) sqrt(2)*sin(2*pi*bsxfun(@times,k,x));
+neg_v=@(k,x,r) sqrt(2)*cos(2*pi*bsxfun(@times,k,x));
+v_i=@(i,x,r) bsxfun(@times,mod(i,2)==0,neg_v(-i/2,x,r))+bsxfun(@times,and(mod(i,2)==1,i>1),pos_v((i-1)/2,x,r))+(i==1);
+u_i=@(i,x,r) bsxfun(@times,lambda_i(i,r),v_i(i,x,r));
+
+i_max=(0:2^mmax-1)';
+y = testfun(i_max/2^mmax);
+yfft_ = fft(y);
+yfft = yfft_;
+yfft(2:2:end) = sqrt(2)*real(yfft_(2:2^(mmax-1)+1))./lambda_i(2:2:size(yfft,1),r)';
+yfft(3:2:end) = -sqrt(2)*imag(yfft_(2:2^(mmax-1)))./lambda_i(3:2:size(yfft,1),r)';
+
+yticks=10.^(-10:5:10);
+ymin = 10^-11;
+ymax = 10^8;
+
+
+%% Plot function
+figure
+xplot=(0:0.002:1);
+yplot=testfun(xplot);
+if strcmp(printc,'color')
+    plot(xplot,yplot,'-');
+else
+    plot(xplot,yplot,'-k');
+end
[…]

### 2019-05-08 ProgramsImages/lambda_k.m

@@ -1,0 +1,3 @@
+function x=lambda_k(k,r)
+    x=abs(k).^(-r);
+    x(k==0)=1;

### 2019-05-27 AutoAlgorithmLinearFunctionalDataVerF.tex
Updates from Overleaf

--- 2019-05-08 AutoAlgorithmLinearFunctionalDataVerE.tex
@@
 This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.
-We focus on cases where the exact solution requires an infinite number of series coefficients, $\widehat{f}_i$, in general.
+We focus on cases where the exact solution requires an infinite number of series coefficients, $\widehat{f}_i$, in general, i.e., all $\lambda_i$ are positive.
 
@@
 For any potential algorithm, we show that there exists some $f \in \calF$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.
-Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals that are used to compute $A(f,\varepsilon)$.
+Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals that are used to compute $A(0,\varepsilon)$.
 Since the output space, $\calG$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \calF$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
@@
 
-\begin{figure}[ht]
-	\centering
-	\begin{tabular}{cc}
-		\includegraphics[width=5.5cm]{ProgramsImages/Function.eps} &
-		\includegraphics[width=5.5cm]{ProgramsImages/FunctionWalshFourierCoeffDecay.eps}
-		\\ (a) & (b) \\
-		\includegraphics[width =5.5cm]{ProgramsImages/Scaled.eps} &
-		\includegraphics[width=5.5cm]{ProgramsImages/ScaledWalshFourierCoeffDecay.eps}
-		\\ (c) & (d) \\
-		\includegraphics[width=5.5cm]{ProgramsImages/Filtered.eps} &
-		\includegraphics[width=5.5cm]{ProgramsImages/FilteredWalshFourierCoeffDecay.eps}
-		\\ (e) & (f)
-	\end{tabular}
-	\caption{(a) The function $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$; (b) The first Fourier coefficients of $f$; (c) The function $f_{\text{big}}=100f$; (d) The first Fourier coefficients of $f_{\text{big}}$; (e) The function $f_{\text{fuzzy}}$ resulting from modifying some of $f$ coefficients; (f) The first Fourier coefficients of $f_{\text{fuzzy}}$.
-\label{fig:fourier_example}}
-\end{figure}
-
 Popular adaptive algorithms encountered typically employ heuristic error bounds.
@@
 \begin{align} \label{decayconedef}
-\calC &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \ \forall j,r \in \bbN \right\} \\
+\calC = \calC_{\bsn,a,b} &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \ \forall j,r \in \bbN \right\} \\
 \nonumber
-& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}ab^r\sigma_{j-r}(f) \ \ \forall j \in \bbN \right\}.
+& = \Bigl\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}ab^r\sigma_{j-r}(f) \ \ \forall j \in \bbN \Bigr\}.
 \end{align}
@@
 
+\frednote{We need some horizontal axis labels for figures (d)--(f).} Figure \ref{fig:fourier_example} shows three functions and their coefficients for the case of Example \ref{exam:exam1} when $r=1$ and $n_j=2^j$.
+There are three functions: $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$, $f_{\text{big}}=100f$ and $f_{\text{fuzzy}}$.
+The function $f_{\text{fuzzy}}$ is obtained by taking $\sigma_8(f_{\text{fuzzy}})=250\sigma_8(f)$ and $\sigma_j(f_{\text{fuzzy}})=\sigma_j(f)$ for $j \ne 8$.
+Both $f$ and $f_{\text{big}}$ lie in the same cones, $\calC_{\bsn,a,b}$, and both appear similarly nice.
+Therefore, we expect adaptive algorithms that are successful for $f$ to also be successful for $f_{\text{big}}$.
+However, $f_{\text{big}}$ does not lie in some of the balls,  $\calB_{\rho}$, that $f$ lies in.
+On the other hand, the high frequency noise in $f_{\text{fuzzy}}$ suggests that only more robust and costly adaptive algorithms would be able to succeed for such an input.
+This corresponds to the fact that $f_{\text{fuzzy}}$ does not lie in all cones, $\calC_{\bsn,a,b}$, that $f$ lies in.
+
+\begin{figure}[ht]
+\newcommand{\figwidth}{3.5cm}
+	\centering
+	\begin{tabular}{c@{\quad}c@{\quad}c}
+		\includegraphics[width=\figwidth]{ProgramsImages/Function.eps} &
+		\includegraphics[width=\figwidth]{ProgramsImages/Scaled.eps} &
+		\includegraphics[width=\figwidth]{ProgramsImages/Filtered.eps}
+		\\ (a) & (b) & (c) \\
+		\includegraphics[width=\figwidth]{ProgramsImages/FunctionWalshFourierCoeffDecay.eps} &
+		\includegraphics[width=\figwidth]{ProgramsImages/ScaledWalshFourierCoeffDecay.eps} &
+		\includegraphics[width=\figwidth]{ProgramsImages/FilteredWalshFourierCoeffDecay.eps}
+		\\ (d) & (e) & (f)
+	\end{tabular}
+	\caption{(a) The function $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$; (b) The function $f_{\text{big}}=100f$; (c) The function $f_{\text{fuzzy}}$ which results from modifying some of $f$ coefficients, in dark green; (d) The first Fourier coefficients of $f$; (e) The first Fourier coefficients of $f_{\text{big}}$; (f) The first Fourier coefficients of $f_{\text{fuzzy}}$.
+\label{fig:fourier_example}}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{algo}
-
+\yuhannote{Please check the result of Theorem 1} \frednote{Yuhan, please put $\rho$ and $\varepsilon$ on left.}\yuhannote{Done. Please double check}
 \begin{theorem}\label{thm:compcost}
@@
 \end{equation}
-Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \frednote{=} n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
-j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}.
+j^\dagger \le \min \left \{j \in \bbN : F(j) \ge \frac{\rho^2 a^4}{\varepsilon^2(1 - b^2)} \right\},
 \end{equation}
-
+% \begin{equation} \label{jdagger}
+% j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} F(j) \right\},
+% \end{equation}
+where $F$ is the strictly increasing function defined as
+\begin{equation} \label{jsum}
+F(j): = \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}, \qquad j \in \N.
+\end{equation}
 \end{theorem}
@@
 \rho \ge \DHJRnorm[\calF]{f} \ge \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
+\ge \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}}}
 \end{equation*}
@@
 \begin{equation} \label{jdaggerlast}
-j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}+1} \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\}.
+j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}} \le \frac{\varepsilon\sqrt{1 - b^2}}{\rho ab } \right\}.
 \end{equation}
@@
 For any $f \in  \calC \cap \calB_\rho$ satisfying $n_{j^*} = \textup{cost}(\widetilde{A},f,\varepsilon) = \textup{cost}(\widetilde{A}, \calC, \varepsilon, \rho) = n_{j^{\dagger}}$ and for any $j < j^* = j^\dagger$,
+\yuhannote{new proof starts here}\frednote{Looks good to me}
 \begin{align*}
-\rho^2 &\ge \DHJRnorm[\calF]{f}^2 = \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=1}^{\infty}}^2 \\
-& \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \\
+\rho^2 &\ge \DHJRnorm[\calF]{f}^2 = \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=1}^{\infty}}^2  \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \\
 & \ge \sum_{k=1}^j \frac{\sigma_k^2(f)}{\lambda_{n_{k-1}+1}^2} \qquad \text{by \eqref{normsigineq}}\\
 & \ge \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}\sigma_j^2(f)}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{\sigma_j^2(f)}{\lambda_{n_{j-1}+1}^2} \qquad \text{by \eqref{decayconedef}} \\
-& = \sigma_j^2(f) \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^{2} \lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
+& = \sigma_j^2(f) \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^{2} \lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]\\
+&> \frac{ \sigma_j^2(f)}{a^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2}  \qquad \text{since } a > 1\\
+&= \frac{ \sigma_j^2(f)}{a^2}\sum_{k=0}^{j-1} \frac{b^{2(k+1-j)}}{\lambda_{n_{k}+1}^2}  \\
+& \ge  \frac{b^2 \sigma_j^2(f)}{a^2} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
+& = \frac{b^2 \sigma_j^2(f)}{a^2} F(j)
+\qquad \text{by } \eqref{jsum}.
 \end{align*}
-Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum includes more terms and $b^{2(k-j)}$ also increases.
 
@@
 \begin{equation*}
-\rho^2 > \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
+ F(j) < \frac{ \rho^2 a^4}{\varepsilon^2(1 - b^2)}.
 \end{equation*}
-Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$, establishing \eqref{jdagger}.
+Note from \eqref{jsum} that $F$ is an increasing function because as $j$ increases, the sum defining $F$ includes more positive terms and $b^{2(k-j)}$ also increases.
+Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$.
+This establishes \eqref{jdagger}.
 \end{proof}
@@
 
+\yuhannote{Also change the analysis and corollary 1}
 The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $(\lambda_{n_j})_{j=0}^\infty$.
 This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $(\lambda_i)_{i=1}^\infty$.
-Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation*} \label{keysum}
-\sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}.
-\end{equation*}
-One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.
+Considering the sum $F(j)$,
+one can imagine that in some cases the first term in the sum $F(j)$ dominates, while in other cases the last term in the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k}}$ behaves with $k$ and $j$.
 These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}$.
@@
 \begin{equation} \label{jdaggerfirst}
-j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}+1} }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{b}\right) \right \rceil.
+j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}} }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{b}\right) \right \rceil.
 \end{equation}
-Moreover, if the $\lambda_{n_{j-1}+1}$ decay as quickly as
+Moreover, if the $\lambda_{n_{j-1}}$ decay as quickly as
 \begin{equation}
 \label{lambdankbd}
-\lambda_{n_{j-1}+1} \le \alpha \beta^j,  \quad j \in \bbN,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
+\lambda_{n_{j-1}} \le \alpha \beta^j,  \quad j \in \bbN,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
 \end{equation}
@@
 j^\dagger \le
-\left \lceil \log\left(\frac{\rho a\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{\beta}\right) \right \rceil.
+\left \lceil \log\left(\frac{\rho a^2\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{\beta}\right) \right \rceil.
 \end{equation}
@@
 \begin{proof}
-Ignoring all but the first term in the sum in \eqref{jdagger} implies that 
+Ignoring all but the first term in the definition of $F$ in \eqref{jsum} implies that 
 \begin{equation*} \label{jsumupperbd}
-j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2}    \right\}.
+j^\dagger \le \min \left \{j \in \bbN : b^{-2j}  \ge  \frac{\rho^2 a^4 \lambda_{n_{0}}^2 }{\varepsilon^2(1 - b^2)} \right\}.
 \end{equation*}
@@
 
-Ignoring all but the term outside the sum leads to the simpler upper bound in \eqref{jdaggerlast}.  If the $\lambda_{n_{j-1}+1}$ decay as assumed in \eqref{lambdankbd} then
+Ignoring all but the last term of the sum \eqref{jsum}. leads to the simpler upper bound similar to  \eqref{jdaggerlast}
+\begin{equation*} 
+j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}}^{-1} \ge \frac{ \rho a^2b}{ \varepsilon\sqrt{1 - b^2}} \right\}.
+\end{equation*}
+If the $\lambda_{n_{j-1}}$ decay as assumed in \eqref{lambdankbd} then
 \[
-j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^j \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
+j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^{-j} \le \frac{\rho a^2b }{ \varepsilon\sqrt{1 - b^2}} \right\},
 \]
@@
 This corollary highlights two limiting factors on the computational cost of our adaptive algorithm, $\widetilde{A}$.
-When $j$ is large enough to make $\lambda_{n_{j-1}+1}\DHJRnorm[\calF]{f}/\varepsilon$ small enough, $\widetilde{A}(f,\varepsilon)$ stops.
-This is statement \eqref{jdaggerlastsimple}, and its precursor, \eqref{jdaggerlast}.
-Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\calC$ in \eqref{decayconedef}, means that $\widetilde{A}(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\DHJRnorm[\calF]{f}/\varepsilon$.
+When $j$ is large enough to make $\lambda_{n_{j-1}}\DHJRnorm[\calF]{f}/\varepsilon$ small enough, $\widetilde{A}(f,\varepsilon)$ stops.
+This is statement \eqref{jdaggerlastsimple}
+and its precursor, \eqref{jdaggerlast}.
+Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\calC$ in \eqref{decayconedef}, means that $\widetilde{A}(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0}\DHJRnorm[\calF]{f}/\varepsilon$.
 
@@
 
+\yuhannote{corollary 2 is not changed} \frednote{I think we need a small change}
 \begin{corollary} \label{cor:tAsameCosthA} Suppose that the sequence $\bsn$ is chosen to satisfy
 \begin{equation} \label{lambdaDecay}
-\lambda_{n_{j+1}+1} \ge c_\lambda \lambda_{n_j+1}, \qquad j \in \bbN, 
+\lambda_{n_{j+1}} \ge c_\lambda \lambda_{n_j}, \qquad j \in \bbN, 
 \end{equation}
@@
 \begin{equation*}
-\lambda_{n_{j^\dagger}+1} \ge c_{\lambda}^2 \lambda_{n_{j^\dagger-2}+1} > \frac{\varepsilon c_{\lambda}^2\sqrt{1 - b^2}}{ab \rho} \ge \lambda_{\widehat{n}+1},
+\lambda_{n_{j^\dagger{{\color{red}+1}}}} \ge c_{\lambda}^{{\color{red}{3}}} \lambda_{n_{j^\dagger-2}} > \frac{\varepsilon c_{\lambda}^{{\color{red}{3}}}\sqrt{1 - b^2}}{\rho ab } = \frac{\omega \varepsilon}{\rho} \ge \lambda_{\widehat{n}+1},
+\qquad \omega := \frac{ c_{\lambda}^{{\color{red}{3}}}\sqrt{1 - b^2}}{ab }
 \end{equation*}
 where $\widehat{n}
-= \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab)$.
-Since the $\lambda_i$ are non-increasing,
+= \textup{cost}(\widehat{A},\calB_{\rho},\omega\varepsilon )$.
+Since the $\lambda_i$ are non-increasing, {\color{red} $n_{j^\dagger+1} \le \widehat{n}+1$, and so $n_{j^\dagger} \le \widehat{n}$.  Thus, }
 \begin{equation*}
-\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = n_{j^\dagger} \le \widehat{n} = \textup{cost}(\widehat{A},\calB_{\rho},\varepsilon c_{\lambda}^2\sqrt{1 - b^2}/ab).
+\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = n_{j^\dagger} \le \widehat{n} = \textup{cost}(\widehat{A},\calB_{\rho}, \omega \varepsilon).
 \end{equation*}
@@
 \end{equation}
-Hence, the $n_j$ are not too far apart with respect to the decay of the $\lambda_i$ as $i \to \infty$.
+\frednote{That is, the subsequence $\lambda_{n_1}, \lambda_{n_2}, \ldots$ cannot decay too quickly.}
 
@@
 
-\frednote{Need to check this proof again}
+\yuhannote{Please check the definition of $j^\ddagger$}
 \begin{theorem} \label{thm:lowbdcomp}
@@
 %\label{compbdB}
-j^{\ddagger} & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}   <
-\frac{\rho^2}{\varepsilon^2}
-\right \}.
+j^{\ddagger} & = \min \left \{ j \in \bbN : F(j+2) \ge \frac{\rho^2}{\varepsilon^2 b^2}
+\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}
+\right \},
 \end{align*}
+where $F(j)$ defined in \eqref{jsum}.
 \end{theorem}
@@
 \begin{align}
-\nonumber
+\label{DHJRetaDef}
 f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)R}, \\
@@
 \end{align*}
-Thus, we have
+Thus, we have \yuhannote{Please check the proof below}
 \begin{align*}
@@
 \sum_{k=0}^{j} \DHJRbignorm[\calF]{u^{(k)}}^2 
-b^{2(k-j)}\\
+b^{2(k-j)} 
+\qquad {\color{red} \text{since } \DHJRbignorm[\calG]{S(u^{(k)})} \ge \lambda_{n_k} \DHJRbignorm[\calF]{u^{(k)}} }\\
 & \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \DHJRbignorm[\calF]{u^{(k)}} \\
-& \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2R^2} \\
+& \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2R^2} 
+\qquad {\color{red} \text{since } b < 1}\\
 &
-=\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
-& =  \rho^2 \left[\left(\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+=\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+\qquad {\color{red} \text{by \eqref{DHJRetaDef}}}\\
+& =  \rho^2 \left[\left(\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
+& = \rho^2 \left[\left(\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right) b^2F(j+1)\right]^{-1} 
+\qquad {\color{red} \text{by \eqref{jsum}}}.
 \end{align*}
+\frednote{This inequality is equivalent to 
+\begin{equation}
+    F(j+1) \ge  \frac{\rho^2}{\varepsilon^2 b^2}
+\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}
+\end{equation}
+}
 
@@
 The next step is to show that the cost of our algorithm is essentially no worse than that of the optimal algorithm.
-\frednote{Now this proof needs fixing.}
+\yuhannote{The proof of theorem 3 needs to be checked.}
 \begin{theorem}
@@
 \end{theorem}
-\begin{proof}
-Let  
-\begin{equation} \label{omegadef}
-    \omega = \sqrt{\frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}},
+\begin{proof} Let
+\begin{equation} \label{newomegadef}
+    \omega = \sqrt{\frac{(1 - b^2)b^4}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}},
 \end{equation}
@@
 \[
-j^\dagger(\varepsilon,\rho) \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}, \]
-and we are showing the explicit dependence of $j^\dagger$ on $\varepsilon$ and $\rho$.  As we have
+j^\dagger(\varepsilon,\rho) \le \min \left \{j \in \bbN : F(j) \ge \frac{\rho^2 a^4}{\varepsilon^2 (1-b^2)}  \right\}. \]
+According to \eqref{lambdaRatio}, for any $\ell \in \mathbb{N}$
 \begin{align*}
- & \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \\
-&\ge  \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2}  \qquad \text{since } a > 1\\
-&\ge  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2}  \\
-&\ge  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
-&\ge  \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4)} \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{by \eqref{lambdaRatio},}
-\end{align*}
-thus 
-\begin{align*} 
-j^\dagger &\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
-&\le \min \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \qquad \text{by \eqref{omegadef} } \\
-&= \max \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} =:j^{\ddagger}.
-\end{align*}
-By Theorem \ref{thm:lowbdcomp}, $\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^{\ddagger}}$, and by the argument above, $n_{j^{\ddagger}} \ge n_{j^\dagger} \ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)$.
-Thus, our algorithm is essentially no more costly than the optimal algorithm.
-\end{proof}
-\tonynote{
-\begin{align*}
-(b^2R^2)^\ell \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} & = (R^2)^\ell\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell}}^2} \\
-& \geq (R^2)^{\ell-1}\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell+1}}^2} \\
-& \geq \sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \\
-& \geq \frac{b^{2(\ell-1)}}{\lambda_{n_{j+\ell-1}}^2}
-\end{align*}
-}
-
-\yuhannote{Let  
-\begin{equation} \label{newomegadef}
-    \omega = \sqrt{\frac{(1 - b^2)b^2}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}},
-\end{equation}
-and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$. 
-For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger(\varepsilon,\rho)}$, where 
-\[
-j^\dagger(\varepsilon,\rho) \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}, \]
-and we are showing the explicit dependence of $j^\dagger$ on $\varepsilon$ and $\rho$.
-As we have
-\begin{align*} 
- & \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \\
-&\ge  \frac{(1 - b^2)}{a^4b^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2}  \qquad \text{since } a > 1\\
-&=  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}+1}^2}  \\
-&\ge  \frac{(1 - b^2)}{a^4} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1},\\
-\end{align*}
-and by \eqref{lambdaRatio}, for any $l \in \mathbb{N}$
-\begin{align*}
-(b^2R^2)^\ell \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} & = (R^2)^\ell\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell}}^2} \\
+ (b^2R^2)^\ell F(j)
+& =(b^2R^2)^\ell \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} 
+ = (R^2)^\ell\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell}}^2} \\
 & \geq (R^2)^{\ell-1}\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell+1}}^2} \\
@@
 \begin{align*} 
- & \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \\
-&\ge  \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)} \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{by \eqref{lambdaRatio}}\\
-&=  \frac{\omega^2}{b^2}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \qquad \text{by \eqref{newomegadef}.}
+  \frac{(1 - b^2)}{a^4} F(j) 
+&\ge  \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)} \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \\
+& = \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)} b^6 F(j+3)\\
+&=  \omega^2\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] b^2 F(j+3) \qquad \text{by \eqref{newomegadef}.}
 \end{align*}
@@
 \begin{align*} 
-j^\dagger(\varepsilon,\rho) &\le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\} \\
-&\le \min \left \{j \in \bbN : \frac{\rho^2}{ \varepsilon^2} \le \frac{\omega^2}{b^2}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \right\} \\
-&= \min \left \{j \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} \le \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j+2} \frac{b^{2(k-j-1)}}{\lambda_{n_{k}}^2} \right\} \\
-&= \max \left \{j' \in \bbN : \frac{\rho^2}{\omega^2 \varepsilon^2} > \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] \sum_{k=0}^{j'+1} \frac{b^{2(k-j'-1)}}{\lambda_{n_{k}}^2} \right\} \\
+j^\dagger(\varepsilon,\rho) &\le \min \left \{j \in \bbN : F(j) \ge \frac{\rho^2 a^4}{\varepsilon^2 (1-b^2)}   \right\} \\
+& =
+ \min \left \{j \in \bbN : \frac{(1 - b^2)}{a^4} F(j) \ge \frac{\rho^2 }{\varepsilon^2 }   \right\} \\
+& \le \min \left \{j \in \bbN : \omega^2\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] b^2 F(j+3) \ge \frac{\rho^2}{\varepsilon^2}  \right\} \\
+& = \min \left \{j \in \bbN :  F(j+3) \ge \frac{\rho^2}{\omega^2 \varepsilon^2 b^2} \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1} \right\} \\
 & = j^{\ddagger}(\omega\varepsilon,\rho) - 1.
@@
 \textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^{\ddagger}} -1 \ge n_{j^{\ddagger}-1} \ge  n_{j^\dagger}\ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) .\]
-Therefore, our algorithm is essentially no more costly than the optimal algorithm. }
+Therefore, our algorithm is essentially no more costly than the optimal algorithm. 
+\end{proof}
 
@@
 
+\begin{acknowledgement}
+The authors would like to thank three anonymous referees for their suggestions which helped to improve the presentation of the results.
+
+\end{acknowledgement}
+
 %\section*{References}

### 2019-05-27 ProgramsImages/WalshFourierCoeffDecay.m

@@ -1,4 +1,4 @@
-printc='bw';
+printc='color';
 
 %if usejava('jvm') || MATLABVERSION <= 7.12
 %% Garbage collection and initialization
@@ -7,16 +7,22 @@ format long e %lots of digits
 %clearvars %clear all variables
 close all %close all figures
 ColorOrder=get(gca,'ColorOrder'); close all
-set(0,'defaultaxesfontsize',21,'defaulttextfontsize',21) %make font larger
+set(0,'defaultaxesfontsize',36,'defaulttextfontsize',36) %make font larger
 set(0,'defaultLineLineWidth',3) %thick lines
 set(0,'defaultTextInterpreter','latex') %latex axis labels
 set(0,'defaultLegendInterpreter','latex') %latex axis labels
-set(0,'defaultLineMarkerSize',40) %latex axis labels
+set(0,'defaultLineMarkerSize',20) %latex axis labels
+
+function_color = [0, 0.4470, 0.7410];
+function_scaled_color = [0.8500, 0.3250, 0.0980];
+function_fuzzy_color = [0.4660, 0.6740, 0.1880];
+fuzzy_coefficients = [0, 0.35, 0]; % [0.9290, 0.6940, 0.1250];
 
 %% Initialize parameters
-mmax=22;
-mplot=12;
+mmax=23;
+mplot=11;
 mlag=4; % the coefficients to shrink wrt mplot
+filter_factor = 2.5*1e+2;
 
 testfun=@(x) exp(-3*x).*sin(3*pi*x.^2);
 
@@ -29,14 +35,14 @@ u_i=@(i,x,r) bsxfun(@times,lambda_i(i,r),v_i(i,x,r));
 
 i_max=(0:2^mmax-1)';
 y = testfun(i_max/2^mmax);
-yfft_ = fft(y);
+yfft_ = fft(y) / 2^mmax;
 yfft = yfft_;
 yfft(2:2:end) = sqrt(2)*real(yfft_(2:2^(mmax-1)+1))./lambda_i(2:2:size(yfft,1),r)';
 yfft(3:2:end) = -sqrt(2)*imag(yfft_(2:2^(mmax-1)))./lambda_i(3:2:size(yfft,1),r)';
 
-yticks=10.^(-10:5:10);
-ymin = 10^-11;
-ymax = 10^8;
+yticks=10.^(-15:5:0);
+ymin = 10^-10;
+ymax = 10^3;
 
 
 %% Plot function
[…]

### 2019-05-28 AutoAlgorithmLinearFunctionalDataVerF.tex
fred edits

@@
 \end{algo}
-\yuhannote{Please check the result of Theorem 1} \frednote{Yuhan, please put $\rho$ and $\varepsilon$ on left.}\yuhannote{Done. Please double check}
+\yuhannote{Please check the result of Theorem 1} 
 \begin{theorem}\label{thm:compcost}
@@
 \end{align*}
-\frednote{This inequality is equivalent to 
+{\color{red} This inequality is equivalent to 
 \begin{equation}
     F(j+1) \ge  \frac{\rho^2}{\varepsilon^2 b^2}
-\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}
+\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1}.
 \end{equation}
-}
 
 This lower bound must be satisfied by $j$ to be consistent with the assumption $\textup{comp}(\calA(\calC),\varepsilon,\rho) \le n_j - 2$.
-Thus, for any $j$ violating this inequality it follows that $\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_j - 1$.
-This implication provides a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$.
+Thus, any $j$ violating this inequality satisfies $\textup{comp}(\calA(\calC),\varepsilon,\rho) \ge n_j - 1$.
+Since $F$ is strictly increasing, the largest $j$ violating this inequality must satisfy
+\begin{equation}
+F(j+1) < \frac{\rho^2}{\varepsilon^2 b^2}
+\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1} \le F(j+2),
+\end{equation}
+which is the definition of  $j^\ddagger$ above in the statement of this theorem.  This proves the lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$. }
 \end{proof}
@@
 \end{theorem}
-\begin{proof} Let
+\begin{proof} 
+{\color{red} We need an inequality relating $F(j)$, which appears in the definition of $j^\dagger$ in Theorem \ref{thm:compcost} and $F(j+3)$, which is related to the definition of $j^\ddagger$ in Theorem \ref{thm:lowbdcomp}.
+According to \eqref{lambdaRatio} and the definition of $F$ in \eqref{jsum}, for any $\ell \in \mathbb{N}$,
+\begin{equation*}
+R^{2\ell} F(j) \ge R^{2\ell} \frac{b^{-2}}{\lambda_{n_{j-1}}^2} \geq \frac{b^{-2}}{\lambda_{n_{j+\ell-1}}^2},
+\end{equation*}
+and so
+\begin{align*}
+b^{-2\ell}[1 + b^2R^2\cdots + (b^2R^2)^\ell] F(j) & \ge F(j)b^{-2\ell} + \frac{b^{-2\ell}}{\lambda_{n_{j}}^2} + \cdots + \frac{b^{-2}}{\lambda_{n_{j+\ell-1}}^2} \\
+& = \sum_{j=0}^{j-1} \frac{b^{2(k - j -\ell)}}{\lambda_{n_{k}}^2} + \frac{b^{-2\ell}}{\lambda_{n_{j}}^2} + \cdots + \frac{b^{-2}}{\lambda_{n_{j+\ell-1}}^2} \\
+& = F(j + \ell).
+\end{align*}
+The $\ell=3$ case of this inequality implies the following lower bound on $F(j)$ in terms of $F(j+3)$:
+\begin{equation*} 
+F(j) \ge  \frac{b^6 F(j+3)}{1 + b^2R^2 + b^4R^4 + b^6R^6} \\
+=  \frac{\omega^2 a^4 b^2}{1 - b^2}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] F(j+3),
+\end{equation*}
+where
 \begin{equation} \label{newomegadef}
@@
 \end{equation}
-and note that it does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$. 
-For any positive $\rho$ and $\varepsilon$, Theorem \ref{thm:compcost} says that $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger(\varepsilon,\rho)}$, where 
-\[
-j^\dagger(\varepsilon,\rho) \le \min \left \{j \in \bbN : F(j) \ge \frac{\rho^2 a^4}{\varepsilon^2 (1-b^2)}  \right\}. \]
-According to \eqref{lambdaRatio}, for any $\ell \in \mathbb{N}$
-\begin{align*}
- (b^2R^2)^\ell F(j)
-& =(b^2R^2)^\ell \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} 
- = (R^2)^\ell\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell}}^2} \\
-& \geq (R^2)^{\ell-1}\sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k-\ell+1}}^2} \\
- & \geq \sum_{k=\ell}^{j+\ell-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2} \\
-& \geq \frac{b^{2(\ell-1)}}{\lambda_{n_{j+\ell-1}}^2},
-\end{align*}
-thus 
-\begin{align*} 
-  \frac{(1 - b^2)}{a^4} F(j) 
-&\ge  \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)} \sum_{k=0}^{j+2} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \\
-& = \frac{(1 - b^2)}{a^4(1 + b^2R^2 + b^4R^4 + b^6R^6)} b^6 F(j+3)\\
-&=  \omega^2\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] b^2 F(j+3) \qquad \text{by \eqref{newomegadef}.}
-\end{align*}
-Hence,
+Note that $\omega$ does not depend on $\rho$ or $\varepsilon$ but only on the definition of $\calC$.
+
+For any positive $\rho$ and $\varepsilon$, let $j^\dagger = j^\dagger(\varepsilon,\rho)$ be defined as in Theorem \ref{thm:compcost} and let $j^\ddagger = j^\ddagger(\varepsilon,\rho)$ be defined as in Theorem \ref{thm:lowbdcomp}.
+Then by those Theorems, $j^\dagger(\varepsilon,\rho)$ can be bounded above in terms of $ j^{\ddagger}(\omega\varepsilon,\rho)$ for $\omega$ defined in \eqref{newomegadef}:
 \begin{align*} 
 j^\dagger(\varepsilon,\rho) &\le \min \left \{j \in \bbN : F(j) \ge \frac{\rho^2 a^4}{\varepsilon^2 (1-b^2)}   \right\} \\
-& =
- \min \left \{j \in \bbN : \frac{(1 - b^2)}{a^4} F(j) \ge \frac{\rho^2 }{\varepsilon^2 }   \right\} \\
-& \le \min \left \{j \in \bbN : \omega^2\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] b^2 F(j+3) \ge \frac{\rho^2}{\varepsilon^2}  \right\} \\
+& \le \min \left \{j \in \bbN : \frac{\omega^2 a^4 b^2}{1 - b^2}\left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right] F(j+3) \ge \frac{\rho^2 a^4}{\varepsilon^2 (1-b^2)}    \right\} \\
 & = \min \left \{j \in \bbN :  F(j+3) \ge \frac{\rho^2}{\omega^2 \varepsilon^2 b^2} \left[\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right]^{-1} \right\} \\
@@
 \end{align*}
-By the argument above, it follows that $j^\ddagger -1 \ge j^\dagger$ and by Theorem 2 so
+By the argument above, it follows that $ j^\dagger(\varepsilon,\rho) \le j^\ddagger(\omega\varepsilon,\rho) -1$, and again by Theorems \ref{thm:compcost} and  \ref{thm:lowbdcomp} it follows that 
 \[
-\textup{comp}(\calA(\calC),\omega\varepsilon,\rho) \ge n_{j^{\ddagger}} -1 \ge n_{j^{\ddagger}-1} \ge  n_{j^\dagger}\ge \textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) .\]
-Therefore, our algorithm is essentially no more costly than the optimal algorithm. 
+\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho)
+= n_{j^\dagger}(\varepsilon,\rho)
+\le n_{j^{\ddagger}(\omega\varepsilon,\rho)-1} 
+\le n_{j^{\ddagger}(\omega\varepsilon,\rho)} -1 
+\le \textup{comp}(\calA(\calC),\omega\varepsilon,\rho) .
+\]
+Therefore, our algorithm is essentially no more costly than the optimal algorithm. }
 \end{proof}

### 2019-06-03 ReplyToReferee2019-Apr.tex
Updates from Overleaf

--- 2019-04-06 ReplyToReferee2019-Apr.tex
@@
 \usepackage{bbm,mathtools,array,longtable,booktabs,graphicx,color,enumitem}
+
+\definecolor{orange}{rgb}{1.0,0.3,0.0}
+\definecolor{violet}{rgb}{0.75,0,1}
+\newcommand{\frednote}[1]{  {\textcolor{red}  {\mbox{**Fred:} #1}}}
+\newcommand{\yuhannote}[1]{ {\textcolor{violet}  {\mbox{**Yuhan:} #1}}}
+\newcommand{\tonynote}[1]{ {\textcolor{orange}  {\mbox{**Tony:} #1}}}
 
@@
 \begin{document}
-\title{Reply to the Referees}
+\title{Response to the Referees}
 \maketitle
+
+\noindent We would like to thank you for your careful reviews of our manuscript and your helpful comments.
+
+\noindent Below, we respond to the points made in your reports.
 
@@
 
+While it is less traditional in numerical analysis to assume that a function belongs to a cone than to a ball, we assert that there are advantages.
+We think of the difficulty of a problem not as the computational cost but as the ability for an algorithm to correctly determine the computational cost.
+Thus, problems inside our cones are easy, but they could be costly depending on the norm of the input function.
+
+Our example in Figure 1 illustrates what an easy problem is.
+When the Fourier coefficients of the input decay steadily, we can easily construct an adaptive algorithm that approximates the solution well, regardless of how large the norm of the input function is.
+On the other hand, when the decay is not steady, this is a difficult problem because the adaptive algorithm may be fooled unless the initial sample size is quite large.
+Our cones are non-convex, which is consistent with what is known about when adaptive algorithms might be effective \cite{Bak71}.
+
 \begin{enumerate}
-    \item[5.] The norm for $\calF$ has been identified.
+    \item The first sentence is Subsection 1.1 has been rephrased.
+    \item The sufficient and necessary conditions of the existence of singular value decomposition has been added  to  the last paragraph of Subsection 1.1
+    \item \textit{linear functionals are used} changed to 
+    \textit{linear functionals that are used}
+    \item Inserted \textit{the} before the algorithm
+    \item The norm for $\calF$ has been identified.
 \end{enumerate}
@@
 \begin{enumerate}[labelwidth = 10ex]
-    \item[$6^{\text{th}}$ \bullet] The norm does depend on the $\lambda_i$ because the $u_i$ depend on the $\lambda_i$.  This is clearer not that the norm for $\calF$ has been identified.
+    \item[$1^{\text{st}}$ \bullet] Replaced
+    $\sum\limits_{i =1 }^n$ by $\sum\limits_{i \in \mathbb{N} }$
+    \item[$2^{\text{nd}}$ \bullet] Added one paragraph to end of \S 1.1 to foreshadow Example 1 and the numerical example.
+    \item[$3^{\text{rd}}$ \bullet] Inserted ``that''
+    \item[$4^{\text{th}}$ \bullet] Replaced $A(0,\varepsilon)$ 
+    with $A(f,\varepsilon)$
+    \item[$5^{\text{th}}$ \bullet] Matched the notation for the sample size to the notation for the corresponding algorithm before Section 3,  for example,
+    $\widehat{A} \leftrightarrow \widehat{n}, \widetilde{A} \leftrightarrow \widetilde{n},
+    A^* \leftrightarrow n^*$. As after section 3, we used a sequence $\bsn = \{n_0, n_1, \ldots \}.$ 
+     \item[$6^{\text{th}}$ \bullet] The norm \emph{does} depend on the $\lambda_i$ because the $u_i$ depend on the $\lambda_i$.  This is clearer now that the norm for $\calF$ has been identified.
+    \item[$7^{\text{th}}$ \bullet] Added $\exists \omega >0:$ to the definition
+    \item[$8^{\text{th}}$ \bullet] Added for some $p>0$
+    \item[$9^{\text{th}}$ \bullet] Changed ``no better than'' to ``no smaller than''
+    \item[$10^{\text{th}}$ \bullet] Thanks for the correction. Changed to $1/2 -p$.
+     \item[$11^{\text{th}}$ \bullet] Changed ``then'' to ``we have''
+      \item[$12^{\text{th}}$ \bullet] Corrected the reference of the formula
+      \item[$13^{\text{th}}$ \bullet] Regarding these proofs:
+       \begin{itemize}
+       \item[$-$] Changed the inequality to 
+      $n + 2\le \textup{comp}(\calA(\calC),\varepsilon,\rho) + 2 \le n_j$ and corresponding places to correct the proof.
+      \item[$-$] As $n$ is the sample size for a particular function of the optimal algorithm, it is possible 
+      $n < \textup{cost}(A^*,\calC,\varepsilon,\rho) =  \textup{comp}(\calA(\calC),\varepsilon,\rho).$ 
+           \item[$-$] Removed ``by (21)''
+           \item[$-$] Added some derivation to illustrate it.
+            \item[$-$] Changed to round brackets
+            \item[$-$] Thanks for the suggestion. To make the proof clear, we used a different notation and way to present it.
+       \end{itemize}
 \end{enumerate}
@@
 
+Regarding the conditions (6) and (7), we have added some examples and explanation after we introduced these two conditions.
+
 \begin{enumerate}
-    \item[??] 
+    \item Changed to ``Hence, the algorithm''
+    \item Changed to ``and the algorithm''
+    \item Changed to ``If for some $p > 0$ ''
+    \item Thanks for the comment. Used a different function.
+    \item Thanks for the comment. Added the examples.
+    \item Have added the period at the end of the formula.
+    \item Thanks for the comment. We added a clarification at the end of Section 2.
+    \item Changed to $\lambda_i |\widehat{f}_i|$
+    \item Changed the assumption to 
+    $\lambda_i |\widehat{f}_i| =\Theta(i^{-p})$
+    \item Removed $\forall j  \ge 1$
+    \item Changed $\div$ to $/$
+    \item There is no $+1$.  The derivation has been checked and expanded.
+    \item Corrected the reference of the formula
+    \item Erased $\le n_{j^\dagger}+1$ and clarified the argument leading to the inequality.
+    \item Thanks for the suggestion. Changed $j^*$ to $j^{\ddagger}$
 \end{enumerate}
 
+\bigskip
+
+\noindent With kind regards,\\[0.25cm]
+The authors,
+
+\noindent Y. Ding, F.J. Hickernell,  and Ll.A. Jim\'{e}nez Rugama.
+
+\bibliographystyle{elsarticle-num}
+\bibliography{FJH23,FJHown23}
+
 \end{document}

### 2019-06-03 AutoAlgorithmLinearFunctionalDataVerF.tex
Updates from Overleaf

@@
 \author{Yuhan Ding \and Fred J. Hickernell \and Llu\'{\i}s Antoni Jim\'{e}nez Rugama}
-\institute{Yuhan Ding \at MCA 310, Department of Mathematics, Misericordia University,\\ 301 Lake St., Dallas, PA, 18612 \email{yding@misericordia.edu}
+\institute{Yuhan Ding \at Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 208, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{yding2@hawk.iit.edu}
 \and
@@
 Since the output space, $\calG$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \calF$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$.
-This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$, and both of these have approximation error no greater than $\varepsilon$, i.e.,
+This means that $A(\pm cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$, and $A(\pm cf,\varepsilon)$ both of have approximation error no greater than $\varepsilon$, i.e.,
 \begin{align*}
@@
 The presumed $A$ does not exist, $\calA(\calF)$ is empty, and our problem is not solvable for $\calF$.
-However, it is solvable for well-chosen subsets of $\calF$, as is shown in the sections below.
+However, our problem is solvable for well-chosen subsets of $\calF$, as is shown in the sections below.
 
@@
 While any algorithm can be fooled, we would like to have precise necessary conditions for being fooled, or equivalently, sufficient conditions for the algorithm to succeed.
-Our adaptive algorithm has such conditions and follows in the vein of adaptive algorithms developed in \cite{HicEtal14a, HIcEtal14b, HicJim16a, JimHic16a}.
+Our adaptive algorithm has such conditions and follows in the vein of adaptive algorithms developed in \cite{HicEtal14a, HIcEtal14b, HicJim16a, JimHic16a, HicEtal17a}.
 
@@
 
-\frednote{We need some horizontal axis labels for figures (d)--(f).} Figure \ref{fig:fourier_example} shows three functions and their coefficients for the case of Example \ref{exam:exam1} when $r=1$ and $n_j=2^j$.
-There are three functions: $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$, $f_{\text{big}}=100f$ and $f_{\text{fuzzy}}$.
+Figure \ref{fig:fourier_example} shows three functions and their coefficients for the case of Example \ref{exam:exam1} when $r=1$ and $n_j=2^j$.
+These  functions are $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$, $f_{\text{big}}=100f$ and $f_{\text{fuzzy}}$.
 The function $f_{\text{fuzzy}}$ is obtained by taking $\sigma_8(f_{\text{fuzzy}})=250\sigma_8(f)$ and $\sigma_j(f_{\text{fuzzy}})=\sigma_j(f)$ for $j \ne 8$.
-Both $f$ and $f_{\text{big}}$ lie in the same cones, $\calC_{\bsn,a,b}$, and both appear similarly nice.
+Both $f$ and $f_{\text{big}}$ lie in the same cones, $\calC_{\bsn,a,b}$, for all $\bsn$, $a$, and $b$, and both appear similarly nice to the eye.
 Therefore, we expect adaptive algorithms that are successful for $f$ to also be successful for $f_{\text{big}}$.
 However, $f_{\text{big}}$ does not lie in some of the balls,  $\calB_{\rho}$, that $f$ lies in.
-On the other hand, the high frequency noise in $f_{\text{fuzzy}}$ suggests that only more robust and costly adaptive algorithms would be able to succeed for such an input.
+On the other hand, the high frequency noise in $f_{\text{fuzzy}}$ suggests that only more robust and costly adaptive algorithms would succeed for such an input.
 This corresponds to the fact that $f_{\text{fuzzy}}$ does not lie in all cones, $\calC_{\bsn,a,b}$, that $f$ lies in.
@@
 \end{algo}
-\yuhannote{Please check the result of Theorem 1} 
+
 \begin{theorem}\label{thm:compcost}
@@
 \end{equation}
-Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \frednote{=} n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
+Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) = n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
 \begin{equation} \label{jdagger}
@@
 For any $f \in  \calC \cap \calB_\rho$ satisfying $n_{j^*} = \textup{cost}(\widetilde{A},f,\varepsilon) = \textup{cost}(\widetilde{A}, \calC, \varepsilon, \rho) = n_{j^{\dagger}}$ and for any $j < j^* = j^\dagger$,
-\yuhannote{new proof starts here}\frednote{Looks good to me}
 \begin{align*}
@@
 
-\yuhannote{Also change the analysis and corollary 1}
 The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $(\lambda_{n_j})_{j=0}^\infty$.
@@
 Ignoring all but the first term in the definition of $F$ in \eqref{jsum} implies that 
-\begin{equation*} \label{jsumupperbd}
-j^\dagger \le \min \left \{j \in \bbN : b^{-2j}  \ge  \frac{\rho^2 a^4 \lambda_{n_{0}}^2 }{\varepsilon^2(1 - b^2)} \right\}.
-\end{equation*}
+\begin{align*} \label{jsumupperbd}
+j^\dagger & \le \min \left \{j \in \bbN : b^{-2j}  \ge  \frac{\rho^2 a^4 \lambda_{n_{0}}^2 }{\varepsilon^2(1 - b^2)} \right\} \\
+& = 
+\min \left \{j \in \bbN : j  \ge  \log\left(\frac{\rho a^2 \lambda_{n_{0}} }{\varepsilon(\sqrt{1 - b^2}}\right) \middle/ \log\left(\frac 1b \right) \right\}.
+\end{align*}
 This implies \eqref{jdaggerfirst}.
 
-Ignoring all but the last term of the sum \eqref{jsum}. leads to the simpler upper bound similar to  \eqref{jdaggerlast}
+Ignoring all but the last term of the sum \eqref{jsum}. leads to the simpler upper bound similar to  \eqref{jdaggerlast}: 
 \begin{equation*} 
@@
 
-\yuhannote{corollary 2 is not changed} \frednote{I think we need a small change}
 \begin{corollary} \label{cor:tAsameCosthA} Suppose that the sequence $\bsn$ is chosen to satisfy
@@
 \begin{equation*}
-\lambda_{n_{j^\dagger{{\color{red}+1}}}} \ge c_{\lambda}^{{\color{red}{3}}} \lambda_{n_{j^\dagger-2}} > \frac{\varepsilon c_{\lambda}^{{\color{red}{3}}}\sqrt{1 - b^2}}{\rho ab } = \frac{\omega \varepsilon}{\rho} \ge \lambda_{\widehat{n}+1},
-\qquad \omega := \frac{ c_{\lambda}^{{\color{red}{3}}}\sqrt{1 - b^2}}{ab }
+\lambda_{n_{j^\dagger}} \ge c_{\lambda}^{2} \lambda_{n_{j^\dagger-2}} > \frac{\varepsilon c_{\lambda}^{2}\sqrt{1 - b^2}}{\rho ab } = \frac{\omega \varepsilon}{\rho} \ge \lambda_{\widehat{n}+1},
+\qquad \omega := \frac{ c_{\lambda}^{2}\sqrt{1 - b^2}}{ab },
 \end{equation*}
@@
 = \textup{cost}(\widehat{A},\calB_{\rho},\omega\varepsilon )$.
-Since the $\lambda_i$ are non-increasing, {\color{red} $n_{j^\dagger+1} \le \widehat{n}+1$, and so $n_{j^\dagger} \le \widehat{n}$.  Thus, }
+Since the $\lambda_i$ are non-increasing and $\lambda_{n_{j^\dagger}} > \lambda_{\hat{n}+1}$, it follows that  $n_{j^\dagger} < \widehat{n}+1$, and so $n_{j^\dagger} \le \widehat{n}$.  Thus, 
 \begin{equation*}
@@
 \end{equation}
-\frednote{That is, the subsequence $\lambda_{n_1}, \lambda_{n_2}, \ldots$ cannot decay too quickly.}
+That is, the subsequence $\lambda_{n_1}, \lambda_{n_2}, \ldots$ cannot decay too quickly.
 
@@
 
-\yuhannote{Please check the definition of $j^\ddagger$}
 \begin{theorem} \label{thm:lowbdcomp}
@@
 \end{align*}
-where $F(j)$ defined in \eqref{jsum}.
+and $F(j)$ is defined in \eqref{jsum}.
 \end{theorem}
@@
 \nonumber
-& \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}  \qquad \text{by \eqref{uConstraint}}\\
+& \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}\\
 & \nonumber = \left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)c^2 \sum_{k=0}^j\frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \\
@@
 \end{align*}
-Thus, we have \yuhannote{Please check the proof below}
+Thus, we have 
 \begin{align*}
@@
 b^{2(k-j)} 
-\qquad {\color{red} \text{since } \DHJRbignorm[\calG]{S(u^{(k)})} \ge \lambda_{n_k} \DHJRbignorm[\calF]{u^{(k)}} }\\
+\qquad  \text{since } \DHJRbignorm[\calG]{S(u^{(k)})} \ge \lambda_{n_k} \DHJRbignorm[\calF]{u^{(k)}} \\
 & \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \DHJRbignorm[\calF]{u^{(k)}} \\
 & \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2R^2} 
-\qquad {\color{red} \text{since } b < 1}\\
+\qquad \text{since } b < 1\\
 &
 =\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
-\qquad {\color{red} \text{by \eqref{DHJRetaDef}}}\\
+\qquad \text{by \eqref{DHJRetaDef}}\\
 & =  \rho^2 \left[\left(\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
 & = \rho^2 \left[\left(\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right) b^2F(j+1)\right]^{-1} 
-\qquad {\color{red} \text{by \eqref{jsum}}}.
+\qquad \text{by \eqref{jsum}}.
 \end{align*}
-{\color{red} This inequality is equivalent to 
+ This inequality is equivalent to 
 \begin{equation}
@@
 \end{equation}
-which is the definition of  $j^\ddagger$ above in the statement of this theorem.  This proves the lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$. }
+which is the definition of  $j^\ddagger$ above in the statement of this theorem.  This proves the lower bound on $\textup{comp}(\calA(\calC),\varepsilon,\rho)$. 
 \end{proof}
@@
 The next step is to show that the cost of our algorithm is essentially no worse than that of the optimal algorithm.
-\yuhannote{The proof of theorem 3 needs to be checked.}
+
 \begin{theorem}
@@
 \begin{proof} 
-{\color{red} We need an inequality relating $F(j)$, which appears in the definition of $j^\dagger$ in Theorem \ref{thm:compcost} and $F(j+3)$, which is related to the definition of $j^\ddagger$ in Theorem \ref{thm:lowbdcomp}.
+We need an inequality relating $F(j)$, which appears in the definition of $j^\dagger$ in Theorem \ref{thm:compcost} and $F(j+3)$, which is related to the definition of $j^\ddagger$ in Theorem \ref{thm:lowbdcomp}.
 According to \eqref{lambdaRatio} and the definition of $F$ in \eqref{jsum}, for any $\ell \in \mathbb{N}$,
@@
 \]
-Therefore, our algorithm is essentially no more costly than the optimal algorithm. }
+Therefore, our algorithm is essentially no more costly than the optimal algorithm. 
 \end{proof}
@@
 \begin{acknowledgement}
-The authors would like to thank three anonymous referees for their suggestions which helped to improve the presentation of the results.
+The authors would like to thank the organizers for a wonderful MCQMC 2018. 
+We also thank the referees for their many helpful suggestions.
+This work is supported in part by National Science Foundation grants DMS-1522687 and DMS-1638521 (SAMSI).
+Yuhan Ding acknowledges the support of the Department of Mathematics, Misercordia University.
 

### 2019-06-03 ProgramsImages/WalshFourierCoeffDecay.m

@@ -95,7 +95,7 @@ set(gca,'Ytick',yticks)
 axis([1 nplot-1 ymin ymax])
 xlabel('\(i\)','interpreter','latex')
 ylabel('\(|\widehat{f}_{i}|\)','interpreter','latex')
-set(gca,'Position',[0.2 0.155 0.75 0.77])
+% set(gca,'Position',[0.2 0.155 0.75 0.77])
 print('FunctionWalshFourierCoeffDecay.eps', '-depsc');
 
 
@@ -113,7 +113,7 @@ set(gca,'Ytick',yticks)
 axis([1 nplot-1 ymin ymax])
 xlabel('\(i\)','interpreter','latex')
 ylabel('\(|\widehat{f}_{\textnormal{big},i}|\)','interpreter','latex')
-set(gca,'Position',[0.2 0.155 0.75 0.77])
+% set(gca,'Position',[0.2 0.155 0.75 0.77])
 print('ScaledWalshFourierCoeffDecay.eps', '-depsc');
 
 
@@ -132,7 +132,7 @@ set(gca,'Ytick',yticks)
 axis([1 nplot-1 ymin ymax])
 xlabel('\(i\)','interpreter','latex')
 ylabel('\(|\widehat{f}_{\textnormal{fuzzy},i}|\)','interpreter','latex')
-set(gca,'Position',[0.2 0.155 0.75 0.77])
+% set(gca,'Position',[0.2 0.155 0.75 0.77])
 print('FilteredWalshFourierCoeffDecay.eps', '-depsc');
 
 %% Plot filtered function
